### 2022-01-03 manuscript.tex
Code [ci skip]
This build is based on
https://github.com/jojoelfe/fowl_template_matching_manuscript/commit/d1e11cd25750e43c45aa7a3781790ef34ec0a49f.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/fowl_template_matching_manuscript/commit/d1e11cd25750e43c45aa7a3781790ef34ec0a49f/checks
https://github.com/jojoelfe/fowl_template_matching_manuscript/actions/runs/1650625430

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Visual proteomics using whole-lamella 2D template matching},
  pdfauthor={Johannes ElferichNikolaus Grigorieff},
  pdflang={en-US},
  pdfkeywords={cryo-EM, visual protemics, ribosome},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage[clean]{svg}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{american}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}

%%%% pandoc-fignos: required package
\usepackage{caption}

%% pandoc-fignos: environment to disable figure caption prefixes
\makeatletter
\newcounter{figno}
\newenvironment{fignos:no-prefix-figure-caption}{
  \caption@ifcompatibility{}{
    \let\oldthefigure\thefigure
    \let\oldtheHfigure\theHfigure
    \renewcommand{\thefigure}{figno:\thefigno}
    \renewcommand{\theHfigure}{figno:\thefigno}
    \stepcounter{figno}
    \captionsetup{labelformat=empty}
  }
}{
  \caption@ifcompatibility{}{
    \captionsetup{labelformat=default}
    \let\thefigure\oldthefigure
    \let\theHfigure\oldtheHfigure
    \addtocounter{figure}{-1}
  }
}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{Visual proteomics using whole-lamella 2D template matching}
\author{}
\date{}

\begin{document}
\maketitle

This manuscript
(\href{https://jojoelfe.github.io/fowl_template_matching_manuscript/v/d1e11cd25750e43c45aa7a3781790ef34ec0a49f/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/fowl_template_matching_manuscript/tree/d1e11cd25750e43c45aa7a3781790ef34ec0a49f}{jojoelfe/fowl\_template\_matching\_manuscript@d1e11cd}
on January 3, 2022.

\hypertarget{authors}{%
\subsection{Authors}\label{authors}}

\begin{itemize}
\item
  \textbf{Johannes Elferich}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/XXXX-XXXX-XXXX-XXXX}{XXXX-XXXX-XXXX-XXXX}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/jojoelfe}{jojoelfe}
  RNA Therapeutic INstitute, UMass Chan Medical SChool; HHMI
\item
  \textbf{Nikolaus Grigorieff}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/XXXX-XXXX-XXXX-XXXX}{XXXX-XXXX-XXXX-XXXX}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/nikogrigorieff}{nikogrigorieff}
  RNA Therapeutic INstitute, UMass Chan Medical SChool; HHMI
\end{itemize}

\hypertarget{abstract}{%
\subsection{Abstract}\label{abstract}}

Localization and characterization of biomolecules inside a cell is the fundamental quest of all biological imaging. Fluorescence microscopy can localize biomolecules inside whole cells and tissues, but its ability to count biomolecules and accuracy of the spatial coordinates is limited by the wavelength of visible light. Cryo-electron microscopy on the other hand provides highly accurate position and orientation information of biomolecules but is often limited to small fields of view inside a cell, providing only limited biological context. In this study we use a data-acquisition scheme called ``Fast Observation of Whole Lamella'' (FOWL) to collect cryo-electron microscopy data over thin central sections, representing roughly 1\% of the total cellular volume, of neutrophil-like mouse cells. We use 2D-template matching to determine localization and orientation of the large subunit of the ribosome in these cross-sections. We furthermore use 2D-template matching to test for complex formation with the small ribosomal subunit and used relative orientations of ribosome to assign ribosomes to polysomes. Overall these results provide a ``map'' of translational activity in cross-sections of mammalian cells. We envision that using these high-throughput cryo-EM data collection and 2D template matching approaches will advance visual proteomics to complement other single-cell ``omics'' techniques, such as flow-cytometry and single-cell sequencing.

\hypertarget{introduction}{%
\subsection{Introduction}\label{introduction}}

\hypertarget{materials-and-methods}{%
\subsection{Materials and Methods}\label{materials-and-methods}}

\hypertarget{grid-preparation}{%
\subsubsection{Grid preparation}\label{grid-preparation}}

ER-HoxA9 cells were maintained in RPMI supplemented with 10\% FBS, penicillin/streptomycin, SCF, and estrogen {[}\protect\hyperlink{ref-1B9Vt9eYu}{1}{]} at 37C and 5\% CO2. 120h prior to gridd freezing cells were washed twice in PBS and cultured in the same medium, except without estrogen. Differentiation was verified by staining with Hoechst-dye and insepction of nuclear morphology. Cells were then counted and diluted to 1\^{}106 cells/ml. Grids ( either 200 mesh copper grids, with a sillicone-oxide and 2um holes with a 2um spacing or 200 mesh gold grids with a thin gold film and 2 um holes in 2um sapcing) were glow-discharged from both sides using a \ldots{} for \ldots{} . 3.5 ul of cells suspension was added to grids on the thin-film side and grids were automatically blotted from the back-side using a GP2 cryoplunger (Leica) for \ldots{} s and rapidly plunged into liquid ethane at -185C.

\hypertarget{fib-milling}{%
\subsubsection{FIB-milling}\label{fib-milling}}

Grids were loaded into a Acquilos 2 FIB/SEM microscope with a stage cooled to -190C. Grids were sputter-coated with platinum for 15s at 45 mA and then coated with a layer of platinum-precursor by openin the GIS-valve for 45s. An overview of the grid was created by montaging SEM images and isolated cells at the center of gridsquares were selected for FB-milling. Lamella were generated automatically using the AutoTEM software, resulting in 6-8 um wide lamella with 150-200 um thickness as determined by FIB-imaging of the lamella edge.

\hypertarget{data-collection}{%
\subsubsection{Data collection}\label{data-collection}}

Grids were loaded into a Krios Titam TEM operated at 300 keV. The microscope was setup with a cross-grating grid on the stageby setting the beam-diameter to 900 nm, resulting in the beam being completely visible in the camera. To establish fringe-free conditions, the ``Fine eucentric'' procedure of serialEM was used to move a square of the cross-grating grid to the eucentric position of the microscope. The effective defocus was then set to 2 um, using the ``autofocus'' routine of serialEM. The objective focus of the microscope was changed until no fringes were visible. The stage was then moved in Z until images had a apparent defocus of 2 um. The differnce in stage Z-position between the eucentric and fringe-free conditions was calculate d and noted to move other areas into fringe-free condition.

Low magnification montages were used to find lamella and lamella that were sufficently thin and free of contamination were selected for automated data collection.

\hypertarget{data-pre-processing}{%
\subsubsection{Data pre-processing}\label{data-pre-processing}}

\hypertarget{template-matching}{%
\subsubsection{Template matching}\label{template-matching}}

\hypertarget{data-analysis}{%
\subsubsection{Data analysis}\label{data-analysis}}

\hypertarget{introduction-1}{%
\subsection{Introduction}\label{introduction-1}}

\hypertarget{introduction-2}{%
\subsection{Introduction}\label{introduction-2}}

\hypertarget{figures}{%
\subsection{Figures}\label{figures}}

\begin{fignos:no-prefix-figure-caption}

\begin{figure}
\centering
\includegraphics{figures/example-figure.pdf}
\caption{This is an example-figurern}
\end{figure}

\end{fignos:no-prefix-figure-caption}

\hypertarget{references}{%
\subsection{References}\label{references}}

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\leavevmode\vadjust pre{\hypertarget{ref-1B9Vt9eYu}{}}%
\CSLLeftMargin{1. }
\CSLRightInline{\textbf{Inhibition of Dihydroorotate Dehydrogenase Overcomes Differentiation Blockade in Acute Myeloid Leukemia}
\CSLBlock{David B Sykes, Youmna S Kfoury, François E Mercier, Mathias J Wawer, Jason M Law, Mark K Haynes, Timothy A Lewis, Amir Schajnovitz, Esha Jain, Dongjun Lee, \ldots{} David T Scadden} \emph{Cell} (2016-09) \url{https://doi.org/f3r5jr}
\CSLBlock{DOI: \href{https://doi.org/10.1016/j.cell.2016.08.057}{10.1016/j.cell.2016.08.057} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/27641501}{27641501} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7360335}{PMC7360335}}}

\end{CSLReferences}

\end{document}

### 2022-01-03 content/code/plot_defocus.py
Initial code

@@ -1,0 +1,16 @@
+import matplotlib.pyplot as plt
+import sqlite3
+import pandas as pd
+import os
+
+dataset = "/scratch/bern/elferich/ER_Hox_120h_20211029_g1_l1/ER_Hox_120h_20211029_g1_l1.db"
+
+
+con = sqlite3.connect(dataset)
+
+
+df1 = pd.read_sql_query(f"SELECT IMAGE_ASSET_ID,IMAGE_ASSETS. FILENAME, MOVIE_ASSETS.FILENAME as movie_filename, CTF_ESTIMATION_ID ,IMAGE_ASSETS.PIXEL_SIZE as image_pixel_size, MOVIE_ASSETS.PIXEL_SIZE as movie_pixel_size, IMAGE_ASSETS.X_SIZE, IMAGE_ASSETS.Y_SIZE  FROM IMAGE_ASSETS INNER JOIN MOVIE_ASSETS ON MOVIE_ASSETS.MOVIE_ASSET_ID == IMAGE_ASSETS.PARENT_MOVIE_ID", con)
+df2 = pd.read_sql_query("SELECT CTF_ESTIMATION_ID,DEFOCUS1,DEFOCUS2,DEFOCUS_ANGLE,OUTPUT_DIAGNOSTIC_FILE,SCORE, DETECTED_RING_RESOLUTION FROM ESTIMATED_CTF_PARAMETERS",con)
+selected_micrographs = pd.merge(df1,df2,on="CTF_ESTIMATION_ID")
+
+plt.hist([(m["DEFOCUS1"]+m["DEFOCUS2"])/2 for i,m in selected_micrographs.iterrows() if m['SCORE']>0.05])

### 2022-01-03 manuscript.tex
Initial code [ci skip]
This build is based on
https://github.com/jojoelfe/fowl_template_matching_manuscript/commit/62df8f94079cea91a7ff27395620b6520811c5b5.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/fowl_template_matching_manuscript/commit/62df8f94079cea91a7ff27395620b6520811c5b5/checks
https://github.com/jojoelfe/fowl_template_matching_manuscript/actions/runs/1650789776

@@
 This manuscript
-(\href{https://jojoelfe.github.io/fowl_template_matching_manuscript/v/d1e11cd25750e43c45aa7a3781790ef34ec0a49f/}{permalink})
+(\href{https://jojoelfe.github.io/fowl_template_matching_manuscript/v/62df8f94079cea91a7ff27395620b6520811c5b5/}{permalink})
 was automatically generated
-from \href{https://github.com/jojoelfe/fowl_template_matching_manuscript/tree/d1e11cd25750e43c45aa7a3781790ef34ec0a49f}{jojoelfe/fowl\_template\_matching\_manuscript@d1e11cd}
+from \href{https://github.com/jojoelfe/fowl_template_matching_manuscript/tree/62df8f94079cea91a7ff27395620b6520811c5b5}{jojoelfe/fowl\_template\_matching\_manuscript@62df8f9}
 on January 3, 2022.

### 2022-01-04 build/build.sh
Maybe Build works now

@@ -98,10 +98,13 @@ fi
 # Create LaTeX output (if BUILD_LATEX environment variable equals "true")
 if [ "${BUILD_LATEX,,}" = "true" ]; then
   echo >&2 "Exporting LaTeX manuscript"
+  ln -s content/images
   pandoc \
     --data-dir="$PANDOC_DATA_DIR" \
     --defaults=common.yaml \
     --defaults=latex.yaml
+  tectonic output/manuscript.tex
+  rm images
 fi
 
 # Spellcheck

### 2022-01-04 build/pandoc/filters/svg2pdf.py

@@ -1,0 +1,45 @@
+
+
+#! /usr/bin/env python
+"""
+Pandoc filter to convert svg files to pdf as suggested at:
+https://github.com/jgm/pandoc/issues/265#issuecomment-27317316
+"""
+
+__author__ = "Jerome Robert"
+
+import mimetypes
+import subprocess
+import os
+import sys
+from pandocfilters import toJSONFilter, Image
+
+# TODO add emf export if fmt=="docx" ?
+fmt_to_option = {
+    "latex": ("--export-filename", "pdf"),
+    "beamer": ("--export-pdf", "pdf"),
+    # because of IE
+    "html": ("--export-png", "png")
+}
+
+
+def svg_to_any(key, value, fmt, meta):
+    if key == 'Image':
+        attrs, alt, [src, title] = value
+        mimet, _ = mimetypes.guess_type(src)
+        option = fmt_to_option.get(fmt)
+        if mimet == 'image/svg+xml' and option:
+            base_name, _ = os.path.splitext(src)
+            eps_name = base_name + "." + option[1]
+            try:
+                mtime = os.path.getmtime(eps_name)
+            except OSError:
+                mtime = -1
+            if mtime < os.path.getmtime(src):
+                cmd_line = ['inkscape', option[0], eps_name, src]
+                sys.stderr.write("Running %s\n" % " ".join(cmd_line))
+                subprocess.call(cmd_line, stdout=sys.stderr.fileno())
+            return Image(attrs, alt, [eps_name, title])
+
+if __name__ == "__main__":
+    toJSONFilter(svg_to_any)

### 2022-01-04 ci/install-spellcheck.sh
Sigh

@@ -8,5 +8,6 @@ set -o errexit \
 
 sudo apt-get update --yes
 sudo apt-get install --yes aspell aspell-en
+sudo apt-get install --yes inkscape
 wget --directory-prefix=build/pandoc/filters \
   https://github.com/pandoc/lua-filters/raw/13c3fa7e97206413609a48a82575cb43137e037f/spellcheck/spellcheck.lua

### 2022-01-04 tikz.tex
new test

    \documentclass[tikz,border=0cm]{standalone}
    \usepackage{graphicx}
    \usepackage{tikz}
    \usetikzlibrary{positioning}
    \usetikzlibrary{arrows,snakes,shapes,fadings}
    \usepackage{fontspec}
    \setmainfont{Roboto}[
      Extension = .otf,
      UprightFont = *-Regular,
      BoldFont = *-Bold,
      ItalicFont = *-Italic,
      BoldItalicFont = *-BoldItalic,
    ]    \usepackage{etoolbox}

    \newcommand{\figwidth}{16cm} 
    \newcommand{\figheight}{10cm} 
    \newcommand{\fontselect}{\large\bf}

    \tikzset{
      labelNode/.style={anchor=south east, above left=0cm and 0cm of anchor, font=\fontselect}, 
      redAnchorNode/.style={anchor=center, left=-0.1cm of anchor, circle, fill=red, minimum size=0.2cm}, 
      graphicNode/.style={anchor=north west, below right=0cm and 0cm of anchor}, 
    }

    \newtoggle{draft}
        \toggletrue{draft}
        % \togglefalse{draft}

    \begin{document}
    \begin{tikzpicture}[every node/.style={inner sep=0pt}]

    \iftoggle{draft}{\node[anchor=south west, rectangle, draw, red, line width=2pt, minimum width=\figwidth, minimum height=\figheight] at (0,0) {};}
    {\node[anchor=south west, rectangle, fill=white, minimum width=\figwidth, minimum height=\figheight] at (0,0) {};};

    \node (anchor) at (0.5,9.35) {}; 
\node[labelNode] {A};
\node[graphicNode] {\includegraphics[scale=0.1]{content/graphics/approach/approach.pdf}

};
\iftoggle{draft}{\node [redAnchorNode] {};};
    \end{tikzpicture}
    \end{document}

### 2022-01-04 ci/install-spellcheck.sh

@@ -8,6 +8,6 @@ set -o errexit \
 
 sudo apt-get update --yes
 sudo apt-get install --yes aspell aspell-en
-sudo apt-get install --yes inkscape
+sudo snap install inkscape --classic
 wget --directory-prefix=build/pandoc/filters \
   https://github.com/pandoc/lua-filters/raw/13c3fa7e97206413609a48a82575cb43137e037f/spellcheck/spellcheck.lua

### 2022-01-04 build/build.sh
and this

@@ -42,11 +42,15 @@ mkdir -p output/figures
 # Create HTML output
 # https://pandoc.org/MANUAL.html
 echo >&2 "Exporting HTML manuscript"
+ln -s content/images
+ln -s content/graphics
+
 pandoc --verbose \
   --data-dir="$PANDOC_DATA_DIR" \
   --defaults=common.yaml \
   --defaults=html.yaml
-
+rm images
+rm graphics
 # Create PDF output (unless BUILD_PDF environment variable equals "false")
 # The double-commas (,,) lowercase the variable.
 # If Docker is not available, use WeasyPrint to create PDF
@@ -99,12 +103,14 @@ fi
 if [ "${BUILD_LATEX,,}" = "true" ]; then
   echo >&2 "Exporting LaTeX manuscript"
   ln -s content/images
+  ln -s content/graphics
   pandoc \
     --data-dir="$PANDOC_DATA_DIR" \
     --defaults=common.yaml \
     --defaults=latex.yaml
   tectonic output/manuscript.tex
   rm images
+  rm graphics
 fi
 
 # Spellcheck

### 2022-01-04 build/build.sh
debug

@@ -104,6 +104,7 @@ if [ "${BUILD_LATEX,,}" = "true" ]; then
   echo >&2 "Exporting LaTeX manuscript"
   ln -s content/images
   ln -s content/graphics
+  ls -R
   pandoc \
     --data-dir="$PANDOC_DATA_DIR" \
     --defaults=common.yaml \

### 2022-01-04 build/build.sh
anotha test

@@ -104,7 +104,7 @@ if [ "${BUILD_LATEX,,}" = "true" ]; then
   echo >&2 "Exporting LaTeX manuscript"
   ln -s content/images
   ln -s content/graphics
-  ls -R
+  ls -lisah images/orcid.pdf
   pandoc \
     --data-dir="$PANDOC_DATA_DIR" \
     --defaults=common.yaml \

### 2022-01-04 build/build.sh
mhm?

@@ -103,6 +103,9 @@ fi
 if [ "${BUILD_LATEX,,}" = "true" ]; then
   echo >&2 "Exporting LaTeX manuscript"
   ln -s content/images
+  cd output
+  ln -s ../content/images
+  cd ..
   ln -s content/graphics
   ls -lisah images/orcid.pdf
   pandoc \
@@ -111,6 +114,7 @@ if [ "${BUILD_LATEX,,}" = "true" ]; then
     --defaults=latex.yaml
   tectonic output/manuscript.tex
   rm images
+  rm output/images
   rm graphics
 fi
 

### 2022-01-04 manuscript.tex
mhm? [ci skip]
This build is based on
https://github.com/jojoelfe/fowl_template_matching_manuscript/commit/3fd92a26614a26949905aec5a87c6e0dabaffd3a.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/fowl_template_matching_manuscript/commit/3fd92a26614a26949905aec5a87c6e0dabaffd3a/checks
https://github.com/jojoelfe/fowl_template_matching_manuscript/actions/runs/1654580313

@@
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
-\usepackage[clean]{svg}
 \ifLuaTeX
@@
 This manuscript
-(\href{https://jojoelfe.github.io/fowl_template_matching_manuscript/v/62df8f94079cea91a7ff27395620b6520811c5b5/}{permalink})
+(\href{https://jojoelfe.github.io/fowl_template_matching_manuscript/v/3fd92a26614a26949905aec5a87c6e0dabaffd3a/}{permalink})
 was automatically generated
-from \href{https://github.com/jojoelfe/fowl_template_matching_manuscript/tree/62df8f94079cea91a7ff27395620b6520811c5b5}{jojoelfe/fowl\_template\_matching\_manuscript@62df8f9}
-on January 3, 2022.
+from \href{https://github.com/jojoelfe/fowl_template_matching_manuscript/tree/3fd92a26614a26949905aec5a87c6e0dabaffd3a}{jojoelfe/fowl\_template\_matching\_manuscript@3fd92a2}
+on January 4, 2022.
 
@@
   \textbf{Johannes Elferich}
-  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
+  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.pdf}
   \href{https://orcid.org/XXXX-XXXX-XXXX-XXXX}{XXXX-XXXX-XXXX-XXXX}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.pdf}
   \href{https://github.com/jojoelfe}{jojoelfe}
@@
   \textbf{Nikolaus Grigorieff}
-  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
+  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.pdf}
   \href{https://orcid.org/XXXX-XXXX-XXXX-XXXX}{XXXX-XXXX-XXXX-XXXX}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.pdf}
   \href{https://github.com/nikogrigorieff}{nikogrigorieff}
@@
 \subsection{Introduction}\label{introduction}}
+
+Understanding of cellular processes requires knowledge of the amount, location, and interaction of biomolecules inside the cell.
+Techniques that measure this can broadly be divided into label, and label-free techniques.
+In label-techniques a probe is physically attahced to a molecule is interest that is able to produce a high signal-to-noise signal, such as a fluorescent probe.
+In label-free techniques the physical properties of molecules themselves are used for detection.
+An example for this is proteomics using mass-spectrometry.
+Broadly the advantage of label-free techniques is that they can provide information over thousands of molecules, while label-techniques offer higher fidelity information for a few molecules.
+Especially spatial information can most of the time only be achieved using label-tehcniques.
+
+Cryo-electron microscopy has the potential to directly measure the arrangement of atoms that compose biomolecules inside of cells, therby allowing label-free detection with high spatial accuracy.
+This has been called ``Visual proteomics''.
+The predominant technique at the moemnt is cryo-electron tomography.
+However, the throughput of these methods in low due to highly complex sample preparation, data acquisition, and data processing.
+We have shown that molecules can be identified by their structural ``fingerprint'' in single projection using ``2D temaplte-matching''.
+
+Here we apply 2D-template matching to neutrophil-ilke murine cells. By employing anew data-acquisition scheme we obtained coverage of the whole ``lamella'' covering roughly 2\% of the cellular volume.
 

### 2022-01-05 manuscript.tex
new name [ci skip]
This build is based on
https://github.com/jojoelfe/fowl_template_matching_manuscript/commit/4eeafd31bd521c439395837768989d548d581f72.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/fowl_template_matching_manuscript/commit/4eeafd31bd521c439395837768989d548d581f72/checks
https://github.com/jojoelfe/fowl_template_matching_manuscript/actions/runs/1658913730

@@
 This manuscript
-(\href{https://jojoelfe.github.io/fowl_template_matching_manuscript/v/3fd92a26614a26949905aec5a87c6e0dabaffd3a/}{permalink})
+(\href{https://jojoelfe.github.io/fowl_template_matching_manuscript/v/4eeafd31bd521c439395837768989d548d581f72/}{permalink})
 was automatically generated
-from \href{https://github.com/jojoelfe/fowl_template_matching_manuscript/tree/3fd92a26614a26949905aec5a87c6e0dabaffd3a}{jojoelfe/fowl\_template\_matching\_manuscript@3fd92a2}
-on January 4, 2022.
+from \href{https://github.com/jojoelfe/fowl_template_matching_manuscript/tree/4eeafd31bd521c439395837768989d548d581f72}{jojoelfe/fowl\_template\_matching\_manuscript@4eeafd3}
+on January 5, 2022.
 

### 2022-01-06 build/build.sh
More stuff works

@@ -19,7 +19,7 @@ DOCKER_RUNNING="$(docker info &> /dev/null && echo "true" || (true && echo "fals
 CI="${CI:-false}"
 BUILD_PDF="${BUILD_PDF:-false}"
 BUILD_DOCX="${BUILD_DOCX:-false}"
-BUILD_LATEX="${BUILD_LATEX:-true}"
+BUILD_LATEX="${BUILD_LATEX:-false}"
 SPELLCHECK="${SPELLCHECK:-false}"
 MANUBOT_USE_DOCKER="${MANUBOT_USE_DOCKER:-$DOCKER_RUNNING}"
 # Pandoc's configuration is specified via files of option defaults

### 2022-01-06 content/code/plot_defocus.py
New plot

@@ -2,15 +2,28 @@ import matplotlib.pyplot as plt
 import sqlite3
 import pandas as pd
 import os
+import contextlib
 
-dataset = "/scratch/bern/elferich/ER_Hox_120h_20211029_g1_l1/ER_Hox_120h_20211029_g1_l1.db"
+datasets = ["/scratch/bern/elferich/ER_Hox_120h_20211029_g1_l1/ER_Hox_120h_20211029_g1_l1.db",
+            "/scratch/bern/elferich/ER_Hox_120h_20211029_g1_l2/ER_Hox_120h_20211029_g1_l2.db",
+            "/scratch/bern/elferich/ER_Hox_120h_20211029_g2_l3/ER_Hox_120h_20211029_g2_l3.db",
+            "/scratch/bern/elferich/ER_Hox_120h_202111029_g2_l4/ER_Hox_120h_202111029_g2_l4.db"]
+defocus = []
 
+for dataset in datasets:
+    print(dataset)
+    with contextlib.closing(sqlite3.connect(dataset)) as con:
 
-con = sqlite3.connect(dataset)
+        df1 = pd.read_sql_query(f"SELECT IMAGE_ASSET_ID,IMAGE_ASSETS. FILENAME, MOVIE_ASSETS.FILENAME as movie_filename, CTF_ESTIMATION_ID ,IMAGE_ASSETS.PIXEL_SIZE as image_pixel_size, MOVIE_ASSETS.PIXEL_SIZE as movie_pixel_size, IMAGE_ASSETS.X_SIZE, IMAGE_ASSETS.Y_SIZE  FROM IMAGE_ASSETS INNER JOIN MOVIE_ASSETS ON MOVIE_ASSETS.MOVIE_ASSET_ID == IMAGE_ASSETS.PARENT_MOVIE_ID", con)
+        df2 = pd.read_sql_query("SELECT CTF_ESTIMATION_ID,DEFOCUS1,DEFOCUS2,DEFOCUS_ANGLE,OUTPUT_DIAGNOSTIC_FILE,SCORE, DETECTED_RING_RESOLUTION FROM ESTIMATED_CTF_PARAMETERS",con)
+        selected_micrographs = pd.merge(df1,df2,on="CTF_ESTIMATION_ID")
 
[…]

### 2022-01-08 content/graphics/approach/logo.tex
Some work

\documentclass[tikz,border=0cm]{standalone}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usetikzlibrary{arrows,snakes,shapes,fadings,calc}
\usepackage{fontspec}
\setmainfont{Roboto}[
  Extension = .otf,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic,
]    
\usepackage{etoolbox}

\newcommand{\figwidth}{7cm} 
\newcommand{\figheight}{10cm} 
\newcommand{\fontselect}{\large\bf}

\begin{document}
\begin{tikzpicture}

  % Include the image in a node
  \node [
      above right,
      inner sep=0] (image) at (0,0) {\includegraphics[width=\textwidth]{approach.png}};

  % Create scope with normalized axes
  \node [above right,inner sep=0,text width=\textwidth ,align=center] at (0,13) {\Huge \textbf{BILACE}};
  \node [above right,inner sep=0,text width=\textwidth ,align=center] at (0,12.5) {\normalsize \textbf{B}eam-\textbf{I}mageshift for \textbf{L}arge \textbf{A}rea \textbf{C}ryo-\textbf{E}lectron microscopy}; 
  \end{tikzpicture}
\end{document}

### 2022-02-20 build/build.sh
Even better build

@@ -39,6 +39,14 @@ manubot process \
 mkdir -p output
 mkdir -p output/figures
 
+# Generate the figures
+
+cp content/figures/* output/figures/
+
+pandoc --verbose \
+  --data-dir="$PANDOC_DATA_DIR" \
+  --defaults=filter_figures.yaml
+
 # Create HTML output
 # https://pandoc.org/MANUAL.html
 echo >&2 "Exporting HTML manuscript"

### 2022-02-20 manuscript.tex
Even better build [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/56181559e858af0a515082cd5c28c9f1b8501873.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/56181559e858af0a515082cd5c28c9f1b8501873/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1873097244

--- 2022-01-03 manuscript.tex
@@
 \def\languageshorthands#1{}
-
-%%%% pandoc-fignos: required package
-\usepackage{caption}
-
-%% pandoc-fignos: environment to disable figure caption prefixes
-\makeatletter
-\newcounter{figno}
-\newenvironment{fignos:no-prefix-figure-caption}{
-  \caption@ifcompatibility{}{
-    \let\oldthefigure\thefigure
-    \let\oldtheHfigure\theHfigure
-    \renewcommand{\thefigure}{figno:\thefigno}
-    \renewcommand{\theHfigure}{figno:\thefigno}
-    \stepcounter{figno}
-    \captionsetup{labelformat=empty}
-  }
-}{
-  \caption@ifcompatibility{}{
-    \captionsetup{labelformat=default}
-    \let\thefigure\oldthefigure
-    \let\theHfigure\oldtheHfigure
-    \addtocounter{figure}{-1}
-  }
-}
-\makeatother
+\usepackage[margin=2cm]{geometry}
+\usepackage{setspace}
+\doublespacing
+\usepackage{lineno}
+\linenumbers
 \ifLuaTeX
@@
 This manuscript
-(\href{https://jojoelfe.github.io/fowl_template_matching_manuscript/v/62df8f94079cea91a7ff27395620b6520811c5b5/}{permalink})
+(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/56181559e858af0a515082cd5c28c9f1b8501873/}{permalink})
 was automatically generated
-from \href{https://github.com/jojoelfe/fowl_template_matching_manuscript/tree/62df8f94079cea91a7ff27395620b6520811c5b5}{jojoelfe/fowl\_template\_matching\_manuscript@62df8f9}
-on January 3, 2022.
+from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/56181559e858af0a515082cd5c28c9f1b8501873}{jojoelfe/deco\_lace\_template\_matching\_manuscript@5618155}
+on February 20, 2022.
 
@@
   \textbf{Johannes Elferich}
-  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
-  \href{https://orcid.org/XXXX-XXXX-XXXX-XXXX}{XXXX-XXXX-XXXX-XXXX}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.pdf}
+  \href{https://orcid.org/0000-0002-9911-706X}{0000-0002-9911-706X}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.pdf}
   \href{https://github.com/jojoelfe}{jojoelfe}
-  RNA Therapeutic INstitute, UMass Chan Medical SChool; HHMI
+  RNA Therapeutic Institute, UMass Chan Medical School; HHMI
 \item
   \textbf{Nikolaus Grigorieff}
-  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
-  \href{https://orcid.org/XXXX-XXXX-XXXX-XXXX}{XXXX-XXXX-XXXX-XXXX}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.pdf}
+  \href{https://orcid.org/0000-0002-1506-909X}{0000-0002-1506-909X}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.pdf}
   \href{https://github.com/nikogrigorieff}{nikogrigorieff}
-  RNA Therapeutic INstitute, UMass Chan Medical SChool; HHMI
+  RNA Therapeutic Institute, UMass Chan Medical School; HHMI
 \end{itemize}
@@
 
-Localization and characterization of biomolecules inside a cell is the fundamental quest of all biological imaging.
+Localization of biomolecules inside a cell is an important goal of biological imaging.
 Fluorescence microscopy can localize biomolecules inside whole cells and tissues, but its ability to count biomolecules and accuracy of the spatial coordinates is limited by the wavelength of visible light.
-Cryo-electron microscopy on the other hand provides highly accurate position and orientation information of biomolecules but is often limited to small fields of view inside a cell, providing only limited biological context.
-In this study we use a data-acquisition scheme called ``Fast Observation of Whole Lamella'' (FOWL) to collect cryo-electron microscopy data over thin central sections, representing roughly 1\% of the total cellular volume, of neutrophil-like mouse cells.
-We use 2D-template matching to determine localization and orientation of the large subunit of the ribosome in these cross-sections.
-We furthermore use 2D-template matching to test for complex formation with the small ribosomal subunit and used relative orientations of ribosome to assign ribosomes to polysomes.
-Overall these results provide a ``map'' of translational activity in cross-sections of mammalian cells.
-We envision that using these high-throughput cryo-EM data collection and 2D template matching approaches will advance visual proteomics to complement other single-cell ``omics'' techniques, such as flow-cytometry and single-cell sequencing.
+On the other hand, cryo-electron microscopy (cryo-EM) provides highly accurate position and orientation information of biomolecules but is often limited to small fields of view inside a cell, providing only limited biological context.
+In this study we use a new data-acquisition scheme called ``Beam-Imageshift for Large Area Cryo-Electron microscopy'' (BILACE) to collect high-resolution cryo-EM data over entire sections (100 -- 200 nm thick lamellae) of neutrophil-like mouse cells, representing roughly 1\% of the total cellular volume.
+We use 2D template matching to determine localization and orientation of the large ribosomal subunit in these sections.
+Furthermore, we use 2D template matching to test detected targets for the presence of the small ribosomal subunit and used the relative orientations of the ribosomes to assign them to polysomes.
+These results provide ``maps'' of translational activity across sections of mammalian cells.
+We envision that using this high-throughput cryo-EM data collection approach together with 2D template matching will advance visual proteomics to complement other single-cell ``omics'' techniques, such as flow-cytometry and single-cell sequencing.
 
@@
 \subsection{Introduction}\label{introduction}}
+
+Understanding of cellular processes requires knowledge of the amounts, location,
+interactions, and conformations of biomolecules inside the cell. Techniques that
+measure this can broadly be divided into label- and label-free techniques. In
+label-techniques a probe is physically attached to a molecule is interest that
+is able to produce a high signal-to-noise signal, such as a fluorescent molecule.
+In label-free techniques the physical properties of molecules themselves are
+used for detection. An example for this is proteomics using mass-spectrometry
+{[}\protect\hyperlink{ref-tSXIKPl7}{1}{]}. The advantage of label-free techniques is that
+they can provide information over thousands of molecules, while label-techniques
+offer higher fidelity information for a few molecules. Especially spatial
+information can most of the time only be achieved using label-techniques, such
+as fluorescence microscopy {[}\protect\hyperlink{ref-VBmW7Aot}{2}{]}.
+
+Cryo-electron microscopy has the potential to directly measure the arrangement
+of atoms that compose biomolecules inside of cells, thereby allowing label-free
+detection with high spatial accuracy. This has been called ``visual proteomics''
+{[}\protect\hyperlink{ref-tGQ6TSUo}{3}{]}. Since cryo-EM requires thin samples (\textless500nm), imaging of
+biomolecules inside cells is either restricted to small organisms, thin
+regions of large cells, or requires thinning of the sample. This can be achieved
+either by mechanical sectioning {[}\protect\hyperlink{ref-g8QavfwP}{4}{]} or by
+milling using a focused ion beam (FIB) {[}\protect\hyperlink{ref-16IhS1Nc4}{5}{]}. This
+complex workflow restricts throughput of cryo-EM imaging of cells. This is
+exacerbated by the fact that at the required magnifications, typical field of
+views (FOV) are very small compared to mammalian cells and the FOV achieved by
+label-techniques such as fluorescence light microscopy. The predominant cryo-EM
+technique for detection of biomolecules according to their shape in cells at the
+moment is cryo-electron tomography {[}\protect\hyperlink{ref-Rksh2dxu}{6}{]}. However,
+the requirement of physically tilt the stage at every FOV, together with a more
+complex workflow that requires highly accurate alignment of various projection,
+further restricts the throughput for molecular detection.
+
+An alternative approach is to identify molecules by their structural
+``fingerprint'' in single projection using ``2D template-matching''
+{[}\protect\hyperlink{ref-Ynb3IP6I}{7},\protect\hyperlink{ref-18KGpXYPE}{8},\protect\hyperlink{ref-10bXZuF3G}{9}{]}. In this method an experimentally obtained 3D model
+of a biomolecule is used to calculate the expected electron density, which is
+called the template. The template is then projected on a fine angular grid and
+the projections are used to find local cross-correlation peaks in a cryo-EM
+micrograph. Since locations of the biomolecule in the Z-direction causes
+predictable aberrations to the projection image, this method can be used to
+calculate 3D coordinates and orientations of a biomolecule in a cellular sample
+{[}\protect\hyperlink{ref-18KGpXYPE}{8}{]}
+
+Hematopoiesis is the process of generating the various cell types of the blood in
+the bone marrow. Disregulation of the process results in diseases like leukemia.
+Understanding how hematopoietic stem and progenitor cells are programmed to
+diffferentiate to the appropriate cell type would be provide new insight how
+hematopoiesis can be misregulated. Of special interest is the regulation of
+translation during hematopoiesis. This is exemplified by the observation that
+genetic defects in the ribosome machinery often leads to hematopoietic
+disease{[}\protect\hyperlink{ref-gRoY21jY}{10}{]}. As such direct quantification of ribosome
+location, number and conformational states could lead to new insight into
+hematopoietic disease {[}\protect\hyperlink{ref-KAJ7221k}{11}{]}.
+
+Here we apply 2D-template matching of ribosomes to cryo-FIB milled
+neutrophil-like murine cells {[}\protect\hyperlink{ref-1B9Vt9eYu}{12}{]}. To increase the
+amount of collected data and to provide un-biased sampling of the whole lamella
+we devised a new data-acquisition scheme, Defocus-corrected large area
+cryo-electron microscopy (DeCo-LACE). We characterize aberration cause by the
+used large beam-image shifts and highly focused beams and find that they can be
+adequately correct to enable ribosome detection by 2D-template matching. The
+resulting data provides a description of ribosome distribution in the whole
+lamellae, which represent roughly 2\% of the cellular volume. We find highly
+heterogeneous density of ribosome within the cell and can identify discrete
+clusters of presumably translationaly active ribosomes, by testing for the
+presence of the small ribosomal subunit. The high accuracy of location and
+orientation of each detected ribosome also allows us to cluster ribosome
+molecules into potential polysomes. Analysis of the throughput in this method
+suggests that for the foreseeable future computation will be the bottleneck for
+visual proteomics.
 
@@
 
-ER-HoxA9 cells were maintained in RPMI supplemented with 10\% FBS, penicillin/streptomycin, SCF, and estrogen {[}\protect\hyperlink{ref-1B9Vt9eYu}{1}{]} at 37C and 5\% CO2.
-120h prior to gridd freezing cells were washed twice in PBS and cultured in the same medium, except without estrogen.
-Differentiation was verified by staining with Hoechst-dye and insepction of nuclear morphology.
-Cells were then counted and diluted to 1\^{}106 cells/ml.
-Grids ( either 200 mesh copper grids, with a sillicone-oxide and 2um holes with a 2um spacing or 200 mesh gold grids with a thin gold film and 2 um holes in 2um sapcing) were glow-discharged from both sides using a \ldots{} for \ldots{} .
-3.5 ul of cells suspension was added to grids on the thin-film side and grids were automatically blotted from the back-side using a GP2 cryoplunger (Leica) for \ldots{} s and rapidly plunged into liquid ethane at -185C.
+ER-HoxA9 cells were maintained in RPMI supplemented with 10\% FBS,
+penicillin/streptomycin, SCF, and estrogen {[}\protect\hyperlink{ref-1B9Vt9eYu}{12}{]} at
+37C and 5\% CO2. 120h prior to grid freezing cells were washed twice in PBS and
+cultured in the same medium, except without estrogen. Differentiation was
+verified by staining with Hoechst-dye and insepction of nuclear morphology.
+Cells were then counted and diluted to 1\^{}106 cells/ml. Grids ( either 200 mesh
+copper grids, with a sillicone-oxide and 2um holes with a 2um spacing or 200
+mesh gold grids with a thin gold film and 2 um holes in 2um sapcing) were
+glow-discharged from both sides using a \ldots{} for \ldots{} . 3.5 ul of cells suspension
+was added to grids on the thin-film side and grids were automatically blotted
+from the back-side using a GP2 cryoplunger (Leica) for \ldots{} s and rapidly plunged
+into liquid ethane at -185C.
 
@@
 
-Grids were loaded into a Acquilos 2 FIB/SEM microscope with a stage cooled to -190C.
-Grids were sputter-coated with platinum for 15s at 45 mA and then coated with a layer of platinum-precursor by openin the GIS-valve for 45s.
-An overview of the grid was created by montaging SEM images and isolated cells at the center of gridsquares were selected for FB-milling.
-Lamella were generated automatically using the AutoTEM software, resulting in 6-8 um wide lamella with 150-200 um thickness as determined by FIB-imaging of the lamella edge.
+Grids were loaded into a Acquilos 2 FIB/SEM microscope with a stage cooled to
+-190C. Grids were sputter-coated with platinum for 15s at 45 mA and then coated
+with a layer of platinum-precursor by openin the GIS-valve for 45s. An overview
+of the grid was created by montaging SEM images and isolated cells at the center
+of gridsquares were selected for FB-milling. Lamella were generated
+automatically using the AutoTEM software, resulting in 6-8 um wide lamella with
+150-200 um thickness as determined by FIB-imaging of the lamella edge.
 
@@
 
-Grids were loaded into a Krios Titam TEM operated at 300 keV.
-The microscope was setup with a cross-grating grid on the stageby setting the beam-diameter to 900 nm, resulting in the beam being completely visible in the camera.
-To establish fringe-free conditions, the ``Fine eucentric'' procedure of serialEM was used to move a square of the cross-grating grid to the eucentric position of the microscope.
-The effective defocus was then set to 2 um, using the ``autofocus'' routine of serialEM.
-The objective focus of the microscope was changed until no fringes were visible.
-The stage was then moved in Z until images had a apparent defocus of 2 um.
-The differnce in stage Z-position between the eucentric and fringe-free conditions was calculate d and noted to move other areas into fringe-free condition.
+Grids were loaded into a Krios Titam TEM operated at 300 keV. The microscope was
+setup with a cross-grating grid on the stageby setting the beam-diameter to 900
+nm, resulting in the beam being completely visible in the camera. To establish
+fringe-free conditions, the ``Fine eucentric'' procedure of serialEM was used to
+move a square of the cross-grating grid to the eucentric position of the
+microscope. The effective defocus was then set to 2 um, using the ``autofocus''
+routine of serialEM. The objective focus of the microscope was changed until no
+fringes were visible. The stage was then moved in Z until images had a apparent
+defocus of 2 um. The differnce in stage Z-position between the eucentric and
+fringe-free conditions was calculate d and noted to move other areas into
+fringe-free condition.
 
-Low magnification montages were used to find lamella and lamella that were sufficently thin and free of contamination were selected for automated data collection.
+Low magnification montages were used to find lamella and lamella that were
+sufficiently thin and free of contamination were selected for automated data
+collection. The corners of the lamella were manually annotated in SerialEM and
+translated into Beam-Imageshift values using SerialEm calibration. A hexagonal
+patter of beam-imageshift positions was calculated that covered the area between
+he four corners in a serpentine way, with a sqrt(3) * 400 nm horizontal spacing
+and 800 nm vertical spacing. Exposures were then taking at each position with a
+30 e/A total dose. After each exposure that defocus was estimated using the
+ctffind function of SerialEM and the focus for th next exposure was corrected by
+the difference between the estimated focus and the desired defocus of 800 um.
+Also after each exposure the deviation of the beam from the center of the camera
+was measured and corrected using the ``CenterBeamFrom IMage'' command of SerialEM.
+
+After datacollection a 20s exposure at 2250x magnification of the lamella at
+200um defocus was taken for visualization purposes.
 
@@
 
+Movies were gain-corrected and motion-corrected using a custom version of
+unblur. To avoid influence of the beam-edge on motion-correction only a quarter
+of the movie in the center of the camera was considered for calculation of the
+estimated motion. After movie frames were aligned and summed a mask for the
+illuminated area was calculated by lowpass filtering the image at \ldots{} A,
+thresholding the image at 10\% of the maximal value and then lowpass filtering
+the mask at \ldots{} A. This mask was then used to replace un-illuminated area with
+gaussian noise, with the same mean and standard deviation as the illuminated
+area. The contrast-transfer function (CTF) was estimated using ctffind, searching
+between 0.02 and 2 um defocus.
+
 \hypertarget{template-matching}{%
 \subsubsection{Template matching}\label{template-matching}}
+
+The search template was generated from the cryo-EM structure of the mouse large
+ribosomal subunit (PDB 6SWA). The \ldots{} subunit was deleted from the model and the
+simulate program of the cisTEM suite was used to calculate an density map from
+the atomic coordinates. The match\_template program was used to search for this
+template in the preprocessed images, using 1.5 deg angular step in out-of-plane
+angles and 1.0 deg in-plane. 21 defocus planes in 200nm steps centered around
+the defocus estimates by ctffind were searches. Matches were defined as peaks
+above a threshold calulated according to .. .(7.75 for most images).
 
@@
 
-\hypertarget{introduction-1}{%
-\subsection{Introduction}\label{introduction-1}}
+\hypertarget{results}{%
+\subsection{Results}\label{results}}
 
-\hypertarget{introduction-2}{%
-\subsection{Introduction}\label{introduction-2}}
+\hypertarget{d-template-matching-can-be-used-to-find-ribosomal-subunits-in-cryo-fib-thinned-lamella-of-mammalian-cells}{%
+\subsubsection{2D-Template matching can be used to find ribosomal subunits in cryo-FIB thinned lamella of mammalian cells}\label{d-template-matching-can-be-used-to-find-ribosomal-subunits-in-cryo-fib-thinned-lamella-of-mammalian-cells}}
+
+To test whether we could detect individual ribosomes in mammalian cells we
+prepared cryo-lamella of mouse neutrophil-like cells. Low-magnification images
+of these lamellas clearly shows cellular features consistent with a
+neutrophil-like phenotype, mainly a segmented nucleus and a plethora of
+membrane-organelles, corresponding to the granules and secretory vesicles of
+neutrophils. We then proceeded to acquire micrographs on this lamella with a
+defocus of 0.5-1.0 um, 30 e/A2/s exposure and 1.5 A pixelsize. We manually
+selected multiple locations in the lamella and focused using standard low-dose
+techniques, i.e.~by first ensuring correct focus by imaging a sacrifical area.
+The resoluting micrographs showed no signs of crystalline ice and had thon-rings
+to resolution, indicating successfull vitrification.
+
+We used an atomic model of the 60S mouse ribosomal subunit (6SWA) for 2D
+template matching. In a subset of images the distribution of cross-correlation
+scores significantly exceeded the distribution expected from non-signifcant
+matching(Figure 1B). In the resulting scaled maximum-intensity maps, clear peaks
+with SNR thresholds up to 10 were apparent (Figure 1C). By using the criterion
+described by for thresholding potential matches we found that in images of
+cytosolic ompartments we found evidence of 10-500 ribosomes in the imaged areas.
+Notably we found no matches in images that were taken in the nuclear
+compartment. In the cytosolic areas we found a drastically different number of
+matches, In somer areas we found only \textasciitilde{} 50 matches er image area, corresponding
+to a concentration of\ldots, while in another area we found more than 500 matches,
+corresponding to a concentration of \ldots{} .
+
+\hypertarget{cryo-emilia-for-2d-imaging-of-whole-lamella}{%
+\subsubsection{cryo-EMILIA for 2D imaging of whole lamella}\label{cryo-emilia-for-2d-imaging-of-whole-lamella}}
+
+In order to obtain high-resolution data for complete lamella we used a new
+approach for data collection. This approach uses three key strategies: (1)
+ensures that every electron that exposes the sample is collected on the camera
+(2) uses beam-image shift to precisely and quickly raster the surface of the
+lamella and (3) uses a focusing strategy that does not rely on a sacrificial
+area.
+
+To ensure that every electron exposing the sample was captured by the detector,
+we focused the electron beam so that the entire beam was placed on the detector.
+During canonical low-dose imaging the microscope is configured so that the focal
+plan is identical to the eucentric plane of the specimen stage. This leaves the
+C2 aperture out of focus, resulting in ripples at the edge of the beam (Figure
+2B). While these ripples are low-resolution features that might not interfere
+with 2D template matching, which is designed to be robust to low-resolution
+noise, we also tested collecting data under a condition where the C2 aperture is
+in focus (Figure 2C).
+
+We then centered a lamella under the electron beam and used beam-image shift of
+the microscope to systematically raster the whole surface of the lamella in a
+hexagonal pattern. Instead of focusing in a sacrificial area, we determined the
+defocus after every exposure using a routine implemented in SerialEM modeled
+after CTFFind. The focus was then adjusted based on the difference between
+desired and measured defocus. Since we used a serpentine pattern for data
+collection every exposure is close to the previous exposure making drastic
+changes in the defocus unlikely. Furthermore we started our acquisition pattern
+on the platinum deposition edge, so the initial exposure where the defocus was
+not yet adjusted did not contain any biologically relevant information.
+
+We used this strategy to collect data on 8 lamella, 4 using the eucentric focus
+condition and 4 using the fringe-free condition. We were able to highly
+consistently collect data with a defocus of 8 um (Figure 2D), both in the
+eucentric focus and fringe-free focus condition. Together with the nominal
+defocus of the microscope this data results in a topological map of the lamella.
+To ensure that data was collected consistently, we mapped defocus values as a
+function of the applied Beam-image shift (Figure 2E). This demonstrated that the
+defocus was consistent over the lamella, with outliers only at isolated images
+and in images containing contamination. We also plotted the measure objective
+astigmatism of the lamella and found that it varies with the applied Beam-image
+shift, become more astigmatic mostly due to beam-image shift in the X
+direction. While approaches exist to correct this during the data-collection, we
+opted to not use these mechanism for these early experiments and instead rely on
+computational correction of these aberrations in order to characterize them.
+
+\hypertarget{d-template-matching-of-cryo-emilia-data-reveals-ribosome-distribution}{%
+\subsubsection{2D-Template matching of cryo-EMILIA data reveals ribosome distribution}\label{d-template-matching-of-cryo-emilia-data-reveals-ribosome-distribution}}
+
+We developed customized preprocessing protocol to images obtained by cryo-EMILIA
+to enable their use for 2D-template matching. First we restricted calculation of
+cross-correlation coefficients between individual movie frames to the central
+portion of the image to prevent artifacts from the beam edges on estimation of
+motion. Then we calculated a mask that defined the illuminated area of the
+micrographs and used it to fill non-illumated areas with gaussian noise,
+matching mean and standard deviation to the illuminated signal (Figure 3A). The
+so processed images were suitable for 2D-template matching and we were able to
+obtained matches with the same model used for the data in Figure 1.
+
+\hypertarget{quantitative-analysis-of-translation-activity}{%
+\subsubsection{Quantitative analysis of translation activity}\label{quantitative-analysis-of-translation-activity}}
+
+\hypertarget{discussion}{%
+\subsection{Discussion}\label{discussion}}
+
+\begin{itemize}
+\item
+  Elizabeth Wright and Grant Jensen Montage tomography papers
+\item
+  Waffle method for higher throughput, automation of fib-milling
+\item
+  Throughput and bottlenecks
+\item
+  Visual proteomics
+\item
+  Granules containing ribosomes?
+\item
+  Threshold implications (no matches on most images)
+\end{itemize}
 
@@
 
-\begin{fignos:no-prefix-figure-caption}
+\begin{figure}
+\hypertarget{fig:initmatching}{%
+\centering
+\includegraphics{figures/figure1_draft.pdf}
+\caption{Template matching of ribosomal large subunits in fib-milled neutrophil like cells}\label{fig:initmatching}
+}
+\end{figure}
 
 \begin{figure}
+\hypertarget{fig:initmatching2}{%
+\centering
+\includegraphics{figures/initmatching2.pdf}
+\caption{This is an example-figurern}\label{fig:initmatching2}
+}
+\end{figure}
+
+\begin{figure}
+\hypertarget{fig:approach}{%
 \centering
 \includegraphics{figures/example-figure.pdf}
-\caption{This is an example-figurern}
+\caption{This is an example-figurern}\label{fig:approach}
+}
 \end{figure}
 
-\end{fignos:no-prefix-figure-caption}
+\begin{figure}
+\hypertarget{fig:approach2}{%
+\centering
+\includegraphics{figures/example-figure2.pdf}
+\caption{This is an example-figurern}\label{fig:approach2}
+}
+\end{figure}
+
+\begin{figure}
+\hypertarget{fig:approach3}{%
+\centering
+\includegraphics{figures/example-figure3.pdf}
+\caption{This is an example-figurern}\label{fig:approach3}
+}
+\end{figure}
+
+\begin{figure}
+\hypertarget{fig:approach4}{%
+\centering
+\includegraphics{figures/example-figure4.pdf}
+\caption{This is an example-figurern}\label{fig:approach4}
+}
+\end{figure}
+
+\begin{figure}
+\hypertarget{fig:matching}{%
+\centering
+\includegraphics{figures/matching.pdf}
+\caption{This is an example-figurern}\label{fig:matching}
+}
+\end{figure}
 
@@
 \begin{CSLReferences}{0}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-tSXIKPl7}{}}%
+\CSLLeftMargin{1. }
+\CSLRightInline{\textbf{Label-free, normalized quantification of complex mass spectrometry data for proteomic analysis}
+\CSLBlock{Noelle M Griffin, Jingyi Yu, Fred Long, Phil Oh, Sabrina Shore, Yan Li, Jim A Koziol, Jan E Schnitzer} \emph{Nature Biotechnology} (2010-01) \url{https://doi.org/fshgnc}
+\CSLBlock{DOI: \href{https://doi.org/10.1038/nbt.1592}{10.1038/nbt.1592} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/20010810}{20010810} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2805705}{PMC2805705}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-VBmW7Aot}{}}%
+\CSLLeftMargin{2. }
+\CSLRightInline{\textbf{Fluorescence microscopy}
+\CSLBlock{Jeff W Lichtman, José-Angel Conchello} \emph{Nature Methods} (2005-12) \url{https://doi.org/bbpg4n}
+\CSLBlock{DOI: \href{https://doi.org/10.1038/nmeth817}{10.1038/nmeth817} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/16299476}{16299476}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-tGQ6TSUo}{}}%
+\CSLLeftMargin{3. }
+\CSLRightInline{\textbf{A visual approach to proteomics}
+\CSLBlock{Stephan Nickell, Christine Kofler, Andrew P Leis, Wolfgang Baumeister} \emph{Nature Reviews Molecular Cell Biology} (2006-03) \url{https://doi.org/d6d5mq}
+\CSLBlock{DOI: \href{https://doi.org/10.1038/nrm1861}{10.1038/nrm1861} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/16482091}{16482091}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-g8QavfwP}{}}%
+\CSLLeftMargin{4. }
+\CSLRightInline{\textbf{Electron microscopy of frozen hydrated sections of vitreous ice and vitrified biological samples}
+\CSLBlock{AW McDowall, J-J Chang, R Freeman, J Lepault, CA Walter, J Dubochet} \emph{Journal of Microscopy} (1983-07) \url{https://doi.org/bdnzmv}
+\CSLBlock{DOI: \href{https://doi.org/10.1111/j.1365-2818.1983.tb04225.x}{10.1111/j.1365-2818.1983.tb04225.x} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/6350598}{6350598}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-16IhS1Nc4}{}}%
+\CSLLeftMargin{5. }
+\CSLRightInline{\textbf{Opening windows into the cell: focused-ion-beam milling for cryo-electron tomography}
+\CSLBlock{Elizabeth Villa, Miroslava Schaffer, Jürgen M Plitzko, Wolfgang Baumeister} \emph{Current Opinion in Structural Biology} (2013-10) \url{https://doi.org/f537jp}
+\CSLBlock{DOI: \href{https://doi.org/10.1016/j.sbi.2013.08.006}{10.1016/j.sbi.2013.08.006} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/24090931}{24090931}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Rksh2dxu}{}}%
+\CSLLeftMargin{6. }
+\CSLRightInline{\textbf{Electron tomography of cells}
+\CSLBlock{Lu Gan, Grant J Jensen} \emph{Quarterly Reviews of Biophysics} (2012-02) \url{https://doi.org/czj9hr}
+\CSLBlock{DOI: \href{https://doi.org/10.1017/s0033583511000102}{10.1017/s0033583511000102} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/22082691}{22082691}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Ynb3IP6I}{}}%
+\CSLLeftMargin{7. }
+\CSLRightInline{\textbf{Single-protein detection in crowded molecular environments in cryo-EM images}
+\CSLBlock{JPeter Rickgauer, Nikolaus Grigorieff, Winfried Denk} \emph{eLife} (2017-05-03) \url{https://doi.org/gnq4q4}
+\CSLBlock{DOI: \href{https://doi.org/10.7554/elife.25648}{10.7554/elife.25648} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/28467302}{28467302} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5453696}{PMC5453696}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-18KGpXYPE}{}}%
+\CSLLeftMargin{8. }
+\CSLRightInline{\textbf{Label-free single-instance protein detection in vitrified cells}
+\CSLBlock{JPeter Rickgauer, Heejun Choi, Jennifer Lippincott-Schwartz, Winfried Denk} \emph{Biophysics} (2020-04-24) \url{https://doi.org/gpbjfd}
+\CSLBlock{DOI: \href{https://doi.org/10.1101/2020.04.22.053868}{10.1101/2020.04.22.053868}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-10bXZuF3G}{}}%
+\CSLLeftMargin{9. }
+\CSLRightInline{\textbf{Locating macromolecular assemblies in cells by 2D template matching with cisTEM}
+\CSLBlock{Bronwyn A Lucas, Benjamin A Himes, Liang Xue, Timothy Grant, Julia Mahamid, Nikolaus Grigorieff} \emph{eLife} (2021-06-11) \url{https://doi.org/gkkc49}
+\CSLBlock{DOI: \href{https://doi.org/10.7554/elife.68946}{10.7554/elife.68946} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/34114559}{34114559} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC8219381}{PMC8219381}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-gRoY21jY}{}}%
+\CSLLeftMargin{10. }
+\CSLRightInline{\textbf{Hallmarks of ribosomopathies}
+\CSLBlock{Kim R Kampen, Sergey O Sulima, Stijn Vereecke, Kim De~Keersmaecker} \emph{Nucleic Acids Research} (2020-02-20) \url{https://doi.org/gpbjfm}
+\CSLBlock{DOI: \href{https://doi.org/10.1093/nar/gkz637}{10.1093/nar/gkz637} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/31350888}{31350888} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7026650}{PMC7026650}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-KAJ7221k}{}}%
+\CSLLeftMargin{11. }
+\CSLRightInline{\textbf{Diagnostic and prognostic implications of ribosomal protein transcript expression patterns in human cancers}
+\CSLBlock{James M Dolezal, Arie P Dash, Edward V Prochownik} \emph{BMC Cancer} (2018-12) \url{https://doi.org/gc87j9}
+\CSLBlock{DOI: \href{https://doi.org/10.1186/s12885-018-4178-z}{10.1186/s12885-018-4178-z} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/29530001}{29530001} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5848553}{PMC5848553}}}
+
 \leavevmode\vadjust pre{\hypertarget{ref-1B9Vt9eYu}{}}%
-\CSLLeftMargin{1. }
+\CSLLeftMargin{12. }
 \CSLRightInline{\textbf{Inhibition of Dihydroorotate Dehydrogenase Overcomes Differentiation Blockade in Acute Myeloid Leukemia}

### 2022-02-20 manuscript.tex
Update word template [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/27bee68862078e46176d358694eaaf9f82467d4e.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/27bee68862078e46176d358694eaaf9f82467d4e/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1873152767

@@
 This manuscript
-(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/56181559e858af0a515082cd5c28c9f1b8501873/}{permalink})
+(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/27bee68862078e46176d358694eaaf9f82467d4e/}{permalink})
 was automatically generated
-from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/56181559e858af0a515082cd5c28c9f1b8501873}{jojoelfe/deco\_lace\_template\_matching\_manuscript@5618155}
+from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/27bee68862078e46176d358694eaaf9f82467d4e}{jojoelfe/deco\_lace\_template\_matching\_manuscript@27bee68}
 on February 20, 2022.

### 2022-02-20 ci/deploy.sh
Don't deploy to gh-pages for now

@@ -96,13 +96,13 @@ ghp-import \
   output
 
 # Deploy the webpage directory to gh-pages
-ghp-import \
-  --no-jekyll \
-  --follow-links \
-  --push \
-  --branch=gh-pages \
-  --message="$MESSAGE" \
-  webpage
+# ghp-import \
+#  --no-jekyll \
+#  --follow-links \
+#  --push \
+#  --branch=gh-pages \
+#  --message="$MESSAGE" \
+#  webpage
 
 if [ $MANUBOT_DEPLOY_VIA_SSH = "true" ]; then
   # Workaround https://github.com/travis-ci/travis-ci/issues/8082

### 2022-02-20 manuscript.tex
Don't deploy to gh-pages for now [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a8f7e15ca68cda59eec8dcd51b56efdb54e9344e.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a8f7e15ca68cda59eec8dcd51b56efdb54e9344e/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1873179503

@@
 This manuscript
-(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/27bee68862078e46176d358694eaaf9f82467d4e/}{permalink})
+(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/a8f7e15ca68cda59eec8dcd51b56efdb54e9344e/}{permalink})
 was automatically generated
-from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/27bee68862078e46176d358694eaaf9f82467d4e}{jojoelfe/deco\_lace\_template\_matching\_manuscript@27bee68}
+from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/a8f7e15ca68cda59eec8dcd51b56efdb54e9344e}{jojoelfe/deco\_lace\_template\_matching\_manuscript@a8f7e15}
 on February 20, 2022.

### 2022-02-21 manuscript.tex
Merge pull request #1 from jojoelfe/rootstock-2022-02-21 [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/fd67573aae85b96b8a70c12b88d9cb7dbe226559.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/fd67573aae85b96b8a70c12b88d9cb7dbe226559/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1876510914

@@
 This manuscript
-(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/a8f7e15ca68cda59eec8dcd51b56efdb54e9344e/}{permalink})
+(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/fd67573aae85b96b8a70c12b88d9cb7dbe226559/}{permalink})
 was automatically generated
-from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/a8f7e15ca68cda59eec8dcd51b56efdb54e9344e}{jojoelfe/deco\_lace\_template\_matching\_manuscript@a8f7e15}
-on February 20, 2022.
+from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/fd67573aae85b96b8a70c12b88d9cb7dbe226559}{jojoelfe/deco\_lace\_template\_matching\_manuscript@fd67573}
+on February 21, 2022.
 
@@
 \CSLRightInline{\textbf{Fluorescence microscopy}
-\CSLBlock{Jeff W Lichtman, José-Angel Conchello} \emph{Nature Methods} (2005-12) \url{https://doi.org/bbpg4n}
+\CSLBlock{Jeff W Lichtman, José-Angel Conchello} \emph{Nature Methods} (2005-11-18) \url{https://doi.org/bbpg4n}
 \CSLBlock{DOI: \href{https://doi.org/10.1038/nmeth817}{10.1038/nmeth817} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/16299476}{16299476}}}
@@
 \CSLRightInline{\textbf{A visual approach to proteomics}
-\CSLBlock{Stephan Nickell, Christine Kofler, Andrew P Leis, Wolfgang Baumeister} \emph{Nature Reviews Molecular Cell Biology} (2006-03) \url{https://doi.org/d6d5mq}
+\CSLBlock{Stephan Nickell, Christine Kofler, Andrew P Leis, Wolfgang Baumeister} \emph{Nature Reviews Molecular Cell Biology} (2006-02-15) \url{https://doi.org/d6d5mq}
 \CSLBlock{DOI: \href{https://doi.org/10.1038/nrm1861}{10.1038/nrm1861} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/16482091}{16482091}}}
@@
 \CSLRightInline{\textbf{Electron tomography of cells}
-\CSLBlock{Lu Gan, Grant J Jensen} \emph{Quarterly Reviews of Biophysics} (2012-02) \url{https://doi.org/czj9hr}
+\CSLBlock{Lu Gan, Grant J Jensen} \emph{Quarterly Reviews of Biophysics} (2011-11-15) \url{https://doi.org/czj9hr}
 \CSLBlock{DOI: \href{https://doi.org/10.1017/s0033583511000102}{10.1017/s0033583511000102} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/22082691}{22082691}}}
@@
 \CSLRightInline{\textbf{Label-free single-instance protein detection in vitrified cells}
-\CSLBlock{JPeter Rickgauer, Heejun Choi, Jennifer Lippincott-Schwartz, Winfried Denk} \emph{Biophysics} (2020-04-24) \url{https://doi.org/gpbjfd}
+\CSLBlock{JPeter Rickgauer, Heejun Choi, Jennifer Lippincott-Schwartz, Winfried Denk} \emph{Cold Spring Harbor Laboratory} (2020-04-24) \url{https://doi.org/gpbjfd}
 \CSLBlock{DOI: \href{https://doi.org/10.1101/2020.04.22.053868}{10.1101/2020.04.22.053868}}}
@@
 \CSLRightInline{\textbf{Hallmarks of ribosomopathies}
-\CSLBlock{Kim R Kampen, Sergey O Sulima, Stijn Vereecke, Kim De~Keersmaecker} \emph{Nucleic Acids Research} (2020-02-20) \url{https://doi.org/gpbjfm}
+\CSLBlock{Kim R Kampen, Sergey O Sulima, Stijn Vereecke, Kim De~Keersmaecker} \emph{Nucleic Acids Research} (2019-07-27) \url{https://doi.org/gpbjfm}
 \CSLBlock{DOI: \href{https://doi.org/10.1093/nar/gkz637}{10.1093/nar/gkz637} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/31350888}{31350888} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7026650}{PMC7026650}}}
@@
 \CSLRightInline{\textbf{Diagnostic and prognostic implications of ribosomal protein transcript expression patterns in human cancers}
-\CSLBlock{James M Dolezal, Arie P Dash, Edward V Prochownik} \emph{BMC Cancer} (2018-12) \url{https://doi.org/gc87j9}
+\CSLBlock{James M Dolezal, Arie P Dash, Edward V Prochownik} \emph{BMC Cancer} (2018-03-12) \url{https://doi.org/gc87j9}
 \CSLBlock{DOI: \href{https://doi.org/10.1186/s12885-018-4178-z}{10.1186/s12885-018-4178-z} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/29530001}{29530001} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5848553}{PMC5848553}}}

### 2022-02-23 content/code/ctf_correct_view.py
Work on views and assembly

@@ -1,6 +1,15 @@
-import pycistem, asyncio
+import pycistem
+from pathlib import Path 
+
+import subprocess
+
+
+directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/views")
+directory.mkdir(parents=True, exist_ok=True)
+
 
 lamella = [
+
     (98, "fff_lamella1.mrc"),
     (99, "fff_lamella2.mrc"),
     (100, "fff_lamella3.mrc"),
@@ -8,15 +17,21 @@ lamella = [
     (83, "euc_lamella1.mrc"),
     (82,"euc_lamella2.mrc"),
     (81,"euc_lamella3.mrc"),
-    (80,"euc_lamella4.mrc")
+    (80,"euc_lamella4.mrc"),
+    (103,"the_lamella1.mrc"),
 ]
+
+
 for l in lamella:
-    p = pycistem.programs.apply_ctf.parameters_from_database("/scratch/bern/elferich/views/views.db",l[0],l[1],
+    p = pycistem.programs.apply_ctf.parameters_from_database("/scratch/bern/elferich/views/views.db",l[0], str(directory / l[1]),
         apply_wiener_filter=True,
+        phase_flip_only=False,
         wiener_filter_falloff_frequency = 720.0,
         wiener_filter_falloff_fudge_factor = 0.9,
         wiener_filter_scale_fudge_factor = 0.4,
         wiener_filter_high_pass_radius= 200.0)
     print(p)
     pycistem.set_cistem_path("/groups/elferich/cisTEM/build/fowl_template_matching_Intel-gpu-debug/src/")
-    asyncio.run(pycistem.programs.apply_ctf.run(p))
+    pycistem.programs.apply_ctf.run(p)
+    subprocess.run(f"/groups/cryoadmin/software/IMOD/imod_4.11.10_RHEL7-64_CUDA10/IMOD/bin/mrc2tif {str(directory / l[1])} {str(directory / l[1]).replace('.mrc','.tif')}", shell=True)
+    subprocess.run(f"/groups/cryoadmin/software/FIJI/Fiji.app/ImageJ-linux64 --ij2 --headless --console -macro content/code/fiji_subtract_bckground.ijm '{ l[1].replace('.mrc','.tif')}'", shell=True)

### 2022-02-23 content/code/plot_acquisition_positions_g1_l1.py

@@ -35,8 +35,8 @@ def get_corners(x,y,radius):
     return [[x+radius,y+radius],[x-radius,y+radius],[x-radius,y-radius],[x+radius,y-radius]]
 
 def get_range(data):
-    min_shift_x = np.min(data.loc[:,"image_shift_pixel_x"]) - 200 * crop_by
-    min_shift_y = np.min(data.loc[:,"image_shift_pixel_y"]) - 200 * crop_by
+    min_shift_x = np.min(data.loc[:,"image_shift_pixel_x"]) - 100 * crop_by
+    min_shift_y = np.min(data.loc[:,"image_shift_pixel_y"]) - 100 * crop_by
     max_shift_x = np.max(data.loc[:,"image_shift_pixel_x"]/crop_by) + 100
     max_shift_y = np.max(data.loc[:,"image_shift_pixel_y"]/crop_by) + 100
     max_image_x = np.max(data.loc[:,"X_SIZE"]/crop_by)
@@ -44,10 +44,10 @@ def get_range(data):
     return (min_shift_x,min_shift_y)
 
 def plot_montage(data,to_show):
-    min_shift_x = np.min(data.loc[:,"image_shift_pixel_x"]/crop_by) - 200
-    min_shift_y = np.min(data.loc[:,"image_shift_pixel_y"]/crop_by) - 200
-    max_shift_x = np.max(data.loc[:,"image_shift_pixel_x"]/crop_by) + 200
-    max_shift_y = np.max(data.loc[:,"image_shift_pixel_y"]/crop_by) + 200
+    min_shift_x = np.min(data.loc[:,"image_shift_pixel_x"]/crop_by) - 100
+    min_shift_y = np.min(data.loc[:,"image_shift_pixel_y"]/crop_by) - 100
+    max_shift_x = np.max(data.loc[:,"image_shift_pixel_x"]/crop_by) + 100
+    max_shift_y = np.max(data.loc[:,"image_shift_pixel_y"]/crop_by) + 100
     max_image_x = np.max(data.loc[:,"X_SIZE"]/crop_by)
     max_image_y = np.max(data.loc[:,"Y_SIZE"]/crop_by)
 
@@ -55,14 +55,13 @@ def plot_montage(data,to_show):
     mask = np.zeros((int(max_shift_y-min_shift_y+max_image_y),int(max_shift_x-min_shift_x+max_image_x)))
[…]

### 2022-02-23 content/code/plot_acquisition_positions_g1_l2.py

@@ -62,7 +62,7 @@ def plot_montage(data,to_show):
             image_data = np.copy(np.flip(mrc.data[0],axis=0))
             image_data = resize(image_data, (image_data.shape[0] // crop_by, image_data.shape[1] // crop_by),anti_aliasing=True)
         
-        with mrcfile.open(image['FILENAME'][:-6]+"_1_mask.mrc") as mrc: 
+        with mrcfile.open(image['FILENAME'][:-6]+"_0_mask.mrc") as mrc: 
             mask_data = np.copy(np.flip(mrc.data[0],axis=0))
             mask_data.dtype = np.uint8
         
@@ -108,15 +108,15 @@ def plot_montage(data,to_show):
 
 
 
-selected_micrographs = utils.get_data_from_db(utils.datasets[2])
-print(utils.datasets[2])
+selected_micrographs = utils.get_data_from_db(utils.datasets[1])
+print(utils.datasets[1])
 print(len(selected_micrographs))
 initial_assembly(selected_micrographs,IS_to_camera=IS_to_camera)
 
 directory = Path("/scratch/bern/elferich/decolace_manuscript_processing/initial_assembly/")
 directory.mkdir(parents=True,exist_ok=True)
 
-image_cache_filename = directory / 'euc_lamella3_cache.npz'
+image_cache_filename = directory / 'euc_lamella2_cache.npz'
 if load_cached_images:
     load = np.load(image_cache_filename)
     assemb = load["image"]
@@ -126,7 +126,7 @@ else:
     (assemb, mask, matches) = plot_montage(selected_micrographs,[i+2 for i,r in selected_micrographs.iterrows()])
     np.savez_compressed(image_cache_filename,matches=matches,mask=mask,image=assemb)
     corr = assemb/mask
-    io.imsave(directory / 'euc_lamella3_image.tif',corr/np.max(corr),plugin='pil')
+    io.imsave(directory / 'euc_lamella2_image.tif',corr/np.max(corr),plugin='pil')
 
 
 exit()

### 2022-02-23 content/code/plot_acquisition_positions_g1_l3_old.py

@@ -6,7 +6,6 @@ import napari
 import mrcfile
 from pathlib import Path
 from skimage.transform import rescale, resize, downscale_local_mean
-from skimage import io
 
 IS_to_camera = np.array([13374,  6053.4,  6394.1,  -13172])
 IS_to_camera.shape = (2,2)
@@ -15,8 +14,6 @@ IS_to_camera.shape = (2,2)
 scaled_x_size = 1200.0
 
 load_cached_images = False
-
-crop_by = 10
 
 def get_scaled_filename(filename):
     p = Path(filename)
@@ -35,32 +32,31 @@ def get_corners(x,y,radius):
     return [[x+radius,y+radius],[x-radius,y+radius],[x-radius,y-radius],[x+radius,y-radius]]
 
 def get_range(data):
-    min_shift_x = np.min(data.loc[:,"image_shift_pixel_x"]) - 200 * crop_by
-    min_shift_y = np.min(data.loc[:,"image_shift_pixel_y"]) - 200 * crop_by
-    max_shift_x = np.max(data.loc[:,"image_shift_pixel_x"]/crop_by) + 100
-    max_shift_y = np.max(data.loc[:,"image_shift_pixel_y"]/crop_by) + 100
-    max_image_x = np.max(data.loc[:,"X_SIZE"]/crop_by)
-    max_image_y = np.max(data.loc[:,"Y_SIZE"]/crop_by)
+    min_shift_x = np.min(data.loc[:,"image_shift_pixel_x"]) - 4000
+    min_shift_y = np.min(data.loc[:,"image_shift_pixel_y"]) - 4000
+    max_shift_x = np.max(data.loc[:,"image_shift_pixel_x"]/4) + 1000
+    max_shift_y = np.max(data.loc[:,"image_shift_pixel_y"]/4) + 1000
+    max_image_x = np.max(data.loc[:,"X_SIZE"]/4)
+    max_image_y = np.max(data.loc[:,"Y_SIZE"]/4)
     return (min_shift_x,min_shift_y)
 
 def plot_montage(data,to_show):
-    min_shift_x = np.min(data.loc[:,"image_shift_pixel_x"]/crop_by) - 200
-    min_shift_y = np.min(data.loc[:,"image_shift_pixel_y"]/crop_by) - 200
-    max_shift_x = np.max(data.loc[:,"image_shift_pixel_x"]/crop_by) + 200
[…]

### 2022-02-23 content/code/plot_acquisition_positions_g1_l4.py

@@ -108,15 +108,15 @@ def plot_montage(data,to_show):
 
 
 
-selected_micrographs = utils.get_data_from_db(utils.datasets[2])
-print(utils.datasets[2])
+selected_micrographs = utils.get_data_from_db(utils.datasets[3])
+print(utils.datasets[3])
 print(len(selected_micrographs))
 initial_assembly(selected_micrographs,IS_to_camera=IS_to_camera)
 
 directory = Path("/scratch/bern/elferich/decolace_manuscript_processing/initial_assembly/")
 directory.mkdir(parents=True,exist_ok=True)
 
-image_cache_filename = directory / 'euc_lamella3_cache.npz'
+image_cache_filename = directory / 'euc_lamella4_cache.npz'
 if load_cached_images:
     load = np.load(image_cache_filename)
     assemb = load["image"]
@@ -126,7 +126,7 @@ else:
     (assemb, mask, matches) = plot_montage(selected_micrographs,[i+2 for i,r in selected_micrographs.iterrows()])
     np.savez_compressed(image_cache_filename,matches=matches,mask=mask,image=assemb)
     corr = assemb/mask
-    io.imsave(directory / 'euc_lamella3_image.tif',corr/np.max(corr),plugin='pil')
+    io.imsave(directory / 'euc_lamella4_image.tif',corr/np.max(corr),plugin='pil')
 
 
 exit()

### 2022-02-23 content/code/plot_acquisition_positions_g2_l1.py

@@ -35,8 +35,8 @@ def get_corners(x,y,radius):
     return [[x+radius,y+radius],[x-radius,y+radius],[x-radius,y-radius],[x+radius,y-radius]]
 
 def get_range(data):
-    min_shift_x = np.min(data.loc[:,"image_shift_pixel_x"]) - 200 * crop_by
-    min_shift_y = np.min(data.loc[:,"image_shift_pixel_y"]) - 200 * crop_by
+    min_shift_x = np.min(data.loc[:,"image_shift_pixel_x"]) - 100 * crop_by
+    min_shift_y = np.min(data.loc[:,"image_shift_pixel_y"]) - 100 * crop_by
     max_shift_x = np.max(data.loc[:,"image_shift_pixel_x"]/crop_by) + 100
     max_shift_y = np.max(data.loc[:,"image_shift_pixel_y"]/crop_by) + 100
     max_image_x = np.max(data.loc[:,"X_SIZE"]/crop_by)
@@ -44,10 +44,10 @@ def get_range(data):
     return (min_shift_x,min_shift_y)
 
 def plot_montage(data,to_show):
-    min_shift_x = np.min(data.loc[:,"image_shift_pixel_x"]/crop_by) - 200
-    min_shift_y = np.min(data.loc[:,"image_shift_pixel_y"]/crop_by) - 200
-    max_shift_x = np.max(data.loc[:,"image_shift_pixel_x"]/crop_by) + 200
-    max_shift_y = np.max(data.loc[:,"image_shift_pixel_y"]/crop_by) + 200
+    min_shift_x = np.min(data.loc[:,"image_shift_pixel_x"]/crop_by) - 100
+    min_shift_y = np.min(data.loc[:,"image_shift_pixel_y"]/crop_by) - 100
+    max_shift_x = np.max(data.loc[:,"image_shift_pixel_x"]/crop_by) + 100
+    max_shift_y = np.max(data.loc[:,"image_shift_pixel_y"]/crop_by) + 100
     max_image_x = np.max(data.loc[:,"X_SIZE"]/crop_by)
     max_image_y = np.max(data.loc[:,"Y_SIZE"]/crop_by)
 
@@ -55,7 +55,6 @@ def plot_montage(data,to_show):
     mask = np.zeros((int(max_shift_y-min_shift_y+max_image_y),int(max_shift_x-min_shift_x+max_image_x)))
[…]

### 2022-02-23 content/code/plot_acquisition_positions_g2_l2.py

@@ -108,15 +108,15 @@ def plot_montage(data,to_show):
 
 
 
-selected_micrographs = utils.get_data_from_db(utils.datasets[2])
-print(utils.datasets[2])
+selected_micrographs = utils.get_data_from_db(utils.datasets[5])
+print(utils.datasets[5])
 print(len(selected_micrographs))
 initial_assembly(selected_micrographs,IS_to_camera=IS_to_camera)
 
 directory = Path("/scratch/bern/elferich/decolace_manuscript_processing/initial_assembly/")
 directory.mkdir(parents=True,exist_ok=True)
 
-image_cache_filename = directory / 'euc_lamella3_cache.npz'
+image_cache_filename = directory / 'fff_lamella2_cache.npz'
 if load_cached_images:
     load = np.load(image_cache_filename)
     assemb = load["image"]
@@ -126,7 +126,7 @@ else:
     (assemb, mask, matches) = plot_montage(selected_micrographs,[i+2 for i,r in selected_micrographs.iterrows()])
     np.savez_compressed(image_cache_filename,matches=matches,mask=mask,image=assemb)
     corr = assemb/mask
-    io.imsave(directory / 'euc_lamella3_image.tif',corr/np.max(corr),plugin='pil')
+    io.imsave(directory / 'fff_lamella2_image.tif',corr/np.max(corr),plugin='pil')
 
 
 exit()

### 2022-02-23 content/code/plot_acquisition_positions_g2_l3.py

@@ -108,15 +108,15 @@ def plot_montage(data,to_show):
 
 
 
-selected_micrographs = utils.get_data_from_db(utils.datasets[2])
-print(utils.datasets[2])
+selected_micrographs = utils.get_data_from_db(utils.datasets[6])
+print(utils.datasets[6])
 print(len(selected_micrographs))
 initial_assembly(selected_micrographs,IS_to_camera=IS_to_camera)
 
 directory = Path("/scratch/bern/elferich/decolace_manuscript_processing/initial_assembly/")
 directory.mkdir(parents=True,exist_ok=True)
 
-image_cache_filename = directory / 'euc_lamella3_cache.npz'
+image_cache_filename = directory / 'fff_lamella3_cache.npz'
 if load_cached_images:
     load = np.load(image_cache_filename)
     assemb = load["image"]
@@ -126,7 +126,7 @@ else:
     (assemb, mask, matches) = plot_montage(selected_micrographs,[i+2 for i,r in selected_micrographs.iterrows()])
     np.savez_compressed(image_cache_filename,matches=matches,mask=mask,image=assemb)
     corr = assemb/mask
-    io.imsave(directory / 'euc_lamella3_image.tif',corr/np.max(corr),plugin='pil')
+    io.imsave(directory / 'fff_lamella3_image.tif',corr/np.max(corr),plugin='pil')
 
 
 exit()

### 2022-02-23 content/code/plot_acquisition_positions_g2_l4.py

@@ -108,15 +108,15 @@ def plot_montage(data,to_show):
 
 
 
-selected_micrographs = utils.get_data_from_db(utils.datasets[2])
-print(utils.datasets[2])
+selected_micrographs = utils.get_data_from_db(utils.datasets[7])
+print(utils.datasets[7])
 print(len(selected_micrographs))
 initial_assembly(selected_micrographs,IS_to_camera=IS_to_camera)
 
 directory = Path("/scratch/bern/elferich/decolace_manuscript_processing/initial_assembly/")
 directory.mkdir(parents=True,exist_ok=True)
 
-image_cache_filename = directory / 'euc_lamella3_cache.npz'
+image_cache_filename = directory / 'fff_lamella4_cache.npz'
 if load_cached_images:
     load = np.load(image_cache_filename)
     assemb = load["image"]
@@ -126,7 +126,7 @@ else:
     (assemb, mask, matches) = plot_montage(selected_micrographs,[i+2 for i,r in selected_micrographs.iterrows()])
     np.savez_compressed(image_cache_filename,matches=matches,mask=mask,image=assemb)
     corr = assemb/mask
-    io.imsave(directory / 'euc_lamella3_image.tif',corr/np.max(corr),plugin='pil')
+    io.imsave(directory / 'fff_lamella4_image.tif',corr/np.max(corr),plugin='pil')
 
 
 exit()

### 2022-02-23 content/code/utils.py

@@ -4,7 +4,7 @@ import sqlite3
 import numpy as np
 
 datasets = ["/scratch/bern/elferich/ER_Hox_120h_20211029_g1_l1/ER_Hox_120h_20211029_g1_l1.db",
-            "/scratch/bern/elferich/ER_Hox_120h_20211029_g1_l1/ER_Hox_120h_20211029_g1_l1.db",
+            "/scratch/bern/elferich/ER_Hox_120h_20211029_g1_l2/ER_Hox_120h_20211029_g1_l2.db",
             "/scratch/bern/elferich/ER_Hox_120h_20211029_g2_l3/ER_Hox_120h_20211029_g2_l3.db",
             "/scratch/bern/elferich/ER_Hox_120h_202111029_g2_l4/ER_Hox_120h_202111029_g2_l4.db",
             "/scratch/bern/elferich/R_Hox_120h_20211108_g2_l1/R_Hox_120h_20211108_g2_l1.db",

### 2022-02-23 manuscript.tex
Work on views and assembly [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/16c528a690632e78c5557a0164f560eef13aa854.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/16c528a690632e78c5557a0164f560eef13aa854/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1887731900

@@
 This manuscript
-(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/fd67573aae85b96b8a70c12b88d9cb7dbe226559/}{permalink})
+(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/16c528a690632e78c5557a0164f560eef13aa854/}{permalink})
 was automatically generated
-from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/fd67573aae85b96b8a70c12b88d9cb7dbe226559}{jojoelfe/deco\_lace\_template\_matching\_manuscript@fd67573}
-on February 21, 2022.
+from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/16c528a690632e78c5557a0164f560eef13aa854}{jojoelfe/deco\_lace\_template\_matching\_manuscript@16c528a}
+on February 23, 2022.
 

### 2022-02-23 manuscript.tex
Mostly work on figure 1 [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/db1bd1a285c0519196fc92fb04c4ad271adf3006.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/db1bd1a285c0519196fc92fb04c4ad271adf3006/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1890188788

@@
 This manuscript
-(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/16c528a690632e78c5557a0164f560eef13aa854/}{permalink})
+(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/db1bd1a285c0519196fc92fb04c4ad271adf3006/}{permalink})
 was automatically generated
-from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/16c528a690632e78c5557a0164f560eef13aa854}{jojoelfe/deco\_lace\_template\_matching\_manuscript@16c528a}
+from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/db1bd1a285c0519196fc92fb04c4ad271adf3006}{jojoelfe/deco\_lace\_template\_matching\_manuscript@db1bd1a}
 on February 23, 2022.
@@
 measure this can broadly be divided into label- and label-free techniques. In
-label-techniques a probe is physically attached to a molecule is interest that
+label-techniques a probe is physically attached to a molecule of interest that
 is able to produce a high signal-to-noise signal, such as a fluorescent molecule.
@@
 \centering
-\includegraphics{figures/figure1_draft.pdf}
-\caption{Template matching of ribosomal large subunits in fib-milled neutrophil like cells}\label{fig:initmatching}
+\includegraphics{figures/initmatching.pdf}
+\caption{2D template matching of the large subunit of the ribosome in fib-milled neutrophil-like cells
+(A) Overview image of the lamella.
+Major cellular regions are labeled, as Nucleus (Nuc), Mitochondria (M), and granular cytoplasm (GrCyt).
+FOVs where high-magnification images for template matching where acquired are indicated as boxes with the number of matches indicated on the bottom right.
+FOVs displayed in Panels B-E are color-coded.
+(B-E) FOVs with projection of ribosome LSU matches shown in green.
+(B) Perinuclear region, the only matches are in the cytoplasmic half.
+(C) Cytoplasmic region with high density of ribosomes (D) Mitochondrium, as expected there are only matches in the cytoplasmic region (E) Cytoplasm, with low density of ribosomes.}\label{fig:initmatching}
 }

### 2022-02-24 manuscript.tex
Slightly nicer figure [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/1e239da5dfa82be752529df88887c5cf4896c57d.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/1e239da5dfa82be752529df88887c5cf4896c57d/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1895058558

@@
 \linenumbers
+
+%% pandoc-fignos: environment for tagged figures
+\newenvironment{fignos:tagged-figure}[1][]{
+    \let\oldthefigure\thefigure
+    \let\oldtheHfigure\theHfigure
+    \renewcommand{\thefigure}{#1}
+    \renewcommand{\theHfigure}{#1}
+  }{
+    \let\thefigure\oldthefigure
+    \let\theHfigure\oldtheHfigure
+    \addtocounter{figure}{-1}
+  }
 \ifLuaTeX
@@
 This manuscript
-(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/db1bd1a285c0519196fc92fb04c4ad271adf3006/}{permalink})
+(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/1e239da5dfa82be752529df88887c5cf4896c57d/}{permalink})
 was automatically generated
-from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/db1bd1a285c0519196fc92fb04c4ad271adf3006}{jojoelfe/deco\_lace\_template\_matching\_manuscript@db1bd1a}
-on February 23, 2022.
+from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/1e239da5dfa82be752529df88887c5cf4896c57d}{jojoelfe/deco\_lace\_template\_matching\_manuscript@1e239da}
+on February 24, 2022.
 
@@
 
+\begin{fignos:tagged-figure}[S1]
+
 \begin{figure}
@@
 \end{figure}
+
+\end{fignos:tagged-figure}
 

### 2022-02-25 manuscript.tex
Remove tex file [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/c726b59baf4d652934928fac32dda6261f8cf435.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/c726b59baf4d652934928fac32dda6261f8cf435/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1899284881

@@
 This manuscript
-(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/1e239da5dfa82be752529df88887c5cf4896c57d/}{permalink})
+(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/c726b59baf4d652934928fac32dda6261f8cf435/}{permalink})
 was automatically generated
-from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/1e239da5dfa82be752529df88887c5cf4896c57d}{jojoelfe/deco\_lace\_template\_matching\_manuscript@1e239da}
-on February 24, 2022.
+from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/c726b59baf4d652934928fac32dda6261f8cf435}{jojoelfe/deco\_lace\_template\_matching\_manuscript@c726b59}
+on February 25, 2022.
 

### 2022-02-25 content/code/plot_acquisition_utils.py
More processing scripts

@@ -11,10 +11,6 @@ from skimage import io
 IS_to_camera = np.array([13374,  6053.4,  6394.1,  -13172])
 IS_to_camera.shape = (2,2)
 
-#orig_x_size = 5120
-scaled_x_size = 1200.0
-
-load_cached_images = False
 
 crop_by = 10
 
@@ -35,8 +31,8 @@ def get_corners(x,y,radius):
     return [[x+radius,y+radius],[x-radius,y+radius],[x-radius,y-radius],[x+radius,y-radius]]
 
 def get_range(data):
-    min_shift_x = np.min(data.loc[:,"image_shift_pixel_x"]) - 200 * crop_by
-    min_shift_y = np.min(data.loc[:,"image_shift_pixel_y"]) - 200 * crop_by
+    min_shift_x = np.min(data.loc[:,"image_shift_pixel_x"]) - 100 * crop_by
+    min_shift_y = np.min(data.loc[:,"image_shift_pixel_y"]) - 100 * crop_by
     max_shift_x = np.max(data.loc[:,"image_shift_pixel_x"]/crop_by) + 100
     max_shift_y = np.max(data.loc[:,"image_shift_pixel_y"]/crop_by) + 100
     max_image_x = np.max(data.loc[:,"X_SIZE"]/crop_by)
@@ -44,10 +40,10 @@ def get_range(data):
     return (min_shift_x,min_shift_y)
 
 def plot_montage(data,to_show):
-    min_shift_x = np.min(data.loc[:,"image_shift_pixel_x"]/crop_by) - 200
-    min_shift_y = np.min(data.loc[:,"image_shift_pixel_y"]/crop_by) - 200
-    max_shift_x = np.max(data.loc[:,"image_shift_pixel_x"]/crop_by) + 200
-    max_shift_y = np.max(data.loc[:,"image_shift_pixel_y"]/crop_by) + 200
+    min_shift_x = np.min(data.loc[:,"image_shift_pixel_x"]/crop_by) - 100
+    min_shift_y = np.min(data.loc[:,"image_shift_pixel_y"]/crop_by) - 100
+    max_shift_x = np.max(data.loc[:,"image_shift_pixel_x"]/crop_by) + 100
+    max_shift_y = np.max(data.loc[:,"image_shift_pixel_y"]/crop_by) + 100
     max_image_x = np.max(data.loc[:,"X_SIZE"]/crop_by)
[…]

### 2022-02-25 content/code/refine_initial_match.py

@@ -1,0 +1,21 @@
+import pycistem
+import numpy as np
+from pathlib import Path
+
+
+pycistem.set_cistem_path("/groups/elferich/cisTEM/build/refine_template_tests_Intel-gpu-debug/src/")
+
+pa = pycistem.programs.refine_template.parameters_from_database("/scratch/bern/elferich/ER_HoxB8_96h/ER_HoxB8_96h.db",
+                                                                     186,
+                                                                     template_match_id=4,
+                                                                     wanted_threshold=7.76,
+                                                                     input_reconstruction="/groups/elferich/mammalian_ribosome_structures/6swa_simulate_bfsca1_5.mrc",)
+print(pa)
+res_my = pycistem.programs.refine_template.run([pa],num_procs=1)
+
+
+directory = Path("/scratch/bern/elferich/decolace_manuscript_processing/initial_matching/")
+directory.mkdir(parents=True,exist_ok=True)
+
+pycistem.programs.refine_template.write_starfile(res_my, str(directory / "506_matches.star"))
+ 

### 2022-02-25 manuscript.tex
Merge branch 'main' of github.com:jojoelfe/deco_lace_template_matching_manuscript into main [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/0b9b63ca1f5f1f419cc06d1da01657a14abcec8d.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/0b9b63ca1f5f1f419cc06d1da01657a14abcec8d/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1899812620

@@
 This manuscript
-(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/c726b59baf4d652934928fac32dda6261f8cf435/}{permalink})
+(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/0b9b63ca1f5f1f419cc06d1da01657a14abcec8d/}{permalink})
 was automatically generated
-from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/c726b59baf4d652934928fac32dda6261f8cf435}{jojoelfe/deco\_lace\_template\_matching\_manuscript@c726b59}
+from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/0b9b63ca1f5f1f419cc06d1da01657a14abcec8d}{jojoelfe/deco\_lace\_template\_matching\_manuscript@0b9b63c}
 on February 25, 2022.

### 2022-02-28 manuscript.tex
Merge branch 'main' of https://github.com/jojoelfe/deco_lace_template_matching_manuscript into main [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/31bc357aa966ffec4212bc97259f92b6b7231438.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/31bc357aa966ffec4212bc97259f92b6b7231438/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1913156797

@@
 This manuscript
-(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/0b9b63ca1f5f1f419cc06d1da01657a14abcec8d/}{permalink})
+(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/31bc357aa966ffec4212bc97259f92b6b7231438/}{permalink})
 was automatically generated
-from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/0b9b63ca1f5f1f419cc06d1da01657a14abcec8d}{jojoelfe/deco\_lace\_template\_matching\_manuscript@0b9b63c}
-on February 25, 2022.
+from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/31bc357aa966ffec4212bc97259f92b6b7231438}{jojoelfe/deco\_lace\_template\_matching\_manuscript@31bc357}
+on February 28, 2022.
 
@@
 \includegraphics{figures/initmatching2.pdf}
-\caption{This is an example-figurern}\label{fig:initmatching2}
+\caption{Maximum intensity projection cross-correlation map of micrograph shown in Figure \ref{fig:initmatching}}\label{fig:initmatching2}
 }
@@
 \centering
-\includegraphics{figures/example-figure.pdf}
-\caption{This is an example-figurern}\label{fig:approach}
+\includegraphics{figures/approach.pdf}
+\caption{DeCo-LACE approach (A) Graphic demonstrating the data-collection strategy for DeCo-LACE}\label{fig:approach}
 }
@@
 \begin{figure}
-\hypertarget{fig:approach2}{%
+\hypertarget{fig:deco_lace_workflow}{%
 \centering
-\includegraphics{figures/example-figure2.pdf}
-\caption{This is an example-figurern}\label{fig:approach2}
+\includegraphics{figures/deco_lace_workflow.pdf}
+\caption{Workflow of DeCo-Lace processing}\label{fig:deco_lace_workflow}
+}
+\end{figure}
+
+\begin{figure}
+\hypertarget{fig:lamella_spatial_info}{%
+\centering
+\includegraphics{figures/lamella_spatial_info.pdf}
+\caption{This is an example-figurern}\label{fig:lamella_spatial_info}
 }

### 2022-03-01 content/code/assemble_montage_euc_1.py
better assembly

@@ -1,0 +1,28 @@
+import matplotlib.pyplot as plt
+import latexipy as lp
+import utils
+import numpy as np
+from pathlib import Path
+from skimage.transform import rescale, resize, downscale_local_mean
+from skimage import io
+
+import assemble_montage_utils as assemble_montage_utils 
+import utils
+
+
+load_cached_images = False
+
+
+directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/initial_assembly/")
+directory.mkdir(parents=True,exist_ok=True)
+
+selected_micrographs = utils.get_data_from_db(utils.datasets[0])
+selected_micrographs = selected_micrographs[40:1019]
+
+print(utils.datasets[0])
+print(len(selected_micrographs))
+metadata = assemble_montage_utils.create_metadata(selected_micrographs,
+                                       IS_to_camera=assemble_montage_utils.IS_to_camera,
+                                       output_base=str(directory / 'euc_lamella1'))
+assemble_montage_utils.create_montage(metadata)
+exit()

### 2022-03-01 content/code/assemble_montage_euc_2.py

@@ -1,0 +1,28 @@
+import matplotlib.pyplot as plt
+import latexipy as lp
+import utils
+import numpy as np
+from pathlib import Path
+from skimage.transform import rescale, resize, downscale_local_mean
+from skimage import io
+
+import assemble_montage_utils as assemble_montage_utils 
+import utils
+
+
+load_cached_images = False
+
+
+directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/initial_assembly/")
+directory.mkdir(parents=True,exist_ok=True)
+
+selected_micrographs = utils.get_data_from_db(utils.datasets[1])
+selected_micrographs = selected_micrographs[5:-2]
+
+print(utils.datasets[1])
+print(len(selected_micrographs))
+metadata = assemble_montage_utils.create_metadata(selected_micrographs,
+                                       IS_to_camera=assemble_montage_utils.IS_to_camera,
+                                       output_base=str(directory / 'euc_lamella2'))
+assemble_montage_utils.create_montage(metadata)
+exit()

### 2022-03-01 content/code/assemble_montage_euc_3.py

@@ -1,0 +1,30 @@
+import matplotlib.pyplot as plt
+import latexipy as lp
+import utils
+import numpy as np
+from pathlib import Path
+from skimage.transform import rescale, resize, downscale_local_mean
+from skimage import io
+
+import assemble_montage_utils as assemble_montage_utils 
+import utils
+
+
+load_cached_images = False
+
+
+directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/initial_assembly/")
+directory.mkdir(parents=True,exist_ok=True)
+
+selected_micrographs = utils.get_data_from_db(utils.datasets[2])
+selected_micrographs = selected_micrographs[35:-5]
+
+print(utils.datasets[2])
+print(len(selected_micrographs))
+metadata = assemble_montage_utils.create_metadata(selected_micrographs,
+                                       IS_to_camera=assemble_montage_utils.IS_to_camera,
+                                       output_base=str(directory / 'euc_lamella3'),
+                                       mask_suffix="_1_mask.mrc")
+print(metadata["tiles"][metadata["tiles"]["tile_y_offset"] == np.max(metadata["tiles"]["tile_y_offset"])])
+assemble_montage_utils.create_montage(metadata)
+exit()

### 2022-03-01 content/code/assemble_montage_euc_4.py

@@ -1,0 +1,30 @@
+import matplotlib.pyplot as plt
+import latexipy as lp
+import utils
+import numpy as np
+from pathlib import Path
+from skimage.transform import rescale, resize, downscale_local_mean
+from skimage import io
+
+import assemble_montage_utils as assemble_montage_utils 
+import utils
+
+
+load_cached_images = False
+
+
+directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/initial_assembly/")
+directory.mkdir(parents=True,exist_ok=True)
+
+selected_micrographs = utils.get_data_from_db(utils.datasets[3])
+selected_micrographs = selected_micrographs[5:-5]
+selected_micrographs = selected_micrographs.drop(selected_micrographs.index[118])
+
+print(utils.datasets[3])
+print(len(selected_micrographs))
+metadata = assemble_montage_utils.create_metadata(selected_micrographs,
+                                       IS_to_camera=assemble_montage_utils.IS_to_camera,
+                                       output_base=str(directory / 'euc_lamella4'),
+                                       mask_suffix="_1_mask.mrc")
+assemble_montage_utils.create_montage(metadata)
+exit()

### 2022-03-01 content/code/assemble_montage_utils.py

@@ -1,0 +1,187 @@
+from curses import meta
+import matplotlib.pyplot as plt
+import latexipy as lp
+import numpy as np
+import mrcfile
+from pathlib import Path
+from skimage.transform import resize
+from skimage import io
+import pandas as pd
+import starfile
+from skimage.util import img_as_uint
+
+IS_to_camera = np.array([13374,  6053.4,  6394.1,  -13172])
+IS_to_camera.shape = (2,2)
+
+
+
+def create_metadata(expand_data, IS_to_camera, output_base, binning=10, image_suffix="_0.mrc", mask_suffix ="_0_mask.mrc"):
+    
+    result_montage = pd.DataFrame({
+        'montage_filename': pd.Series(dtype='string'),
+        'matches_montage_filename': pd.Series(dtype='string'),
+        'montage_pixel_size': pd.Series(dtype='float'),
+        'montage_binning': pd.Series(dtype='float'),
+        'montage_x_size': pd.Series(dtype='int'),
+        'montage_y_size': pd.Series(dtype='int'),
+    })
+
+    result_tiles = pd.DataFrame({
+        'tile_filename': pd.Series(dtype='object'),
+        'tile_x_offset': pd.Series(dtype='int'),
+        'tile_y_offset': pd.Series(dtype='int'),
+        'tile_pixel_size': pd.Series(dtype='float'),
+        'tile_x_size': pd.Series(dtype='int'),
+        'tile_y_size': pd.Series(dtype='int'),
+        'tile_orig_x_size': pd.Series(dtype='int'),
+        'tile_orig_y_size': pd.Series(dtype='int'),
+        'tile_x_crop_center': pd.Series(dtype='int'),
+        'tile_y_crop_center': pd.Series(dtype='int'),
+        'tile_mask_filename': pd.Series(dtype='object'),
+        'tile_plotted_result_filename': pd.Series(dtype='object'),
+        'tile_image_shift_x': pd.Series(dtype='float'),
+        'tile_image_shift_y': pd.Series(dtype='float'),
+    })
+
+
+    for i, item in expand_data.iterrows():
+
+        # Initially convert image shift to unbinned pixels
+        image_shift = np.array([item["IMAGE_SHIFT_X"],item["IMAGE_SHIFT_Y"]])
+        shift_in_camera_pixels = np.dot(IS_to_camera,image_shift)
+        shift_in_image_pixel = (shift_in_camera_pixels / (item["image_pixel_size"]/(item["movie_pixel_size"])))
[…]

### 2022-03-01 content/code/plot_acquisition_positions_g1_l1.py

@@ -1,57 +1,0 @@
-import matplotlib.pyplot as plt
-import latexipy as lp
-import utils
-import numpy as np
-import napari
-import mrcfile
-from pathlib import Path
-from skimage.transform import rescale, resize, downscale_local_mean
-from skimage import io
-
-import plot_acquisition_utils 
-import utils
-
-
-load_cached_images = False
-
-
-selected_micrographs = utils.get_data_from_db(utils.datasets[0])
-selected_micrographs = selected_micrographs[40:1020]
-print(utils.datasets[0])
-print(len(selected_micrographs))
-plot_acquisition_utils.initial_assembly(selected_micrographs,IS_to_camera=plot_acquisition_utils.IS_to_camera)
-
-
-
-directory = Path("/scratch/bern/elferich/decolace_manuscript_processing/initial_assembly/")
-directory.mkdir(parents=True,exist_ok=True)
-
-image_cache_filename = directory / 'euc_lamella1_cache.npz'
-if load_cached_images:
-    load = np.load(image_cache_filename)
-    assemb = load["image"]
-    mask = load["mask"]
-    matches = load["matches"]
-else:
-    (assemb, mask, matches) = plot_acquisition_utils.plot_montage(selected_micrographs,[i for i in range(2,1010)])
-    np.savez_compressed(image_cache_filename,matches=matches,mask=mask,image=assemb)
-    corr = assemb/mask
-    io.imsave(directory / 'euc_lamella1_image.tif',corr/np.max(corr),plugin='pil')
-
-
-exit()
-centers = [get_corners(m['IMAGE_SHIFT_X']*150,m['IMAGE_SHIFT_Y']*150,36) for i,m in selected_micrographs.iterrows()]
-#assemb=np.zeros((100,100))
-scale = 0.15 * crop_by
-viewer = napari.view_image(assemb/mask,contrast_limits=(0,10),interpolation='bilinear',scale=(scale,scale))
-viewer.add_image(mask,contrast_limits=(0,10),interpolation='bilinear',scale=(scale,scale))
-viewer.add_image(matches,contrast_limits=(0,100000),interpolation='bilinear',blending='additive',colormap='red' ,scale=(scale,scale))
-
-radius = 250
[…]

### 2022-03-01 content/code/plot_acquisition_utils.py

@@ -1,105 +1,0 @@
-import matplotlib.pyplot as plt
-import latexipy as lp
-import utils
-import numpy as np
-import napari
-import mrcfile
-from pathlib import Path
-from skimage.transform import rescale, resize, downscale_local_mean
-from skimage import io
-
-IS_to_camera = np.array([13374,  6053.4,  6394.1,  -13172])
-IS_to_camera.shape = (2,2)
-
-
-crop_by = 10
-
-def get_scaled_filename(filename):
-    p = Path(filename)
-    return p.parent.joinpath("Scaled").joinpath(p.name)
-
-def initial_assembly(expand_data, IS_to_camera):
-    for item in expand_data.iterrows():
-        image_shift = np.array([item[1]["IMAGE_SHIFT_X"],item[1]["IMAGE_SHIFT_Y"]])
-        shift_in_camera_pixels = np.dot(IS_to_camera,image_shift)
-        largest_size = np.max([item[1]["X_SIZE"],item[1]["Y_SIZE"]])
-        shift_in_image_pixel = (shift_in_camera_pixels / (item[1]["image_pixel_size"]/(item[1]["movie_pixel_size"])))
-        expand_data.loc[item[0],"image_shift_pixel_x"] = shift_in_image_pixel[0]
-        expand_data.loc[item[0],"image_shift_pixel_y"] = shift_in_image_pixel[1]
-
-def get_corners(x,y,radius):
-    return [[x+radius,y+radius],[x-radius,y+radius],[x-radius,y-radius],[x+radius,y-radius]]
-
-def get_range(data):
-    min_shift_x = np.min(data.loc[:,"image_shift_pixel_x"]) - 100 * crop_by
-    min_shift_y = np.min(data.loc[:,"image_shift_pixel_y"]) - 100 * crop_by
-    max_shift_x = np.max(data.loc[:,"image_shift_pixel_x"]/crop_by) + 100
-    max_shift_y = np.max(data.loc[:,"image_shift_pixel_y"]/crop_by) + 100
-    max_image_x = np.max(data.loc[:,"X_SIZE"]/crop_by)
-    max_image_y = np.max(data.loc[:,"Y_SIZE"]/crop_by)
-    return (min_shift_x,min_shift_y)
-
-def plot_montage(data,to_show):
-    min_shift_x = np.min(data.loc[:,"image_shift_pixel_x"]/crop_by) - 100
-    min_shift_y = np.min(data.loc[:,"image_shift_pixel_y"]/crop_by) - 100
[…]

### 2022-03-01 manuscript.tex
better assembly [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/faafadc025e8ca90737699af9c8f5d76cfeef9a3.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/faafadc025e8ca90737699af9c8f5d76cfeef9a3/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1913640880

@@
 This manuscript
-(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/31bc357aa966ffec4212bc97259f92b6b7231438/}{permalink})
+(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/faafadc025e8ca90737699af9c8f5d76cfeef9a3/}{permalink})
 was automatically generated
-from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/31bc357aa966ffec4212bc97259f92b6b7231438}{jojoelfe/deco\_lace\_template\_matching\_manuscript@31bc357}
-on February 28, 2022.
+from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/faafadc025e8ca90737699af9c8f5d76cfeef9a3}{jojoelfe/deco\_lace\_template\_matching\_manuscript@faafadc}
+on March 1, 2022.
 

### 2022-03-02 content/code/assemble_matches.py
Refine macthes + assemble

@@ -1,0 +1,30 @@
+import starfile
+import utils
+from pathlib import Path
+
+
+montage_directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/initial_assembly/")
+refine_directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/lamella_refine/")
+assembled_directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/assemble/")
+assembled_directory.mkdir(exist_ok=True,parents=True)
+for (database, name) in utils.dataset_info[4:5]:
+    print(name)
+    montage_info = starfile.read(montage_directory / f"{name}.star")
+    refine_info = starfile.read(refine_directory / f"{name}_refine.star")
+    print(len(refine_info.index))
+    # Make sure both sides use image 0
+    montage_info["tiles"]["tile_filename"] = montage_info["tiles"]["tile_filename"].apply(lambda x: x.replace("_1.mrc","_0.mrc"))
+    refine_info["image_filename"] = refine_info["image_filename"].apply(lambda x: x.replace("_1.mrc","_0.mrc"))
+
+    # Join the two dataframes
+    info = montage_info["tiles"].merge(refine_info, how="right", left_on="tile_filename", right_on="image_filename")
+    #print(info.loc[0])
+    info["tile_x"] = info["x"]
+    info["tile_y"] = info["y"]
+    info["x"] = info["tile_x"] + info["tile_x_offset"]
+    info["y"] = info["tile_y"] - info["tile_y_offset"]
+    info["image_filename"] = montage_info["montage"]["montage_filename"].loc[0]
+    print(info["template_filename"].unique())
+    print(info["image_filename"].unique())
+    # Write the new starfile
+    starfile.write(info, assembled_directory / f"{name}_assembled_matches.star",overwrite=True)

### 2022-03-02 content/code/assemble_montage_euc_1.py

@@ -24,5 +24,5 @@ print(len(selected_micrographs))
 metadata = assemble_montage_utils.create_metadata(selected_micrographs,
                                        IS_to_camera=assemble_montage_utils.IS_to_camera,
                                        output_base=str(directory / 'euc_lamella1'))
-assemble_montage_utils.create_montage(metadata)
+#assemble_montage_utils.create_montage(metadata)
 exit()

### 2022-03-02 content/code/assemble_montage_euc_2.py

@@ -24,5 +24,5 @@ print(len(selected_micrographs))
 metadata = assemble_montage_utils.create_metadata(selected_micrographs,
                                        IS_to_camera=assemble_montage_utils.IS_to_camera,
                                        output_base=str(directory / 'euc_lamella2'))
-assemble_montage_utils.create_montage(metadata)
+#assemble_montage_utils.create_montage(metadata)
 exit()

### 2022-03-02 content/code/assemble_montage_euc_4.py

@@ -26,5 +26,5 @@ metadata = assemble_montage_utils.create_metadata(selected_micrographs,
                                        IS_to_camera=assemble_montage_utils.IS_to_camera,
                                        output_base=str(directory / 'euc_lamella4'),
                                        mask_suffix="_1_mask.mrc")
-assemble_montage_utils.create_montage(metadata)
+#assemble_montage_utils.create_montage(metadata)
 exit()

### 2022-03-02 content/code/assemble_montage_fff_1.py

@@ -16,14 +16,16 @@ load_cached_images = False
 directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/initial_assembly/")
 directory.mkdir(parents=True,exist_ok=True)
 
-selected_micrographs = utils.get_data_from_db(utils.datasets[2])
-selected_micrographs = selected_micrographs[35:-5]
+selected_micrographs = utils.get_data_from_db(utils.datasets[4])
+selected_micrographs = selected_micrographs[5:]
+selected_micrographs = selected_micrographs.drop(selected_micrographs.index[131])
 
-print(utils.datasets[2])
+
+print(utils.datasets[4])
 print(len(selected_micrographs))
 metadata = assemble_montage_utils.create_metadata(selected_micrographs,
                                        IS_to_camera=assemble_montage_utils.IS_to_camera,
-                                       output_base=str(directory / 'euc_lamella3'),
+                                       output_base=str(directory / 'fff_lamella1'),
                                        mask_suffix="_1_mask.mrc")
 #assemble_montage_utils.create_montage(metadata)
 exit()

### 2022-03-02 content/code/assemble_montage_fff_2.py

@@ -16,14 +16,14 @@ load_cached_images = False
 directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/initial_assembly/")
 directory.mkdir(parents=True,exist_ok=True)
 
-selected_micrographs = utils.get_data_from_db(utils.datasets[2])
-selected_micrographs = selected_micrographs[35:-5]
+selected_micrographs = utils.get_data_from_db(utils.datasets[5])
+selected_micrographs = selected_micrographs[5:]
 
-print(utils.datasets[2])
+print(utils.datasets[5])
 print(len(selected_micrographs))
 metadata = assemble_montage_utils.create_metadata(selected_micrographs,
                                        IS_to_camera=assemble_montage_utils.IS_to_camera,
-                                       output_base=str(directory / 'euc_lamella3'),
+                                       output_base=str(directory / 'fff_lamella2'),
                                        mask_suffix="_1_mask.mrc")
 #assemble_montage_utils.create_montage(metadata)
 exit()

### 2022-03-02 content/code/assemble_montage_fff_3.py

@@ -16,14 +16,14 @@ load_cached_images = False
 directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/initial_assembly/")
 directory.mkdir(parents=True,exist_ok=True)
 
-selected_micrographs = utils.get_data_from_db(utils.datasets[2])
-selected_micrographs = selected_micrographs[35:-5]
+selected_micrographs = utils.get_data_from_db(utils.datasets[6])
+selected_micrographs = selected_micrographs[5:-5]
 
-print(utils.datasets[2])
+print(utils.datasets[6])
 print(len(selected_micrographs))
 metadata = assemble_montage_utils.create_metadata(selected_micrographs,
                                        IS_to_camera=assemble_montage_utils.IS_to_camera,
-                                       output_base=str(directory / 'euc_lamella3'),
+                                       output_base=str(directory / 'fff_lamella3'),
                                        mask_suffix="_1_mask.mrc")
 #assemble_montage_utils.create_montage(metadata)
 exit()

### 2022-03-02 content/code/assemble_montage_fff_4.py

@@ -16,14 +16,15 @@ load_cached_images = False
 directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/initial_assembly/")
 directory.mkdir(parents=True,exist_ok=True)
 
-selected_micrographs = utils.get_data_from_db(utils.datasets[2])
-selected_micrographs = selected_micrographs[35:-5]
+selected_micrographs = utils.get_data_from_db(utils.datasets[7])
+selected_micrographs = selected_micrographs[5:-5]
+#selected_micrographs = selected_micrographs.drop(selected_micrographs.index[118])
 
-print(utils.datasets[2])
+print(utils.datasets[7])
 print(len(selected_micrographs))
 metadata = assemble_montage_utils.create_metadata(selected_micrographs,
                                        IS_to_camera=assemble_montage_utils.IS_to_camera,
-                                       output_base=str(directory / 'euc_lamella3'),
+                                       output_base=str(directory / 'fff_lamella4'),
                                        mask_suffix="_1_mask.mrc")
 #assemble_montage_utils.create_montage(metadata)
 exit()

### 2022-03-02 content/code/assemble_montage_utils.py

@@ -101,9 +101,9 @@ def create_metadata(expand_data, IS_to_camera, output_base, binning=10, image_su
         matches_filenames = list(matches_dir.glob(Path(item['FILENAME'][:-6]).name +"*plotted_result*.mrc"))
         #print(matches_filenames)
         if len(matches_filenames) > 0:
-            new_entry['tile_plotted_result_filename'] = matches_filenames[0]
+            new_entry['tile_plotted_result_filename'] = str(matches_filenames[0])
         else:
-            new_entry['tile_plotted_result_filename'] = ""
+            new_entry['tile_plotted_result_filename'] = "None"
         # Calulate the offset
         insert_point_x = item["image_shift_pixel_x"] 
         insert_point_y = item["image_shift_pixel_y"]

### 2022-03-02 content/code/plot_acquisition_positions.py

@@ -1,130 +1,0 @@
-import matplotlib.pyplot as plt
-import latexipy as lp
-import utils
-import numpy as np
-import napari
-import mrcfile
-from pathlib import Path
-from skimage.transform import rescale, resize, downscale_local_mean
-
-IS_to_camera = np.array([13374,  6053.4,  6394.1,  -13172])
-IS_to_camera.shape = (2,2)
-
-#orig_x_size = 5120
-scaled_x_size = 1200.0
-
-load_cached_images = True
-
-def get_scaled_filename(filename):
-    p = Path(filename)
-    return p.parent.joinpath("Scaled").joinpath(p.name)
-
-def initial_assembly(expand_data, IS_to_camera):
-    for item in expand_data.iterrows():
-        image_shift = np.array([item[1]["IMAGE_SHIFT_X"],item[1]["IMAGE_SHIFT_Y"]])
-        shift_in_camera_pixels = np.dot(IS_to_camera,image_shift)
-        largest_size = np.max([item[1]["X_SIZE"],item[1]["Y_SIZE"]])
-        shift_in_image_pixel = (shift_in_camera_pixels / (item[1]["image_pixel_size"]/(item[1]["movie_pixel_size"])))
-        expand_data.loc[item[0],"image_shift_pixel_x"] = shift_in_image_pixel[0]
-        expand_data.loc[item[0],"image_shift_pixel_y"] = shift_in_image_pixel[1]
-
-def get_corners(x,y,radius):
-    return [[x+radius,y+radius],[x-radius,y+radius],[x-radius,y-radius],[x+radius,y-radius]]
-
-def get_range(data):
-    min_shift_x = np.min(data.loc[:,"image_shift_pixel_x"]) - 4000
-    min_shift_y = np.min(data.loc[:,"image_shift_pixel_y"]) - 4000
-    max_shift_x = np.max(data.loc[:,"image_shift_pixel_x"]/4) + 1000
-    max_shift_y = np.max(data.loc[:,"image_shift_pixel_y"]/4) + 1000
-    max_image_x = np.max(data.loc[:,"X_SIZE"]/4)
-    max_image_y = np.max(data.loc[:,"Y_SIZE"]/4)
-    return (min_shift_x,min_shift_y)
-
-def plot_montage(data,to_show):
-    min_shift_x = np.min(data.loc[:,"image_shift_pixel_x"]/4) - 1000
-    min_shift_y = np.min(data.loc[:,"image_shift_pixel_y"]/4) - 1000
[…]

### 2022-03-02 content/code/plot_acquisition_positions_g1_l2.py

@@ -1,147 +1,0 @@
-import matplotlib.pyplot as plt
-import latexipy as lp
-import utils
-import numpy as np
-import napari
-import mrcfile
-from pathlib import Path
-from skimage.transform import rescale, resize, downscale_local_mean
-from skimage import io
-
-IS_to_camera = np.array([13374,  6053.4,  6394.1,  -13172])
-IS_to_camera.shape = (2,2)
-
-#orig_x_size = 5120
-scaled_x_size = 1200.0
-
-load_cached_images = False
-
-crop_by = 10
-
-def get_scaled_filename(filename):
-    p = Path(filename)
-    return p.parent.joinpath("Scaled").joinpath(p.name)
-
-def initial_assembly(expand_data, IS_to_camera):
-    for item in expand_data.iterrows():
-        image_shift = np.array([item[1]["IMAGE_SHIFT_X"],item[1]["IMAGE_SHIFT_Y"]])
-        shift_in_camera_pixels = np.dot(IS_to_camera,image_shift)
-        largest_size = np.max([item[1]["X_SIZE"],item[1]["Y_SIZE"]])
-        shift_in_image_pixel = (shift_in_camera_pixels / (item[1]["image_pixel_size"]/(item[1]["movie_pixel_size"])))
-        expand_data.loc[item[0],"image_shift_pixel_x"] = shift_in_image_pixel[0]
-        expand_data.loc[item[0],"image_shift_pixel_y"] = shift_in_image_pixel[1]
-
-def get_corners(x,y,radius):
-    return [[x+radius,y+radius],[x-radius,y+radius],[x-radius,y-radius],[x+radius,y-radius]]
-
-def get_range(data):
-    min_shift_x = np.min(data.loc[:,"image_shift_pixel_x"]) - 200 * crop_by
-    min_shift_y = np.min(data.loc[:,"image_shift_pixel_y"]) - 200 * crop_by
-    max_shift_x = np.max(data.loc[:,"image_shift_pixel_x"]/crop_by) + 100
-    max_shift_y = np.max(data.loc[:,"image_shift_pixel_y"]/crop_by) + 100
-    max_image_x = np.max(data.loc[:,"X_SIZE"]/crop_by)
-    max_image_y = np.max(data.loc[:,"Y_SIZE"]/crop_by)
-    return (min_shift_x,min_shift_y)
-
-def plot_montage(data,to_show):
-    min_shift_x = np.min(data.loc[:,"image_shift_pixel_x"]/crop_by) - 200
[…]

### 2022-03-02 content/code/plot_acquisition_positions_g1_l3.py

@@ -1,147 +1,0 @@
-import matplotlib.pyplot as plt
-import latexipy as lp
-import utils
-import numpy as np
-import napari
-import mrcfile
-from pathlib import Path
-from skimage.transform import rescale, resize, downscale_local_mean
-from skimage import io
-
-IS_to_camera = np.array([13374,  6053.4,  6394.1,  -13172])
-IS_to_camera.shape = (2,2)
-
-#orig_x_size = 5120
-scaled_x_size = 1200.0
-
-load_cached_images = False
-
-crop_by = 10
-
-def get_scaled_filename(filename):
-    p = Path(filename)
-    return p.parent.joinpath("Scaled").joinpath(p.name)
-
-def initial_assembly(expand_data, IS_to_camera):
-    for item in expand_data.iterrows():
-        image_shift = np.array([item[1]["IMAGE_SHIFT_X"],item[1]["IMAGE_SHIFT_Y"]])
-        shift_in_camera_pixels = np.dot(IS_to_camera,image_shift)
-        largest_size = np.max([item[1]["X_SIZE"],item[1]["Y_SIZE"]])
-        shift_in_image_pixel = (shift_in_camera_pixels / (item[1]["image_pixel_size"]/(item[1]["movie_pixel_size"])))
-        expand_data.loc[item[0],"image_shift_pixel_x"] = shift_in_image_pixel[0]
-        expand_data.loc[item[0],"image_shift_pixel_y"] = shift_in_image_pixel[1]
-
-def get_corners(x,y,radius):
-    return [[x+radius,y+radius],[x-radius,y+radius],[x-radius,y-radius],[x+radius,y-radius]]
-
-def get_range(data):
-    min_shift_x = np.min(data.loc[:,"image_shift_pixel_x"]) - 200 * crop_by
-    min_shift_y = np.min(data.loc[:,"image_shift_pixel_y"]) - 200 * crop_by
-    max_shift_x = np.max(data.loc[:,"image_shift_pixel_x"]/crop_by) + 100
-    max_shift_y = np.max(data.loc[:,"image_shift_pixel_y"]/crop_by) + 100
-    max_image_x = np.max(data.loc[:,"X_SIZE"]/crop_by)
-    max_image_y = np.max(data.loc[:,"Y_SIZE"]/crop_by)
-    return (min_shift_x,min_shift_y)
-
-def plot_montage(data,to_show):
-    min_shift_x = np.min(data.loc[:,"image_shift_pixel_x"]/crop_by) - 200
[…]

### 2022-03-02 content/code/plot_acquisition_positions_g1_l3_old.py

@@ -1,131 +1,0 @@
-import matplotlib.pyplot as plt
-import latexipy as lp
-import utils
-import numpy as np
-import napari
-import mrcfile
-from pathlib import Path
-from skimage.transform import rescale, resize, downscale_local_mean
-
-IS_to_camera = np.array([13374,  6053.4,  6394.1,  -13172])
-IS_to_camera.shape = (2,2)
-
-#orig_x_size = 5120
-scaled_x_size = 1200.0
-
-load_cached_images = False
-
-def get_scaled_filename(filename):
-    p = Path(filename)
-    return p.parent.joinpath("Scaled").joinpath(p.name)
-
-def initial_assembly(expand_data, IS_to_camera):
-    for item in expand_data.iterrows():
-        image_shift = np.array([item[1]["IMAGE_SHIFT_X"],item[1]["IMAGE_SHIFT_Y"]])
-        shift_in_camera_pixels = np.dot(IS_to_camera,image_shift)
-        largest_size = np.max([item[1]["X_SIZE"],item[1]["Y_SIZE"]])
-        shift_in_image_pixel = (shift_in_camera_pixels / (item[1]["image_pixel_size"]/(item[1]["movie_pixel_size"])))
-        expand_data.loc[item[0],"image_shift_pixel_x"] = shift_in_image_pixel[0]
-        expand_data.loc[item[0],"image_shift_pixel_y"] = shift_in_image_pixel[1]
-
-def get_corners(x,y,radius):
-    return [[x+radius,y+radius],[x-radius,y+radius],[x-radius,y-radius],[x+radius,y-radius]]
-
-def get_range(data):
-    min_shift_x = np.min(data.loc[:,"image_shift_pixel_x"]) - 4000
-    min_shift_y = np.min(data.loc[:,"image_shift_pixel_y"]) - 4000
-    max_shift_x = np.max(data.loc[:,"image_shift_pixel_x"]/4) + 1000
-    max_shift_y = np.max(data.loc[:,"image_shift_pixel_y"]/4) + 1000
-    max_image_x = np.max(data.loc[:,"X_SIZE"]/4)
-    max_image_y = np.max(data.loc[:,"Y_SIZE"]/4)
-    return (min_shift_x,min_shift_y)
-
-def plot_montage(data,to_show):
-    min_shift_x = np.min(data.loc[:,"image_shift_pixel_x"]/4) - 1000
-    min_shift_y = np.min(data.loc[:,"image_shift_pixel_y"]/4) - 1000
[…]

### 2022-03-02 content/code/plot_acquisition_positions_g1_l4.py

@@ -1,147 +1,0 @@
-import matplotlib.pyplot as plt
-import latexipy as lp
-import utils
-import numpy as np
-import napari
-import mrcfile
-from pathlib import Path
-from skimage.transform import rescale, resize, downscale_local_mean
-from skimage import io
-
-IS_to_camera = np.array([13374,  6053.4,  6394.1,  -13172])
-IS_to_camera.shape = (2,2)
-
-#orig_x_size = 5120
-scaled_x_size = 1200.0
-
-load_cached_images = False
-
-crop_by = 10
-
-def get_scaled_filename(filename):
-    p = Path(filename)
-    return p.parent.joinpath("Scaled").joinpath(p.name)
-
-def initial_assembly(expand_data, IS_to_camera):
-    for item in expand_data.iterrows():
-        image_shift = np.array([item[1]["IMAGE_SHIFT_X"],item[1]["IMAGE_SHIFT_Y"]])
-        shift_in_camera_pixels = np.dot(IS_to_camera,image_shift)
-        largest_size = np.max([item[1]["X_SIZE"],item[1]["Y_SIZE"]])
-        shift_in_image_pixel = (shift_in_camera_pixels / (item[1]["image_pixel_size"]/(item[1]["movie_pixel_size"])))
-        expand_data.loc[item[0],"image_shift_pixel_x"] = shift_in_image_pixel[0]
-        expand_data.loc[item[0],"image_shift_pixel_y"] = shift_in_image_pixel[1]
-
-def get_corners(x,y,radius):
-    return [[x+radius,y+radius],[x-radius,y+radius],[x-radius,y-radius],[x+radius,y-radius]]
-
-def get_range(data):
-    min_shift_x = np.min(data.loc[:,"image_shift_pixel_x"]) - 200 * crop_by
-    min_shift_y = np.min(data.loc[:,"image_shift_pixel_y"]) - 200 * crop_by
-    max_shift_x = np.max(data.loc[:,"image_shift_pixel_x"]/crop_by) + 100
-    max_shift_y = np.max(data.loc[:,"image_shift_pixel_y"]/crop_by) + 100
-    max_image_x = np.max(data.loc[:,"X_SIZE"]/crop_by)
-    max_image_y = np.max(data.loc[:,"Y_SIZE"]/crop_by)
-    return (min_shift_x,min_shift_y)
-
-def plot_montage(data,to_show):
-    min_shift_x = np.min(data.loc[:,"image_shift_pixel_x"]/crop_by) - 200
[…]

### 2022-03-02 content/code/plot_acquisition_positions_g2_l1.py

@@ -1,142 +1,0 @@
-import matplotlib.pyplot as plt
-import latexipy as lp
-import utils
-import numpy as np
-import napari
-import mrcfile
-from pathlib import Path
-from skimage.transform import rescale, resize, downscale_local_mean
-from skimage import io
-
-IS_to_camera = np.array([13374,  6053.4,  6394.1,  -13172])
-IS_to_camera.shape = (2,2)
-
-#orig_x_size = 5120
-scaled_x_size = 1200.0
-
-load_cached_images = False
-
-crop_by = 10
-
-def get_scaled_filename(filename):
-    p = Path(filename)
-    return p.parent.joinpath("Scaled").joinpath(p.name)
-
-def initial_assembly(expand_data, IS_to_camera):
-    for item in expand_data.iterrows():
-        image_shift = np.array([item[1]["IMAGE_SHIFT_X"],item[1]["IMAGE_SHIFT_Y"]])
-        shift_in_camera_pixels = np.dot(IS_to_camera,image_shift)
-        largest_size = np.max([item[1]["X_SIZE"],item[1]["Y_SIZE"]])
-        shift_in_image_pixel = (shift_in_camera_pixels / (item[1]["image_pixel_size"]/(item[1]["movie_pixel_size"])))
-        expand_data.loc[item[0],"image_shift_pixel_x"] = shift_in_image_pixel[0]
-        expand_data.loc[item[0],"image_shift_pixel_y"] = shift_in_image_pixel[1]
-
-def get_corners(x,y,radius):
-    return [[x+radius,y+radius],[x-radius,y+radius],[x-radius,y-radius],[x+radius,y-radius]]
-
-def get_range(data):
-    min_shift_x = np.min(data.loc[:,"image_shift_pixel_x"]) - 100 * crop_by
-    min_shift_y = np.min(data.loc[:,"image_shift_pixel_y"]) - 100 * crop_by
-    max_shift_x = np.max(data.loc[:,"image_shift_pixel_x"]/crop_by) + 100
-    max_shift_y = np.max(data.loc[:,"image_shift_pixel_y"]/crop_by) + 100
-    max_image_x = np.max(data.loc[:,"X_SIZE"]/crop_by)
-    max_image_y = np.max(data.loc[:,"Y_SIZE"]/crop_by)
-    return (min_shift_x,min_shift_y)
-
-def plot_montage(data,to_show):
-    min_shift_x = np.min(data.loc[:,"image_shift_pixel_x"]/crop_by) - 100
[…]

### 2022-03-02 content/code/plot_acquisition_positions_g2_l2.py

@@ -1,147 +1,0 @@
-import matplotlib.pyplot as plt
-import latexipy as lp
-import utils
-import numpy as np
-import napari
-import mrcfile
-from pathlib import Path
-from skimage.transform import rescale, resize, downscale_local_mean
-from skimage import io
-
-IS_to_camera = np.array([13374,  6053.4,  6394.1,  -13172])
-IS_to_camera.shape = (2,2)
-
-#orig_x_size = 5120
-scaled_x_size = 1200.0
-
-load_cached_images = False
-
-crop_by = 10
-
-def get_scaled_filename(filename):
-    p = Path(filename)
-    return p.parent.joinpath("Scaled").joinpath(p.name)
-
-def initial_assembly(expand_data, IS_to_camera):
-    for item in expand_data.iterrows():
-        image_shift = np.array([item[1]["IMAGE_SHIFT_X"],item[1]["IMAGE_SHIFT_Y"]])
-        shift_in_camera_pixels = np.dot(IS_to_camera,image_shift)
-        largest_size = np.max([item[1]["X_SIZE"],item[1]["Y_SIZE"]])
-        shift_in_image_pixel = (shift_in_camera_pixels / (item[1]["image_pixel_size"]/(item[1]["movie_pixel_size"])))
-        expand_data.loc[item[0],"image_shift_pixel_x"] = shift_in_image_pixel[0]
-        expand_data.loc[item[0],"image_shift_pixel_y"] = shift_in_image_pixel[1]
-
-def get_corners(x,y,radius):
-    return [[x+radius,y+radius],[x-radius,y+radius],[x-radius,y-radius],[x+radius,y-radius]]
-
-def get_range(data):
-    min_shift_x = np.min(data.loc[:,"image_shift_pixel_x"]) - 200 * crop_by
-    min_shift_y = np.min(data.loc[:,"image_shift_pixel_y"]) - 200 * crop_by
-    max_shift_x = np.max(data.loc[:,"image_shift_pixel_x"]/crop_by) + 100
-    max_shift_y = np.max(data.loc[:,"image_shift_pixel_y"]/crop_by) + 100
-    max_image_x = np.max(data.loc[:,"X_SIZE"]/crop_by)
-    max_image_y = np.max(data.loc[:,"Y_SIZE"]/crop_by)
-    return (min_shift_x,min_shift_y)
-
-def plot_montage(data,to_show):
-    min_shift_x = np.min(data.loc[:,"image_shift_pixel_x"]/crop_by) - 200
[…]

### 2022-03-02 content/code/plot_acquisition_positions_g2_l3.py

@@ -1,147 +1,0 @@
-import matplotlib.pyplot as plt
-import latexipy as lp
-import utils
-import numpy as np
-import napari
-import mrcfile
-from pathlib import Path
-from skimage.transform import rescale, resize, downscale_local_mean
-from skimage import io
-
-IS_to_camera = np.array([13374,  6053.4,  6394.1,  -13172])
-IS_to_camera.shape = (2,2)
-
-#orig_x_size = 5120
-scaled_x_size = 1200.0
-
-load_cached_images = False
-
-crop_by = 10
-
-def get_scaled_filename(filename):
-    p = Path(filename)
-    return p.parent.joinpath("Scaled").joinpath(p.name)
-
-def initial_assembly(expand_data, IS_to_camera):
-    for item in expand_data.iterrows():
-        image_shift = np.array([item[1]["IMAGE_SHIFT_X"],item[1]["IMAGE_SHIFT_Y"]])
-        shift_in_camera_pixels = np.dot(IS_to_camera,image_shift)
-        largest_size = np.max([item[1]["X_SIZE"],item[1]["Y_SIZE"]])
-        shift_in_image_pixel = (shift_in_camera_pixels / (item[1]["image_pixel_size"]/(item[1]["movie_pixel_size"])))
-        expand_data.loc[item[0],"image_shift_pixel_x"] = shift_in_image_pixel[0]
-        expand_data.loc[item[0],"image_shift_pixel_y"] = shift_in_image_pixel[1]
-
-def get_corners(x,y,radius):
-    return [[x+radius,y+radius],[x-radius,y+radius],[x-radius,y-radius],[x+radius,y-radius]]
-
-def get_range(data):
-    min_shift_x = np.min(data.loc[:,"image_shift_pixel_x"]) - 200 * crop_by
-    min_shift_y = np.min(data.loc[:,"image_shift_pixel_y"]) - 200 * crop_by
-    max_shift_x = np.max(data.loc[:,"image_shift_pixel_x"]/crop_by) + 100
-    max_shift_y = np.max(data.loc[:,"image_shift_pixel_y"]/crop_by) + 100
-    max_image_x = np.max(data.loc[:,"X_SIZE"]/crop_by)
-    max_image_y = np.max(data.loc[:,"Y_SIZE"]/crop_by)
-    return (min_shift_x,min_shift_y)
-
-def plot_montage(data,to_show):
-    min_shift_x = np.min(data.loc[:,"image_shift_pixel_x"]/crop_by) - 200
[…]

### 2022-03-02 content/code/plot_acquisition_positions_g2_l4.py

@@ -1,147 +1,0 @@
-import matplotlib.pyplot as plt
-import latexipy as lp
-import utils
-import numpy as np
-import napari
-import mrcfile
-from pathlib import Path
-from skimage.transform import rescale, resize, downscale_local_mean
-from skimage import io
-
-IS_to_camera = np.array([13374,  6053.4,  6394.1,  -13172])
-IS_to_camera.shape = (2,2)
-
-#orig_x_size = 5120
-scaled_x_size = 1200.0
-
-load_cached_images = False
-
-crop_by = 10
-
-def get_scaled_filename(filename):
-    p = Path(filename)
-    return p.parent.joinpath("Scaled").joinpath(p.name)
-
-def initial_assembly(expand_data, IS_to_camera):
-    for item in expand_data.iterrows():
-        image_shift = np.array([item[1]["IMAGE_SHIFT_X"],item[1]["IMAGE_SHIFT_Y"]])
-        shift_in_camera_pixels = np.dot(IS_to_camera,image_shift)
-        largest_size = np.max([item[1]["X_SIZE"],item[1]["Y_SIZE"]])
-        shift_in_image_pixel = (shift_in_camera_pixels / (item[1]["image_pixel_size"]/(item[1]["movie_pixel_size"])))
-        expand_data.loc[item[0],"image_shift_pixel_x"] = shift_in_image_pixel[0]
-        expand_data.loc[item[0],"image_shift_pixel_y"] = shift_in_image_pixel[1]
-
-def get_corners(x,y,radius):
-    return [[x+radius,y+radius],[x-radius,y+radius],[x-radius,y-radius],[x+radius,y-radius]]
-
-def get_range(data):
-    min_shift_x = np.min(data.loc[:,"image_shift_pixel_x"]) - 200 * crop_by
-    min_shift_y = np.min(data.loc[:,"image_shift_pixel_y"]) - 200 * crop_by
-    max_shift_x = np.max(data.loc[:,"image_shift_pixel_x"]/crop_by) + 100
-    max_shift_y = np.max(data.loc[:,"image_shift_pixel_y"]/crop_by) + 100
-    max_image_x = np.max(data.loc[:,"X_SIZE"]/crop_by)
-    max_image_y = np.max(data.loc[:,"Y_SIZE"]/crop_by)
-    return (min_shift_x,min_shift_y)
-
-def plot_montage(data,to_show):
-    min_shift_x = np.min(data.loc[:,"image_shift_pixel_x"]/crop_by) - 200
[…]

### 2022-03-02 content/code/refine_lamellae.py

@@ -1,0 +1,28 @@
+import pycistem
+import numpy as np
+from pathlib import Path
+import utils
+
+
+pycistem.set_cistem_path("/groups/elferich/cisTEM/build/refine_template_tests_Intel-gpu-debug/src/")
+
+for (database, name) in utils.dataset_info[7:]:
+    pa = []
+    results = utils.get_tm_data_from_db(database)
+    for i, row in results.iterrows():
+        pa.append(pycistem.programs.refine_template.parameters_from_database(database,
+                                                                        row["IMAGE_ASSET_ID"],
+                                                                        template_match_id=row["TEMPLATE_MATCH_JOB_ID"],
+                                                                        wanted_threshold=7.75,
+                                                                        input_reconstruction="/groups/elferich/mammalian_ribosome_structures/6swa_simulate_bfsca1_5.mrc",))
+    print(name)
+    print(len(pa))
+    print(pa[0])
+    res_my = pycistem.programs.refine_template.run(pa,num_procs=20,num_threads=3)
+
+
+    directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/lamella_refine/")
+    directory.mkdir(parents=True,exist_ok=True)
+
+    pycistem.programs.refine_template.write_starfile(res_my, str(directory / f"{name}_refine.star"))
+    

### 2022-03-02 content/code/utils.py

@@ -12,6 +12,24 @@ datasets = ["/scratch/bern/elferich/ER_Hox_120h_20211029_g1_l1/ER_Hox_120h_20211
             "/scratch/bern/elferich/ER_Hox_120h_20211108_g2_l3/ER_Hox_120h_20211108_g2_l3.db",
             "/scratch/bern/elferich/ER_Hox_120h_20211108_g2_l4/ER_Hox_120h_20211108_g2_l4.db"]
 
+dataset_names = ["euc_lamella1",
+                 "euc_lamella2",
+                 "euc_lamella3",
+                 "euc_lamella4",
+                 "fff_lamella1",
+                 "fff_lamella2",
+                 "fff_lamella3",
+                 "fff_lamella4"]
+
+dataset_info = [(dataset,dataset_names[i]) for i,dataset in enumerate(datasets)]
+                 
+
+def get_tm_data_from_db(dataset):
+    # Open the database
+    with contextlib.closing(sqlite3.connect(dataset)) as con:
+        df1 = pd.read_sql_query("SELECT * FROM TEMPLATE_MATCH_LIST", con)
+    return df1
+
 def get_data_from_db(dataset,get_movement=False):
     with contextlib.closing(sqlite3.connect(dataset)) as con:
 

### 2022-03-02 manuscript.tex
Refine macthes + assemble [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/00311ccf9074082904cef550d9b63ff61297b3c1.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/00311ccf9074082904cef550d9b63ff61297b3c1/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1923840837

@@
 This manuscript
-(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/faafadc025e8ca90737699af9c8f5d76cfeef9a3/}{permalink})
+(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/00311ccf9074082904cef550d9b63ff61297b3c1/}{permalink})
 was automatically generated
-from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/faafadc025e8ca90737699af9c8f5d76cfeef9a3}{jojoelfe/deco\_lace\_template\_matching\_manuscript@faafadc}
-on March 1, 2022.
+from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/00311ccf9074082904cef550d9b63ff61297b3c1}{jojoelfe/deco\_lace\_template\_matching\_manuscript@00311cc}
+on March 2, 2022.
 

### 2022-03-03 build/build.sh
Workflow figure

@@ -143,7 +143,6 @@ if [ "${BUILD_LATEX}" = "true" ]; then
     --defaults=latex.yaml
   tectonic output/manuscript.tex
   rm images
-  rm output/images
   rm output/graphics
   rm graphics
   rm figures

### 2022-03-03 build/pandoc/filters/svg2pdf.py

@@ -35,7 +35,7 @@ def svg_to_any(key, value, fmt, meta):
                 mtime = os.path.getmtime(eps_name)
             except OSError:
                 mtime = -1
-            if mtime < os.path.getmtime(src):
+            if mtime == -1:
                 cmd_line = ['inkscape', option[0], eps_name, src]
                 sys.stderr.write("Running %s\n" % " ".join(cmd_line))
                 subprocess.call(cmd_line, stdout=sys.stderr.fileno())

### 2022-03-03 figures/approach.tex
Workflow figure [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a4570afcb2725b9980fa97358516050b0a2697d3.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a4570afcb2725b9980fa97358516050b0a2697d3/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1925656087

    \documentclass[tikz,border=0cm]{standalone}
    \usepackage{graphicx}
    \usepackage{tikz}
    \usepackage{contour}
    \contourlength{0.6pt}
    \usetikzlibrary{positioning}
    \usetikzlibrary{arrows,snakes,shapes,fadings}
    \usetikzlibrary{fit}
    \usetikzlibrary{backgrounds}
    \usepackage{fontspec}
    \setmainfont{Roboto}[
      Extension = .otf,
      UprightFont = *-Regular,
      BoldFont = *-Bold,
      ItalicFont = *-Italic,
      BoldItalicFont = *-BoldItalic,
    ]    \usepackage{etoolbox} 
    \usepackage{enumitem}
    \setlist{nosep,leftmargin=*}
    \newcommand{\figwidth}{25cm} 
    \newcommand{\figheight}{10cm} 
    \newcommand{\fontselect}{\large\bf} 
    \newcommand{\fontannot}{\bf}

    \tikzset{
      labelNode/.style={anchor=south east, above left=0cm and 0cm of anchor, font=\fontselect}, 
      annotNode/.style={anchor=center, font=\fontannot},
      redAnchorNode/.style={anchor=center, left=-0.1cm of anchor, circle, fill=red, minimum size=0.2cm}, 
      graphicNode/.style={anchor=north west, below right=0cm and 0cm of anchor}, 
      titleNode/.style={anchor=south west, above right=0cm and 0cm of anchor}, 
      mnNode/.style={below left=0.1cm and 0cm of rect.south east, font=\fontannot},
      block/.style = {rectangle, draw, fill=gray!20, text width=12em, text centered, rounded corners, minimum height=2em,inner sep=0.5em},
      line/.style = {draw, -latex'}
    }

    \newtoggle{draft}
     \togglefalse{draft}
     %\togglefalse{draft}

    \begin{document}
    \begin{tikzpicture}[
      every node/.style={inner sep=0pt},
      box/.style = {draw=#1, line width=0.8mm,inner sep=0.0mm}
    ]

    \iftoggle{draft}{\node[anchor=south west, rectangle, draw, red, line width=2pt, minimum width=\figwidth, minimum height=\figheight] at (0,0) {};}
    {
      \begin{scope}[on background layer]

      \node[anchor=south west, rectangle, fill=white, minimum width=\figwidth, minimum height=\figheight] at (0,0) {};
      \end{scope}
    };

    \node (anchor) at (0.5,9.35) {}; 
\node[labelNode] {A};
\node[graphicNode] {\includegraphics[width=5cm]{content/graphics/approach/approach.png}};

\node (anchor) at (6.0,9.35) {}; 
\node[labelNode] {B};

% Place nodes
\node [block] (init) at (8.0,8.35) {\textbf{START} \\ Collect overview image};
\node [block, below = 0.3cm of init.south] (identify) {Setup hexagonal grid covering lamella area};
\node [block, below = 0.3cm of identify.south] (mutate) {Beam-imageshift to tile n=i};
\node [block, below = 0.3cm of mutate.south] (transfer) {Capture exposure and determine defocus by CTF fitting};
\node [block, below = 0.3cm of transfer.south] (evaluate) {Adjust defocus by difference between expected and measured value};

% Draw edges
\path [line] (init) -- (identify);
\path [line] (identify) -- (mutate);
\path [line] (mutate) -- (transfer);
\path [line] (transfer) -- (evaluate);
\path [line] (evaluate) -|  ([xshift=0.5cm, yshift=0cm]transfer.east) |- (mutate);

\node (anchor) at (17.0,9.35) {}; 
\node[labelNode] {Q};
\node[graphicNode] {\includegraphics[width=5cm]{content/images/ac_strategy.png}};
\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (11.5,9.35) {}; 
\node[labelNode] {C};
\node[titleNode] {Eucentric Focus};
\node[graphicNode] {\includegraphics[height=3.0cm]{content/images/fringebeam.png}};
\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (15,9.35) {}; 
\node[labelNode] {D};
\node[titleNode] {Fringe-free Focus};
\node[graphicNode] {\includegraphics[height=3.0cm]{content/images/nofringebeam.png}};
\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (11.5,4.85) {}; 
\node[labelNode] {E};
\node[graphicNode] {\includegraphics[height=4.3cm]{content/code/img/defocusplot.pdf}};
\iftoggle{draft}{\node [redAnchorNode] {};};

    \iftoggle{draft}{\draw[lightgray,step=1] (0,0) grid (\figwidth,\figheight);}{};
    \end{tikzpicture}
    \end{document}

### 2022-03-03 figures/deco_lace_workflow.tex
Workflow figure [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a4570afcb2725b9980fa97358516050b0a2697d3.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a4570afcb2725b9980fa97358516050b0a2697d3/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1925656087

    \documentclass[tikz,border=0cm]{standalone}
    \usepackage{graphicx}
    \usepackage{tikz}
    \usepackage{contour}
    \contourlength{0.6pt}
    \usetikzlibrary{positioning}
    \usetikzlibrary{arrows,snakes,shapes,fadings}
    \usetikzlibrary{fit}
    \usetikzlibrary{backgrounds}
    \usepackage{fontspec}
    \setmainfont{Roboto}[
      Extension = .otf,
      UprightFont = *-Regular,
      BoldFont = *-Bold,
      ItalicFont = *-Italic,
      BoldItalicFont = *-BoldItalic,
    ]    \usepackage{etoolbox} 
    \usepackage{enumitem}
    \setlist{nosep,leftmargin=*}
    \newcommand{\figwidth}{18cm} 
    \newcommand{\figheight}{18cm} 
    \newcommand{\fontselect}{\large\bf} 
    \newcommand{\fontannot}{\bf}

    \tikzset{
      labelNode/.style={anchor=south east, above left=0cm and 0cm of anchor, font=\fontselect}, 
      annotNode/.style={anchor=center, font=\fontannot},
      redAnchorNode/.style={anchor=center, left=-0.1cm of anchor, circle, fill=red, minimum size=0.2cm}, 
      graphicNode/.style={anchor=north west, below right=0cm and 0cm of anchor}, 
      titleNode/.style={anchor=south west, above right=0cm and 0cm of anchor}, 
      mnNode/.style={below left=0.1cm and 0cm of rect.south east, font=\fontannot},
      block/.style = {rectangle, draw, fill=gray!20, text width=12em, text centered, rounded corners, minimum height=2em,inner sep=0.5em},
      line/.style = {draw, -latex'}
    }

    \newtoggle{draft}
     \togglefalse{draft}
     %\togglefalse{draft}

    \begin{document}
    \begin{tikzpicture}[
      every node/.style={inner sep=0pt},
      box/.style = {draw=#1, line width=0.8mm,inner sep=0.0mm}
    ]

    \iftoggle{draft}{\node[anchor=south west, rectangle, draw, red, line width=2pt, minimum width=\figwidth, minimum height=\figheight] at (0,0) {};}
    {
      \begin{scope}[on background layer]

      \node[anchor=south west, rectangle, fill=white, minimum width=\figwidth, minimum height=\figheight] at (0,0) {};
      \end{scope}
    };

    \begin{scope}[
          blocks/.style = {rectangle, draw, fill=blue!20, text width=15em, align=center, rounded corners, minimum height=2em,inner sep=0.5em},
          inputs/.style = {rectangle,draw,fill=cyan!20, inner sep=0.5em},
          every path/.style={line width=1pt}
]
\node [inputs,anchor=north] (struc) at (3.0,17.5) {\textbf{6SWA Structure}};

\node [inputs,anchor=north] (movies) at (9.0,17.5) {\textbf{Movies}};
\node [inputs,anchor=north] (meta) at (15.0,17.5) {\textbf{SerialEM Metadata}};

\node [inputs,anchor=north] (over) at (3.0,1.5) {\textbf{Overview Image}};

\node [blocks,anchor=north] (simu) at (3.0,15.5) {\textbf{Generate Template} \\ \textit{simulate}
\begin{itemize}
    \item   Generate electron density map at 1.5{\AA}  pixel-size
\end{itemize}};

\node [blocks,anchor=north] (mc) at (9.0,15.5) {\textbf{Motion correction} \\ \textit{unblur\_decolace}
\begin{itemize}
    \item   Motion correction using central area of movie
    \item   Mask out unilluminated areas and replace with noise
\end{itemize}};

\node [inputs,below = 0.5 cm of mc.south] (images) {\textbf{Images}};

\node [blocks,below = 0.5 cm of images.south] (ctf) {\textbf{Ctf estimation} \\ \textit{ctffind4} 
\begin{itemize}
    \item Standard CTF estimation
\end{itemize}};
\node [blocks,below = 0.7 cm of ctf.south] (match) {\textbf{Template matching} \\ \textit{match\_template} \\ Template matching using 6swa as template};

\begin{scope}[on background layer]

\node[draw,very thick, dashed, inner sep=0.5em, rounded corners, fill=blue!10,
    fit=(mc) (ctf) (match)] (gui) {};
\end{scope}
\node[below left=0.1cm and 0cm of gui.south east, font=\fontannot] {cisTEM GUI};

\node [blocks,below = 1.4 cm of match.south] (refine) {\textbf{Refine matches} \\ \textit{refine\_matches.py/refine\_template} \\ Refine matches and compile list of all matches in a lamella};

\node [inputs,below = 0.5 cm of refine.south] (refstar) {\textbf{matches\_in\_tiles.star}};

\node [blocks,anchor=center] (assem) at (images.east -| meta.south) {\textbf{Assemble montage} \\ \textit{assemble\_montage.py} 
\begin{itemize}
    \item Create list of all tiles and their respective coordinates
    \item Create binned montage image
\end{itemize}};

\node [inputs,below = 0.5 cm of assem.south] (monstar) {\textbf{montage.star}};

\node [blocks,anchor=center] (assemma) at (refstar.east -| monstar.south) {\textbf{Assemble matches} \\ \textit{assemble\_matches.py} 
\begin{itemize}
    \item Transfer coordinates of matches into the montage coordinate system
\end{itemize}};

\node [inputs,below = 0.5 cm of assemma.south] (monmastar) {\textbf{matches\_in\_montage.star}};

%% Draw lines
\draw[->] (struc) -- (simu);

\draw[->] (movies) -- (mc);
\draw[->] (mc) -- (images);
\draw[->] (images) -- (ctf);
\draw[->] (ctf) -- (match);
\draw[->] (match) -- (refine);

\draw[->] (meta) -- (assem);
\draw[->] (images) -- (assem);

\draw[->] (simu) |- (match);
\draw[->] (simu) |- (refine);

\draw[->] (assem) -- (monstar);
\draw[->] (monstar) -- (assemma);

\draw[->] (refine) -- (refstar);
\draw[->] (refstar) -- (assemma);
\draw[->] (assemma) -- (monmastar);

\end{scope}
    \iftoggle{draft}{\draw[lightgray,step=1] (0,0) grid (\figwidth,\figheight);}{};
    \end{tikzpicture}
    \end{document}

### 2022-03-03 figures/example-figure3.tex
Workflow figure [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a4570afcb2725b9980fa97358516050b0a2697d3.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a4570afcb2725b9980fa97358516050b0a2697d3/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1925656087

--- 2022-03-03 figures/approach.tex
@@
     \setlist{nosep,leftmargin=*}
-    \newcommand{\figwidth}{25cm} 
-    \newcommand{\figheight}{10cm} 
+    \newcommand{\figwidth}{16.5cm} 
+    \newcommand{\figheight}{9cm} 
     \newcommand{\fontselect}{\large\bf} 
@@
 
-    \node (anchor) at (0.5,9.35) {}; 
+    \node (anchor) at (0.5,8.35) {}; 
 \node[labelNode] {A};
-\node[graphicNode] {\includegraphics[width=5cm]{content/graphics/approach/approach.png}};
-
-\node (anchor) at (6.0,9.35) {}; 
-\node[labelNode] {B};
-
-% Place nodes
-\node [block] (init) at (8.0,8.35) {\textbf{START} \\ Collect overview image};
-\node [block, below = 0.3cm of init.south] (identify) {Setup hexagonal grid covering lamella area};
-\node [block, below = 0.3cm of identify.south] (mutate) {Beam-imageshift to tile n=i};
-\node [block, below = 0.3cm of mutate.south] (transfer) {Capture exposure and determine defocus by CTF fitting};
-\node [block, below = 0.3cm of transfer.south] (evaluate) {Adjust defocus by difference between expected and measured value};
-
-% Draw edges
-\path [line] (init) -- (identify);
-\path [line] (identify) -- (mutate);
-\path [line] (mutate) -- (transfer);
-\path [line] (transfer) -- (evaluate);
-\path [line] (evaluate) -|  ([xshift=0.5cm, yshift=0cm]transfer.east) |- (mutate);
-
-\node (anchor) at (17.0,9.35) {}; 
-\node[labelNode] {Q};
-\node[graphicNode] {\includegraphics[width=5cm]{content/images/ac_strategy.png}};
+\node[graphicNode] {\includegraphics[width=7.5cm]{content/code/img/movement_vs_bs_plot.pdf}};
 \iftoggle{draft}{\node [redAnchorNode] {};};
 
-\node (anchor) at (11.5,9.35) {}; 
-\node[labelNode] {C};
-\node[titleNode] {Eucentric Focus};
-\node[graphicNode] {\includegraphics[height=3.0cm]{content/images/fringebeam.png}};
-\iftoggle{draft}{\node [redAnchorNode] {};};
-
-\node (anchor) at (15,9.35) {}; 
-\node[labelNode] {D};
-\node[titleNode] {Fringe-free Focus};
-\node[graphicNode] {\includegraphics[height=3.0cm]{content/images/nofringebeam.png}};
-\iftoggle{draft}{\node [redAnchorNode] {};};
-
-\node (anchor) at (11.5,4.85) {}; 
-\node[labelNode] {E};
-\node[graphicNode] {\includegraphics[height=4.3cm]{content/code/img/defocusplot.pdf}};
+\node (anchor) at (8.5,8.35) {}; 
+\node[labelNode] {B};
+\node[graphicNode] {\includegraphics[width=7.5cm]{content/code/img/thickness_by_intensity_vs_bs_plot.pdf}};
 \iftoggle{draft}{\node [redAnchorNode] {};};

### 2022-03-03 figures/example-figure4.tex
Workflow figure [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a4570afcb2725b9980fa97358516050b0a2697d3.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a4570afcb2725b9980fa97358516050b0a2697d3/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1925656087

--- 2022-03-03 figures/approach.tex
@@
     \setlist{nosep,leftmargin=*}
-    \newcommand{\figwidth}{25cm} 
-    \newcommand{\figheight}{10cm} 
+    \newcommand{\figwidth}{20cm} 
+    \newcommand{\figheight}{13cm} 
     \newcommand{\fontselect}{\large\bf} 
@@
 
-    \node (anchor) at (0.5,9.35) {}; 
+    \node (anchor) at (0.5,12.35) {}; 
 \node[labelNode] {A};
-\node[graphicNode] {\includegraphics[width=5cm]{content/graphics/approach/approach.png}};
-
-\node (anchor) at (6.0,9.35) {}; 
+\node[graphicNode] {\includegraphics[height=5.2cm]{content/images/slicer000.png}};
+\iftoggle{draft}{\node [redAnchorNode] {};};
+\node (anchor) at (6.5,12.35) {}; 
 \node[labelNode] {B};
-
-% Place nodes
-\node [block] (init) at (8.0,8.35) {\textbf{START} \\ Collect overview image};
-\node [block, below = 0.3cm of init.south] (identify) {Setup hexagonal grid covering lamella area};
-\node [block, below = 0.3cm of identify.south] (mutate) {Beam-imageshift to tile n=i};
-\node [block, below = 0.3cm of mutate.south] (transfer) {Capture exposure and determine defocus by CTF fitting};
-\node [block, below = 0.3cm of transfer.south] (evaluate) {Adjust defocus by difference between expected and measured value};
-
-% Draw edges
-\path [line] (init) -- (identify);
-\path [line] (identify) -- (mutate);
-\path [line] (mutate) -- (transfer);
-\path [line] (transfer) -- (evaluate);
-\path [line] (evaluate) -|  ([xshift=0.5cm, yshift=0cm]transfer.east) |- (mutate);
-
-\node (anchor) at (17.0,9.35) {}; 
-\node[labelNode] {Q};
-\node[graphicNode] {\includegraphics[width=5cm]{content/images/ac_strategy.png}};
+\node[graphicNode] {\includegraphics[height=5.2cm]{content/images/slicer001.png}};
+\iftoggle{draft}{\node [redAnchorNode] {};};
+\node (anchor) at (11,12.35) {}; 
+\node[labelNode] {C};
+\node[graphicNode] {\includegraphics[height=5.2cm]{content/images/slicer002.png}};
+\iftoggle{draft}{\node [redAnchorNode] {};};
+\node (anchor) at (15.5,12.35) {}; 
+\node[labelNode] {D};
+\node[graphicNode] {\includegraphics[height=5.2cm]{content/images/slicer003.png}};
 \iftoggle{draft}{\node [redAnchorNode] {};};
 
-\node (anchor) at (11.5,9.35) {}; 
-\node[labelNode] {C};
-\node[titleNode] {Eucentric Focus};
-\node[graphicNode] {\includegraphics[height=3.0cm]{content/images/fringebeam.png}};
+\node (anchor) at (0.5,6.5) {}; 
+\node[labelNode] {E};
+\node[graphicNode] {\includegraphics[height=5.2cm]{content/images/slicer005.png}};
 \iftoggle{draft}{\node [redAnchorNode] {};};
-
-\node (anchor) at (15,9.35) {}; 
-\node[labelNode] {D};
-\node[titleNode] {Fringe-free Focus};
-\node[graphicNode] {\includegraphics[height=3.0cm]{content/images/nofringebeam.png}};
+\node (anchor) at (5,6.5) {}; 
+\node[labelNode] {F};
+\node[graphicNode] {\includegraphics[height=5.2cm]{content/images/slicer006.png}};
 \iftoggle{draft}{\node [redAnchorNode] {};};
-
-\node (anchor) at (11.5,4.85) {}; 
-\node[labelNode] {E};
-\node[graphicNode] {\includegraphics[height=4.3cm]{content/code/img/defocusplot.pdf}};
+\node (anchor) at (9.5,6.5) {}; 
+\node[labelNode] {G};
+\node[graphicNode] {\includegraphics[height=5.2cm]{content/images/slicer007.png}};
+\iftoggle{draft}{\node [redAnchorNode] {};};
+\node (anchor) at (14.5,6.5) {}; 
+\node[labelNode] {H};
+\node[graphicNode] {\includegraphics[height=5.2cm]{content/images/slicer008.png}};
 \iftoggle{draft}{\node [redAnchorNode] {};};

### 2022-03-03 figures/initmatching.tex
Workflow figure [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a4570afcb2725b9980fa97358516050b0a2697d3.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a4570afcb2725b9980fa97358516050b0a2697d3/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1925656087

--- 2022-03-03 figures/approach.tex
@@
     \setlist{nosep,leftmargin=*}
-    \newcommand{\figwidth}{25cm} 
+    \newcommand{\figwidth}{19cm} 
     \newcommand{\figheight}{10cm} 
@@
 \node[labelNode] {A};
-\node[graphicNode] {\includegraphics[width=5cm]{content/graphics/approach/approach.png}};
+\node[graphicNode] {\includegraphics[height=9cm]{content/images/the_lamella.png}};
 
-\node (anchor) at (6.0,9.35) {}; 
+\node[annotNode] at (3.5,8.35) {\contour{white}{Nuc}};
+\node[annotNode] at (1.75,4.0) {\contour{white}{Nuc}};
+
+\node[annotNode] at (3.2,4.7) {\contour{white}{M}};
+\node[annotNode] at (2.75,2.25) {\contour{white}{M}};
+
+\node[annotNode] at (1.5,8.0) {\contour{white}{GrCyt}};
+\node[annotNode] at (4.5,3.5) {\contour{white}{GrCyt}};
+
+\node (rect) at (1.1,7.5) [anchor=center,draw,thick,minimum width=0.85cm,minimum height=0.6cm,color=blue!60] {};
+\node[mnNode, color=blue!60] {\contour{white}{2}};
+
+\node (rect) at (3.2,7.3) [anchor=center,draw,thick,minimum width=0.85cm,minimum height=0.6cm,color=blue!60] {};
+\node[mnNode, color=blue!60] {\contour{white}{0}};
+
+\node (rect) at (4.5,6.25) [anchor=center,draw,thick,minimum width=0.85cm,minimum height=0.6cm,color=red] {};
+\node[mnNode, color=red] {\contour{white}{506}};
+
+\node (rect) at (3.4,5.5) [anchor=center,draw,thick,minimum width=0.85cm,minimum height=0.6cm,color=blue!60] {};
+\node[mnNode, color=blue!60] {\contour{white}{16}};
+
+\node (rect) at (2.75,3.5) [anchor=center,draw,thick,minimum width=0.85cm,minimum height=0.6cm,color=green] {};
+\node[mnNode, color=green] {\contour{white}{30}};
+
+\node (rect) at (2.65,2.35) [anchor=center,draw,thick,minimum width=0.85cm,minimum height=0.6cm,color=orange] {};
+\node[mnNode, color=orange] {\contour{white}{17}};
+
+\node (rect) at (1.25,1.5) [anchor=center,draw,thick,minimum width=0.85cm,minimum height=0.6cm,color=blue!60] {};
+\node[mnNode, color=blue!60] {\contour{white}{8}};
+
+\node (rect) at (4.0,2.2) [anchor=center,draw,thick,minimum width=0.85cm,minimum height=0.6cm,color=magenta] {};
+\node[mnNode, color=magenta] {\contour{white}{52}};
+
+\node (anchor) at (6.5,9.35) {}; 
 \node[labelNode] {B};
+\node (img) [graphicNode]  {\includegraphics[height=4cm]{content/images/30_matches.png}};
+\node (n3) [box=green, fit=(img)] {};
 
-% Place nodes
-\node [block] (init) at (8.0,8.35) {\textbf{START} \\ Collect overview image};
-\node [block, below = 0.3cm of init.south] (identify) {Setup hexagonal grid covering lamella area};
-\node [block, below = 0.3cm of identify.south] (mutate) {Beam-imageshift to tile n=i};
-\node [block, below = 0.3cm of mutate.south] (transfer) {Capture exposure and determine defocus by CTF fitting};
-\node [block, below = 0.3cm of transfer.south] (evaluate) {Adjust defocus by difference between expected and measured value};
+\node (anchor) at (12.75,9.35) {}; 
+\node[labelNode] {C};
+\node (img) [graphicNode]  {\includegraphics[height=4cm]{content/images/506_matches.png}};
+\node (n3) [box=red, fit=(img)] {};
 
-% Draw edges
-\path [line] (init) -- (identify);
-\path [line] (identify) -- (mutate);
-\path [line] (mutate) -- (transfer);
-\path [line] (transfer) -- (evaluate);
-\path [line] (evaluate) -|  ([xshift=0.5cm, yshift=0cm]transfer.east) |- (mutate);
+\node (anchor) at (6.5,4.75) {}; 
+\node[labelNode] {D};
+\node (img) [graphicNode]  {\includegraphics[height=4cm]{content/images/17_matches.png}};
+\node (n3) [box=orange, fit=(img)] {};
 
-\node (anchor) at (17.0,9.35) {}; 
-\node[labelNode] {Q};
-\node[graphicNode] {\includegraphics[width=5cm]{content/images/ac_strategy.png}};
-\iftoggle{draft}{\node [redAnchorNode] {};};
+\node (anchor) at (12.75,4.75) {}; 
+\node[labelNode] {E};
+\node (img) [graphicNode]  {\includegraphics[height=4cm]{content/images/52_matches.png}};
+\node (n3) [box=magenta, fit=(img)] {};
 
-\node (anchor) at (11.5,9.35) {}; 
-\node[labelNode] {C};
-\node[titleNode] {Eucentric Focus};
-\node[graphicNode] {\includegraphics[height=3.0cm]{content/images/fringebeam.png}};
-\iftoggle{draft}{\node [redAnchorNode] {};};
-
-\node (anchor) at (15,9.35) {}; 
-\node[labelNode] {D};
-\node[titleNode] {Fringe-free Focus};
-\node[graphicNode] {\includegraphics[height=3.0cm]{content/images/nofringebeam.png}};
-\iftoggle{draft}{\node [redAnchorNode] {};};
-
-\node (anchor) at (11.5,4.85) {}; 
-\node[labelNode] {E};
-\node[graphicNode] {\includegraphics[height=4.3cm]{content/code/img/defocusplot.pdf}};
-\iftoggle{draft}{\node [redAnchorNode] {};};
+%%\iftoggle{draft}{\node [redAnchorNode] {};};
 

### 2022-03-03 figures/lamella_spatial_info.tex
Workflow figure [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a4570afcb2725b9980fa97358516050b0a2697d3.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a4570afcb2725b9980fa97358516050b0a2697d3/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1925656087

--- 2022-03-03 figures/example-figure3.tex
@@
 \node[labelNode] {A};
-\node[graphicNode] {\includegraphics[width=7.5cm]{content/code/img/movement_vs_bs_plot.pdf}};
+\node[graphicNode] {\includegraphics[width=7.5cm]{content/code/img/defocus_defocus_vs_bs_plot.pdf}};
+\iftoggle{draft}{\node [redAnchorNode] {};};
+
+\node (anchor) at (0.5,4.35) {}; 
+\node[labelNode] {B};
+\node[graphicNode] {\includegraphics[width=7.5cm]{content/code/img/defocus_astigmatism_vs_bs_plot.pdf}};
 \iftoggle{draft}{\node [redAnchorNode] {};};
@@
 \node (anchor) at (8.5,8.35) {}; 
-\node[labelNode] {B};
-\node[graphicNode] {\includegraphics[width=7.5cm]{content/code/img/thickness_by_intensity_vs_bs_plot.pdf}};
+\node[labelNode] {C};
+\node[graphicNode] {\includegraphics[width=7.5cm]{content/code/img/defocus_angle_vs_bs_plot.pdf}};
 \iftoggle{draft}{\node [redAnchorNode] {};};

### 2022-03-03 figures/matching.tex
Workflow figure [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a4570afcb2725b9980fa97358516050b0a2697d3.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a4570afcb2725b9980fa97358516050b0a2697d3/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1925656087

--- 2022-03-03 figures/approach.tex
@@
     \setlist{nosep,leftmargin=*}
-    \newcommand{\figwidth}{25cm} 
-    \newcommand{\figheight}{10cm} 
+    \newcommand{\figwidth}{16cm} 
+    \newcommand{\figheight}{13cm} 
     \newcommand{\fontselect}{\large\bf} 
@@
 \node[labelNode] {A};
-\node[graphicNode] {\includegraphics[width=5cm]{content/graphics/approach/approach.png}};
-
-\node (anchor) at (6.0,9.35) {}; 
-\node[labelNode] {B};
-
-% Place nodes
-\node [block] (init) at (8.0,8.35) {\textbf{START} \\ Collect overview image};
-\node [block, below = 0.3cm of init.south] (identify) {Setup hexagonal grid covering lamella area};
-\node [block, below = 0.3cm of identify.south] (mutate) {Beam-imageshift to tile n=i};
-\node [block, below = 0.3cm of mutate.south] (transfer) {Capture exposure and determine defocus by CTF fitting};
-\node [block, below = 0.3cm of transfer.south] (evaluate) {Adjust defocus by difference between expected and measured value};
-
-% Draw edges
-\path [line] (init) -- (identify);
-\path [line] (identify) -- (mutate);
-\path [line] (mutate) -- (transfer);
-\path [line] (transfer) -- (evaluate);
-\path [line] (evaluate) -|  ([xshift=0.5cm, yshift=0cm]transfer.east) |- (mutate);
-
-\node (anchor) at (17.0,9.35) {}; 
-\node[labelNode] {Q};
-\node[graphicNode] {\includegraphics[width=5cm]{content/images/ac_strategy.png}};
-\iftoggle{draft}{\node [redAnchorNode] {};};
-
-\node (anchor) at (11.5,9.35) {}; 
-\node[labelNode] {C};
-\node[titleNode] {Eucentric Focus};
-\node[graphicNode] {\includegraphics[height=3.0cm]{content/images/fringebeam.png}};
-\iftoggle{draft}{\node [redAnchorNode] {};};
-
-\node (anchor) at (15,9.35) {}; 
-\node[labelNode] {D};
-\node[titleNode] {Fringe-free Focus};
-\node[graphicNode] {\includegraphics[height=3.0cm]{content/images/nofringebeam.png}};
-\iftoggle{draft}{\node [redAnchorNode] {};};
-
-\node (anchor) at (11.5,4.85) {}; 
-\node[labelNode] {E};
-\node[graphicNode] {\includegraphics[height=4.3cm]{content/code/img/defocusplot.pdf}};
+\node[graphicNode] {\includegraphics[width=7.5cm]{content/images/screenie.png}};
 \iftoggle{draft}{\node [redAnchorNode] {};};

### 2022-03-03 manuscript.tex
Workflow figure [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a4570afcb2725b9980fa97358516050b0a2697d3.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a4570afcb2725b9980fa97358516050b0a2697d3/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1925656087

@@
 This manuscript
-(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/00311ccf9074082904cef550d9b63ff61297b3c1/}{permalink})
+(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/a4570afcb2725b9980fa97358516050b0a2697d3/}{permalink})
 was automatically generated
-from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/00311ccf9074082904cef550d9b63ff61297b3c1}{jojoelfe/deco\_lace\_template\_matching\_manuscript@00311cc}
-on March 2, 2022.
+from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/a4570afcb2725b9980fa97358516050b0a2697d3}{jojoelfe/deco\_lace\_template\_matching\_manuscript@a4570af}
+on March 3, 2022.
 
@@
 \begin{figure}
-\hypertarget{fig:deco_lace_workflow}{%
-\centering
-\includegraphics{figures/deco_lace_workflow.pdf}
-\caption{Workflow of DeCo-Lace processing}\label{fig:deco_lace_workflow}
-}
-\end{figure}
-
-\begin{figure}
 \hypertarget{fig:lamella_spatial_info}{%
@@
 \caption{This is an example-figurern}\label{fig:matching}
+}
+\end{figure}
+
+\begin{figure}
+\hypertarget{fig:deco_lace_workflow}{%
+\centering
+\includegraphics{figures/deco_lace_workflow.pdf}
+\caption{Workflow of DeCo-Lace processing}\label{fig:deco_lace_workflow}
 }

### 2022-03-07 manuscript.tex
Nikos comments [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/287b9950fc2bff7878d36aa1cbf2cb7f2082f798.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/287b9950fc2bff7878d36aa1cbf2cb7f2082f798/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1948085649

@@
 This manuscript
-(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/a4570afcb2725b9980fa97358516050b0a2697d3/}{permalink})
+(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/287b9950fc2bff7878d36aa1cbf2cb7f2082f798/}{permalink})
 was automatically generated
-from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/a4570afcb2725b9980fa97358516050b0a2697d3}{jojoelfe/deco\_lace\_template\_matching\_manuscript@a4570af}
-on March 3, 2022.
+from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/287b9950fc2bff7878d36aa1cbf2cb7f2082f798}{jojoelfe/deco\_lace\_template\_matching\_manuscript@287b995}
+on March 7, 2022.
 
@@
 
-Localization of biomolecules inside a cell is an important goal of biological imaging.
-Fluorescence microscopy can localize biomolecules inside whole cells and tissues, but its ability to count biomolecules and accuracy of the spatial coordinates is limited by the wavelength of visible light.
-On the other hand, cryo-electron microscopy (cryo-EM) provides highly accurate position and orientation information of biomolecules but is often limited to small fields of view inside a cell, providing only limited biological context.
-In this study we use a new data-acquisition scheme called ``Beam-Imageshift for Large Area Cryo-Electron microscopy'' (BILACE) to collect high-resolution cryo-EM data over entire sections (100 -- 200 nm thick lamellae) of neutrophil-like mouse cells, representing roughly 1\% of the total cellular volume.
-We use 2D template matching to determine localization and orientation of the large ribosomal subunit in these sections.
-Furthermore, we use 2D template matching to test detected targets for the presence of the small ribosomal subunit and used the relative orientations of the ribosomes to assign them to polysomes.
-These results provide ``maps'' of translational activity across sections of mammalian cells.
-We envision that using this high-throughput cryo-EM data collection approach together with 2D template matching will advance visual proteomics to complement other single-cell ``omics'' techniques, such as flow-cytometry and single-cell sequencing.
+Localization of biomolecules inside a cell is an important goal of biological
+imaging. Fluorescence microscopy can localize biomolecules inside whole cells
+and tissues, but its ability to count biomolecules and accuracy of the spatial
+coordinates is limited by the wavelength of visible light. Cryo-electron
+microscopy (cryo-EM) provides highly accurate position and orientation
+information of biomolecules but is often confined to small fields of view inside
+a cell, limiting biological context. In this study we use a new data-acquisition
+scheme called ``Defocus-Corrected Large-Area cryo-EM'' (DeCo-LACE) to collect
+high-resolution cryo-EM data over entire sections (100 -- 200 nm thick lamellae)
+of neutrophil-like mouse cells, representing roughly 1\% of the total cellular
+volume. We use 2D template matching (2DTM) to determine localization and orientation
+of the large ribosomal subunit in these sections, detect bound small
+ribosomal subunits and assign ribosomes to polysomes based on their relative orientations to each other. These data provide ``maps'' of translational activity across
+sections of mammalian cells. This new high-throughput cryo-EM
+data collection approach together with 2DTM will advance visual
+proteomics and complement other single-cell ``omics'' techniques, such as
+flow-cytometry and single-cell sequencing.
 
@@
 
-Understanding of cellular processes requires knowledge of the amounts, location,
-interactions, and conformations of biomolecules inside the cell. Techniques that
-measure this can broadly be divided into label- and label-free techniques. In
-label-techniques a probe is physically attached to a molecule of interest that
-is able to produce a high signal-to-noise signal, such as a fluorescent molecule.
-In label-free techniques the physical properties of molecules themselves are
-used for detection. An example for this is proteomics using mass-spectrometry
-{[}\protect\hyperlink{ref-tSXIKPl7}{1}{]}. The advantage of label-free techniques is that
-they can provide information over thousands of molecules, while label-techniques
-offer higher fidelity information for a few molecules. Especially spatial
-information can most of the time only be achieved using label-techniques, such
-as fluorescence microscopy {[}\protect\hyperlink{ref-VBmW7Aot}{2}{]}.
+A major goal in understanding cellular processes is the knowledge of the
+amounts, location, interactions, and conformations of biomolecules
+inside the cell. This knowledge can be obtained by approaches broadly
+divided into label- and label-free techniques. In label-dependent
+techniques a probe is physically attached to a molecule of interest that
+is able to detected with a high signal-to-noise signal, such as a
+fluorescent molecule. In label-free techniques the physical properties
+of molecules themselves are used for detection. An example for this is
+proteomics using mass-spectrometry {[}\protect\hyperlink{ref-tSXIKPl7}{1}{]}. The advantage
+of label-free techniques is that they can provide information over
+thousands of molecules, while label-techniques offer highly specific
+information for a few molecules. Especially spatial information can
+often only be achieved using label-dependent techniques, such as
+fluorescence microscopy {[}\protect\hyperlink{ref-VBmW7Aot}{2}{]}.
 
-Cryo-electron microscopy has the potential to directly measure the arrangement
-of atoms that compose biomolecules inside of cells, thereby allowing label-free
-detection with high spatial accuracy. This has been called ``visual proteomics''
-{[}\protect\hyperlink{ref-tGQ6TSUo}{3}{]}. Since cryo-EM requires thin samples (\textless500nm), imaging of
-biomolecules inside cells is either restricted to small organisms, thin
-regions of large cells, or requires thinning of the sample. This can be achieved
-either by mechanical sectioning {[}\protect\hyperlink{ref-g8QavfwP}{4}{]} or by
-milling using a focused ion beam (FIB) {[}\protect\hyperlink{ref-16IhS1Nc4}{5}{]}. This
-complex workflow restricts throughput of cryo-EM imaging of cells. This is
-exacerbated by the fact that at the required magnifications, typical field of
-views (FOV) are very small compared to mammalian cells and the FOV achieved by
-label-techniques such as fluorescence light microscopy. The predominant cryo-EM
-technique for detection of biomolecules according to their shape in cells at the
-moment is cryo-electron tomography {[}\protect\hyperlink{ref-Rksh2dxu}{6}{]}. However,
-the requirement of physically tilt the stage at every FOV, together with a more
-complex workflow that requires highly accurate alignment of various projection,
-further restricts the throughput for molecular detection.
+Cryo-electron microscopy has the potential to directly visualize the
+arrangement of atoms that compose biomolecules inside of cells, thereby
+allowing label-free detection with high spatial accuracy. This has been
+called ``visual proteomics'' {[}\protect\hyperlink{ref-tGQ6TSUo}{3}{]}. Since cryo-EM
+requires thin samples (\textless500nm), imaging of biomolecules inside cells is
+restricted to small organisms, thin regions of cells, or samples that
+have been suitably thinned. Thinning can be achieved either by
+mechanical sectioning {[}\protect\hyperlink{ref-g8QavfwP}{4}{]} or by
+milling using a focused ion beam (FIB) {[}\protect\hyperlink{ref-16IhS1Nc4}{5}{]}. his complex workflow
+leads to a low throughput of cryo-EM imaging of cells and is further
+limited by the fact that at the required magnifications, typical fields
+of view (FOV) are very small compared to mammalian cells, and the FOV
+achieved by label-techniques such as fluorescence light microscopy. The
+predominant cryo-EM technique for the localization of biomolecules of
+defined size and shape inside cells is cryo-electron tomography {[}\protect\hyperlink{ref-Rksh2dxu}{6}{]}. However, the requirement of a tilt series at
+every imaged location and subsequent image alignment, severely limits
+the throughput for molecular localization.
 
 An alternative approach is to identify molecules by their structural
-``fingerprint'' in single projection using ``2D template-matching''
-{[}\protect\hyperlink{ref-Ynb3IP6I}{7},\protect\hyperlink{ref-18KGpXYPE}{8},\protect\hyperlink{ref-10bXZuF3G}{9}{]}. In this method an experimentally obtained 3D model
-of a biomolecule is used to calculate the expected electron density, which is
-called the template. The template is then projected on a fine angular grid and
-the projections are used to find local cross-correlation peaks in a cryo-EM
-micrograph. Since locations of the biomolecule in the Z-direction causes
-predictable aberrations to the projection image, this method can be used to
-calculate 3D coordinates and orientations of a biomolecule in a cellular sample
+``fingerprint'' in single projection using ``2D template-matching'' (2DTM)
+{[}\protect\hyperlink{ref-Ynb3IP6I}{7},\protect\hyperlink{ref-18KGpXYPE}{8},\protect\hyperlink{ref-10bXZuF3G}{9}{]}. In this
+method a 3D model of a biomolecule is used as a template to find 2D
+projections that match the molecules visible in the electron
+micrographs. This method requires a projection search on a fine angular
+grid, and the projections are used to find local cross-correlation peaks
+with the micrograph. Since the location of a biomolecule in the
+z-direction causes predictable aberrations to the projection image, this
+method can be used to calculate complete 3D coordinates and orientations
+of a biomolecule in a cellular sample
 {[}\protect\hyperlink{ref-18KGpXYPE}{8}{]}
@@
 neutrophil-like murine cells {[}\protect\hyperlink{ref-1B9Vt9eYu}{12}{]}. To increase the
-amount of collected data and to provide un-biased sampling of the whole lamella
-we devised a new data-acquisition scheme, Defocus-corrected large area
-cryo-electron microscopy (DeCo-LACE). We characterize aberration cause by the
-used large beam-image shifts and highly focused beams and find that they can be
-adequately correct to enable ribosome detection by 2D-template matching. The
-resulting data provides a description of ribosome distribution in the whole
-lamellae, which represent roughly 2\% of the cellular volume. We find highly
-heterogeneous density of ribosome within the cell and can identify discrete
-clusters of presumably translationaly active ribosomes, by testing for the
-presence of the small ribosomal subunit. The high accuracy of location and
-orientation of each detected ribosome also allows us to cluster ribosome
-molecules into potential polysomes. Analysis of the throughput in this method
-suggests that for the foreseeable future computation will be the bottleneck for
-visual proteomics.
+amount of collected data and to provide unbiased sampling of the whole
+lamella, we devised a new data-acquisition scheme, Defocus-corrected
+large area cryo-electron microscopy (DeCo-LACE). We characterize
+aberration cause by the used large beam-image shifts and highly focused
+beams and find that they can be adequately corrected to enable ribosome
+detection by 2DTM. The resulting data provide a description of ribosome
+distribution in the whole lamellae, which represent roughly 2\% of the
+cellular volume. We find highly heterogeneous density of ribosome within
+the cell and can identify discrete clusters of presumably
+translationally active ribosomes, by testing for the presence of the
+small ribosomal subunit. The high accuracy of location and orientation
+of each detected ribosome also allows us to cluster ribosome molecules
+into potential polysomes. Analysis of the throughput in this method
+suggests that for the foreseeable future computation will be the
+bottleneck for visual proteomics.
 

### 2022-03-08 content/code/assemble_matches.py
Fixed flipping in Y axis + work on refining assembly by cc

@@ -7,7 +7,7 @@ montage_directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing
 refine_directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/lamella_refine/")
 assembled_directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/assemble/")
 assembled_directory.mkdir(exist_ok=True,parents=True)
-for (database, name) in utils.dataset_info[4:5]:
+for (database, name) in utils.dataset_info:
     print(name)
     montage_info = starfile.read(montage_directory / f"{name}.star")
     refine_info = starfile.read(refine_directory / f"{name}_refine.star")
@@ -22,7 +22,7 @@ for (database, name) in utils.dataset_info[4:5]:
     info["tile_x"] = info["x"]
     info["tile_y"] = info["y"]
     info["x"] = info["tile_x"] + info["tile_x_offset"]
-    info["y"] = info["tile_y"] - info["tile_y_offset"]
+    info["y"] = info["tile_y"] + info["tile_y_offset"]
     info["image_filename"] = montage_info["montage"]["montage_filename"].loc[0]
     print(info["template_filename"].unique())
     print(info["image_filename"].unique())

### 2022-03-08 content/code/assemble_montage_fff_4.py

@@ -26,5 +26,5 @@ metadata = assemble_montage_utils.create_metadata(selected_micrographs,
                                        IS_to_camera=assemble_montage_utils.IS_to_camera,
                                        output_base=str(directory / 'fff_lamella4'),
                                        mask_suffix="_1_mask.mrc")
-#assemble_montage_utils.create_montage(metadata)
+assemble_montage_utils.create_montage(metadata)
 exit()

### 2022-03-08 content/code/assemble_montage_utils.py

@@ -55,7 +55,7 @@ def create_metadata(expand_data, IS_to_camera, output_base, binning=10, image_su
         crop_center_x = item["CROP_CENTER_X"] 
         crop_center_y = item["CROP_CENTER_Y"] 
         expand_data.loc[i,"image_shift_pixel_x"] = shift_in_image_pixel[0] + crop_x + crop_center_x
-        expand_data.loc[i,"image_shift_pixel_y"] = shift_in_image_pixel[1] + crop_y - crop_center_y
+        expand_data.loc[i,"image_shift_pixel_y"] = - shift_in_image_pixel[1] + crop_y - crop_center_y
         
     
     # Get the range of the shifts taking binning into account
@@ -141,13 +141,13 @@ def create_montage(metadata ):
     for i, tile in tile_info.iterrows():
         
         with mrcfile.open(tile['tile_filename']) as mrc: 
-            tile_data = np.copy(np.flip(mrc.data[0],axis=0))
+            tile_data = np.copy(mrc.data[0])
             tile_dimensions = (int(tile_data.shape[0]// montage_info['montage_binning']),int(tile_data.shape[1]// montage_info['montage_binning']))
             
             tile_data = resize(tile_data,tile_dimensions,anti_aliasing=True)
         
         with mrcfile.open(tile['tile_mask_filename']) as mrc: 
-            mask_data = np.copy(np.flip(mrc.data[0],axis=0))
+            mask_data = np.copy(mrc.data[0])
             mask_data.dtype = np.uint8
         
         
@@ -166,9 +166,9 @@ def create_montage(metadata ):
         mask[insertion_slice] += mask_resized
         
         
-        if len(str(tile['tile_plotted_result_filename'])) > 0:
+        if str(tile['tile_plotted_result_filename']) != "None":
             with mrcfile.open(tile['tile_plotted_result_filename']) as mrc: 
-                match_data = np.copy(np.flip(mrc.data[0],axis=0))
+                match_data = np.copy(mrc.data[0])
                 if np.max(match_data) > 300000:
                     print(i)
                     print(tile['tile_filename'])

### 2022-03-08 content/code/create_match_star.py

@@ -1,0 +1,12 @@
+import pycistem
+import numpy as np
+from pathlib import Path
+import utils
+
+
+pycistem.set_cistem_path("/groups/elferich/cisTEM/build/refine_template_tests_Intel-gpu-debug/src/")
+
+for (database, name) in utils.dataset_info:
+    directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/lamella_match/")
+    directory.mkdir(parents=True,exist_ok=True)
+    pycistem.database.write_match_template_to_starfile(database,directory / f"{name}_match.star",overwrite=True,switch_phi_psi=True)

### 2022-03-08 content/code/refine_lamellae.py

@@ -6,7 +6,7 @@ import utils
 
 pycistem.set_cistem_path("/groups/elferich/cisTEM/build/refine_template_tests_Intel-gpu-debug/src/")
 
-for (database, name) in utils.dataset_info[7:]:
+for (database, name) in utils.dataset_info[-1:]:
     pa = []
     results = utils.get_tm_data_from_db(database)
     for i, row in results.iterrows():
@@ -24,5 +24,5 @@ for (database, name) in utils.dataset_info[7:]:
     directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/lamella_refine/")
     directory.mkdir(parents=True,exist_ok=True)
 
-    pycistem.programs.refine_template.write_starfile(res_my, str(directory / f"{name}_refine.star"))
+    pycistem.programs.refine_template.write_starfile(res_my, str(directory / f"{name}_refine.star"),overwrite=True)
     

### 2022-03-08 content/code/refine_montage_by_cc.py

@@ -1,0 +1,122 @@
+from pyexpat.errors import XML_ERROR_INCORRECT_ENCODING
+import numpy as np
+import starfile
+from scipy.spatial import KDTree
+import multiprocessing
+from skimage.registration._masked_phase_cross_correlation import cross_correlate_masked
+import mrcfile
+import matplotlib.pyplot as plt
+from scipy import ndimage as ndi
+import pycistem
+import numpy as np
+from pathlib import Path
+import utils
+from skimage import transform
+
+
+def calculate_crosscorrelations(tile_data,num_proc=20):
+    points = np.array([(a["tile_x_offset"]/a["tile_pixel_size"],a["tile_y_offset"]/a["tile_pixel_size"]) for i,a in tile_data.iterrows()])
+    kd_tree = KDTree(points)
+
+    pairs = kd_tree.query_pairs(r=3000)
+    row_pairs = [(tile_data.iloc[a[0]],tile_data.iloc[a[1]]) for a in pairs]
+    pool = multiprocessing.Pool(processes=num_proc)
+    shifts = pool.map(determine_shift_by_cc, row_pairs)
+    pool.close()
+    pool.join()
+    shifts = np.array(shifts)
+    pairs=np.array(list(pairs))
+    return((pairs,shifts))
+
+def determine_shift_by_cc(doubled,diagnostic=False):
+    # Given the infow of two images, calculate the refined relative shifts by crosscorrelation return
+    im1, im2 = doubled
+    im1["image_shift_pixel_x"] = im1["tile_x_offset"]/im1["tile_pixel_size"]
+    im1["image_shift_pixel_y"] = im1["tile_y_offset"]/im1["tile_pixel_size"]
+    im2["image_shift_pixel_x"] = im2["tile_x_offset"]/im2["tile_pixel_size"]
+    im2["image_shift_pixel_y"] = im2["tile_y_offset"]/im2["tile_pixel_size"]
+
+    if diagnostic:
+        fig, axs = plt.subplots(4,4,figsize=(15,15))
+    with mrcfile.open(im1["tile_filename"]) as mrc: 
+            reference = np.copy(np.flip(mrc.data[0],axis=0))
+    with mrcfile.open(im2["tile_filename"]) as mrc: 
+            moving = np.copy(np.flip(mrc.data[0],axis=0))
+    if diagnostic:
+        axs[2][1].imshow(moving,cmap="Greys_r")
[…]

### 2022-03-08 manuscript.tex
Merge branch 'main' of github.com:jojoelfe/deco_lace_template_matching_manuscript into main [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/4e9e2eda33d911a965d898af77d32172b9a3ec9d.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/4e9e2eda33d911a965d898af77d32172b9a3ec9d/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1953050404

@@
 This manuscript
-(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/287b9950fc2bff7878d36aa1cbf2cb7f2082f798/}{permalink})
+(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/4e9e2eda33d911a965d898af77d32172b9a3ec9d/}{permalink})
 was automatically generated
-from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/287b9950fc2bff7878d36aa1cbf2cb7f2082f798}{jojoelfe/deco\_lace\_template\_matching\_manuscript@287b995}
-on March 7, 2022.
+from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/4e9e2eda33d911a965d898af77d32172b9a3ec9d}{jojoelfe/deco\_lace\_template\_matching\_manuscript@4e9e2ed}
+on March 8, 2022.
 

### 2022-03-09 content/code/refine_montage_by_cc.py
Work on creating a nicer montage

@@ -12,14 +12,28 @@ import numpy as np
 from pathlib import Path
 import utils
 from skimage import transform
+from scipy import optimize
+import logging
+from rich.logging import RichHandler
+import pandas as pd
+import assemble_montage_utils
+
+
+FORMAT = "%(message)s"
+logging.basicConfig(
+    level="NOTSET", format=FORMAT, datefmt="[%X]", handlers=[RichHandler()]
+)
 
 
 def calculate_crosscorrelations(tile_data,num_proc=20):
+    logger = logging.getLogger("ref_mon")
+
     points = np.array([(a["tile_x_offset"]/a["tile_pixel_size"],a["tile_y_offset"]/a["tile_pixel_size"]) for i,a in tile_data.iterrows()])
     kd_tree = KDTree(points)
 
     pairs = kd_tree.query_pairs(r=3000)
     row_pairs = [(tile_data.iloc[a[0]],tile_data.iloc[a[1]]) for a in pairs]
+    logger.info(f"There are {len(points)} tiles and {len(pairs)} pairs")
     pool = multiprocessing.Pool(processes=num_proc)
     shifts = pool.map(determine_shift_by_cc, row_pairs)
     pool.close()
@@ -39,9 +53,9 @@ def determine_shift_by_cc(doubled,diagnostic=False):
     if diagnostic:
         fig, axs = plt.subplots(4,4,figsize=(15,15))
     with mrcfile.open(im1["tile_filename"]) as mrc: 
-            reference = np.copy(np.flip(mrc.data[0],axis=0))
+            reference = np.copy(mrc.data[0])
     with mrcfile.open(im2["tile_filename"]) as mrc: 
-            moving = np.copy(np.flip(mrc.data[0],axis=0))
+            moving = np.copy(mrc.data[0])
     if diagnostic:
         axs[2][1].imshow(moving,cmap="Greys_r")
     diff = (im2['image_shift_pixel_x']-im1['image_shift_pixel_x'],im2['image_shift_pixel_y']-im1['image_shift_pixel_y'])
@@ -54,11 +68,11 @@ def determine_shift_by_cc(doubled,diagnostic=False):
         axs[0][1].imshow(moving,cmap="Greys_r")
  
     with mrcfile.open(im1["tile_mask_filename"]) as mrc: 
-            reference_mask = np.copy(np.flip(mrc.data[0],axis=0))
+            reference_mask = np.copy(mrc.data[0])
             reference_mask.dtype = np.uint8
[…]

### 2022-03-09 manuscript.tex
Work on creating a nicer montage [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/7e5fee3254041c2c66855e84f72b36c476ba1cb0.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/7e5fee3254041c2c66855e84f72b36c476ba1cb0/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1954684852

@@
 This manuscript
-(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/4e9e2eda33d911a965d898af77d32172b9a3ec9d/}{permalink})
+(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/7e5fee3254041c2c66855e84f72b36c476ba1cb0/}{permalink})
 was automatically generated
-from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/4e9e2eda33d911a965d898af77d32172b9a3ec9d}{jojoelfe/deco\_lace\_template\_matching\_manuscript@4e9e2ed}
-on March 8, 2022.
+from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/7e5fee3254041c2c66855e84f72b36c476ba1cb0}{jojoelfe/deco\_lace\_template\_matching\_manuscript@7e5fee3}
+on March 9, 2022.
 

### 2022-03-21 content/code/assemble_matches.py
Changes to montage processing

@@ -1,9 +1,12 @@
+from numpy import byte
 import starfile
 import utils
 from pathlib import Path
+import mrcfile
+import numpy as np
 
 
-montage_directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/initial_assembly/")
+montage_directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/refined_assembly/")
 refine_directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/lamella_refine/")
 assembled_directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/assemble/")
 assembled_directory.mkdir(exist_ok=True,parents=True)
@@ -17,14 +20,43 @@ for (database, name) in utils.dataset_info:
     refine_info["image_filename"] = refine_info["image_filename"].apply(lambda x: x.replace("_1.mrc","_0.mrc"))
 
     # Join the two dataframes
-    info = montage_info["tiles"].merge(refine_info, how="right", left_on="tile_filename", right_on="image_filename")
+    info = montage_info["tiles"].merge(refine_info, how="inner", left_on="tile_filename", right_on="image_filename")
     #print(info.loc[0])
     info["tile_x"] = info["x"]
     info["tile_y"] = info["y"]
     info["x"] = info["tile_x"] + info["tile_x_offset"]
     info["y"] = info["tile_y"] + info["tile_y_offset"]
     info["image_filename"] = montage_info["montage"]["montage_filename"].loc[0]
+    info["pixel_size"] = montage_info["montage"]["montage_pixel_size"].loc[0]
     print(info["template_filename"].unique())
     print(info["image_filename"].unique())
+
+    info["mask_value"] = 0.0
+    info["display"] = False
+    #Check the value of the mask at each match
+    for mask_filename in info["tile_mask_filename"].unique():
+        # Open mask and convert to 0-1 floats
+        if mask_filename == None: 
+            continue
+        with mrcfile.open(mask_filename) as mask:
+            mask_data = np.copy(mask.data[0])
+            mask_data.dtype = np.uint8
+            mask_float = mask_data/255.0
+    #    
+        peak_indices = info.loc[info["tile_mask_filename"] == mask_filename].index.tolist()
+        for i in peak_indices:
+            try:
[…]

### 2022-03-21 content/code/assemble_montage_fff_4.py

@@ -26,5 +26,5 @@ metadata = assemble_montage_utils.create_metadata(selected_micrographs,
                                        IS_to_camera=assemble_montage_utils.IS_to_camera,
                                        output_base=str(directory / 'fff_lamella4'),
                                        mask_suffix="_1_mask.mrc")
-assemble_montage_utils.create_montage(metadata)
+#assemble_montage_utils.create_montage(metadata)
 exit()

### 2022-03-21 content/code/assemble_montage_utils.py

@@ -9,6 +9,8 @@ from skimage import io
 import pandas as pd
 import starfile
 from skimage.util import img_as_uint
+import json
+from scipy.ndimage import binary_erosion
 
 IS_to_camera = np.array([13374,  6053.4,  6394.1,  -13172])
 IS_to_camera.shape = (2,2)
@@ -41,6 +43,8 @@ def create_metadata(expand_data, IS_to_camera, output_base, binning=10, image_su
         'tile_plotted_result_filename': pd.Series(dtype='object'),
         'tile_image_shift_x': pd.Series(dtype='float'),
         'tile_image_shift_y': pd.Series(dtype='float'),
+        'tile_microscope_focus': pd.Series(dtype='float'),
+        'tile_defocus': pd.Series(dtype='float'),
     })
 
 
@@ -96,6 +100,8 @@ def create_metadata(expand_data, IS_to_camera, output_base, binning=10, image_su
         new_entry['tile_y_crop_center'] = item['CROP_CENTER_Y']
         new_entry['tile_image_shift_x'] = item['IMAGE_SHIFT_X']
         new_entry['tile_image_shift_y'] = item['IMAGE_SHIFT_Y']
+        new_entry['tile_microscope_focus'] = json.loads(item['CONTENT_JSON'])["Defocus"]
+        new_entry['tile_defocus'] = (item['DEFOCUS1'] + item['DEFOCUS2'])/2
         matches_dir = Path(item['FILENAME']).parent.parent / 'TemplateMatching' 
         #print(Path(item['FILENAME'][:-6]).name +"*plotted_result*.mrc")
         matches_filenames = list(matches_dir.glob(Path(item['FILENAME'][:-6]).name +"*plotted_result*.mrc"))
@@ -181,6 +187,69 @@ def create_montage(metadata ):
     big /= mask
     big /= np.max(big)
     matches /= np.max(matches)
+    io.imsave(montage_info['montage_filename'],img_as_uint(big),plugin='tifffile')
+    io.imsave(montage_info['matches_montage_filename'],img_as_uint(matches),plugin='tifffile')
+
+def create_montage_bin_after(metadata,erode_mask=0 ):
+
+    montage_info = metadata['montage'].iloc[0]
+
+    montage_dimensions = (montage_info['montage_y_size']*montage_info['montage_binning'], montage_info['montage_x_size']*montage_info['montage_binning'])
[…]

### 2022-03-21 content/code/refine_montage_by_cc.py

@@ -17,15 +17,20 @@ import logging
 from rich.logging import RichHandler
 import pandas as pd
 import assemble_montage_utils
+from skimage import filters
+from functools import partial
+from scipy.ndimage import binary_erosion
 
 
 FORMAT = "%(message)s"
 logging.basicConfig(
     level="NOTSET", format=FORMAT, datefmt="[%X]", handlers=[RichHandler()]
 )
+loggers = [logging.getLogger(name) for name in logging.root.manager.loggerDict]
+for logger in loggers:
+    logger.setLevel(logging.INFO)
 
-
-def calculate_crosscorrelations(tile_data,num_proc=20):
+def calculate_crosscorrelations(tile_data,num_proc=20,erode_mask=0):
     logger = logging.getLogger("ref_mon")
 
     points = np.array([(a["tile_x_offset"]/a["tile_pixel_size"],a["tile_y_offset"]/a["tile_pixel_size"]) for i,a in tile_data.iterrows()])
@@ -35,14 +40,13 @@ def calculate_crosscorrelations(tile_data,num_proc=20):
     row_pairs = [(tile_data.iloc[a[0]],tile_data.iloc[a[1]]) for a in pairs]
     logger.info(f"There are {len(points)} tiles and {len(pairs)} pairs")
     pool = multiprocessing.Pool(processes=num_proc)
-    shifts = pool.map(determine_shift_by_cc, row_pairs)
+    shifts = pool.map(partial(determine_shift_by_cc,erode_mask=erode_mask), row_pairs)
     pool.close()
     pool.join()
-    shifts = np.array(shifts)
-    pairs=np.array(list(pairs))
-    return((pairs,shifts))
+    shifts = pd.DataFrame([a for a in shifts if a is not None])
+    return(shifts)
 
-def determine_shift_by_cc(doubled,diagnostic=False):
+def determine_shift_by_cc(doubled,diagnostic=False,erode_mask=0):
     # Given the infow of two images, calculate the refined relative shifts by crosscorrelation return
     im1, im2 = doubled
     im1["image_shift_pixel_x"] = im1["tile_x_offset"]/im1["tile_pixel_size"]
@@ -54,8 +58,13 @@ def determine_shift_by_cc(doubled,diagnostic=False):
         fig, axs = plt.subplots(4,4,figsize=(15,15))
     with mrcfile.open(im1["tile_filename"]) as mrc: 
             reference = np.copy(mrc.data[0])
[…]

### 2022-03-21 content/code/utils.py

@@ -36,7 +36,7 @@ def get_data_from_db(dataset,get_movement=False):
         df1 = pd.read_sql_query(f"SELECT IMAGE_ASSET_ID,MOVIE_ASSET_ID,IMAGE_ASSETS.FILENAME, MOVIE_ASSETS.FILENAME as movie_filename, CTF_ESTIMATION_ID , ALIGNMENT_ID, IMAGE_ASSETS.PIXEL_SIZE as image_pixel_size, MOVIE_ASSETS.PIXEL_SIZE as movie_pixel_size, IMAGE_ASSETS.X_SIZE, IMAGE_ASSETS.Y_SIZE, IMAGE_ASSETS.ORIGINAL_X_SIZE, IMAGE_ASSETS.ORIGINAL_Y_SIZE, IMAGE_ASSETS.CROP_CENTER_X, IMAGE_ASSETS.CROP_CENTER_Y  FROM IMAGE_ASSETS INNER JOIN MOVIE_ASSETS ON MOVIE_ASSETS.MOVIE_ASSET_ID == IMAGE_ASSETS.PARENT_MOVIE_ID", con)
         df2 = pd.read_sql_query("SELECT CTF_ESTIMATION_ID,DEFOCUS1,DEFOCUS2,DEFOCUS_ANGLE,OUTPUT_DIAGNOSTIC_FILE,SCORE, DETECTED_RING_RESOLUTION FROM ESTIMATED_CTF_PARAMETERS",con)
         selected_micrographs = pd.merge(df1,df2,on="CTF_ESTIMATION_ID")
-        df3 = pd.read_sql_query(f"SELECT MOVIE_ASSET_ID,IMAGE_SHIFT_X, IMAGE_SHIFT_Y FROM MOVIE_ASSETS_METADATA",con)
+        df3 = pd.read_sql_query(f"SELECT MOVIE_ASSET_ID,IMAGE_SHIFT_X, IMAGE_SHIFT_Y, CONTENT_JSON FROM MOVIE_ASSETS_METADATA",con)
         selected_micrographs = pd.merge(selected_micrographs,df3,on="MOVIE_ASSET_ID")
         selected_micrographs["TOTAL_MOVEMENT"] = 0
         if get_movement:

### 2022-03-21 manuscript.tex
Changes to montage processing [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/51095028c49de7986e39cc0ee234d0f6cdbddee1.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/51095028c49de7986e39cc0ee234d0f6cdbddee1/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2017398572

@@
 This manuscript
-(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/7e5fee3254041c2c66855e84f72b36c476ba1cb0/}{permalink})
+(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/51095028c49de7986e39cc0ee234d0f6cdbddee1/}{permalink})
 was automatically generated
-from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/7e5fee3254041c2c66855e84f72b36c476ba1cb0}{jojoelfe/deco\_lace\_template\_matching\_manuscript@7e5fee3}
-on March 9, 2022.
+from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/51095028c49de7986e39cc0ee234d0f6cdbddee1}{jojoelfe/deco\_lace\_template\_matching\_manuscript@5109502}
+on March 21, 2022.
 

### 2022-03-24 content/code/assemble_matches.py
More processing

@@ -10,17 +10,22 @@ montage_directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing
 refine_directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/lamella_refine/")
 assembled_directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/assemble/")
 assembled_directory.mkdir(exist_ok=True,parents=True)
-for (database, name) in utils.dataset_info:
+for (database, name) in utils.dataset_info[5:6]:
     print(name)
     montage_info = starfile.read(montage_directory / f"{name}.star")
     refine_info = starfile.read(refine_directory / f"{name}_refine.star")
     print(len(refine_info.index))
+    print(len(montage_info["tiles"].index))
     # Make sure both sides use image 0
     montage_info["tiles"]["tile_filename"] = montage_info["tiles"]["tile_filename"].apply(lambda x: x.replace("_1.mrc","_0.mrc"))
     refine_info["image_filename"] = refine_info["image_filename"].apply(lambda x: x.replace("_1.mrc","_0.mrc"))
-
+    montage_info["tiles"]["tile_filename"] = montage_info["tiles"]["tile_filename"].apply(lambda x: x.replace("_2.mrc","_0.mrc"))
+    refine_info["image_filename"] = refine_info["image_filename"].apply(lambda x: x.replace("_2.mrc","_0.mrc"))
+    montage_info["tiles"]["tile_filename"] = montage_info["tiles"]["tile_filename"].apply(lambda x: x.replace("_3.mrc","_0.mrc"))
+    refine_info["image_filename"] = refine_info["image_filename"].apply(lambda x: x.replace("_3.mrc","_0.mrc"))
     # Join the two dataframes
     info = montage_info["tiles"].merge(refine_info, how="inner", left_on="tile_filename", right_on="image_filename")
+    print(len(info.index))
     #print(info.loc[0])
     info["tile_x"] = info["x"]
     info["tile_y"] = info["y"]

### 2022-03-24 content/code/assemble_montage_utils.py

@@ -1,4 +1,5 @@
 from curses import meta
+from selectors import EpollSelector
 import matplotlib.pyplot as plt
 import latexipy as lp
 import numpy as np
@@ -190,10 +191,15 @@ def create_montage(metadata ):
     io.imsave(montage_info['montage_filename'],img_as_uint(big),plugin='tifffile')
     io.imsave(montage_info['matches_montage_filename'],img_as_uint(matches),plugin='tifffile')
 
-def create_montage_bin_after(metadata,erode_mask=0 ):
+def create_montage_bin_after(metadata,erode_mask=0,gain=None,blend=True ):
 
     montage_info = metadata['montage'].iloc[0]
-
+    if gain is not None:
+        with mrcfile.open(gain) as mrc:
+            gain_data = mrc.data.copy()
+        gain_data[gain_data < 0.5] = 1.0
+    else:
+        gain_data = None
     montage_dimensions = (montage_info['montage_y_size']*montage_info['montage_binning'], montage_info['montage_x_size']*montage_info['montage_binning'])
     montage_binned_dimension = (montage_info['montage_y_size'], montage_info['montage_x_size'])
     big = np.zeros(montage_dimensions,dtype=float)
@@ -209,7 +215,19 @@ def create_montage_bin_after(metadata,erode_mask=0 ):
             tile_dimensions = (int(tile_data.shape[0]),int(tile_data.shape[1]))
             tile_data *= tile["tile_intensity_correction"]
             #tile_data = resize(tile_data,tile_dimensions,anti_aliasing=True)
+        if tile_data.shape[1] > gain_data.shape[1] or tile_data.shape[0] > gain_data.shape[0]:
+            print("Skipping tile as it is larger than the gain")
+            continue
+        x_offset = (gain_data.shape[1]-tile_data.shape[1])//2
+        y_offset = (gain_data.shape[0]-tile_data.shape[0])//2
+        print(tile_data.mean())
         
+        pers_gain = gain_data[y_offset:y_offset+tile_data.shape[0],x_offset:x_offset+tile_data.shape[1]]
+        print(pers_gain.mean())
+        tile_data /= pers_gain
+        print(tile_data.mean())
+        print(tile_data.dtype)
+        print(pers_gain.dtype)
         with mrcfile.open(tile['tile_mask_filename']) as mrc: 
             mask_data = np.copy(mrc.data[0])
             mask_data.dtype = np.uint8
[…]

### 2022-03-24 content/code/plot_average_images_plus_matches.py

@@ -1,0 +1,171 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import latexipy as lp
+import json
+from pathlib import Path
+import logging
+from rich.logging import RichHandler
+import mrcfile
+
+FORMAT = "%(message)s"
+logging.basicConfig(
+    level="NOTSET", format=FORMAT, datefmt="[%X]", handlers=[RichHandler()]
+)
+loggers = [logging.getLogger(name) for name in logging.root.manager.loggerDict]
+for logger in loggers:
+    logger.setLevel(logging.INFO)
+
+import utils
+
+intensity = {}
+gain_average = {}
+all_average = {}
+selected_micrographs = {}
+
+exclude = {
+    "euc_lamella1": [49,82,86,89,126,130],
+    "euc_lamella2": [59,61,62,81],
+    "euc_lamella3": [49,61,78],
+    "euc_lamella4": [25],
+    "fff_lamella1": [2,23,24,33,34],
+    "fff_lamella2": [7,8,9,521,522,523,524,543,544,545,546],
+    "fff_lamella3": [8,9,10,11,39,515,516,519,520],
+    "fff_lamella4": [7,13]
+
+}
+
+output_dir = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/averages/")
+output_dir.mkdir(exist_ok=True, parents=True)
+max_x = {}
+max_y = {}
+for dataset, dataset_name in utils.dataset_info:
+    logging.info(dataset)
+    selected_micrographs[dataset] = utils.get_data_from_db(dataset)
+    with open(Path(dataset).stem +"_thickness.json","r") as fp:
+        thickness_data = json.load(fp)
+    selected_micrographs[dataset]["thickness"] = 0
+    for i, micrograph in selected_micrographs[dataset].iterrows():
+        if micrograph['movie_filename'] in thickness_data:
+            selected_micrographs[dataset].loc[i,"thickness"] = thickness_data[micrograph['movie_filename']]
+    if dataset_name.startswith("euc"):
+        selected_micrographs[dataset] = selected_micrographs[dataset].loc[
+            (selected_micrographs[dataset]['X_SIZE'] > 3200) &
+            (selected_micrographs[dataset]['X_SIZE'] < 3360) &
+            (selected_micrographs[dataset]['Y_SIZE'] > 3200) &
+            (selected_micrographs[dataset]['Y_SIZE'] < 3360)]
[…]

### 2022-03-24 content/code/plot_matches_on_average.py

@@ -1,0 +1,62 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import latexipy as lp
+import json
+from pathlib import Path
+import logging
+from rich.logging import RichHandler
+import mrcfile
+import starfile
+import matplotlib
+
+FORMAT = "%(message)s"
+logging.basicConfig(
+    level="NOTSET", format=FORMAT, datefmt="[%X]", handlers=[RichHandler()]
+)
+loggers = [logging.getLogger(name) for name in logging.root.manager.loggerDict]
+for logger in loggers:
+    logger.setLevel(logging.INFO)
+
+import utils
+
+refine_input_dir = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/assemble/")
+average_input_dir = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/averages/")
+image = {}
+matches = {}
+for dataset, dataset_name in utils.dataset_info:
+    logger.info(dataset_name)
+    matches[dataset] = starfile.read(refine_input_dir / f"{dataset_name}_assembled_matches.star")
+    if dataset_name.startswith("euc"):
+        matches[dataset] = matches[dataset].loc[
+                (matches[dataset]['tile_x_size'] > 3200) &
+                (matches[dataset]['tile_x_size'] < 3360) &
+                (matches[dataset]['tile_y_size'] > 3200) &
+                (matches[dataset]['tile_y_size'] < 3360)]
+    else:
+        matches[dataset] = matches[dataset].loc[
+                (matches[dataset]['tile_x_size'] > 3350) &
+                (matches[dataset]['tile_x_size'] < 3510) &
+                (matches[dataset]['tile_y_size'] > 3320) &
+                (matches[dataset]['tile_y_size'] < 3480)]
+    with mrcfile.open(average_input_dir / f"{dataset_name}_av.mrc") as mrc:
+        image[dataset] = mrc.data.copy()
+    u = dataset
+    
+
+
+
+
+lp.latexify()
+with lp.figure("micrograph_with_matches",size=lp.figure_size(ratio=0.4,doc_width_pt=1000),tight_layout=False):
+    fig, axs = plt.subplots(2,4,sharey=True,sharex=True,constrained_layout=True)
+    axs = axs.flatten()
+    for i, dataset in enumerate(utils.datasets):
+
+        axs[i].set_title(utils.dataset_names[i])
[…]

### 2022-03-24 content/code/refine_montage_by_cc.py

@@ -198,7 +198,7 @@ pycistem.set_cistem_path("/groups/elferich/cisTEM/build/refine_template_tests_In
 input_directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/initial_assembly/")
 output_directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/refined_assembly/")
 output_directory.mkdir(exist_ok=True,parents=True)
-for (database, name) in utils.dataset_info[:4]:
+for (database, name) in utils.dataset_info[-4:]:
     logger.info(f"Working on {name}")
     montage_data = starfile.read(input_directory/f"{name}.star")
     tile_data = montage_data["tiles"]
@@ -209,6 +209,9 @@ for (database, name) in utils.dataset_info[:4]:
     erode_mask = 0 
     if name.startswith("euc"):
         erode_mask = 100
+        logger.info("Eroding mask by 100 pixels")
+    else: 
+        erode_mask = 10
         logger.info("Eroding mask by 100 pixels")
     #shifts = calculate_crosscorrelations(tile_data,num_proc=20,erode_mask=erode_mask)
     #starfile.write(shifts,output_directory/f"{name}_shifts.star",overwrite=True)
@@ -252,4 +255,4 @@ for (database, name) in utils.dataset_info[:4]:
         "tiles": tile_data
     }
     starfile.write(results,output_directory/f"{name}.star",overwrite=True)
-    assemble_montage_utils.create_montage_bin_after(results,erode_mask=erode_mask)
+    assemble_montage_utils.create_montage_bin_after(results,erode_mask=erode_mask,gain="/scratch/bern/elferich/deco_lace_manuscript_processing/averages/fff_gain.mrc",blend=True)

### 2022-03-24 manuscript.tex
More processing [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/5ab70871e48b8aa4babdd6e438d9db2fb1a1092a.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/5ab70871e48b8aa4babdd6e438d9db2fb1a1092a/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2035868531

--- 2022-03-09 manuscript.tex
@@
 This manuscript
-(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/7e5fee3254041c2c66855e84f72b36c476ba1cb0/}{permalink})
+(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/5ab70871e48b8aa4babdd6e438d9db2fb1a1092a/}{permalink})
 was automatically generated
-from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/7e5fee3254041c2c66855e84f72b36c476ba1cb0}{jojoelfe/deco\_lace\_template\_matching\_manuscript@7e5fee3}
-on March 9, 2022.
+from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/5ab70871e48b8aa4babdd6e438d9db2fb1a1092a}{jojoelfe/deco\_lace\_template\_matching\_manuscript@5ab7087}
+on March 24, 2022.
 

### 2022-03-28 content/code/plot_average_images_plus_matches.py
Image processing

@@ -118,7 +118,20 @@ for dataset, dataset_name in utils.dataset_info:
 gain /= gain.mean()
 with mrcfile.new(output_dir / f"fff_gain.mrc", overwrite=True) as mrc:
     mrc.set_data(np.float32(gain))
+max_x_euc = max([max_x[k] for k in max_x if k.startswith("euc")])
+max_y_euc = max([max_y[k] for k in max_y if k.startswith("euc")])
+gain = np.zeros((max_y_euc,max_x_euc))
+for dataset, dataset_name in utils.dataset_info:
     
+    if dataset_name.startswith("euc"):
+        with mrcfile.open(output_dir / f"{dataset_name}_av_gain.mrc") as mrc:
+            data = mrc.data
+        x_offset =int( (max_x_euc-data.shape[1])/2)
+        y_offset = int((max_y_euc-data.shape[0])/2)
+        gain[y_offset:y_offset+data.shape[0],x_offset:x_offset+data.shape[1]] += data
+gain /= gain.mean()
+with mrcfile.new(output_dir / f"euc_gain.mrc", overwrite=True) as mrc:
+    mrc.set_data(np.float32(gain))
 
 lp.latexify()
 with lp.figure("averaged_images",size=lp.figure_size(ratio=0.5,doc_width_pt=500),tight_layout=False):

### 2022-03-28 content/code/refine_montage_by_cc_it2.py

@@ -1,0 +1,263 @@
+from pyexpat.errors import XML_ERROR_INCORRECT_ENCODING
+import numpy as np
+import starfile
+from scipy.spatial import KDTree
+import multiprocessing
+from skimage.registration._masked_phase_cross_correlation import cross_correlate_masked
+import mrcfile
+import matplotlib.pyplot as plt
+from scipy import ndimage as ndi
+import pycistem
+import numpy as np
+from pathlib import Path
+import utils
+from skimage import transform
+from scipy import optimize
+import logging
+from rich.logging import RichHandler
+import pandas as pd
+import assemble_montage_utils
+from skimage import filters
+from functools import partial
+from scipy.ndimage import binary_erosion
+
+
+FORMAT = "%(message)s"
+logging.basicConfig(
+    level="NOTSET", format=FORMAT, datefmt="[%X]", handlers=[RichHandler()]
+)
+loggers = [logging.getLogger(name) for name in logging.root.manager.loggerDict]
+for logger in loggers:
+    logger.setLevel(logging.INFO)
+
+def calculate_crosscorrelations(tile_data,num_proc=20,erode_mask=0):
+    logger = logging.getLogger("ref_mon")
+
+    points = np.array([(a["tile_x_offset"]/a["tile_pixel_size"],a["tile_y_offset"]/a["tile_pixel_size"]) for i,a in tile_data.iterrows()])
+    kd_tree = KDTree(points)
+
+    pairs = kd_tree.query_pairs(r=3000)
+    row_pairs = [(tile_data.iloc[a[0]],tile_data.iloc[a[1]]) for a in pairs]
+    logger.info(f"There are {len(points)} tiles and {len(pairs)} pairs")
+    pool = multiprocessing.Pool(processes=num_proc)
+    shifts = pool.map(partial(determine_shift_by_cc,erode_mask=erode_mask), row_pairs)
+    pool.close()
+    pool.join()
+    shifts = pd.DataFrame([a for a in shifts if a is not None])
+    return(shifts)
+
+def determine_shift_by_cc(doubled,diagnostic=False,erode_mask=0):
+    # Given the infow of two images, calculate the refined relative shifts by crosscorrelation return
+    im1, im2 = doubled
+    im1["image_shift_pixel_x"] = im1["tile_x_offset"]/im1["tile_pixel_size"]
+    im1["image_shift_pixel_y"] = im1["tile_y_offset"]/im1["tile_pixel_size"]
[…]

### 2022-03-28 manuscript.tex
Image processing [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a352115c27ccb3b7fa2977015e71c3c7dbb4f954.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a352115c27ccb3b7fa2977015e71c3c7dbb4f954/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2052830940

--- 2022-03-09 manuscript.tex
@@
 This manuscript
-(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/7e5fee3254041c2c66855e84f72b36c476ba1cb0/}{permalink})
+(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/a352115c27ccb3b7fa2977015e71c3c7dbb4f954/}{permalink})
 was automatically generated
-from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/7e5fee3254041c2c66855e84f72b36c476ba1cb0}{jojoelfe/deco\_lace\_template\_matching\_manuscript@7e5fee3}
-on March 9, 2022.
+from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/a352115c27ccb3b7fa2977015e71c3c7dbb4f954}{jojoelfe/deco\_lace\_template\_matching\_manuscript@a352115}
+on March 28, 2022.
 

### 2022-03-29 content/code/assemble_matches.py
Material for figures

@@ -6,13 +6,13 @@ import mrcfile
 import numpy as np
 
 
-montage_directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/refined_assembly/")
+montage_directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/refined_assembly_it2/")
 refine_directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/lamella_refine/")
 assembled_directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/assemble/")
 assembled_directory.mkdir(exist_ok=True,parents=True)
-for (database, name) in utils.dataset_info[5:6]:
+for (database, name) in utils.dataset_info:
     print(name)
-    montage_info = starfile.read(montage_directory / f"{name}.star")
+    montage_info = starfile.read(montage_directory / f"{name}_t2.star")
     refine_info = starfile.read(refine_directory / f"{name}_refine.star")
     print(len(refine_info.index))
     print(len(montage_info["tiles"].index))

### 2022-03-29 content/code/assemble_montage_utils.py

@@ -191,13 +191,14 @@ def create_montage(metadata ):
     io.imsave(montage_info['montage_filename'],img_as_uint(big),plugin='tifffile')
     io.imsave(montage_info['matches_montage_filename'],img_as_uint(matches),plugin='tifffile')
 
-def create_montage_bin_after(metadata,erode_mask=0,gain=None,blend=True ):
+def create_montage_bin_after(metadata,erode_mask=0,gain=None,blend=True,gain_mult=1.0 ):
 
     montage_info = metadata['montage'].iloc[0]
     if gain is not None:
         with mrcfile.open(gain) as mrc:
             gain_data = mrc.data.copy()
         gain_data[gain_data < 0.5] = 1.0
+        gain_data *= gain_mult
     else:
         gain_data = None
     montage_dimensions = (montage_info['montage_y_size']*montage_info['montage_binning'], montage_info['montage_x_size']*montage_info['montage_binning'])

### 2022-03-29 content/code/plot_average_images_plus_matches.py

@@ -19,6 +19,7 @@ import utils
 
 intensity = {}
 gain_average = {}
+gain_all_average = {}
 all_average = {}
 selected_micrographs = {}
 
@@ -64,6 +65,7 @@ for dataset, dataset_name in utils.dataset_info:
     max_x[dataset_name] = max_xsize
     max_y[dataset_name] = max_ysize
     gain_average[dataset] = np.zeros((max_ysize,max_xsize))
+    gain_all_average[dataset] = np.zeros((max_ysize,max_xsize))
     all_average[dataset] = np.zeros((max_ysize,max_xsize))
     logging.info(f"Average image has shape {gain_average[dataset].shape}")
 
@@ -91,9 +93,12 @@ for dataset, dataset_name in utils.dataset_info:
             gain_counter += 1
             gain_average[dataset][y_offset:y_offset+data.shape[0],
                                     x_offset:x_offset+data.shape[1]] += data
-            with mrcfile.new(output_dir / f"diag_{dataset_name}_av_{i:03}.mrc", overwrite=True) as mrc:
-                mrc.set_data(data)
-            print(f"diag_{dataset_name}_av_{i:03}.mrc",np.mean(data),np.sum(mask_data))
+            
+            #with mrcfile.new(output_dir / f"diag_{dataset_name}_av_{i:03}.mrc", overwrite=True) as mrc:
+            #    mrc.set_data(data)
+            #print(f"diag_{dataset_name}_av_{i:03}.mrc",np.mean(data),np.sum(mask_data))
+        gain_all_average[dataset][y_offset:y_offset+data.shape[0],
+                                    x_offset:x_offset+data.shape[1]] += data
         data *= mask_data
         all_average[dataset][y_offset:y_offset+data.shape[0],
                                 x_offset:x_offset+data.shape[1]] += data
@@ -103,10 +108,13 @@ for dataset, dataset_name in utils.dataset_info:
         mrc.set_data(np.float32(all_average[dataset]))
     with mrcfile.new(output_dir / f"{dataset_name}_av_gain.mrc", overwrite=True) as mrc:
         mrc.set_data(np.float32(gain_average[dataset]))
+    with mrcfile.new(output_dir / f"{dataset_name}_av_gain_all.mrc", overwrite=True) as mrc:
[…]

### 2022-03-29 content/code/refine_montage_by_cc.py

@@ -22,6 +22,13 @@ from functools import partial
 from scipy.ndimage import binary_erosion
 
 
+# Original lowpass
+# filters.butterworth(reference,cutoff_frequency_ratio=0.05,order=4.0,
+# high_pass=False)
+# Changing to 0.02 for t2
+
+ver = "_t2"
+
 FORMAT = "%(message)s"
 logging.basicConfig(
     level="NOTSET", format=FORMAT, datefmt="[%X]", handlers=[RichHandler()]
@@ -58,12 +65,12 @@ def determine_shift_by_cc(doubled,diagnostic=False,erode_mask=0):
         fig, axs = plt.subplots(4,4,figsize=(15,15))
     with mrcfile.open(im1["tile_filename"]) as mrc: 
             reference = np.copy(mrc.data[0])
-            reference = filters.butterworth(reference,cutoff_frequency_ratio=0.05,order=4.0, high_pass=False)
+            reference = filters.butterworth(reference,cutoff_frequency_ratio=0.02,order=4.0, high_pass=False)
     with mrcfile.open(im2["tile_filename"]) as mrc: 
             moving = np.copy(mrc.data[0])
             if diagnostic:
                 axs[2][0].imshow(moving,cmap="Greys_r")
-            moving = filters.butterworth(moving,cutoff_frequency_ratio=0.05,order=4.0, high_pass=False)
+            moving = filters.butterworth(moving,cutoff_frequency_ratio=0.02,order=4.0, high_pass=False)
 
     if diagnostic:
         axs[2][1].imshow(moving,cmap="Greys_r")
@@ -198,7 +205,7 @@ pycistem.set_cistem_path("/groups/elferich/cisTEM/build/refine_template_tests_In
 input_directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/initial_assembly/")
 output_directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/refined_assembly/")
 output_directory.mkdir(exist_ok=True,parents=True)
-for (database, name) in utils.dataset_info[-4:]:
+for (database, name) in utils.dataset_info:
     logger.info(f"Working on {name}")
     montage_data = starfile.read(input_directory/f"{name}.star")
     tile_data = montage_data["tiles"]
@@ -213,9 +220,9 @@ for (database, name) in utils.dataset_info[-4:]:
     else: 
         erode_mask = 10
         logger.info("Eroding mask by 100 pixels")
[…]

### 2022-03-29 content/code/refine_montage_by_cc_it2.py

@@ -21,7 +21,7 @@ from skimage import filters
 from functools import partial
 from scipy.ndimage import binary_erosion
 
-
+ver = "_t2"
 FORMAT = "%(message)s"
 logging.basicConfig(
     level="NOTSET", format=FORMAT, datefmt="[%X]", handlers=[RichHandler()]
@@ -58,12 +58,12 @@ def determine_shift_by_cc(doubled,diagnostic=False,erode_mask=0):
         fig, axs = plt.subplots(4,4,figsize=(15,15))
     with mrcfile.open(im1["tile_filename"]) as mrc: 
             reference = np.copy(mrc.data[0])
-            reference = filters.butterworth(reference,cutoff_frequency_ratio=0.05,order=4.0, high_pass=False)
+            reference = filters.butterworth(reference,cutoff_frequency_ratio=0.02,order=4.0, high_pass=False)
     with mrcfile.open(im2["tile_filename"]) as mrc: 
             moving = np.copy(mrc.data[0])
             if diagnostic:
                 axs[2][0].imshow(moving,cmap="Greys_r")
-            moving = filters.butterworth(moving,cutoff_frequency_ratio=0.05,order=4.0, high_pass=False)
+            moving = filters.butterworth(moving,cutoff_frequency_ratio=0.02,order=4.0, high_pass=False)
 
     if diagnostic:
         axs[2][1].imshow(moving,cmap="Greys_r")
@@ -200,7 +200,7 @@ output_directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/
 output_directory.mkdir(exist_ok=True,parents=True)
 for (database, name) in utils.dataset_info:
     logger.info(f"Working on {name}")
-    montage_data = starfile.read(input_directory/f"{name}.star")
+    montage_data = starfile.read(input_directory/f"{name}{ver}.star")
     tile_data = montage_data["tiles"]
     # Set index of tile_data to tile_file_name
     tile_data["filename_index"] = tile_data["tile_filename"]
@@ -209,12 +209,12 @@ for (database, name) in utils.dataset_info:
     erode_mask = 0 
     if name.startswith("euc"):
         erode_mask = 100
-        logger.info("Eroding mask by 100 pixels")
+        logger.info("Eroding mask by 130 pixels")
     else: 
         erode_mask = 50
-        logger.info("Eroding mask by 100 pixels")
+        logger.info("Eroding mask by 90 pixels")
[…]

### 2022-03-29 figures/approach.tex
Some minor writing [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/0a724b0da1586e2992e709189796c245a3f07ccf.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/0a724b0da1586e2992e709189796c245a3f07ccf/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2060706992

@@
     \setlist{nosep,leftmargin=*}
-    \newcommand{\figwidth}{25cm} 
-    \newcommand{\figheight}{10cm} 
+    \newcommand{\figwidth}{20cm} 
+    \newcommand{\figheight}{15cm} 
     \newcommand{\fontselect}{\large\bf} 
@@
       graphicNode/.style={anchor=north west, below right=0cm and 0cm of anchor}, 
-      titleNode/.style={anchor=south west, above right=0cm and 0cm of anchor}, 
       mnNode/.style={below left=0.1cm and 0cm of rect.south east, font=\fontannot},
@@
 
-    \node (anchor) at (0.5,9.35) {}; 
+    \node (anchor) at (0.5,14.35) {}; 
 \node[labelNode] {A};
 \node[graphicNode] {\includegraphics[width=5cm]{content/graphics/approach/approach.png}};
+\draw [densely dotted, red,thick] (3,14.5) -- (3,10);
+\draw [densely dotted, red,thick] (3,9.2) -- (3,6.4);
 
-\node (anchor) at (6.0,9.35) {}; 
+\tikzset{dimen/.style={<->,>=latex,thin,every rectangle node/.style={above right=0.2cm and -0.3cm,fill=white,midway,font=\sffamily}}}
+
+\draw (3.55,10.4) -- ++(0,1.5) coordinate (D1) -- +(0,5pt);
+\draw (4.15,10.4) -- ++(0,1.5) coordinate (D2) -- +(0,5pt);
+\draw [dimen] (D1) -- (D2) node {$D_{Beam}$};
+
+\draw [->, very thick] (3,10) -- ++(0.5,-0.2)  coordinate (S1) node[midway,below left] {$IS_X$} ;
+\draw [->, very thick] (S1) -- (3.85,10.4) node[midway,below right] {$IS_Y$};
+
+\node (anchor) at (6.0,14.35) {}; 
 \node[labelNode] {B};
@@
 % Place nodes
-\node [block] (init) at (8.0,8.35) {\textbf{START} \\ Collect overview image};
+\node [block] (init) at (8.0,13.35) {\textbf{START} \\ Collect overview image};
 \node [block, below = 0.3cm of init.south] (identify) {Setup hexagonal grid covering lamella area};
@@
 
-\node (anchor) at (17.0,9.35) {}; 
-\node[labelNode] {Q};
-\node[graphicNode] {\includegraphics[width=5cm]{content/images/ac_strategy.png}};
+\node (anchor) at (11.5,14.35) {}; 
+\node[labelNode] {C};
+\node[graphicNode] {\includegraphics[width=8cm]{content/images/ac_strategy.png}};
 \iftoggle{draft}{\node [redAnchorNode] {};};
 
-\node (anchor) at (11.5,9.35) {}; 
+\node (anchor) at (0.5,4.5) {}; 
 \node[labelNode] {C};
-\node[titleNode] {Eucentric Focus};
-\node[graphicNode] {\includegraphics[height=3.0cm]{content/images/fringebeam.png}};
+\node[graphicNode] (euc) {\includegraphics[height=4.0cm]{content/images/fringebeam.png}};
+\node[above = 0cm and 0cm of euc.north] {Eucentric Focus};
+
 \iftoggle{draft}{\node [redAnchorNode] {};};
 
-\node (anchor) at (15,9.35) {}; 
+\node (anchor) at (5.5,4.5) {}; 
 \node[labelNode] {D};
-\node[titleNode] {Fringe-free Focus};
-\node[graphicNode] {\includegraphics[height=3.0cm]{content/images/nofringebeam.png}};
+\node[graphicNode] (fff) {\includegraphics[height=4.0cm]{content/images/nofringebeam.png}};
+\node[above = 0cm and 0cm of fff.north] {Fringe-free Focus};
 \iftoggle{draft}{\node [redAnchorNode] {};};
 
-\node (anchor) at (11.5,4.85) {}; 
+\node (anchor) at (10.5,4.5) {}; 
 \node[labelNode] {E};
-\node[graphicNode] {\includegraphics[height=4.3cm]{content/code/img/defocusplot.pdf}};
+\node[anchor=north west, below right=-0.5cm and 0cm of anchor] {\includegraphics[height=4.8cm]{content/code/img/defocusplot.pdf}};
 \iftoggle{draft}{\node [redAnchorNode] {};};

### 2022-03-29 figures/initmatching2.tex
Workflow figure [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a4570afcb2725b9980fa97358516050b0a2697d3.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a4570afcb2725b9980fa97358516050b0a2697d3/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1925656087
Some minor writing [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/0a724b0da1586e2992e709189796c245a3f0

--- 2022-03-03 figures/example-figure3.tex
@@
     \setlist{nosep,leftmargin=*}
-    \newcommand{\figwidth}{16.5cm} 
+    \newcommand{\figwidth}{13cm} 
     \newcommand{\figheight}{9cm} 
@@
 \node[labelNode] {A};
-\node[graphicNode] {\includegraphics[width=7.5cm]{content/code/img/movement_vs_bs_plot.pdf}};
-\iftoggle{draft}{\node [redAnchorNode] {};};
-
-\node (anchor) at (8.5,8.35) {}; 
-\node[labelNode] {B};
-\node[graphicNode] {\includegraphics[width=7.5cm]{content/code/img/thickness_by_intensity_vs_bs_plot.pdf}};
+\node[graphicNode] {\includegraphics[width=12cm]{content/code/img/initial_map_match.pdf}};
 \iftoggle{draft}{\node [redAnchorNode] {};};

### 2022-03-29 manuscript.tex
Some minor writing [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/0a724b0da1586e2992e709189796c245a3f07ccf.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/0a724b0da1586e2992e709189796c245a3f07ccf/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2060706992

@@
 \linenumbers
+\usepackage{cleveref}
 
@@
 This manuscript
-(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/a352115c27ccb3b7fa2977015e71c3c7dbb4f954/}{permalink})
+(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/0a724b0da1586e2992e709189796c245a3f07ccf/}{permalink})
 was automatically generated
-from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/a352115c27ccb3b7fa2977015e71c3c7dbb4f954}{jojoelfe/deco\_lace\_template\_matching\_manuscript@a352115}
-on March 28, 2022.
+from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/0a724b0da1586e2992e709189796c245a3f07ccf}{jojoelfe/deco\_lace\_template\_matching\_manuscript@0a724b0}
+on March 29, 2022.
 
@@
 
-\hypertarget{d-template-matching-can-be-used-to-find-ribosomal-subunits-in-cryo-fib-thinned-lamella-of-mammalian-cells}{%
-\subsubsection{2D-Template matching can be used to find ribosomal subunits in cryo-FIB thinned lamella of mammalian cells}\label{d-template-matching-can-be-used-to-find-ribosomal-subunits-in-cryo-fib-thinned-lamella-of-mammalian-cells}}
+\hypertarget{dtm-detects-large-ribosomal-subunits-in-cryo-fib-lamella-of-mammalian-cells}{%
+\subsubsection{2DTM detects large ribosomal subunits in cryo-FIB lamella of mammalian cells}\label{dtm-detects-large-ribosomal-subunits-in-cryo-fib-lamella-of-mammalian-cells}}
 
@@
 membrane-organelles, corresponding to the granules and secretory vesicles of
-neutrophils. We then proceeded to acquire micrographs on this lamella with a
-defocus of 0.5-1.0 um, 30 e/A2/s exposure and 1.5 A pixelsize. We manually
-selected multiple locations in the lamella and focused using standard low-dose
-techniques, i.e.~by first ensuring correct focus by imaging a sacrifical area.
-The resoluting micrographs showed no signs of crystalline ice and had thon-rings
-to resolution, indicating successfull vitrification.
+neutrophils (Fig. \ref{fig:initmatching}A). We then proceeded to acquire
+micrographs on this lamella with a defocus of 0.5-1.0 um, 30 e/A2/s exposure and
+1.5 A pixelsize. We manually selected multiple locations in the lamella and
+focused using standard low-dose techniques where focusing is performed on a sacrificial area. The resulting micrographs showed no signs of
+crystalline ice and had Thon-rings to resolution, indicating successful
+vitrification.
 
@@
 scores significantly exceeded the distribution expected from non-signifcant
-matching(Figure 1B). In the resulting scaled maximum-intensity maps, clear peaks
-with SNR thresholds up to 10 were apparent (Figure 1C). By using the criterion
-described by for thresholding potential matches we found that in images of
-cytosolic ompartments we found evidence of 10-500 ribosomes in the imaged areas.
-Notably we found no matches in images that were taken in the nuclear
-compartment. In the cytosolic areas we found a drastically different number of
-matches, In somer areas we found only \textasciitilde{} 50 matches er image area, corresponding
-to a concentration of\ldots, while in another area we found more than 500 matches,
-corresponding to a concentration of \ldots{} .
-
-\hypertarget{cryo-emilia-for-2d-imaging-of-whole-lamella}{%
-\subsubsection{cryo-EMILIA for 2D imaging of whole lamella}\label{cryo-emilia-for-2d-imaging-of-whole-lamella}}
+matching. In the resulting scaled maximum-intensity maps, clear peaks
+with SNR thresholds up to 10 were apparent (Fig. \ref{fig:initmatching2}A). By
+using the criterion described by for thresholding potential matches we found
+that in images of cytosolic compartments we found evidence of 10-500 ribosomes in
+the imaged areas. Notably we found no matches in images that were taken in the
+nuclear compartment. In the cytosolic areas we found a drastically different
+number of matches, In some areas we found only \textasciitilde{} 50 matches er image area, while
+in another area we found more than 500 matches . This ten-fold difference in
+local ribosome concentration , but we realized that current data acquistion
+protocols are limited in that only a small area of the lamella is actually
+imaged and, due to the manual selection of acquision positions based on the
+overview image, might be biased towards cellular region that appear appealing to
+the experimentalist. We therefore set out to collect cryo-EM data for 2DTM from
+mammalian lamella in a high-throughput unbiased fashion.
+\#\#\# DECO-LACE for 2D imaging of whole lamella
 

### 2022-03-30 manuscript.tex
Merge branch 'main' of github.com:jojoelfe/deco_lace_template_matching_manuscript into main [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/2d0a9a5debbbf44b5f9d5797d38db68589012013.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/2d0a9a5debbbf44b5f9d5797d38db68589012013/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2065944123

@@
 This manuscript
-(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/0a724b0da1586e2992e709189796c245a3f07ccf/}{permalink})
+(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/2d0a9a5debbbf44b5f9d5797d38db68589012013/}{permalink})
 was automatically generated
-from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/0a724b0da1586e2992e709189796c245a3f07ccf}{jojoelfe/deco\_lace\_template\_matching\_manuscript@0a724b0}
-on March 29, 2022.
+from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/2d0a9a5debbbf44b5f9d5797d38db68589012013}{jojoelfe/deco\_lace\_template\_matching\_manuscript@2d0a9a5}
+on March 30, 2022.
 

### 2022-04-07 content/code/latexipy/_latexipy.py
Minor figure improvements

@@ -254,7 +254,7 @@ def save_figure(filename, directory, exts, mkdir=True,
     
     if tight_layout:
         try:
-            plt.tight_layout(pad=0.2)
+            plt.tight_layout(pad=0.4, w_pad=0.5, h_pad=1.0)
         except ValueError as e:
             warnings.warn('No figures to save.')
 

### 2022-04-07 content/code/plot_matches_on_average.py

@@ -54,9 +54,16 @@ with lp.figure("micrograph_with_matches",size=lp.figure_size(ratio=0.4,doc_width
 
         axs[i].set_title(utils.dataset_names[i])
         axs[i].imshow(image[dataset],cmap="gray")
+        
         colormap = plt.cm.viridis #or any other colormap
         normalize = matplotlib.colors.Normalize(vmin=7, vmax=10)
-        print(len(matches[dataset]["tile_x"]/1.5))
         s = axs[i].scatter(matches[dataset]["tile_x"]/1.5,matches[dataset]["tile_y"]/1.5,s=1,c=matches[dataset]["peak_value"],cmap=colormap,norm=normalize)
-    plt.colorbar(s)
+        axs[i].set_xlim(0,image[dataset].shape[1])
+        axs[i].set_ylim(image[dataset].shape[0],0)
+        # Hide Axes
+        axs[i].axis('off')
+    # PLace colorbar outside of plot
+    fig.subplots_adjust(right=0.8)
+    cbar_ax = fig.add_axes([0.85, 0.15, 0.05, 0.7])
+    fig.colorbar(s, cax=cbar_ax)
 

### 2022-04-07 content/code/plot_matches_per_tile.py

@@ -1,0 +1,51 @@
+import matplotlib.pyplot as plt
+import latexipy as lp
+import utils
+import starfile
+from pathlib import Path
+import numpy as np
+
+matches_per_tile = []
+
+for dataset, name in utils.dataset_info:
+    assembled_directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/assemble/")
+    data  =  starfile.read(assembled_directory / f"{name}_assembled_matches.star")
+    #Count occurence of tile_filename in data
+    counts = data["tile_filename"].value_counts()
+    counts = counts[counts > 1]
+    matches_per_tile.append(counts)
+
+lp.latexify()
+with lp.figure("matches_per_tile_plot",tight_layout=False):
+    flierprops = dict(marker='o', markerfacecolor='grey', markeredgecolor='grey', markersize=2, linestyle='none')
+
+    fig, axs = plt.subplots(1,2,sharey=True,constrained_layout=True)
+    bp1 = axs[0].boxplot(matches_per_tile[0:4],flierprops=flierprops)
+    bp2 = axs[1].boxplot(matches_per_tile[4:8],flierprops=flierprops)
+    axs[0].set_title("Eucentric Focus")
+    axs[1].set_title("Fringe-free Focus")
+    axs[0].set_xlabel("Lamella")
+    axs[1].set_xlabel("Lamella")
+    axs[0].set_ylabel("Matches per tile")
+    axs[0].set_xticks([1,2,3,4])
+    axs[1].set_xticks([1,2,3,4])
+    axs[0].set_ylim(0,100)
+
+    pos = np.arange(4) + 1
+    upper_labels = [f"n={len(s)}" for s in matches_per_tile[0:4]]
+    weights = ['bold', 'semibold']
+    for tick, label in zip(range(4), axs[0].get_xticklabels()):
+        k = tick % 2
+        axs[0].text(pos[tick], .92, upper_labels[tick],
+                transform=axs[0].get_xaxis_transform(),
+                horizontalalignment='center', size='x-small',
+                )
+    upper_labels = [f"n={len(s)}" for s in matches_per_tile[4:8]]
+    weights = ['bold', 'semibold']
+    for tick, label in zip(range(4), axs[1].get_xticklabels()):
+        k = tick % 2
+        axs[1].text(pos[tick], .92, upper_labels[tick],
+                transform=axs[1].get_xaxis_transform(),
+                horizontalalignment='center', size='x-small',
+                )
+

### 2022-04-07 content/code/plot_num_matches.py

@@ -1,0 +1,26 @@
+import matplotlib.pyplot as plt
+import latexipy as lp
+import utils
+import starfile
+from pathlib import Path
+
+num_matches = []
+
+for dataset, name in utils.dataset_info:
+    assembled_directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/assemble/")
+    data  =  starfile.read(assembled_directory / f"{name}_assembled_matches.star")
+    num_matches.append(len(data[data["display"]]))
+
+lp.latexify()
+with lp.figure("num_matches_plot",tight_layout=True):
+    fig, axs = plt.subplots(1,2,sharey=True)
+    axs[0].bar(range(1,5),num_matches[0:4], align='center', color='grey', edgecolor='black', linewidth=0.5)
+    axs[1].bar(range(1,5),num_matches[4:8], align='center', color='grey', edgecolor='black', linewidth=0.5)
+    axs[0].set_title("Eucentric Focus")
+    axs[1].set_title("Fringe-free Focus")
+    axs[0].set_xlabel("Lamella")
+    axs[1].set_xlabel("Lamella")
+    axs[0].set_ylabel("# Matches")
+    axs[0].set_xticks([1,2,3,4])
+    axs[1].set_xticks([1,2,3,4])
+    plt.tight_layout(pad=0.4, w_pad=0.5, h_pad=1.0)

### 2022-04-07 content/code/plot_scores.py

@@ -1,0 +1,28 @@
+import matplotlib.pyplot as plt
+import latexipy as lp
+import utils
+import starfile
+from pathlib import Path
+
+scores = []
+
+for dataset, name in utils.dataset_info:
+    assembled_directory = Path("/scratch/bern/elferich/deco_lace_manuscript_processing/assemble/")
+    data  =  starfile.read(assembled_directory / f"{name}_assembled_matches.star")
+    scores.append(data[data["display"]]["peak_value"])
+
+lp.latexify()
+with lp.figure("scores_plot",tight_layout=False):
+    flierprops = dict(marker='o', markerfacecolor='grey', markeredgecolor='grey', markersize=2, linestyle='none')
+
+    fig, axs = plt.subplots(1,2,sharey=True,constrained_layout=True)
+    axs[0].boxplot(scores[0:4],flierprops=flierprops)
+    axs[1].boxplot(scores[4:8],flierprops=flierprops)
+    axs[0].set_title("Eucentric Focus")
+    axs[1].set_title("Fringe-free Focus")
+    axs[0].set_xlabel("Lamella")
+    axs[1].set_xlabel("Lamella")
+    axs[0].set_ylabel("Peak height")
+    axs[0].set_xticks([1,2,3,4])
+    axs[1].set_xticks([1,2,3,4])
+

### 2022-04-07 figures/approach.tex
Minor figure [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/56ce938e8d7fb4ca49b0ca90d4ceca7386ae3b0f.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/56ce938e8d7fb4ca49b0ca90d4ceca7386ae3b0f/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2110566960

@@
     \newcommand{\figwidth}{20cm} 
-    \newcommand{\figheight}{15cm} 
+    \newcommand{\figheight}{20cm} 
     \newcommand{\fontselect}{\large\bf} 
@@
 
-    \node (anchor) at (0.5,14.35) {}; 
+    \node (anchor) at (0.5,19.35) {}; 
 \node[labelNode] {A};
 \node[graphicNode] {\includegraphics[width=5cm]{content/graphics/approach/approach.png}};
-\draw [densely dotted, red,thick] (3,14.5) -- (3,10);
-\draw [densely dotted, red,thick] (3,9.2) -- (3,6.4);
+\draw [densely dotted, red,thick] (3,19.5) -- (3,15.0);
+\draw [densely dotted, red,thick] (3,14.2) -- (3,11.4);
 
@@
 
-\draw (3.55,10.4) -- ++(0,1.5) coordinate (D1) -- +(0,5pt);
-\draw (4.15,10.4) -- ++(0,1.5) coordinate (D2) -- +(0,5pt);
+\draw (3.55,15.4) -- ++(0,1.5) coordinate (D1) -- +(0,5pt);
+\draw (4.15,15.4) -- ++(0,1.5) coordinate (D2) -- +(0,5pt);
 \draw [dimen] (D1) -- (D2) node {$D_{Beam}$};
 
-\draw [->, very thick] (3,10) -- ++(0.5,-0.2)  coordinate (S1) node[midway,below left] {$IS_X$} ;
-\draw [->, very thick] (S1) -- (3.85,10.4) node[midway,below right] {$IS_Y$};
+\draw [->, very thick] (3,15) -- ++(0.5,-0.2)  coordinate (S1) node[midway,below left] {$IS_X$} ;
+\draw [->, very thick] (S1) -- (3.85,15.4) node[midway,below right] {$IS_Y$};
 
-\node (anchor) at (6.0,14.35) {}; 
+\node (anchor) at (6.0,19.35) {}; 
 \node[labelNode] {B};
@@
 % Place nodes
-\node [block] (init) at (8.0,13.35) {\textbf{START} \\ Collect overview image};
+\node [block] (init) at (8.0,18.35) {\textbf{START} \\ Collect overview image};
 \node [block, below = 0.3cm of init.south] (identify) {Setup hexagonal grid covering lamella area};
@@
 
-\node (anchor) at (11.5,14.35) {}; 
+\node (anchor) at (11.5,19.35) {}; 
 \node[labelNode] {C};
@@
 
-\node (anchor) at (0.5,4.5) {}; 
-\node[labelNode] {C};
+\node (anchor) at (0.5,9.5) {}; 
+\node[labelNode] {D};
 \node[graphicNode] (euc) {\includegraphics[height=4.0cm]{content/images/fringebeam.png}};
@@
 
-\node (anchor) at (5.5,4.5) {}; 
-\node[labelNode] {D};
+\node (anchor) at (5.5,9.5) {}; 
+\node[labelNode] {E};
 \node[graphicNode] (fff) {\includegraphics[height=4.0cm]{content/images/nofringebeam.png}};
@@
 
-\node (anchor) at (10.5,4.5) {}; 
-\node[labelNode] {E};
+\node (anchor) at (10.5,9.5) {}; 
+\node[labelNode] {F};
 \node[anchor=north west, below right=-0.5cm and 0cm of anchor] {\includegraphics[height=4.8cm]{content/code/img/defocusplot.pdf}};
 \iftoggle{draft}{\node [redAnchorNode] {};};
+
+\node (anchor) at (0.5,4.5) {}; 
+\node[labelNode] {G};
+\node[graphicNode] {\includegraphics[height=4.5cm]{content/images/euc_lamella1_view_morph.png}};
+
+\node (anchor) at (5,4.5) {}; 
+\node[labelNode] {H};
+\node[graphicNode] {\includegraphics[height=4.5cm]{content/images/euc_lamella1_1000px.png}};
+
+\node (anchor) at (9.5,4.5) {}; 
+\node[labelNode] {I};
+\node[graphicNode] {\includegraphics[height=4.5cm]{content/images/fff_lamella4_view_morphed.png}};
+
+\node (anchor) at (14,4.5) {}; 
+\node[labelNode] {J};
+\node[graphicNode] {\includegraphics[height=4.5cm]{content/images/fff_lamella4_1000px.png}};
 

### 2022-04-07 figures/crop_unblur.tex
Minor figure [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/56ce938e8d7fb4ca49b0ca90d4ceca7386ae3b0f.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/56ce938e8d7fb4ca49b0ca90d4ceca7386ae3b0f/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2110566960

--- 2022-03-29 figures/approach.tex
@@
     \setlist{nosep,leftmargin=*}
-    \newcommand{\figwidth}{20cm} 
-    \newcommand{\figheight}{15cm} 
+    \newcommand{\figwidth}{20.0cm} 
+    \newcommand{\figheight}{10cm} 
     \newcommand{\fontselect}{\large\bf} 
@@
 
-    \node (anchor) at (0.5,14.35) {}; 
+    \def\panelheight{4.6cm}
+
+\node (anchor) at (0.5,9.5) {}; 
 \node[labelNode] {A};
-\node[graphicNode] {\includegraphics[width=5cm]{content/graphics/approach/approach.png}};
-\draw [densely dotted, red,thick] (3,14.5) -- (3,10);
-\draw [densely dotted, red,thick] (3,9.2) -- (3,6.4);
+\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/images/crop_unblur_initial.png}};
+\node (box1) [box=red, fit=(panel), dashed] {};
 
-\tikzset{dimen/.style={<->,>=latex,thin,every rectangle node/.style={above right=0.2cm and -0.3cm,fill=white,midway,font=\sffamily}}}
+\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
+\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/code/img/crop_unblur_motiontrace_initial.png}};
 
-\draw (3.55,10.4) -- ++(0,1.5) coordinate (D1) -- +(0,5pt);
-\draw (4.15,10.4) -- ++(0,1.5) coordinate (D2) -- +(0,5pt);
-\draw [dimen] (D1) -- (D2) node {$D_{Beam}$};
+\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
+\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/code/img/crop_unblur_mip_initial_alignment.png}};
 
-\draw [->, very thick] (3,10) -- ++(0.5,-0.2)  coordinate (S1) node[midway,below left] {$IS_X$} ;
-\draw [->, very thick] (S1) -- (3.85,10.4) node[midway,below right] {$IS_Y$};
+\node (anchor) at ([shift={(1.5,0.0cm)}]0.5,9.5 -| panel.north east) {}; 
+\node[labelNode] {B};
+\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/images/crop_unblur_cropped.png}};
+\node (box2) [box=red, fit=(panel), dashed] {};
 
-\node (anchor) at (6.0,14.35) {}; 
-\node[labelNode] {B};
+\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
+\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/code/img/crop_unblur_motiontrace_cropped.png}};
 
-% Place nodes
-\node [block] (init) at (8.0,13.35) {\textbf{START} \\ Collect overview image};
-\node [block, below = 0.3cm of init.south] (identify) {Setup hexagonal grid covering lamella area};
-\node [block, below = 0.3cm of identify.south] (mutate) {Beam-imageshift to tile n=i};
-\node [block, below = 0.3cm of mutate.south] (transfer) {Capture exposure and determine defocus by CTF fitting};
-\node [block, below = 0.3cm of transfer.south] (evaluate) {Adjust defocus by difference between expected and measured value};
+\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
+\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/code/img/crop_unblur_mip_cropped_alignment.png}};
 
-% Draw edges
-\path [line] (init) -- (identify);
-\path [line] (identify) -- (mutate);
-\path [line] (mutate) -- (transfer);
-\path [line] (transfer) -- (evaluate);
-\path [line] (evaluate) -|  ([xshift=0.5cm, yshift=0cm]transfer.east) |- (mutate);
+\node (anchor) at ([shift={(1.5,0.0cm)}]0.5,9.5 -| panel.north east) {}; 
+\node[labelNode] {C};
+\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/images/crop_unblur_initial.png}};
+\draw[red, dashed, line width=0.8mm] ([shift={(-0.7,-1.2cm)}]panel.north east) -- 
+                                     ([shift={(0.7,-1.2cm)}]panel.north west) --
+                                     ([shift={(0.7,1.2cm)}]panel.south west) --
+                                     ([shift={(-0.7,1.2cm)}]panel.south east) --
+                                     ([shift={(-0.7,-1.2cm)}]panel.north east);
 
-\node (anchor) at (11.5,14.35) {}; 
-\node[labelNode] {C};
-\node[graphicNode] {\includegraphics[width=8cm]{content/images/ac_strategy.png}};
-\iftoggle{draft}{\node [redAnchorNode] {};};
+\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
+\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/code/img/crop_unblur_motiontrace_final.png}};
 
-\node (anchor) at (0.5,4.5) {}; 
-\node[labelNode] {C};
-\node[graphicNode] (euc) {\includegraphics[height=4.0cm]{content/images/fringebeam.png}};
-\node[above = 0cm and 0cm of euc.north] {Eucentric Focus};
-
-\iftoggle{draft}{\node [redAnchorNode] {};};
-
-\node (anchor) at (5.5,4.5) {}; 
-\node[labelNode] {D};
-\node[graphicNode] (fff) {\includegraphics[height=4.0cm]{content/images/nofringebeam.png}};
-\node[above = 0cm and 0cm of fff.north] {Fringe-free Focus};
-\iftoggle{draft}{\node [redAnchorNode] {};};
-
-\node (anchor) at (10.5,4.5) {}; 
-\node[labelNode] {E};
-\node[anchor=north west, below right=-0.5cm and 0cm of anchor] {\includegraphics[height=4.8cm]{content/code/img/defocusplot.pdf}};
-\iftoggle{draft}{\node [redAnchorNode] {};};
+\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
+\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/code/img/crop_unblur_mip_final_alignment.png}};
 

### 2022-04-07 figures/lamella_images.tex
Minor figure [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/56ce938e8d7fb4ca49b0ca90d4ceca7386ae3b0f.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/56ce938e8d7fb4ca49b0ca90d4ceca7386ae3b0f/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2110566960

--- 2022-04-07 figures/crop_unblur.tex
@@
     \newcommand{\figwidth}{20.0cm} 
-    \newcommand{\figheight}{10cm} 
+    \newcommand{\figheight}{5cm} 
     \newcommand{\fontselect}{\large\bf} 
@@
 
-\node (anchor) at (0.5,9.5) {}; 
+\node (anchor) at (0.5,4.5) {}; 
 \node[labelNode] {A};
-\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/images/crop_unblur_initial.png}};
-\node (box1) [box=red, fit=(panel), dashed] {};
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/slicer000.png}};
+\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/slicer001.png}};
+\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/slicer002.png}};
+\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/slicer003.png}};
 
-\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
-\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/code/img/crop_unblur_motiontrace_initial.png}};
-
-\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
-\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/code/img/crop_unblur_mip_initial_alignment.png}};
-
-\node (anchor) at ([shift={(1.5,0.0cm)}]0.5,9.5 -| panel.north east) {}; 
-\node[labelNode] {B};
-\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/images/crop_unblur_cropped.png}};
-\node (box2) [box=red, fit=(panel), dashed] {};
-
-\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
-\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/code/img/crop_unblur_motiontrace_cropped.png}};
-
-\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
-\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/code/img/crop_unblur_mip_cropped_alignment.png}};
-
-\node (anchor) at ([shift={(1.5,0.0cm)}]0.5,9.5 -| panel.north east) {}; 
-\node[labelNode] {C};
-\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/images/crop_unblur_initial.png}};
-\draw[red, dashed, line width=0.8mm] ([shift={(-0.7,-1.2cm)}]panel.north east) -- 
-                                     ([shift={(0.7,-1.2cm)}]panel.north west) --
-                                     ([shift={(0.7,1.2cm)}]panel.south west) --
-                                     ([shift={(-0.7,1.2cm)}]panel.south east) --
-                                     ([shift={(-0.7,-1.2cm)}]panel.north east);
-
-\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
-\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/code/img/crop_unblur_motiontrace_final.png}};
-
-\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
-\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/code/img/crop_unblur_mip_final_alignment.png}};
+\node (anchor) at ([shift={(0.0cm,-0.5cm)}]0.5,0 |- panel.south) {}; 
+\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/images/slicer005.png}};
+\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
+\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/images/slicer006.png}};
+\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
+\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/images/slicer007.png}};
+\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
+\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/images/slicer008.png}};
 

### 2022-04-07 figures/lamella_motion_thickness.tex
Minor figure [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/56ce938e8d7fb4ca49b0ca90d4ceca7386ae3b0f.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/56ce938e8d7fb4ca49b0ca90d4ceca7386ae3b0f/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2110566960

--- 2022-04-07 figures/crop_unblur.tex
@@
 \node[labelNode] {A};
-\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/images/crop_unblur_initial.png}};
-\node (box1) [box=red, fit=(panel), dashed] {};
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/movement_vs_bs_plot_euc_lamella1.png}};
+\node (anchor) at ([shift={(-0.4,0.0cm)}]panel.north east) {}; 
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/movement_vs_bs_plot_euc_lamella2.png}};
+\node (anchor) at ([shift={(-0.4,0.0cm)}]panel.north east) {}; 
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/movement_vs_bs_plot_euc_lamella3.png}};
+\node (anchor) at ([shift={(-0.4,0.0cm)}]panel.north east) {}; 
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/movement_vs_bs_plot_euc_lamella4.png}};
 
-\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
-\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/code/img/crop_unblur_motiontrace_initial.png}};
+\node (anchor) at ([shift={(0.0cm,-0.5cm)}]0.5,0 |- panel.south) {}; 
+\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/code/img/movement_vs_bs_plot_fff_lamella1.png}};
+\node (anchor) at ([shift={(-0.4,0.0cm)}]panel.north east) {}; 
+\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/code/img/movement_vs_bs_plot_fff_lamella2.png}};
+\node (anchor) at ([shift={(-0.4,0.0cm)}]panel.north east) {};
+\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/code/img/movement_vs_bs_plot_fff_lamella3.png}};
+\node (anchor) at ([shift={(-0.4,0.0cm)}]panel.north east) {}; 
+\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/code/img/movement_vs_bs_plot_fff_lamella4.png}};
+\node (anchor) at ([shift={(-1.0cm,4.0cm)}]panel.north east) {}; 
+\node[graphicNode] (key) {\includegraphics[height=\panelheight]{content/code/img/movement_vs_bs_plot_colorbar.png}};
 
-\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
-\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/code/img/crop_unblur_mip_initial_alignment.png}};
+\node (anchor) at ([shift={(0.0cm,-1.0cm)}]0.5,0 |- panel.south) {}; 
+\node[labelNode] {B};
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/thickness_by_intensity_vs_bs_plot_euc_lamella1.png}};
+\node (anchor) at ([shift={(-0.4cm,0.0cm)}]panel.north east) {}; 
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/thickness_by_intensity_vs_bs_plot_euc_lamella2.png}};
+\node (anchor) at ([shift={(-0.4cm,0.0cm)}]panel.north east) {}; 
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/thickness_by_intensity_vs_bs_plot_euc_lamella3.png}};
+\node (anchor) at ([shift={(-0.4cm,0.0cm)}]panel.north east) {}; 
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/thickness_by_intensity_vs_bs_plot_euc_lamella4.png}};
 
-\node (anchor) at ([shift={(1.5,0.0cm)}]0.5,9.5 -| panel.north east) {}; 
-\node[labelNode] {B};
-\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/images/crop_unblur_cropped.png}};
-\node (box2) [box=red, fit=(panel), dashed] {};
-
-\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
-\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/code/img/crop_unblur_motiontrace_cropped.png}};
-
-\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
-\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/code/img/crop_unblur_mip_cropped_alignment.png}};
-
-\node (anchor) at ([shift={(1.5,0.0cm)}]0.5,9.5 -| panel.north east) {}; 
-\node[labelNode] {C};
-\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/images/crop_unblur_initial.png}};
-\draw[red, dashed, line width=0.8mm] ([shift={(-0.7,-1.2cm)}]panel.north east) -- 
-                                     ([shift={(0.7,-1.2cm)}]panel.north west) --
-                                     ([shift={(0.7,1.2cm)}]panel.south west) --
-                                     ([shift={(-0.7,1.2cm)}]panel.south east) --
-                                     ([shift={(-0.7,-1.2cm)}]panel.north east);
-
-\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
-\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/code/img/crop_unblur_motiontrace_final.png}};
-
-\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
-\node[graphicNode] (panel) {\includegraphics[width=5cm]{content/code/img/crop_unblur_mip_final_alignment.png}};
+\node (anchor) at ([shift={(0.0cm,-0.5cm)}]0.5,0 |- panel.south) {}; 
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/thickness_by_intensity_vs_bs_plot_fff_lamella1.png}};
+\node (anchor) at ([shift={(-0.4cm,0.0cm)}]panel.north east) {}; 
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/thickness_by_intensity_vs_bs_plot_fff_lamella2.png}};
+\node (anchor) at ([shift={(-0.4cm,0.0cm)}]panel.north east) {}; 
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/thickness_by_intensity_vs_bs_plot_fff_lamella3.png}};
+\node (anchor) at ([shift={(-0.4cm,0.0cm)}]panel.north east) {}; 
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/thickness_by_intensity_vs_bs_plot_fff_lamella4.png}};
+\node (anchor) at ([shift={(-1.0cm,4.0cm)}]panel.north east) {}; 
+\node[graphicNode] (key) {\includegraphics[height=\panelheight]{content/code/img/thickness_by_intensity_vs_bs_plot_colorbar.png}};
 

### 2022-04-07 figures/lamella_spatial_info.tex
Minor figure [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/56ce938e8d7fb4ca49b0ca90d4ceca7386ae3b0f.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/56ce938e8d7fb4ca49b0ca90d4ceca7386ae3b0f/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2110566960

@@
     \setlist{nosep,leftmargin=*}
-    \newcommand{\figwidth}{16.5cm} 
-    \newcommand{\figheight}{9cm} 
+    \newcommand{\figwidth}{20.0cm} 
+    \newcommand{\figheight}{10cm} 
     \newcommand{\fontselect}{\large\bf} 
@@
 
-    \node (anchor) at (0.5,8.35) {}; 
+    \def\panelheight{4.6cm}
+
+\node (anchor) at (0.5,9.5) {}; 
 \node[labelNode] {A};
-\node[graphicNode] {\includegraphics[width=7.5cm]{content/code/img/defocus_defocus_vs_bs_plot.pdf}};
-\iftoggle{draft}{\node [redAnchorNode] {};};
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/defocus_defocus_vs_bs_plot_euc_lamella1.png}};
+\node (anchor) at ([shift={(-0.4cm,0.0cm)}]panel.north east) {}; 
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/defocus_defocus_vs_bs_plot_euc_lamella2.png}};
+\node (anchor) at ([shift={(-0.4cm,0.0cm)}]panel.north east) {}; 
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/defocus_defocus_vs_bs_plot_euc_lamella3.png}};
+\node (anchor) at ([shift={(-0.4cm,0.0cm)}]panel.north east) {}; 
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/defocus_defocus_vs_bs_plot_euc_lamella4.png}};
 
-\node (anchor) at (0.5,4.35) {}; 
+\node (anchor) at ([shift={(0.0cm,-0.5cm)}]0.5,0 |- panel.south) {}; 
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/defocus_defocus_vs_bs_plot_fff_lamella1.png}};
+\node (anchor) at ([shift={(-0.4cm,0.0cm)}]panel.north east) {}; 
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/defocus_defocus_vs_bs_plot_fff_lamella2.png}};
+\node (anchor) at ([shift={(-0.4cm,0.0cm)}]panel.north east) {}; 
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/defocus_defocus_vs_bs_plot_fff_lamella3.png}};
+\node (anchor) at ([shift={(-0.4cm,0.0cm)}]panel.north east) {}; 
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/defocus_defocus_vs_bs_plot_fff_lamella4.png}};
+\node (anchor) at ([shift={(-0.4cm,4.0cm)}]panel.north east) {}; 
+\node[graphicNode] (key) {\includegraphics[height=\panelheight]{content/code/img/defocus_defocus_vs_bs_plot_colorbar.png}};
+
+\node (anchor) at ([shift={(0.0cm,-1.0cm)}]0.5,0 |- panel.south) {}; 
 \node[labelNode] {B};
-\node[graphicNode] {\includegraphics[width=7.5cm]{content/code/img/defocus_astigmatism_vs_bs_plot.pdf}};
-\iftoggle{draft}{\node [redAnchorNode] {};};
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/defocus_astigmatism_vs_bs_plot_euc_lamella1.png}};
+\node (anchor) at ([shift={(-0.4cm,0.0cm)}]panel.north east) {}; 
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/defocus_astigmatism_vs_bs_plot_euc_lamella2.png}};
+\node (anchor) at ([shift={(-0.4cm,0.0cm)}]panel.north east) {}; 
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/defocus_astigmatism_vs_bs_plot_euc_lamella3.png}};
+\node (anchor) at ([shift={(-0.4cm,0.0cm)}]panel.north east) {}; 
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/defocus_astigmatism_vs_bs_plot_euc_lamella4.png}};
 
-\node (anchor) at (8.5,8.35) {}; 
-\node[labelNode] {C};
-\node[graphicNode] {\includegraphics[width=7.5cm]{content/code/img/defocus_angle_vs_bs_plot.pdf}};
-\iftoggle{draft}{\node [redAnchorNode] {};};
+\node (anchor) at ([shift={(0.0cm,-0.5cm)}]0.5,0 |- panel.south) {}; 
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/defocus_astigmatism_vs_bs_plot_fff_lamella1.png}};
+\node (anchor) at ([shift={(-0.4cm,0.0cm)}]panel.north east) {}; 
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/defocus_astigmatism_vs_bs_plot_fff_lamella2.png}};
+\node (anchor) at ([shift={(-0.4cm,0.0cm)}]panel.north east) {}; 
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/defocus_astigmatism_vs_bs_plot_fff_lamella3.png}};
+\node (anchor) at ([shift={(-0.4cm,0.0cm)}]panel.north east) {}; 
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/defocus_astigmatism_vs_bs_plot_fff_lamella4.png}};
+\node (anchor) at ([shift={(-0.4cm,4.0cm)}]panel.north east) {}; 
+\node[graphicNode] (key) {\includegraphics[height=\panelheight]{content/code/img/defocus_astigmatism_vs_bs_plot_colorbar.png}};
 

### 2022-04-07 figures/matching_euc.tex
Minor figure [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/56ce938e8d7fb4ca49b0ca90d4ceca7386ae3b0f.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/56ce938e8d7fb4ca49b0ca90d4ceca7386ae3b0f/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2110566960

--- 2022-03-29 figures/approach.tex
@@
     \setlist{nosep,leftmargin=*}
-    \newcommand{\figwidth}{20cm} 
-    \newcommand{\figheight}{15cm} 
+    \newcommand{\figwidth}{17cm} 
+    \newcommand{\figheight}{10cm} 
     \newcommand{\fontselect}{\large\bf} 
@@
 
-    \node (anchor) at (0.5,14.35) {}; 
+\node (anchor) at (0.5,9.5) {}; 
 \node[labelNode] {A};
-\node[graphicNode] {\includegraphics[width=5cm]{content/graphics/approach/approach.png}};
-\draw [densely dotted, red,thick] (3,14.5) -- (3,10);
-\draw [densely dotted, red,thick] (3,9.2) -- (3,6.4);
+\node[graphicNode] {\includegraphics[height=12cm]{content/images/euc_lamella1_1000px.png}};
+\node[graphicNode] {\includegraphics[height=12cm]{content/images/euc_lamella1_just_matches.png}};
 
-\tikzset{dimen/.style={<->,>=latex,thin,every rectangle node/.style={above right=0.2cm and -0.3cm,fill=white,midway,font=\sffamily}}}
+\node (anchor) at (11.0,9.5) {}; 
+\node[labelNode] {B};
+\node[anchor=north west, below right=0cm and -4.5cm of anchor] {\includegraphics[height=12cm]{content/images/euc_lamella1_just_matches_side.png}};
 
-\draw (3.55,10.4) -- ++(0,1.5) coordinate (D1) -- +(0,5pt);
-\draw (4.15,10.4) -- ++(0,1.5) coordinate (D2) -- +(0,5pt);
-\draw [dimen] (D1) -- (D2) node {$D_{Beam}$};
+\node (anchor) at (13.0,9.5) {}; 
+\node[labelNode] {C};
+\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/euc_lamella1_just_matches_er_ribos.png}};
 
-\draw [->, very thick] (3,10) -- ++(0.5,-0.2)  coordinate (S1) node[midway,below left] {$IS_X$} ;
-\draw [->, very thick] (S1) -- (3.85,10.4) node[midway,below right] {$IS_Y$};
+\node (anchor) at (13.0,6.5) {}; 
+\node[labelNode] {D};
+\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/euc_lamella1_just_matches_nucleus.png}};
 
-\node (anchor) at (6.0,14.35) {}; 
-\node[labelNode] {B};
+\node (anchor) at (13.,3.5) {}; 
+\node[labelNode] {E};
+\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/euc_lamella1_just_matches_circle.png}};
 
-% Place nodes
-\node [block] (init) at (8.0,13.35) {\textbf{START} \\ Collect overview image};
-\node [block, below = 0.3cm of init.south] (identify) {Setup hexagonal grid covering lamella area};
-\node [block, below = 0.3cm of identify.south] (mutate) {Beam-imageshift to tile n=i};
-\node [block, below = 0.3cm of mutate.south] (transfer) {Capture exposure and determine defocus by CTF fitting};
-\node [block, below = 0.3cm of transfer.south] (evaluate) {Adjust defocus by difference between expected and measured value};
-
-% Draw edges
-\path [line] (init) -- (identify);
-\path [line] (identify) -- (mutate);
-\path [line] (mutate) -- (transfer);
-\path [line] (transfer) -- (evaluate);
-\path [line] (evaluate) -|  ([xshift=0.5cm, yshift=0cm]transfer.east) |- (mutate);
-
-\node (anchor) at (11.5,14.35) {}; 
-\node[labelNode] {C};
-\node[graphicNode] {\includegraphics[width=8cm]{content/images/ac_strategy.png}};
-\iftoggle{draft}{\node [redAnchorNode] {};};
-
-\node (anchor) at (0.5,4.5) {}; 
-\node[labelNode] {C};
-\node[graphicNode] (euc) {\includegraphics[height=4.0cm]{content/images/fringebeam.png}};
-\node[above = 0cm and 0cm of euc.north] {Eucentric Focus};
-
-\iftoggle{draft}{\node [redAnchorNode] {};};
-
-\node (anchor) at (5.5,4.5) {}; 
-\node[labelNode] {D};
-\node[graphicNode] (fff) {\includegraphics[height=4.0cm]{content/images/nofringebeam.png}};
-\node[above = 0cm and 0cm of fff.north] {Fringe-free Focus};
-\iftoggle{draft}{\node [redAnchorNode] {};};
-
-\node (anchor) at (10.5,4.5) {}; 
-\node[labelNode] {E};
-\node[anchor=north west, below right=-0.5cm and 0cm of anchor] {\includegraphics[height=4.8cm]{content/code/img/defocusplot.pdf}};
-\iftoggle{draft}{\node [redAnchorNode] {};};
+\node (anchor) at (13.0,0.5) {}; 
+\node[labelNode] {F};
+\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/euc_lamella1_just_matches_contained.png}};
 

### 2022-04-07 figures/matching_fff.tex
Minor figure [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/56ce938e8d7fb4ca49b0ca90d4ceca7386ae3b0f.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/56ce938e8d7fb4ca49b0ca90d4ceca7386ae3b0f/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2110566960

--- 2022-04-07 figures/matching_euc.tex
@@
 \node[labelNode] {A};
-\node[graphicNode] {\includegraphics[height=12cm]{content/images/euc_lamella1_1000px.png}};
-\node[graphicNode] {\includegraphics[height=12cm]{content/images/euc_lamella1_just_matches.png}};
+\node[graphicNode] {\includegraphics[height=12cm]{content/images/fff_lamella4_1000px.png}};
+\node[graphicNode] {\includegraphics[height=12cm]{content/images/fff_lamella4_just_matches.png}};
 
@@
 \node[labelNode] {B};
-\node[anchor=north west, below right=0cm and -4.5cm of anchor] {\includegraphics[height=12cm]{content/images/euc_lamella1_just_matches_side.png}};
+\node[anchor=north west, below right=0cm and -4cm of anchor] {\includegraphics[height=12cm]{content/images/fff_lamella4_just_matches_side.png}};
 
@@
 \node[labelNode] {C};
-\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/euc_lamella1_just_matches_er_ribos.png}};
+\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/fff_lamella4_just_matches_det3.png}};
 
@@
 \node[labelNode] {D};
-\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/euc_lamella1_just_matches_nucleus.png}};
+\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/fff_lamella4_just_matches_det1.png}};
 
-\node (anchor) at (13.,3.5) {}; 
+\node (anchor) at (13.0,3.5) {}; 
 \node[labelNode] {E};
-\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/euc_lamella1_just_matches_circle.png}};
+\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/fff_lamella4_just_matches_det4.png}};
 
-\node (anchor) at (13.0,0.5) {}; 
+\node (anchor) at (13,0.5) {}; 
 \node[labelNode] {F};
-\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/euc_lamella1_just_matches_contained.png}};
+\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/fff_lamella4_just_matches_det6.png}};
 

### 2022-04-07 figures/matching_stat.tex
Minor figure [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/56ce938e8d7fb4ca49b0ca90d4ceca7386ae3b0f.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/56ce938e8d7fb4ca49b0ca90d4ceca7386ae3b0f/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2110566960

--- 2022-04-07 figures/matching_fff.tex
@@
     \setlist{nosep,leftmargin=*}
-    \newcommand{\figwidth}{17cm} 
-    \newcommand{\figheight}{10cm} 
+    \newcommand{\figwidth}{15cm} 
+    \newcommand{\figheight}{3cm} 
     \newcommand{\fontselect}{\large\bf} 
@@
 
-\node (anchor) at (0.5,9.5) {}; 
+\node (anchor) at (0.5,2.5) {}; 
 \node[labelNode] {A};
-\node[graphicNode] {\includegraphics[height=12cm]{content/images/fff_lamella4_1000px.png}};
-\node[graphicNode] {\includegraphics[height=12cm]{content/images/fff_lamella4_just_matches.png}};
-
-\node (anchor) at (11.0,9.5) {}; 
+\node[graphicNode] (panel) {\includegraphics[width=4.5cm]{content/code/img/num_matches_plot.png}};
+\node (anchor) at ([shift={(0.5cm,0.0)}]panel.north east) {}; 
 \node[labelNode] {B};
-\node[anchor=north west, below right=0cm and -4cm of anchor] {\includegraphics[height=12cm]{content/images/fff_lamella4_just_matches_side.png}};
-
-\node (anchor) at (13.0,9.5) {}; 
+\node[graphicNode] (panel) {\includegraphics[width=4.5cm]{content/code/img/scores_plot.png}};
+\node (anchor) at ([shift={(0.5cm,0.0)}]panel.north east) {}; 
 \node[labelNode] {C};
-\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/fff_lamella4_just_matches_det3.png}};
-
-\node (anchor) at (13.0,6.5) {}; 
+\node[graphicNode] {\includegraphics[width=4.5cm]{content/code/img/matches_per_tile_plot.png}};
+\node (anchor) at ([shift={(0.0cm,-1.0)}]0.5,2.5 |- panel.south east) {}; 
 \node[labelNode] {D};
-\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/fff_lamella4_just_matches_det1.png}};
-
-\node (anchor) at (13.0,3.5) {}; 
-\node[labelNode] {E};
-\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/fff_lamella4_just_matches_det4.png}};
-
-\node (anchor) at (13,0.5) {}; 
-\node[labelNode] {F};
-\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/fff_lamella4_just_matches_det6.png}};
-
+\node[graphicNode] {\includegraphics[width=14cm]{content/code/img/micrograph_with_matches.png}};
     \iftoggle{draft}{\draw[lightgray,step=1] (0,0) grid (\figwidth,\figheight);}{};

### 2022-04-07 manuscript.tex
Minor figure [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/56ce938e8d7fb4ca49b0ca90d4ceca7386ae3b0f.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/56ce938e8d7fb4ca49b0ca90d4ceca7386ae3b0f/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2110566960

@@
 This manuscript
-(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/2d0a9a5debbbf44b5f9d5797d38db68589012013/}{permalink})
+(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/56ce938e8d7fb4ca49b0ca90d4ceca7386ae3b0f/}{permalink})
 was automatically generated
-from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/2d0a9a5debbbf44b5f9d5797d38db68589012013}{jojoelfe/deco\_lace\_template\_matching\_manuscript@2d0a9a5}
-on March 30, 2022.
+from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/56ce938e8d7fb4ca49b0ca90d4ceca7386ae3b0f}{jojoelfe/deco\_lace\_template\_matching\_manuscript@56ce938}
+on April 7, 2022.
 
@@
 1.5 A pixelsize. We manually selected multiple locations in the lamella and
-focused using standard low-dose techniques where focusing is performed on a sacrificial area. The resulting micrographs showed no signs of
-crystalline ice and had Thon-rings to resolution, indicating successful
-vitrification.
+focused using standard low-dose techniques where focusing is performed on a
+sacrificial area. The resulting micrographs showed no signs of crystalline ice
+and had Thon-rings to resolution, indicating successful vitrification.
 
@@
 scores significantly exceeded the distribution expected from non-signifcant
-matching. In the resulting scaled maximum-intensity maps, clear peaks
-with SNR thresholds up to 10 were apparent (Fig. \ref{fig:initmatching2}A). By
-using the criterion described by for thresholding potential matches we found
-that in images of cytosolic compartments we found evidence of 10-500 ribosomes in
-the imaged areas. Notably we found no matches in images that were taken in the
+matching. In the resulting scaled maximum-intensity maps, clear peaks with SNR
+thresholds up to 10 were apparent (Fig. \ref{fig:initmatching2}A). By using the
+criterion described by for thresholding potential matches we found that in
+images of cytosolic compartments we found evidence of 10-500 ribosomes in the
+imaged areas. Notably we found no matches in images that were taken in the
 nuclear compartment. In the cytosolic areas we found a drastically different
@@
 mammalian lamella in a high-throughput unbiased fashion.
-\#\#\# DECO-LACE for 2D imaging of whole lamella
+
+\hypertarget{deco-lace-for-2d-imaging-of-whole-lamella}{%
+\subsubsection{DECO-LACE for 2D imaging of whole lamella}\label{deco-lace-for-2d-imaging-of-whole-lamella}}
 
@@
 astigmatism of the lamella and found that it varies with the applied Beam-image
-shift, become more astigmatic mostly due to beam-image shift in the X
-direction. While approaches exist to correct this during the data-collection, we
-opted to not use these mechanism for these early experiments and instead rely on
+shift, become more astigmatic mostly due to beam-image shift in the X direction.
+While approaches exist to correct this during the data-collection, we opted to
+not use these mechanism for these early experiments and instead rely on
 computational correction of these aberrations in order to characterize them.
@@
 portion of the image to prevent artifacts from the beam edges on estimation of
-motion. Then we calculated a mask that defined the illuminated area of the
-micrographs and used it to fill non-illumated areas with gaussian noise,
-matching mean and standard deviation to the illuminated signal (Figure 3A). The
+motion {[}Figure S{]}. Then we calculated a mask that defined the illuminated area
+of the micrographs and used it to fill non-illumated areas with gaussian noise,
+matching mean and standard deviation to the illuminated signal (Figure S). The
 so processed images were suitable for 2D-template matching and we were able to
 obtained matches with the same model used for the data in Figure 1.
+
+We then matched all individual tiles for ribosomes and assembled a montaged view
+as described above (Figure \ref{fig:matching} A+G). The resulting montages reveal
+ribsome distribution throughout the FIB-milled slice of individual cells.
+Organelles like the nucleus and mitochondria only show sporadic matches with low
+SNRs, consistent with the estimated false-positive rate on one per tile. During
+the assembly we calculated the Z positions from the indivdual estimated defocus
+levels and the focus plane of the microscope during acquisition of each tile.
+When viewed from the side the ribosome position therefore show the slope of the
+lamella in the microscope frame. Furthermore, the positions are also consistent
+with an uneven thickness of the lamella, thinner at the leading edge, even
+though, lamella were generated using the ``overtilt'' approach {[}cite{]}.
 
@@
   Threshold implications (no matches on most images)
+\item
+  K3 not linear
 \end{itemize}
@@
 \centering
-\includegraphics{figures/initmatching.pdf}
+\includegraphics{figures/initmatching.png}
 \caption{2D template matching of the large subunit of the ribosome in fib-milled neutrophil-like cells
@@
 \centering
-\includegraphics{figures/initmatching2.pdf}
-\caption{Maximum intensity projection cross-correlation map of micrograph shown in Figure \ref{fig:initmatching}}\label{fig:initmatching2}
+\includegraphics{figures/initmatching2.png}
+\caption{2D template matching of the large subunit of the ribosome in fib-milled
+neutrophil-like cells (A) Maximum intensity projection cross-correlation map of
+micrograph shown in Figure
+\ref{fig:initmatching} (B+C) 3D plot of MIP regions indicated by color boxes in Panel A}\label{fig:initmatching2}
 }
@@
 \centering
-\includegraphics{figures/approach.pdf}
-\caption{DeCo-LACE approach (A) Graphic demonstrating the data-collection strategy for DeCo-LACE}\label{fig:approach}
+\includegraphics{figures/approach.png}
+\caption{DeCo-LACE approach (A) Graphic demonstrating the data-collection strategy for
+DeCo-LACE. The electron beam is condensed to a diameter \(D_{Beam}\) that allows captured of
+the whole illuminated area on the camera. Beam-image shift along X and Y
+(\(BIS_X\),\$\(BIS_Y\)) is used to raster the whole lamella
+(B) Diagram of the collection algorithm
+(C) Example overview image of a lamella with the designated acquisition
+positions and the used beam diameter indicated with red circles
+(D+E) Representative micrographs takne with a condensed beam at eucentric focus
+(D) or fringe-free focus (E)
+(F) Boxplot of defocus measured by ctffind of micrographs taken by the DeCo-Lace
+approach on 4 lamella images at eucentric focus and 4 lamella imaged with
+fringe-free focus.
+(F+G) Lamella overview images of lamella imaged at eucentric focus (F) Overview
+image taken at low magnification (40Å pixel size) (G) Overview created by
+montaging high magnification images taken with the DeCo-Lace approach (1.5Å
+pixelsize)
+(H+I) Lamella overview images of lamella imaged at fringe-free focus (H) Overview
+image taken at low magnification (40Å pixel size) (I) Overview created by
+montaging high magnification images taken with the DeCo-Lace approach (1.5Å
+pixelsize)}\label{fig:approach}
+}
+\end{figure}
+
+\begin{fignos:tagged-figure}[S2]
+
+\begin{figure}
+\hypertarget{fig:lamella_images}{%
+\centering
+\includegraphics{figures/lamella_images.png}
+\caption{Overview images of lamellae imaged using the DeCo-LACE approach taken at low-magnification}\label{fig:lamella_images}
+}
+\end{figure}
+
+\end{fignos:tagged-figure}
+
+\begin{fignos:tagged-figure}[S3]
+
+\begin{figure}
+\hypertarget{fig:lamella_spatial_info}{%
+\centering
+\includegraphics{figures/lamella_spatial_info.png}
+\caption{Defocus estimation of individual tiles of DeCo-Lace montages
+(A) Defocus values of individual micrographs taken using the DeCo-Lace approach
+plotted as a function of the Beam-Image-Shift values.
+(B) Defocus astigmatism of individual micrographs taken using the DeCo-Lace approach
+plotted as a function of the Beam-Image-Shift values.}\label{fig:lamella_spatial_info}
+}
+\end{figure}
+
+\end{fignos:tagged-figure}
+
+\begin{fignos:tagged-figure}[S4]
+
+\begin{figure}
+\hypertarget{fig:crop_unblur}{%
+\centering
+\includegraphics{figures/crop_unblur.png}
+\caption{Motion correction of movies with condensed beams.
+At the top of each panel is an average of the movie that was motion-corrected
+with a red dashed box indicating the region that was used to estimate shifts.
+Below is a graph indicating the estimated shifts of the individual frames of the
+movie. Below this is the MIP of 2DTM using the large subunit of the mouse ribosome.
+(A) Motion correction of the whole movie
+(B) Notion correction of a cropped region of the movie that eliminates the beam
+edges
+(C) Motion correction of the whole movie, using only hte cropped region to
+estimate the shifts}\label{fig:crop_unblur}
+}
+\end{figure}
+
+\end{fignos:tagged-figure}
+
+\begin{fignos:tagged-figure}[S5]
+
+\begin{figure}
+\hypertarget{fig:lamella_motion_thickness}{%
+\centering
+\includegraphics{figures/lamella_motion_thickness.png}
+\caption{Motion correction of individual tiles imaged using the DeCo-LACE approach
+(A) Total estimated motion of individual micrographs taken using the DeCo-Lace approach
+plotted as a function of the Beam-Image-Shift values.
+(B) Electron intensity of individual micrographs taken using the DeCo-Lace approach
+plotted as a function of the Beam-Image-Shift values.}\label{fig:lamella_motion_thickness}
+}
+\end{figure}
+
+\end{fignos:tagged-figure}
+
+\begin{figure}
+\hypertarget{fig:matching_stat}{%
+\centering
+\includegraphics{figures/matching_stat.png}
+\caption{This is an example-figurern}\label{fig:matching_stat}
 }
@@
 \begin{figure}
-\hypertarget{fig:lamella_spatial_info}{%
+\hypertarget{fig:matching_euc}{%
 \centering
-\includegraphics{figures/lamella_spatial_info.pdf}
-\caption{This is an example-figurern}\label{fig:lamella_spatial_info}
+\includegraphics{figures/matching_euc.png}
+\caption{Template matching in lamella imaged using the DeCo-Lace approach at eucentric focus}\label{fig:matching_euc}
 }
@@
 \begin{figure}
-\hypertarget{fig:approach3}{%
+\hypertarget{fig:matching_fff}{%
 \centering
-\includegraphics{figures/example-figure3.pdf}
-\caption{This is an example-figurern}\label{fig:approach3}
-}
-\end{figure}
-
-\begin{figure}
-\hypertarget{fig:approach4}{%
-\centering
-\includegraphics{figures/example-figure4.pdf}
-\caption{This is an example-figurern}\label{fig:approach4}
-}
-\end{figure}
-
-\begin{figure}
-\hypertarget{fig:matching}{%
-\centering
-\includegraphics{figures/matching.pdf}
-\caption{This is an example-figurern}\label{fig:matching}
+\includegraphics{figures/matching_fff.png}
+\caption{This is an example-figurern}\label{fig:matching_fff}
 }
@@
 \centering
-\includegraphics{figures/deco_lace_workflow.pdf}
+\includegraphics{figures/deco_lace_workflow.png}
 \caption{Workflow of DeCo-Lace processing}\label{fig:deco_lace_workflow}

### 2022-04-14 build/build.sh
Disable pdf from html

@@ -63,43 +63,43 @@ pandoc --verbose \
 rm images
 rm graphics
 # Create PDF output (unless BUILD_PDF environment variable equals "false")
-# If Docker is not available, use WeasyPrint to create PDF
-if [ "${BUILD_PDF}" != "false" ] && [ "${MANUBOT_USE_DOCKER}" != "true" ]; then
-  echo >&2 "Exporting PDF manuscript using WeasyPrint"
-  if [ -L images ]; then rm images; fi  # if images is a symlink, remove it
-  ln -s content/images
-  pandoc \
-    --data-dir="$PANDOC_DATA_DIR" \
-    --defaults=common.yaml \
-    --defaults=html.yaml \
-    --defaults=pdf-weasyprint.yaml
-  rm images
-fi
-
-# If Docker is available, use athenapdf to create PDF
-if [ "${BUILD_PDF}" != "false" ] && [ "${MANUBOT_USE_DOCKER}" == "true" ]; then
-  echo >&2 "Exporting PDF manuscript using Docker + Athena"
-  if [ "${CI}" = "true" ]; then
-    # Incease --delay for CI builds to ensure the webpage fully renders, even when the CI server is under high load.
-    # Local builds default to a shorter --delay to minimize runtime, assuming proper rendering is less crucial.
-    MANUBOT_ATHENAPDF_DELAY="${MANUBOT_ATHENAPDF_DELAY:-5000}"
-    echo >&2 "Continuous integration build detected. Setting athenapdf --delay=$MANUBOT_ATHENAPDF_DELAY"
-  fi
-  if [ -d output/images ]; then rm -rf output/images; fi  # if images is a directory, remove it
-  cp -R -L content/images output/
-  docker run \
-    --rm \
-    --shm-size=1g \
-    --volume="$(pwd)/output:/converted/" \
-    --security-opt=seccomp:unconfined \
-    arachnysdocker/athenapdf:2.16.0 \
-    athenapdf \
-    --delay=${MANUBOT_ATHENAPDF_DELAY:-1100} \
-    --pagesize=A4 \
-    manuscript.html manuscript.pdf
-  rm -rf output/images
-fi
-
+## If Docker is not available, use WeasyPrint to create PDF
+#if [ "${BUILD_PDF}" != "false" ] && [ "${MANUBOT_USE_DOCKER}" != "true" ]; then
+#  echo >&2 "Exporting PDF manuscript using WeasyPrint"
[…]

### 2022-04-14 manuscript.tex
Disable pdf from html [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/38fd04bb92cfffb0ea0e0e112da741a0da4b716a.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/38fd04bb92cfffb0ea0e0e112da741a0da4b716a/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2166630527

@@
 This manuscript
-(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/56ce938e8d7fb4ca49b0ca90d4ceca7386ae3b0f/}{permalink})
+(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/38fd04bb92cfffb0ea0e0e112da741a0da4b716a/}{permalink})
 was automatically generated
-from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/56ce938e8d7fb4ca49b0ca90d4ceca7386ae3b0f}{jojoelfe/deco\_lace\_template\_matching\_manuscript@56ce938}
-on April 7, 2022.
+from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/38fd04bb92cfffb0ea0e0e112da741a0da4b716a}{jojoelfe/deco\_lace\_template\_matching\_manuscript@38fd04b}
+on April 14, 2022.
 
@@
 
-ER-HoxA9 cells were maintained in RPMI supplemented with 10\% FBS,
+ER-HoxA9 cells were maintained in RPMI medium supplemented with 10\% FBS,
 penicillin/streptomycin, SCF, and estrogen {[}\protect\hyperlink{ref-1B9Vt9eYu}{12}{]} at
-37C and 5\% CO2. 120h prior to grid freezing cells were washed twice in PBS and
-cultured in the same medium, except without estrogen. Differentiation was
-verified by staining with Hoechst-dye and insepction of nuclear morphology.
-Cells were then counted and diluted to 1\^{}106 cells/ml. Grids ( either 200 mesh
+37C and 5\% CO2. 120h prior to grid preparation, cells were washed twice in PBS
+and cultured in the same medium except without estrogen. Differentiation was
+verified by staining with Hoechst-dye and inspection of nuclear morphology.
+Cells were then counted and diluted to \(1\cdot10^6\) cells/ml. Grids ( either 200 mesh
 copper grids, with a sillicone-oxide and 2um holes with a 2um spacing or 200
-mesh gold grids with a thin gold film and 2 um holes in 2um sapcing) were
-glow-discharged from both sides using a \ldots{} for \ldots{} . 3.5 ul of cells suspension
-was added to grids on the thin-film side and grids were automatically blotted
-from the back-side using a GP2 cryoplunger (Leica) for \ldots{} s and rapidly plunged
-into liquid ethane at -185C.
+mesh gold grids with a thin gold film and 2 um holes in 2um spacing) were
+glow-discharged from both sides using a 15 mA for 45s . 3.5 ul of cell
+suspension was added to grids on the thin-film side and grids were automatically
+blotted from the back side using a GP2 cryoplunger (Leica) for 8 s and rapidly
+plunged into liquid ethane at -185°C.
 
@@
 Grids were loaded into a Acquilos 2 FIB/SEM microscope with a stage cooled to
--190C. Grids were sputter-coated with platinum for 15s at 45 mA and then coated
-with a layer of platinum-precursor by openin the GIS-valve for 45s. An overview
+-190°C. Grids were sputter-coated with platinum for 15s at 45 mA and then coated
+with a layer of platinum-precursor by opening the GIS-valve for 45s. An overview
 of the grid was created by montaging SEM images and isolated cells at the center
 of gridsquares were selected for FB-milling. Lamella were generated
-automatically using the AutoTEM software, resulting in 6-8 um wide lamella with
-150-200 um thickness as determined by FIB-imaging of the lamella edge.
+automatically using the AutoTEM software, with the following parameters:
+
+\begin{itemize}
+\tightlist
+\item
+  Milling angle: 20°
+\item
+  Rough milling: 3.2 µm thickness, 0.5nA current
+\item
+  Medium milling: 1.8 µm thickness, 0.3nA current, 1.0° overtilt
+\item
+  Fine milling: 1.0 µm tchickness, 0.1nA current, 0.5° overtilt
+\item
+  Finer milling: 700 nm thickness, 0.1nA curent, 0.2° overtilt
+\item
+  Polish 1: 450nm thickness, 50 pA current
+\item
+  Polish 2: 200nm thickness, 30 pA current
+\end{itemize}
+
+This resulted in 6-8 um wide lamella with
+150-250nm thickness as determined by FIB-imaging of the lamella edge.
 
@@
 
-Grids were loaded into a Krios Titam TEM operated at 300 keV. The microscope was
-setup with a cross-grating grid on the stageby setting the beam-diameter to 900
-nm, resulting in the beam being completely visible in the camera. To establish
-fringe-free conditions, the ``Fine eucentric'' procedure of serialEM was used to
-move a square of the cross-grating grid to the eucentric position of the
-microscope. The effective defocus was then set to 2 um, using the ``autofocus''
-routine of serialEM. The objective focus of the microscope was changed until no
-fringes were visible. The stage was then moved in Z until images had a apparent
-defocus of 2 um. The differnce in stage Z-position between the eucentric and
-fringe-free conditions was calculate d and noted to move other areas into
-fringe-free condition.
+Grids were loaded into a Krios Titan TEM (Thermore Fisher) operated at 300 keV
+and equipped with a BioQuantum energy filter (Gatan) and K3 camera (Gatan). The
+microscope was aligned using a cross-grating grid on the stage. Prior to each
+session we carefully performed the Image/Beam calibration in nanoprobe. Then we
+set the magnification to a pixel size of 1.76Å and condensed the beam to \textasciitilde{}
+900nm diameter, resulting in the beam being completely visible on the camera.
+To establish fringe-free conditions, the ``Fine eucentric'' procedure of serialEM
+was used to move a square of the cross-grating grid to the eucentric position of
+the microscope. The effective defocus was then set to 2 um, using the
+``autofocus'' routine of serialEM. The objective focus of the microscope was
+changed until no fringes were visible. The stage was then moved in Z until
+images had a apparent defocus of 2 um. The difference in stage Z-position
+between the eucentric and fringe-free conditions was then used to move other
+areas into fringe-free condition.
 
@@
 sufficiently thin and free of contamination were selected for automated data
-collection. The corners of the lamella were manually annotated in SerialEM and
-translated into Beam-Imageshift values using SerialEm calibration. A hexagonal
-patter of beam-imageshift positions was calculated that covered the area between
-he four corners in a serpentine way, with a sqrt(3) * 400 nm horizontal spacing
-and 800 nm vertical spacing. Exposures were then taking at each position with a
-30 e/A total dose. After each exposure that defocus was estimated using the
-ctffind function of SerialEM and the focus for th next exposure was corrected by
-the difference between the estimated focus and the desired defocus of 800 um.
-Also after each exposure the deviation of the beam from the center of the camera
-was measured and corrected using the ``CenterBeamFrom IMage'' command of SerialEM.
+collection. Vverview images of each lamella were taken at 2250x magnification
+(39Å pixel-sixe). The corners of the lamella in the overview image were manually
+annotated in SerialEM and translated into Beam-Imageshift values using SerialEM
+calibration. A hexagonal pattern of Beam-Imageshift positions was calculated
+that covered the area between the four corners in a serpentine way, with a
+sqrt(3) * 400 nm horizontal spacing and 800 nm vertical spacing. Exposures were
+then taken at each position with a 30 e/Å2 total dose. After each exposure that
+defocus was estimated using the ctffind function of SerialEM and the focus for
+the next exposure was corrected by the difference between the estimated focus
+and the desired defocus of 800 nm. Furthermore, after each exposure the
+deviation of the beam from the center of the camera was measured and corrected
+using the ``CenterBeamFromImage'' command of SerialEM.
 
 After datacollection a 20s exposure at 2250x magnification of the lamella at
-200um defocus was taken for visualization purposes.
+200um defocus was taken for visualization purposes. A python script implementing
+this procedure is available at {[}Link to repo{]}.
 
@@
 
-Movies were gain-corrected and motion-corrected using a custom version of
-unblur. To avoid influence of the beam-edge on motion-correction only a quarter
+To avoid influence of the beam-edge on motion-correction only a quarter
 of the movie in the center of the camera was considered for calculation of the
 estimated motion. After movie frames were aligned and summed a mask for the
-illuminated area was calculated by lowpass filtering the image at \ldots{} A,
+illuminated area was calculated by lowpass filtering the image at 100Å,
 thresholding the image at 10\% of the maximal value and then lowpass filtering
-the mask at \ldots{} A. This mask was then used to replace un-illuminated area with
+the mask at 100Å. This mask was then used to replace un-illuminated area with
 gaussian noise, with the same mean and standard deviation as the illuminated
-area. The contrast-transfer function (CTF) was estimated using ctffind, searching
+area. A custom version of the unblur program implementing this procedure is
+available at (TODO).
+The contrast-transfer function (CTF) was estimated using ctffind, searching
 between 0.02 and 2 um defocus.
 
-\hypertarget{template-matching}{%
-\subsubsection{Template matching}\label{template-matching}}
+\hypertarget{dtm}{%
+\subsubsection{2DTM}\label{dtm}}
 
 The search template was generated from the cryo-EM structure of the mouse large
-ribosomal subunit (PDB 6SWA). The \ldots{} subunit was deleted from the model and the
+ribosomal subunit (PDB 6SWA) using the simulate program in cisTEM {[}cite{]}. The
+atomic coordinates corresponding to Epb1 were deleted from the model and the
 simulate program of the cisTEM suite was used to calculate an density map from
 the atomic coordinates. The match\_template program was used to search for this
-template in the preprocessed images, using 1.5 deg angular step in out-of-plane
-angles and 1.0 deg in-plane. 21 defocus planes in 200nm steps centered around
-the defocus estimates by ctffind were searches. Matches were defined as peaks
-above a threshold calulated according to .. .(7.75 for most images).
+template in the preprocessed images, using 1.5° angular step in out-of-plane
+angles and 1.0° in-plane. 11 defocus planes in 20nm steps centered around
+the defocus estimates by ctffind were searched. Matches were defined as peaks
+above a threshold of 7.75, which was chosen based on a one false positive per
+tile criterium {[}cite{]}.
 
-\hypertarget{data-analysis}{%
-\subsubsection{Data analysis}\label{data-analysis}}
+\hypertarget{deco-lace-data-processing}{%
+\subsubsection{DeCo-LACE data processing}\label{deco-lace-data-processing}}
+
+An overview of the data analysis pipeline is shown in Fig.
+\ref{fig:deco_lace_workflow}. Initial coordinates of each Tile \(i\), \(\textbf{c}_{init,i}\) were derived
+from the Beam-Image-Shift of the tile \(BIS_i\) and the ISToCamera matrix
+\(\mathbf{IC}\):
+
+\[\textbf{c}_{init,i} = \mathbf{IC} \cdot BIS_i\]
+
+To refine the montage a list of overlapping tile pairs
+\(|\textbf{c}_i-\textbf{c}_j| < 900\textrm{nm}\) were compiled and the offsets
+\(\textbf{o}_{i,j} = \textbf{c}_i-\textbf{c}_j\) were refined by using a masked
+cross-correlation of the overlap region as implemented in the scikit-image
+package {[}cite{]}. Refined coordinates were then derived by minimizing the
+least-deviation of the new offsets and tile positions:
+
+\[ min\sum_{pairs}{(\textbf{o}_{refined,i,j} - (\textbf{c}_i-\textbf{c}_j))^2}\]
+
+using the scipy package {[}cite{]}. This refinement was then repeated once more.
+
+The x,y coordinates of 2DTM match \(n\) in the tile \(i\), \(\textbf{m}^\textrm{T}_{n,i}\), was
+transformed into the montage frame by adding the coordinate of the tile.
+
+\[ \textbf{m}^\textrm{M}_n = \textbf{m}^\textrm{T}_{n,i} +
+\textbf{c}_i\]
+
+The z coordinate of each match was calculated as the sum of the defocus offset
+for each match, the estimated defocus of the tile, and the nominal defocus of
+the microscope when the tile was acquired. The python scripts used are available
+under {[}repolink{]}.
 
@@
 neutrophils (Fig. \ref{fig:initmatching}A). We then proceeded to acquire
-micrographs on this lamella with a defocus of 0.5-1.0 um, 30 e/A2/s exposure and
-1.5 A pixelsize. We manually selected multiple locations in the lamella and
-focused using standard low-dose techniques where focusing is performed on a
+micrographs on this lamella with a defocus of 0.5-1.0 um, 30 e/Å2/s exposure and
+1.5 Å pixelsize. We manually selected multiple locations in the lamella and
+acquired micrographs using standard low-dose techniques where focusing is performed on a
 sacrificial area. The resulting micrographs showed no signs of crystalline ice
-and had Thon-rings to resolution, indicating successful vitrification.
+and smooth bilayered membranes (Fig. \ref{fig:initmatching}C,D), indicating successful vitrification.
 
-We used an atomic model of the 60S mouse ribosomal subunit (6SWA) for 2D
-template matching. In a subset of images the distribution of cross-correlation
+We used an atomic model of the 60S mouse ribosomal subunit (6SWA) for 2DTM. In a subset of images the distribution of cross-correlation
 scores significantly exceeded the distribution expected from non-signifcant
@@
 images of cytosolic compartments we found evidence of 10-500 ribosomes in the
-imaged areas. Notably we found no matches in images that were taken in the
-nuclear compartment. In the cytosolic areas we found a drastically different
-number of matches, In some areas we found only \textasciitilde{} 50 matches er image area, while
-in another area we found more than 500 matches . This ten-fold difference in
+imaged areas (Fig. \ref{fig:initmatching}B-E). Notably, we found no matches in images ares corresponding to the
+nucleus(Fig. \ref{fig:initmatching}B) or mitochondria (Fig. \ref{fig:initmatching}D). In the cytosolic areas we found a drastically different
+number of matches, In some areas we found only \textasciitilde{} 50 matches per image area (Fig. \ref{fig:initmatching}E), while
+in another area we found more than 500 matches (Fig. \ref{fig:initmatching}C). This ten-fold difference in
 local ribosome concentration , but we realized that current data acquistion
@@
 lamella and (3) uses a focusing strategy that does not rely on a sacrificial
-area.
+area (Fig. \ref{fig:approach}A).
 
@@
 plan is identical to the eucentric plane of the specimen stage. This leaves the
-C2 aperture out of focus, resulting in ripples at the edge of the beam (Figure
-2B). While these ripples are low-resolution features that might not interfere
+C2 aperture out of focus, resulting in ripples at the edge of the beam (Fig. \ref{fig:approach}D). While these ripples are low-resolution features that might not interfere
 with 2D template matching, which is designed to be robust to low-resolution
 noise, we also tested collecting data under a condition where the C2 aperture is
-in focus (Figure 2C).
+in focus (Fig. \ref{fig:approach}E).
 
@@
 the microscope to systematically raster the whole surface of the lamella in a
-hexagonal pattern. Instead of focusing in a sacrificial area, we determined the
-defocus after every exposure using a routine implemented in SerialEM modeled
-after CTFFind. The focus was then adjusted based on the difference between
-desired and measured defocus. Since we used a serpentine pattern for data
+hexagonal pattern(Fig. \ref{fig:approach}A,C). Instead of focusing in a sacrificial area, we determined the
+defocus after every exposure by fitting the Thon rings. The focus was then adjusted based on the difference between
+desired and measured defocus (Fig. \ref{fig:approach}B). Since we used a serpentine pattern for data
 collection every exposure is close to the previous exposure making drastic
@@
 We used this strategy to collect data on 8 lamella, 4 using the eucentric focus
-condition and 4 using the fringe-free condition. We were able to highly
-consistently collect data with a defocus of 8 um (Figure 2D), both in the
-eucentric focus and fringe-free focus condition. Together with the nominal
-defocus of the microscope this data results in a topological map of the lamella.
+condition, from hereon referred to as Lamella\textsubscript{EUC}, and 4 using the fringe-free
+condition, from hereon referred to as Lamella\textsubscript{FFF}(Fig. \ref{fig:lamella_images}).
+We were able to highly consistently collect data with a defocus of 800nm (Fig.
+\ref{fig:approach}F), both in the eucentric focus and fringe-free focus condition.
 To ensure that data was collected consistently, we mapped defocus values as a
-function of the applied Beam-image shift (Figure 2E). This demonstrated that the
-defocus was consistent over the lamella, with outliers only at isolated images
-and in images containing contamination. We also plotted the measure objective
-astigmatism of the lamella and found that it varies with the applied Beam-image
-shift, become more astigmatic mostly due to beam-image shift in the X direction.
-While approaches exist to correct this during the data-collection, we opted to
-not use these mechanism for these early experiments and instead rely on
-computational correction of these aberrations in order to characterize them.
+function of the applied Beam-image shift (Fig. \ref{fig:lamella_spatial_info}A).
+This demonstrated that the defocus was consistent over the lamella, with
+outliers only at isolated images and in images containing contamination. We also
+plotted the measure objective astigmatism of the lamella and found that it
+varies with the applied Beam-image shift, become more astigmatic mostly due to
+beam-image shift in the X direction(Fig. \ref{fig:lamella_spatial_info}B). While
+approaches exist to correct this during the data-collection {[}cite{]}, we opted to not use
+these approaches in our initial experiments. We reasoned that because 2DTM depends on high-resolution information, this would be an excellent test of how much these aberration affect imaging.
 
-\hypertarget{d-template-matching-of-cryo-emilia-data-reveals-ribosome-distribution}{%
-\subsubsection{2D-Template matching of cryo-EMILIA data reveals ribosome distribution}\label{d-template-matching-of-cryo-emilia-data-reveals-ribosome-distribution}}
+We assembled the tile micrographs into a montage using the Beam-Image-shift value and the SerialEM calibration followed by cross-correlation based refinement (see Methods).
+In the resulting montages the same cellular features than in the overview images are apparent (Fig.
+\ref{fig:lamella_spatial_info}G-J), however due to the high magnification and low defocus many more details, such as the membrane bilayer seperation can be observed.
+For montages collected using the eucentric there are clearly visible fringes at the edges between the tiles, which are absent in the fringe-free focus montage.
+However, it is unclear whether these fringes impede molecular detection or due to their low-resolution nature are only an aesthetic issue.
+We also note that the tiling pattern is visible in the montages, which we believe is due to the non-linear behaviour of the K3 camera (see Dicussion).
 
-We developed customized preprocessing protocol to images obtained by cryo-EMILIA
-to enable their use for 2D-template matching. First we restricted calculation of
-cross-correlation coefficients between individual movie frames to the central
-portion of the image to prevent artifacts from the beam edges on estimation of
-motion {[}Figure S{]}. Then we calculated a mask that defined the illuminated area
-of the micrographs and used it to fill non-illumated areas with gaussian noise,
-matching mean and standard deviation to the illuminated signal (Figure S). The
-so processed images were suitable for 2D-template matching and we were able to
-obtained matches with the same model used for the data in Figure 1.
+While inspecting the montages we noticed that the membrane vesicles and granules are highly variable in size and electron density of their content.
+We found furthermore that a substantial number of granules with a high electron density seemed to contain a membrane-enclosed inclusion with electron-density similar to the surrounding cytosol (Fig.
+{[}TODO{]}).
+{[}Describe measurements{]}
 
-We then matched all individual tiles for ribosomes and assembled a montaged view
-as described above (Figure \ref{fig:matching} A+G). The resulting montages reveal
-ribsome distribution throughout the FIB-milled slice of individual cells.
-Organelles like the nucleus and mitochondria only show sporadic matches with low
-SNRs, consistent with the estimated false-positive rate on one per tile. During
-the assembly we calculated the Z positions from the indivdual estimated defocus
-levels and the focus plane of the microscope during acquisition of each tile.
-When viewed from the side the ribosome position therefore show the slope of the
-lamella in the microscope frame. Furthermore, the positions are also consistent
-with an uneven thickness of the lamella, thinner at the leading edge, even
-though, lamella were generated using the ``overtilt'' approach {[}cite{]}.
+\hypertarget{dtm-of-deco-lace-data-reveals-ribosome-distribution-in-cellular-cross-sections}{%
+\subsubsection{2DTM of DeCo-LACE data reveals ribosome distribution in cellular cross-sections}\label{dtm-of-deco-lace-data-reveals-ribosome-distribution-in-cellular-cross-sections}}
 
-\hypertarget{quantitative-analysis-of-translation-activity}{%
-\subsubsection{Quantitative analysis of translation activity}\label{quantitative-analysis-of-translation-activity}}
+In initial attempts of using 2DTM on micrographs acquired with the DeCo-LACE
+protocol, we did not observe any SNR peaks above threshold using the large
+subunit of the mouse ribosome (Fig. \ref{fig:crop_unblur}A). We reasoned that the
+edges of the beam might interfere with motion-correction of the movie as they
+would remain stationary or move differently than the sample. Indeed when we
+cropped movie to exclude the beam edges we found that the estimated motion was
+larger than estimated on the uncropped movie (Fig. \ref{fig:crop_unblur}B).
+Furthermore, in the motion-corrected average we could identify SNR peaks above
+detection threshold (Fig. \ref{fig:crop_unblur}B), indicating that 2DTM is very
+sensitive to accurate motion correction and that the beam edge did interfere
+with motion-correction. In order to avoid having to crop the movies we
+implemented a function in unblur to consider only the cropped area for
+estimation of shifts, but average the complete movie (Fig. \ref{fig:crop_unblur}B).
+Using this approach we motion-corrected all tiles in the 8 lamella and found
+consistently total motion below 1Å per frame (Fig.
+\ref{fig:lamella_motion_thickness} A). In some lamella we found increased motion in
+the center of the lamella, which indicates that mechanical stability of
+FIB-milled lamella might not be homogeneous over the lamella surface. In some
+micrographs we also observed that the beam edges gave rise to artifacts in the
+cross-correlation mip and numerous false-positive matches at the edge of the
+illuminated area (Fig. TODO). A similar phenomenon was observed on isolated
+``hot'' pixels in the unilluminated area. To overcome this issue we implemented a
+function in unblur to replace unillluminated areas in the micrograph with
+gaussian noise, with mean and standard deviation matched to the illuminated
+portion of the micrograph (Fig. TODO). Together, these special pre-processing
+steps enabled us to perform 2DTM on all tiles of the 8 lamellae.
+
+We then used the refined tile positions to calculate the positions of the
+matched LSUs in the lamellae (Fig. \ref{fig:matching_euc} A, Fig.
+\ref{fig:matching_fff} A). Overlaying these positions of the lamella montages
+reveal ribsome distribution throughout the FIB-milled slice of individual cells.
+Organelles like the nucleus and mitochondria only showed sporadic matches with
+low SNRs, consistent with the estimated false-positive rate on one per tile.
+During the assembly we calculated the Z positions from the indivdual estimated
+defocus levels and the focus plane of the microscope during acquisition of each
+tile. When viewed from the side the ribosome position therefore show the slope
+of the lamella in the microscope frame (Fig. \ref{fig:matching_euc} B, Fig.
+\ref{fig:matching_fff} B). Furthermore, the side-views indicated that lamellae were
+thinner at the leading edge. Indeed, when we plotted the electron intensities in
+individual tiles as a function of Beam-Image shift we observed substantially
+higher intensities at the leading edge, which in energy-filtered TEM indicates a
+thinner sample {[}cite{]}. Even though we prepared the lamellae with the ``overtile''
+approach {[}cite{]}, this means that ribosome densities across the lamellae can be
+schewed by the changes in thickness and better sample preparation methods are
+needed to generate more even samples.
+
+Close inspection of the ribosome positions in the lamellae revealed multi
+interesting features. Ribosomes could be seen associating with the membrane, in
+patterns reminiscent of the rough endoplasmic reticulum (Fig.
+\ref{fig:matching_euc} C, Fig. \ref{fig:matching_fff} C) or the outer nuclear membrane
+(Fig. \ref{fig:matching_euc} D). We also observed ribosomes forming ring-like
+structures (Fig. \ref{fig:matching_euc} E), potentially indicating circularized
+mRNAs {[}cite{]}. While ribosomes were for the most part excluded from the numerous
+granules observed in the cytoplasm, in some circumstances we observed clusters
+of ribosomes in the lower electron density inclusion in the class of
+double-membraned granules described earlier (Fig. \ref{fig:matching_euc} F, Fig.
+\ref{fig:matching_fff} D,E). It is, in principle, possible that these matches are
+situated above or below the imaged granule, since the granules position in Z
+cannot be determined using a 2D projection. However, in the case of Fig.
+\ref{fig:matching_fff} E, the matched ribosomes span the whole lamella in the Z
+direction, while a position above or below the granule would result in ribosome
+situated exlusively at the top or bottom of the lamella. This conclusive
+evidence of ribosomes in the inclusion is consistent with the earlier hypothesis
+that the inclusion is of cytoplasmic origin.
+
+Between the 8 lamellae we found different number of matches (Fig.
+\ref{fig:matching_stat} A). Lamella\textsubscript{EUC} 1 resulted in the most matches, but also has the largest surface area and contained
+cytoplasm of two cells. Lamella\textsubscript{FFF} 4 had the fewest matches, but this particular slice was dominated by a circular
+nucleus slice, with only small pockets of cytoplasm (Fig.
+\ref{fig:lamella_images}). In an attempt to normalize for these differences in
+lamella surface area we compared the number of matches per tile in tiles which
+contained more than one match, which should exclude tiles with non-cytosolic
+content (Fig. \ref{fig:matching_stat} B). While this measure had less variablity,
+there were still differences. Lamella\textsubscript{EUC} 4 had not only the fewest
+matches, but also the lowest density, which could be due to the thickness of the
+lamella or due to a slice through low-ribosome content region. Lamella\textsubscript{FFF}
+3 had substantially higher number of ribosomes per tile. Since all
+of these lamella were milled into identical cells under identical conditions,
+this underscores the necessity to collect data on large numbers of lamella in
+order to overcome inherent variability. When comparing the distribution of
+scores between the lamella we found them to be fairly comparable with a median
+of \ldots. Lamella\textsubscript{EUC} 1 had slightly lower scores compared to others,
+potentially due to the large size and connected mechanical instabillity during
+imaging. Overall we did not observe a difference in number or SNR of matches between eucentric or fringe-free focus illumination that was bigger that inter-lamella variability.
+
+Since the SNR values of 2DTM are highly sensitive to image quality we reasoned we could use them to verify that DeCo-LACE does not introduce systematic errors.
+We first wondered whether the unusually condensed beam would be prone to non-parallel illumination or whether at the outside of the beam unknown aberration would distort the image.
+We reasoned that this would lead to lower SNR values at the inside edge of the illuminated area.
+When we plotted SNR values in all 8 lamellae as a function of there location in tiles we found high SNR value up to the edge of the illuminated area for both eucentric and fringe-free focus illumination, again demonstrating that both illumination schemed are suitable for DeCo-LACE.
+
+We also wondered whether high Beam-Image shift values would lead aberration due to the astigmatism or beam tilt {[}cite{]}. {[}TODO plot scores vs BIS, euc vs fff{]}
+
+\hypertarget{computation-is-the-bottleneck-of-visual-proteomics}{%
+\subsubsection{Computation is the bottleneck of visual proteomics}\label{computation-is-the-bottleneck-of-visual-proteomics}}
+
+As described above the variability of lamella, both in terms of technique such as area, thickness and mechanical stability, and of biology, such as selection of cell and location of the slice in relation to the complete cell, could be overcome by collecting orders of magnitude more data.
+This will be essential to allow robust statistical comparisons of macromolecule number and location between different experimental conditions.
 
@@
   Throughput and bottlenecks
+\item
+  lamella mechanical properties, radiation damage, other ways to to thin?
+\item
+  eucentric vs fringe free illumination
 \item
@@
 \includegraphics{figures/matching_stat.png}
-\caption{This is an example-figurern}\label{fig:matching_stat}
+\caption{Statistics of 2DTM on lamella imaged using DeCo-LACE (A) Number of matches of
+each lamella (B) Distribution of matches per tile in each lamella. Only tiles
+with two or more matches were included (C) Distribution of SNRs in each lamella
+(D) For each lamella an average of all tiles is shown. Overlaid is a scatterplot
+of all matches in these tiles according to their in-tile coordinates.
+Scatterplot is color according to the SNR. There are no matches in the top
+circle-circle intersection due to radiation damage from previous exposures.}\label{fig:matching_stat}
 }
@@
 \includegraphics{figures/matching_euc.png}
-\caption{Template matching in lamella imaged using the DeCo-Lace approach at eucentric focus}\label{fig:matching_euc}
+\caption{Template matching in lamella imaged using the DeCo-Lace approach at eucentric
+focus (A) Montage of Lamella\(_\textrm{EUC}\) 1 overlaid with matches according to
+their montage coordinates (B) Side view of matches in the lamella, such that the
+direction of the electron beam is horizontal. (C-F) Magnified area of panel A
+showing rough ER with associated ribosomes(C), outer nuclear membrane with
+associated ribosomes (D), ribsomes arranged in a circular fashion(E), ribosomes
+enclosed in a less electron dense inclusion in a granule(F).}\label{fig:matching_euc}
 }
@@
 \includegraphics{figures/matching_fff.png}
-\caption{This is an example-figurern}\label{fig:matching_fff}
+\caption{Template matching in lamella imaged using the DeCo-Lace approach at fringe-free
+focus (A) Montage of Lamella\(_\textrm{FFF}\) 4 overlaid with matches according to
+their montage coordinates (B) Side view of matches in the lamella, such that the
+direction of the electron beam is horizontal. (C-E) Magnified area of panel A
+showing rough ER with associated ribosomes(C) and ribosomes
+enclosed in a less electron dense inclusion in a granule(D,E). (F) Side view of
+panel E with ribosomes situated inside the granule colored accoding
+to SNR and other ribosomes colored in grey.}\label{fig:matching_fff}
 }
@@
 \leavevmode\vadjust pre{\hypertarget{ref-tSXIKPl7}{}}%
-\CSLLeftMargin{1. }
+\CSLLeftMargin{1. }%
 \CSLRightInline{\textbf{Label-free, normalized quantification of complex mass spectrometry data for proteomic analysis}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-VBmW7Aot}{}}%
-\CSLLeftMargin{2. }
+\CSLLeftMargin{2. }%
 \CSLRightInline{\textbf{Fluorescence microscopy}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-tGQ6TSUo}{}}%
-\CSLLeftMargin{3. }
+\CSLLeftMargin{3. }%
 \CSLRightInline{\textbf{A visual approach to proteomics}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-g8QavfwP}{}}%
-\CSLLeftMargin{4. }
+\CSLLeftMargin{4. }%
 \CSLRightInline{\textbf{Electron microscopy of frozen hydrated sections of vitreous ice and vitrified biological samples}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-16IhS1Nc4}{}}%
-\CSLLeftMargin{5. }
+\CSLLeftMargin{5. }%
 \CSLRightInline{\textbf{Opening windows into the cell: focused-ion-beam milling for cryo-electron tomography}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Rksh2dxu}{}}%
-\CSLLeftMargin{6. }
+\CSLLeftMargin{6. }%
 \CSLRightInline{\textbf{Electron tomography of cells}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Ynb3IP6I}{}}%
-\CSLLeftMargin{7. }
+\CSLLeftMargin{7. }%
 \CSLRightInline{\textbf{Single-protein detection in crowded molecular environments in cryo-EM images}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-18KGpXYPE}{}}%
-\CSLLeftMargin{8. }
+\CSLLeftMargin{8. }%
 \CSLRightInline{\textbf{Label-free single-instance protein detection in vitrified cells}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-10bXZuF3G}{}}%
-\CSLLeftMargin{9. }
+\CSLLeftMargin{9. }%
 \CSLRightInline{\textbf{Locating macromolecular assemblies in cells by 2D template matching with cisTEM}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-gRoY21jY}{}}%
-\CSLLeftMargin{10. }
+\CSLLeftMargin{10. }%
 \CSLRightInline{\textbf{Hallmarks of ribosomopathies}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-KAJ7221k}{}}%
-\CSLLeftMargin{11. }
+\CSLLeftMargin{11. }%
 \CSLRightInline{\textbf{Diagnostic and prognostic implications of ribosomal protein transcript expression patterns in human cancers}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1B9Vt9eYu}{}}%
-\CSLLeftMargin{12. }
+\CSLLeftMargin{12. }%
 \CSLRightInline{\textbf{Inhibition of Dihydroorotate Dehydrogenase Overcomes Differentiation Blockade in Acute Myeloid Leukemia}

### 2022-04-14 content/code/refine_initial_match.py
minor processing

@@ -5,8 +5,36 @@ from pathlib import Path
 
 pycistem.set_cistem_path("/groups/elferich/cisTEM/build/refine_template_tests_Intel-gpu-debug/src/")
 
+#pa = pycistem.programs.refine_template.parameters_from_database("/scratch/bern/elferich/ER_HoxB8_96h/ER_HoxB8_96h.db",
+#                                                                     186,
+#                                                                     template_match_id=4,
+#                                                                     wanted_threshold=7.76,
+#                                                                     input_reconstruction="/groups/elferich/mammalian_ribosome_structures/6swa_simulate_bfsca1_5.mrc",)
+#print(pa)
+#res_my = pycistem.programs.refine_template.run([pa],num_procs=1,)
+#
+#
+#directory = Path("/scratch/bern/elferich/decolace_manuscript_processing/initial_matching/")
+#directory.mkdir(parents=True,exist_ok=True)
+#
+#pycistem.programs.refine_template.write_starfile(res_my, str(directory / "506_matches.star"))
+#
+#pa = pycistem.programs.refine_template.parameters_from_database("/scratch/bern/elferich/ER_HoxB8_96h/ER_HoxB8_96h.db",
+#                                                                     185,
+#                                                                     template_match_id=4,
+#                                                                     wanted_threshold=7.76,
+#                                                                     input_reconstruction="/groups/elferich/mammalian_ribosome_structures/6swa_simulate_bfsca1_5.mrc",)
+#print(pa)
+#res_my = pycistem.programs.refine_template.run([pa],num_procs=1)
+#
+#
+#directory = Path("/scratch/bern/elferich/decolace_manuscript_processing/initial_matching/")
+#directory.mkdir(parents=True,exist_ok=True)
+#
+#pycistem.programs.refine_template.write_starfile(res_my, str(directory / "30_matches.star"))
+ 
 pa = pycistem.programs.refine_template.parameters_from_database("/scratch/bern/elferich/ER_HoxB8_96h/ER_HoxB8_96h.db",
-                                                                     186,
+                                                                     184,
                                                                      template_match_id=4,
                                                                      wanted_threshold=7.76,
                                                                      input_reconstruction="/groups/elferich/mammalian_ribosome_structures/6swa_simulate_bfsca1_5.mrc",)
@@ -17,5 +45,18 @@ res_my = pycistem.programs.refine_template.run([pa],num_procs=1)
[…]

### 2022-05-19 figures/approach.tex
minor edits [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/5f9575bbee2059d4e92d5c821f29682c4a661e49.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/5f9575bbee2059d4e92d5c821f29682c4a661e49/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2354476139

--- 2022-03-29 figures/approach.tex
@@
     \usetikzlibrary{fit}
+    \usetikzlibrary{calc}
+    \def\centerarc[#1](#2)(#3:#4:#5){ \draw[#1] ($(#2)+({#5*cos(#3)},{#5*sin(#3)})$) arc (#3:#4:#5); }
+    \usetikzlibrary{3d}
     \usetikzlibrary{backgrounds}
@@
     \newcommand{\figwidth}{20cm} 
-    \newcommand{\figheight}{15cm} 
+    \newcommand{\figheight}{10cm} 
     \newcommand{\fontselect}{\large\bf} 
@@
 
-    \node (anchor) at (0.5,14.35) {}; 
+    \node (anchor) at (0.5,9.35) {}; 
 \node[labelNode] {A};
 \node[graphicNode] {\includegraphics[width=5cm]{content/graphics/approach/approach.png}};
-\draw [densely dotted, red,thick] (3,14.5) -- (3,10);
-\draw [densely dotted, red,thick] (3,9.2) -- (3,6.4);
+\draw [densely dotted, red,thick] (3,9.5) -- (3,5.0);
+\draw [densely dotted, red,thick] (3,4.2) -- (3,1.4);
 
@@
 
-\draw (3.55,10.4) -- ++(0,1.5) coordinate (D1) -- +(0,5pt);
-\draw (4.15,10.4) -- ++(0,1.5) coordinate (D2) -- +(0,5pt);
+\draw (3.55,5.4) -- ++(0,1.5) coordinate (D1) -- +(0,5pt);
+\draw (4.15,5.4) -- ++(0,1.5) coordinate (D2) -- +(0,5pt);
 \draw [dimen] (D1) -- (D2) node {$D_{Beam}$};
 
-\draw [->, very thick] (3,10) -- ++(0.5,-0.2)  coordinate (S1) node[midway,below left] {$IS_X$} ;
-\draw [->, very thick] (S1) -- (3.85,10.4) node[midway,below right] {$IS_Y$};
+\draw [->, very thick] (3,5) -- ++(0.5,-0.2)  coordinate (S1) node[midway,below left] {$BIS_X$} ;
+\draw [->, very thick] (S1) -- (3.85,5.4) node[midway,below right] {$BIS_Y$};
 
-\node (anchor) at (6.0,14.35) {}; 
+\node (anchor) at (6.0,9.35) {}; 
 \node[labelNode] {B};
@@
 % Place nodes
-\node [block] (init) at (8.0,13.35) {\textbf{START} \\ Collect overview image};
+\node [block] (init) at (8.0,8.35) {\textbf{START} \\ Collect overview image};
 \node [block, below = 0.3cm of init.south] (identify) {Setup hexagonal grid covering lamella area};
@@
 
-\node (anchor) at (11.5,14.35) {}; 
+\node (anchor) at (11.5,9.35) {}; 
 \node[labelNode] {C};
-\node[graphicNode] {\includegraphics[width=8cm]{content/images/ac_strategy.png}};
+% X axis is 9.4um
+\node[graphicNode] (image) {\includegraphics[width=8cm]{content/code/img/acquisition_positions.png}};
+\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]image.south west) -- ([xshift=1.35cm, yshift=0.3cm]image.south west);
+\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]image.south west) -- ([xshift=1.35cm, yshift=0.3cm]image.south west);
 \iftoggle{draft}{\node [redAnchorNode] {};};
 
-\node (anchor) at (0.5,4.5) {}; 
-\node[labelNode] {C};
+\node (anchor) at (0.5,-0.5) {}; 
+\node[labelNode] {D};
 \node[graphicNode] (euc) {\includegraphics[height=4.0cm]{content/images/fringebeam.png}};
-\node[above = 0cm and 0cm of euc.north] {Eucentric Focus};
-
+\node[anchor=center] at ([shift={(0.0cm,0.3cm)}]euc.north) {Eucentric Focus};
+\draw [line width=1.25mm,white] ([xshift=-0.05cm, yshift=0.1cm]euc.south east) -- ([xshift=-0.8cm, yshift=0.1cm]euc.south east);
 \iftoggle{draft}{\node [redAnchorNode] {};};
 
-\node (anchor) at (5.5,4.5) {}; 
-\node[labelNode] {D};
+\node (anchor) at (5.5,-0.5) {}; 
+\node[labelNode] {E};
 \node[graphicNode] (fff) {\includegraphics[height=4.0cm]{content/images/nofringebeam.png}};
-\node[above = 0cm and 0cm of fff.north] {Fringe-free Focus};
+\node[anchor=center] at ([shift={(0.0cm,0.3cm)}]fff.north) {Fringe-free Focus};
+\draw [line width=1.25mm,white] ([xshift=-0.05cm, yshift=0.1cm]fff.south east) -- ([xshift=-0.8cm, yshift=0.1cm]fff.south east);
 \iftoggle{draft}{\node [redAnchorNode] {};};
 
-\node (anchor) at (10.5,4.5) {}; 
-\node[labelNode] {E};
+\node (anchor) at (10.5,-0.5) {}; 
+\node[labelNode] {F};
 \node[anchor=north west, below right=-0.5cm and 0cm of anchor] {\includegraphics[height=4.8cm]{content/code/img/defocusplot.pdf}};
 \iftoggle{draft}{\node [redAnchorNode] {};};
-
     \iftoggle{draft}{\draw[lightgray,step=1] (0,0) grid (\figwidth,\figheight);}{};

### 2022-05-19 figures/assembly.tex
minor edits [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/5f9575bbee2059d4e92d5c821f29682c4a661e49.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/5f9575bbee2059d4e92d5c821f29682c4a661e49/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2354476139

--- 2022-03-29 figures/approach.tex
@@
     \setlist{nosep,leftmargin=*}
-    \newcommand{\figwidth}{20cm} 
-    \newcommand{\figheight}{15cm} 
+    \newcommand{\figwidth}{15cm} 
+    \newcommand{\figheight}{5cm} 
     \newcommand{\fontselect}{\large\bf} 
@@
 
-    \node (anchor) at (0.5,14.35) {}; 
+    \def\panelheight{6.0cm}
+
+\node (anchor) at (0.5,13.0) {}; 
 \node[labelNode] {A};
-\node[graphicNode] {\includegraphics[width=5cm]{content/graphics/approach/approach.png}};
-\draw [densely dotted, red,thick] (3,14.5) -- (3,10);
-\draw [densely dotted, red,thick] (3,9.2) -- (3,6.4);
+\node[graphicNode] (img) {\includegraphics[height=\panelheight,trim=0.0 0 0cm 0, clip]{content/images/euc_lamella1_view.png}};
+% Title
+\node[anchor=center,align=center] at ([shift={(0.0cm,0.6cm)}]img.north) {\baselineskip=8pt   \\ 38Å pixel size \\ 300μm defocus};
+% scalebar - physical height is 12810 nm
+\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]img.south west) -- ([xshift=0.5cm + \panelheight / 12.81 , yshift=0.3cm]img.south west);
+\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]img.south west) -- ([xshift=0.5cm + \panelheight / 12.81, yshift=0.3cm]img.south west);
 
-\tikzset{dimen/.style={<->,>=latex,thin,every rectangle node/.style={above right=0.2cm and -0.3cm,fill=white,midway,font=\sffamily}}}
+\node (anchor) at (5.5,13.0) {}; 
+\node[labelNode] {B};
+\node[graphicNode] (img) {\includegraphics[height=6.0cm,trim=0 0 0cm 0, clip]{content/images/euc_lamella1_assm.png}};
+\node[anchor=center,align=center] at ([shift={(0.0cm,0.7cm)}]img.north) {\baselineskip=8pt Eucentric Focus \\ 1.76Å pixel size \\ 800nm defocus};
+% Red Box
+\node (rect) at (6.52,10.78) [anchor=center,draw,thick,minimum width=0.375cm,minimum height=0.469cm,color=red] {};
+% scalebar - physical height is 12810 nm
+\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]img.south west) -- ([xshift=0.5cm + \panelheight / 12.81 , yshift=0.3cm]img.south west);
+\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]img.south west) -- ([xshift=0.5cm + \panelheight / 12.81, yshift=0.3cm]img.south west);
 
-\draw (3.55,10.4) -- ++(0,1.5) coordinate (D1) -- +(0,5pt);
-\draw (4.15,10.4) -- ++(0,1.5) coordinate (D2) -- +(0,5pt);
-\draw [dimen] (D1) -- (D2) node {$D_{Beam}$};
+\node (anchor) at (10.6,13.0) {}; 
+\node[labelNode] {C};
+% height is 750 nm
+\node[graphicNode] (image) {\includegraphics[height=6.0cm]{content/images/euc_lam1_zoomin.png}};
+\node (n3) [box=red, fit=(image)] {};
+\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]image.south west) -- ([xshift=1.3cm, yshift=0.3cm]image.south west);
+\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]image.south west) -- ([xshift=1.3cm, yshift=0.3cm]image.south west);
 
-\draw [->, very thick] (3,10) -- ++(0.5,-0.2)  coordinate (S1) node[midway,below left] {$IS_X$} ;
-\draw [->, very thick] (S1) -- (3.85,10.4) node[midway,below right] {$IS_Y$};
+\node (anchor) at (0.5,5.0) {}; 
+\node[labelNode] {D};
+\node[graphicNode] (img) {\includegraphics[height=6.0cm,trim=0 0 0cm 0, clip]{content/images/fff_lamella4_view.png}};
+\node[anchor=center,align=center] at ([shift={(0.0cm,0.6cm)}]img.north) {\baselineskip=8pt  \\ 38Å pixel size \\ 300μm defocus};
+% scalebar - physical height is 9337.5 nm
+\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]img.south west) -- ([xshift=0.5cm + \panelheight / 9.3375 , yshift=0.3cm]img.south west);
+\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]img.south west) -- ([xshift=0.5cm + \panelheight / 9.3375, yshift=0.3cm]img.south west);
 
-\node (anchor) at (6.0,14.35) {}; 
-\node[labelNode] {B};
+\node (anchor) at (5.8,5.0) {}; 
+\node[labelNode] {E};
+\node[graphicNode] (img) {\includegraphics[height=6.0cm,trim=0 0 0cm 0, clip]{content/images/fff_lamella4_assm.png}};
+\node[anchor=center,align=center] at ([shift={(0.0cm,0.7cm)}]img.north) {\baselineskip=2pt Fringe-free Focus \\ 1.76Å pixel size \\ 800nm defocus};
+\node (rect) at (8.438,3.83) [anchor=center,draw,thick,minimum width=0.375cm,minimum height=0.469cm,color=red] {};
+% scalebar - physical height is 9337.5 nm
+\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]img.south west) -- ([xshift=0.5cm + \panelheight / 9.3375 , yshift=0.3cm]img.south west);
+\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]img.south west) -- ([xshift=0.5cm + \panelheight / 9.3375, yshift=0.3cm]img.south west);
 
-% Place nodes
-\node [block] (init) at (8.0,13.35) {\textbf{START} \\ Collect overview image};
-\node [block, below = 0.3cm of init.south] (identify) {Setup hexagonal grid covering lamella area};
-\node [block, below = 0.3cm of identify.south] (mutate) {Beam-imageshift to tile n=i};
-\node [block, below = 0.3cm of mutate.south] (transfer) {Capture exposure and determine defocus by CTF fitting};
-\node [block, below = 0.3cm of transfer.south] (evaluate) {Adjust defocus by difference between expected and measured value};
-
-% Draw edges
-\path [line] (init) -- (identify);
-\path [line] (identify) -- (mutate);
-\path [line] (mutate) -- (transfer);
-\path [line] (transfer) -- (evaluate);
-\path [line] (evaluate) -|  ([xshift=0.5cm, yshift=0cm]transfer.east) |- (mutate);
-
-\node (anchor) at (11.5,14.35) {}; 
-\node[labelNode] {C};
-\node[graphicNode] {\includegraphics[width=8cm]{content/images/ac_strategy.png}};
-\iftoggle{draft}{\node [redAnchorNode] {};};
-
-\node (anchor) at (0.5,4.5) {}; 
-\node[labelNode] {C};
-\node[graphicNode] (euc) {\includegraphics[height=4.0cm]{content/images/fringebeam.png}};
-\node[above = 0cm and 0cm of euc.north] {Eucentric Focus};
-
-\iftoggle{draft}{\node [redAnchorNode] {};};
-
-\node (anchor) at (5.5,4.5) {}; 
-\node[labelNode] {D};
-\node[graphicNode] (fff) {\includegraphics[height=4.0cm]{content/images/nofringebeam.png}};
-\node[above = 0cm and 0cm of fff.north] {Fringe-free Focus};
-\iftoggle{draft}{\node [redAnchorNode] {};};
-
-\node (anchor) at (10.5,4.5) {}; 
-\node[labelNode] {E};
-\node[anchor=north west, below right=-0.5cm and 0cm of anchor] {\includegraphics[height=4.8cm]{content/code/img/defocusplot.pdf}};
-\iftoggle{draft}{\node [redAnchorNode] {};};
-
+\node (anchor) at (11.0,5.0) {}; 
+\node[labelNode] {F};
+% height is 750 nm
+\node[graphicNode] (image) {\includegraphics[height=6.0cm]{content/images/fff_lam4_zoomin.png}};
+\node (n3) [box=red, fit=(image)] {};
+\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]image.south west) -- ([xshift=1.3cm, yshift=0.3cm]image.south west);
+\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]image.south west) -- ([xshift=1.3cm, yshift=0.3cm]image.south west);
     \iftoggle{draft}{\draw[lightgray,step=1] (0,0) grid (\figwidth,\figheight);}{};

### 2022-05-19 figures/crop_unblur.tex
minor edits [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/5f9575bbee2059d4e92d5c821f29682c4a661e49.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/5f9575bbee2059d4e92d5c821f29682c4a661e49/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2354476139

@@
 
+\node (anchor) at ([shift={(0.0,-1.0cm)}]0.5,9.5 |- panel.south east) {}; 
+\node[labelNode] {D};
+\node[graphicNode] (panel) {\includegraphics[height=5cm]{content/images/deco_unblur/zap000.png}};
+\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
+\node[graphicNode] (panel2) {\includegraphics[height=5cm]{content/images/deco_unblur/zap002.png}};
+
+\node (anchor) at ([shift={(1.5,0.0cm)}] panel.north east) {}; 
+\node[labelNode] {E};
+\node[graphicNode] (panel) {\includegraphics[height=5cm]{content/images/deco_unblur/zap001.png}};
+\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
+\node[graphicNode] (panel) {\includegraphics[height=5cm]{content/images/deco_unblur/zap004.png}};
+
     \iftoggle{draft}{\draw[lightgray,step=1] (0,0) grid (\figwidth,\figheight);}{};

### 2022-05-19 figures/matching_fff.tex
minor edits [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/5f9575bbee2059d4e92d5c821f29682c4a661e49.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/5f9575bbee2059d4e92d5c821f29682c4a661e49/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2354476139

@@
 
+\newlength{\panelheight}
+\setlength{\panelheight}{12cm}
+
 \node (anchor) at (0.5,9.5) {}; 
 \node[labelNode] {A};
-\node[graphicNode] {\includegraphics[height=12cm]{content/images/fff_lamella4_1000px.png}};
-\node[graphicNode] {\includegraphics[height=12cm]{content/images/fff_lamella4_just_matches.png}};
+\node[graphicNode] (assm) {\includegraphics[height=\panelheight]{content/images/fff_lamella4_assm.png}};
+\node[graphicNode] {\includegraphics[height=\panelheight]{content/images/fff_lamella4.png}};
+\node (rect) at (5.35,5.5) [anchor=center,draw,thick,minimum width=0.4cm,minimum height=0.4cm,color=red] {};
+\node (rect) at (8.05,1.75) [anchor=center,draw,thick,minimum width=0.6cm,minimum height=0.6cm,color=green] {};
+\node (rect) at (6.45,-1.23) [anchor=center,draw,thick,minimum width=0.5cm,minimum height=0.5cm,color=blue!60] {};
+% scalebar - physical height is 9337.5nm
+\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]assm.south west) -- ([xshift=0.5cm + \panelheight / 9.3375 , yshift=0.3cm]assm.south west);
+\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]assm.south west) -- ([xshift=0.5cm + \panelheight / 9.3375, yshift=0.3cm]assm.south west);
 
@@
 \node[labelNode] {B};
-\node[anchor=north west, below right=0cm and -4cm of anchor] {\includegraphics[height=12cm]{content/images/fff_lamella4_just_matches_side.png}};
+\node[anchor=north west, below right=0cm and 0.0cm of anchor] (side) {\includegraphics[height=12cm, trim=15.5cm 0 2cm 0]{content/images/fff_lamella4_side.png}};
 
+\draw [->, thick] ($ (assm.east) + (0.1,0) $) -- node[above=0.2cm, align=center] (c) {} ($ (side.west) + (0.2,0) $);
+
+\centerarc [canvas is zx plane at y=0.75, ->](c.center)(-90:180:0.15);
+\draw [very thick] ($ (c.center) + (0,-0.1) $) -- ($ (c.center) + (0,0.2) $);
+\node at ($ (c.center) + (0.5,0) $) {90°};
+
+\newlength{\panelheightm}
+\setlength{\panelheightm}{2.8cm}
 \node (anchor) at (13.0,9.5) {}; 
 \node[labelNode] {C};
-\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/fff_lamella4_just_matches_det3.png}};
+\node[graphicNode] (pan) {\includegraphics[height=2.8cm]{content/images/fff_lamella4_detail2.png}};
+\node (n3) [box=red, fit=(pan)] {};
+% scalebar - physical height is 300 nm
+\draw [line width=1.55mm,white] ([xshift=0.2cm, yshift=0.2cm]pan.south west) -- ([xshift=0.2cm + \panelheightm / 3 , yshift=0.2cm]pan.south west);
+\draw [line width=0.7mm,black] ([xshift=0.2cm, yshift=0.2cm]pan.south west) -- ([xshift=0.2cm + \panelheightm / 3, yshift=0.2cm]pan.south west);
 
@@
 \node[labelNode] {D};
-\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/fff_lamella4_just_matches_det1.png}};
+\node[graphicNode] (pan) {\includegraphics[height=2.8cm]{content/images/fff_lamella4_detail1.png}};
+\node (n3) [box=green, fit=(pan)] {};
+% scalebar - physical height is 500 nm
+\draw [line width=1.55mm,white] ([xshift=0.2cm, yshift=0.2cm]pan.south west) -- ([xshift=0.2cm + \panelheightm / 5 , yshift=0.2cm]pan.south west);
+\draw [line width=0.7mm,black] ([xshift=0.2cm, yshift=0.2cm]pan.south west) -- ([xshift=0.2cm + \panelheightm / 5, yshift=0.2cm]pan.south west);
 
@@
 \node[labelNode] {E};
-\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/fff_lamella4_just_matches_det4.png}};
+\node[graphicNode] (pan){\includegraphics[height=2.8cm]{content/images/fff_lamella4_detail3_back.png}};
+\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/fff_lamella4_detail3_close.png}};
+\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/fff_lamella4_detail3_far.png}};
+\node (n3) [box=blue!60, fit=(pan)] {};
+% scalebar - physical height is 400 nm
+\draw [line width=1.55mm,white] ([xshift=0.2cm, yshift=0.2cm]pan.south west) -- ([xshift=0.2cm + \panelheightm / 4 , yshift=0.2cm]pan.south west);
+\draw [line width=0.7mm,black] ([xshift=0.2cm, yshift=0.2cm]pan.south west) -- ([xshift=0.2cm + \panelheightm / 4, yshift=0.2cm]pan.south west);
 
@@
 \node[labelNode] {F};
-\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/fff_lamella4_just_matches_det6.png}};
+\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/fff_lamella4_detail3_far_side.png}};
+\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/fff_lamella4_detail3_close_side.png}};
 

### 2022-05-19 manuscript.tex
minor edits [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/5f9575bbee2059d4e92d5c821f29682c4a661e49.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/5f9575bbee2059d4e92d5c821f29682c4a661e49/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2354476139

--- 2022-03-30 manuscript.tex
@@
 \hypersetup{
-  pdftitle={Visual proteomics using whole-lamella 2D template matching},
+  pdftitle={Defocus Corrected Large Area Cryo-EM (DeCo-LACE) for Label-Free Detection of Molecules across Entire Cell Sections},
   pdfauthor={Johannes ElferichNikolaus Grigorieff},
@@
 
-\title{Visual proteomics using whole-lamella 2D template matching}
+\title{Defocus Corrected Large Area Cryo-EM (DeCo-LACE) for Label-Free Detection of Molecules across Entire Cell Sections}
 \author{}
@@
 This manuscript
-(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/2d0a9a5debbbf44b5f9d5797d38db68589012013/}{permalink})
+(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/5f9575bbee2059d4e92d5c821f29682c4a661e49/}{permalink})
 was automatically generated
-from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/2d0a9a5debbbf44b5f9d5797d38db68589012013}{jojoelfe/deco\_lace\_template\_matching\_manuscript@2d0a9a5}
-on March 30, 2022.
+from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/5f9575bbee2059d4e92d5c821f29682c4a661e49}{jojoelfe/deco\_lace\_template\_matching\_manuscript@5f9575b}
+on May 19, 2022.
 
@@
 high-resolution cryo-EM data over entire sections (100 -- 200 nm thick lamellae)
-of neutrophil-like mouse cells, representing roughly 1\% of the total cellular
+of neutrophil-like mouse cells, representing 1-2\% of the total cellular
 volume. We use 2D template matching (2DTM) to determine localization and orientation
-of the large ribosomal subunit in these sections, detect bound small
-ribosomal subunits and assign ribosomes to polysomes based on their relative orientations to each other. These data provide ``maps'' of translational activity across
+of the large ribosomal subunit in these sections. These data provide ``maps'' of translational activity across
 sections of mammalian cells. This new high-throughput cryo-EM
@@
 techniques a probe is physically attached to a molecule of interest that
-is able to detected with a high signal-to-noise signal, such as a
-fluorescent molecule. In label-free techniques the physical properties
+is able to be detected by its strong signal, such as a
+fluorescent molecule. In label-free techniques, the physical properties
 of molecules themselves are used for detection. An example for this is
@@
 of label-free techniques is that they can provide information over
-thousands of molecules, while label-techniques offer highly specific
+thousands of molecules, while label-dependent techniques offer highly specific
 information for a few molecules. Especially spatial information can
@@
 
-Cryo-electron microscopy has the potential to directly visualize the
+Cryo-electron microscopy (cryo-EM) has the potential to directly visualize the
 arrangement of atoms that compose biomolecules inside of cells, thereby
@@
 mechanical sectioning {[}\protect\hyperlink{ref-g8QavfwP}{4}{]} or by
-milling using a focused ion beam (FIB) {[}\protect\hyperlink{ref-16IhS1Nc4}{5}{]}. his complex workflow
+milling using a focused ion beam (FIB) {[}\protect\hyperlink{ref-16IhS1Nc4}{5}{]}. This complex workflow
 leads to a low throughput of cryo-EM imaging of cells and is further
@@
 of view (FOV) are very small compared to mammalian cells, and the FOV
-achieved by label-techniques such as fluorescence light microscopy. The
+achieved by label-dependent techniques such as fluorescence light microscopy. The
 predominant cryo-EM technique for the localization of biomolecules of
@@
 {[}\protect\hyperlink{ref-Ynb3IP6I}{7},\protect\hyperlink{ref-18KGpXYPE}{8},\protect\hyperlink{ref-10bXZuF3G}{9}{]}. In this
-method a 3D model of a biomolecule is used as a template to find 2D
+method, a 3D model of a biomolecule is used as a template to find 2D
 projections that match the molecules visible in the electron
@@
 of a biomolecule in a cellular sample
-{[}\protect\hyperlink{ref-18KGpXYPE}{8}{]}
+{[}\protect\hyperlink{ref-18KGpXYPE}{8}{]}.
 
-Hematopoiesis is the process of generating the various cell types of the blood in
-the bone marrow. Disregulation of the process results in diseases like leukemia.
-Understanding how hematopoietic stem and progenitor cells are programmed to
-diffferentiate to the appropriate cell type would be provide new insight how
-hematopoiesis can be misregulated. Of special interest is the regulation of
-translation during hematopoiesis. This is exemplified by the observation that
-genetic defects in the ribosome machinery often leads to hematopoietic
-disease{[}\protect\hyperlink{ref-gRoY21jY}{10}{]}. As such direct quantification of ribosome
-location, number and conformational states could lead to new insight into
-hematopoietic disease {[}\protect\hyperlink{ref-KAJ7221k}{11}{]}.
-
-Here we apply 2D-template matching of ribosomes to cryo-FIB milled
-neutrophil-like murine cells {[}\protect\hyperlink{ref-1B9Vt9eYu}{12}{]}. To increase the
-amount of collected data and to provide unbiased sampling of the whole
-lamella, we devised a new data-acquisition scheme, Defocus-corrected
-large area cryo-electron microscopy (DeCo-LACE). We characterize
-aberration cause by the used large beam-image shifts and highly focused
-beams and find that they can be adequately corrected to enable ribosome
-detection by 2DTM. The resulting data provide a description of ribosome
-distribution in the whole lamellae, which represent roughly 2\% of the
-cellular volume. We find highly heterogeneous density of ribosome within
-the cell and can identify discrete clusters of presumably
-translationally active ribosomes, by testing for the presence of the
-small ribosomal subunit. The high accuracy of location and orientation
-of each detected ribosome also allows us to cluster ribosome molecules
-into potential polysomes. Analysis of the throughput in this method
-suggests that for the foreseeable future computation will be the
-bottleneck for visual proteomics.
+Here we apply 2DTM of the ribosome large subunit (LSU) to cryo-FIB milled
+neutrophil-like murine cells {[}\protect\hyperlink{ref-1B9Vt9eYu}{10}{]}. We chose these
+cells because genetic defects in the ribosome machinery often leads to
+hematopoietic disease {[}\protect\hyperlink{ref-gRoY21jY}{11}{]} and direct quantification of
+ribosome location, number and conformational states in hematopoietic cells could
+lead to new insight into hematopoietic disease {[}\protect\hyperlink{ref-KAJ7221k}{12}{]}.
+To increase the amount of collected data and to provide unbiased sampling of the
+whole lamella, we devised a new data-acquisition scheme, ``Defocus-Corrected
+Large Area Cryo-Electron microscopy'' (DeCo-LACE). 2DTM allows us to test whether
+aberrations caused by large beam-image shifts and highly condensed beams
+deteriorate the high-resolution signal. We find that these aberrations do not
+impede LSU detection by 2DTM. The resulting data provide a description of
+ribosome distribution in an entire lamella, which represent 1-2\% of the cellular
+volume. We find a highly heterogeneous density of ribosomes within the cell.
+Analysis of the throughput in this method suggests that for the foreseeable
+future computation will be the bottleneck for visual proteomics.
 
@@
 
-ER-HoxA9 cells were maintained in RPMI supplemented with 10\% FBS,
-penicillin/streptomycin, SCF, and estrogen {[}\protect\hyperlink{ref-1B9Vt9eYu}{12}{]} at
-37C and 5\% CO2. 120h prior to grid freezing cells were washed twice in PBS and
-cultured in the same medium, except without estrogen. Differentiation was
-verified by staining with Hoechst-dye and insepction of nuclear morphology.
-Cells were then counted and diluted to 1\^{}106 cells/ml. Grids ( either 200 mesh
-copper grids, with a sillicone-oxide and 2um holes with a 2um spacing or 200
-mesh gold grids with a thin gold film and 2 um holes in 2um sapcing) were
-glow-discharged from both sides using a \ldots{} for \ldots{} . 3.5 ul of cells suspension
-was added to grids on the thin-film side and grids were automatically blotted
-from the back-side using a GP2 cryoplunger (Leica) for \ldots{} s and rapidly plunged
-into liquid ethane at -185C.
+ER-HoxA9 cells were maintained in RPMI medium supplemented with 10\% FBS,
+penicillin/streptomycin, SCF, and estrogen {[}\protect\hyperlink{ref-1B9Vt9eYu}{10}{]} at
+37 °C and 5\% CO2. 120 h prior to grid preparation, cells were washed twice in PBS
+and cultured in the same medium except without estrogen. Differentiation was
+verified by staining with Hoechst-dye and inspection of nuclear morphology.
+Cells were then counted and diluted to \(1\cdot10^6\) cells/ml. Grids (either 200
+mesh copper grids, with a sillicone-oxide and 2 µm holes with a 2 µm spacing or
+200 mesh gold grids with a thin gold film and 2 µm holes in 2 µm spacing) were
+glow-discharged from both sides using a 15 mA for 45 s. 3.5 µl of cell suspension
+was added to grids on the thin-film side and grids were blotted from the back
+side using a GP2 cryoplunger (Leica) for 8 s and rapidly plunged into liquid
+ethane at -185 °C.
 
@@
 
-Grids were loaded into a Acquilos 2 FIB/SEM microscope with a stage cooled to
--190C. Grids were sputter-coated with platinum for 15s at 45 mA and then coated
-with a layer of platinum-precursor by openin the GIS-valve for 45s. An overview
-of the grid was created by montaging SEM images and isolated cells at the center
-of gridsquares were selected for FB-milling. Lamella were generated
-automatically using the AutoTEM software, resulting in 6-8 um wide lamella with
-150-200 um thickness as determined by FIB-imaging of the lamella edge.
+Grids were loaded into an Aquilos 2 FIB/SEM (Thermo Fisher) instrument with a
+stage cooled to -190 °C. Grids were sputter-coated with platinum for 15 s at 45 mA
+and then coated with a layer of platinum-precursor by opening the GIS-valve for
+45 s. An overview of the grid was created by montaging SEM images and isolated
+cells at the center of gridsquares were selected for FIB-milling. Lamellae were
+generated automatically using the AutoTEM software (Thermo Fisher), with the
+following parameters:
+
+\begin{itemize}
+\tightlist
+\item
+  Milling angle: 20°
+\item
+  Rough milling: 3.2 µm thickness, 0.5 nA current
+\item
+  Medium milling: 1.8 µm thickness, 0.3 nA current, 1.0° overtilt
+\item
+  Fine milling: 1.0 µm tchickness, 0.1 nA current, 0.5° overtilt
+\item
+  Finer milling: 700 nm thickness, 0.1 nA curent, 0.2° overtilt
+\item
+  Polish 1: 450 nm thickness, 50 pA current
+\item
+  Polish 2: 200 nm thickness, 30 pA current
+\end{itemize}
+
+This resulted in 6-10 µm wide lamella with 150-250 nm thickness as determined by
+FIB-imaging of the lamella edges.
 
@@
 
-Grids were loaded into a Krios Titam TEM operated at 300 keV. The microscope was
-setup with a cross-grating grid on the stageby setting the beam-diameter to 900
-nm, resulting in the beam being completely visible in the camera. To establish
-fringe-free conditions, the ``Fine eucentric'' procedure of serialEM was used to
-move a square of the cross-grating grid to the eucentric position of the
-microscope. The effective defocus was then set to 2 um, using the ``autofocus''
-routine of serialEM. The objective focus of the microscope was changed until no
-fringes were visible. The stage was then moved in Z until images had a apparent
-defocus of 2 um. The differnce in stage Z-position between the eucentric and
-fringe-free conditions was calculate d and noted to move other areas into
-fringe-free condition.
+Grids were loaded into a Titan Krios TEM (Thermo Fisher) operated at 300 keV and
+equipped with a BioQuantum energy filter (Gatan) and K3 camera (Gatan). The
+microscope was aligned using a cross-grating grid on the stage. Prior to each
+session, we carefully performed the ``Image/Beam'' calibration in nanoprobe. We
+set the magnification to a pixel size of 1.76 Å and condensed the beam to \textasciitilde{} 900 nm
+diameter, resulting in the beam being completely visible on the camera. To
+establish fringe-free conditions, the ``Fine eucentric'' procedure of SerialEM {[}\protect\hyperlink{ref-19ZFerhph}{13}{]} was
+used to move a square of the cross-grating grid to the eucentric position of the
+microscope. The effective defocus was then set to 2 µm, using the ``autofocus''
+routine of SerialEM. The objective focus of the microscope was changed until no
+fringes were visible. The stage was then moved in Z until images had an apparent
+defocus of 2 µm. The difference in stage Z-position between the eucentric and
+fringe-free conditions was used to move other areas into fringe-free condition.
 
-Low magnification montages were used to find lamella and lamella that were
+Low magnification montages were used to find lamellae and lamellae that were
 sufficiently thin and free of contamination were selected for automated data
-collection. The corners of the lamella were manually annotated in SerialEM and
-translated into Beam-Imageshift values using SerialEm calibration. A hexagonal
-patter of beam-imageshift positions was calculated that covered the area between
-he four corners in a serpentine way, with a sqrt(3) * 400 nm horizontal spacing
-and 800 nm vertical spacing. Exposures were then taking at each position with a
-30 e/A total dose. After each exposure that defocus was estimated using the
-ctffind function of SerialEM and the focus for th next exposure was corrected by
-the difference between the estimated focus and the desired defocus of 800 um.
-Also after each exposure the deviation of the beam from the center of the camera
-was measured and corrected using the ``CenterBeamFrom IMage'' command of SerialEM.
+collection. Overview images of each lamella were taken at 2250x magnification
+(38 Å pixel size). The corners of the lamella in the overview image were manually
+annotated in SerialEM and translated into beam image-shift values using SerialEM's
+calibration. A hexagonal pattern of beam image-shift positions was calculated
+that covered the area between the four corners in a serpentine way, with a
+\(\sqrt{3}\cdot425\) nm horizontal spacing and \(3/4\cdot 850\) nm vertical spacing. Exposures were
+taken at each position with a 30 e\textsuperscript{-}/Å\(^2\) total dose. After each exposure, the
+defocus was estimated using the ctffind function of SerialEM and the focus for
+the next exposure was corrected by the difference between the estimated focus
+and the desired defocus of 800 nm. Furthermore, after each exposure the
+deviation of the beam from the center of the camera was measured and corrected
+using the ``CenterBeamFromImage'' command of SerialEM.
 
-After datacollection a 20s exposure at 2250x magnification of the lamella at
-200um defocus was taken for visualization purposes.
+After data collection, a 20 s exposure at 2250x magnification of the lamella at
+200 μm defocus was taken for visualization purposes. A Python script implementing
+this procedure is available at {[}Link to repo{]}.
 
-\hypertarget{data-pre-processing}{%
-\subsubsection{Data pre-processing}\label{data-pre-processing}}
+\hypertarget{deco-lace-data-processing}{%
+\subsubsection{DeCo-LACE data processing}\label{deco-lace-data-processing}}
 
-Movies were gain-corrected and motion-corrected using a custom version of
-unblur. To avoid influence of the beam-edge on motion-correction only a quarter
-of the movie in the center of the camera was considered for calculation of the
-estimated motion. After movie frames were aligned and summed a mask for the
-illuminated area was calculated by lowpass filtering the image at \ldots{} A,
-thresholding the image at 10\% of the maximal value and then lowpass filtering
-the mask at \ldots{} A. This mask was then used to replace un-illuminated area with
-gaussian noise, with the same mean and standard deviation as the illuminated
-area. The contrast-transfer function (CTF) was estimated using ctffind, searching
-between 0.02 and 2 um defocus.
+An overview of the data analysis pipeline is shown in Fig.
+\ref{fig:deco_lace_workflow}.
 
-\hypertarget{template-matching}{%
-\subsubsection{Template matching}\label{template-matching}}
+\hypertarget{pre-processing}{%
+\paragraph{Pre-processing}\label{pre-processing}}
 
-The search template was generated from the cryo-EM structure of the mouse large
-ribosomal subunit (PDB 6SWA). The \ldots{} subunit was deleted from the model and the
-simulate program of the cisTEM suite was used to calculate an density map from
-the atomic coordinates. The match\_template program was used to search for this
-template in the preprocessed images, using 1.5 deg angular step in out-of-plane
-angles and 1.0 deg in-plane. 21 defocus planes in 200nm steps centered around
-the defocus estimates by ctffind were searches. Matches were defined as peaks
-above a threshold calulated according to .. .(7.75 for most images).
+Motion-correction, dose weighting and other preprocessing as detailed below was performed using \emph{cis}TEM {[}\protect\hyperlink{ref-MUY42yxp}{14}{]}.
+To avoid influence of the beam-edge on motion-correction, only a quarter of the
+movie in the center of the camera was considered for calculation of the
+estimated motion. After movie frames were aligned and summed, a mask for the
+illuminated area was calculated by lowpass filtering the image with a 100 Å
+resolution cutoff, thresholding the image at 10\% of the maximal value and then lowpass
+filtering the mask again with a 100 Å resolution cutoff to smooth the mask edges. This mask was
+then used to select dark areas in the image and fill the pixels with
+Gaussian noise, with the same mean and standard deviation as the illuminated
+area. A custom version of the unblur program {[}\protect\hyperlink{ref-1G4Y94qCy}{15}{]}
+implementing this procedure is available at {[}link to decolace branch{]}. During motion correction images were resampled to a pixel size of 1.5 Å. The
+contrast-transfer function (CTF) was estimated using ctffind
+{[}\protect\hyperlink{ref-n43f3Sqs}{16}{]}, searching between 0.2 and 2 μm defocus.
 
-\hypertarget{data-analysis}{%
-\subsubsection{Data analysis}\label{data-analysis}}
+\hypertarget{dtm}{%
+\paragraph{2DTM}\label{dtm}}
+
+The search template was generated from the atomic model of the mouse LSU
+(PDB 6SWA, exluding the Epb1 subunit) using the cryo-EM simulator implemented in \emph{cis}TEM
+{[}\protect\hyperlink{ref-q2PSamkS}{17}{]}. The
+match\_template program {[}\protect\hyperlink{ref-10bXZuF3G}{9}{]} was used to search for this
+template in the movie-aligned, exposure-filtered and masked images, using a 1.5°
+angular step in out-of-plane angles and a 1.0° angular step in-plane. 11 defocus
+planes in 20 nm steps centered around the ctffind-determined defocus were searched. Targets
+were defined as detected when their matches with the template produced peaks
+with a singal-to-noise ratio (SNR) above a threshold of 7.75, which was chosen
+based on the one-false-positive-per-tile criterion {[}\protect\hyperlink{ref-Ynb3IP6I}{7}{]}.
+
+\hypertarget{montage-assembly}{%
+\paragraph{Montage assembly}\label{montage-assembly}}
+
+The coordinates of each tile \(i\),
+\(\mathbf{c}_{i}\) {[}2D Vector in pixels{]} were initialized using beam image-shift of the tile, \(\mathbf{b}_i\) {[}2D Vector in μm{]},
+and the ISToCamera matrix \(\mathbf{IC}\), as calibrated by SerialEM:
+
+\[\mathbf{c}_{i} = \mathbf{IC} \cdot \mathbf{b}_i\]
+
+A list of tile pairs \(i,j\) that overlap were assembled by selecting images where
+\(|\mathbf{c}_i-\mathbf{c}_j| < D_{Beam}\).
+In order to calculate the precise offset between tiles \(i\) and \(j\), \(\mathbf{r}_{i,j}\), we calculated the cross-correlation between the two tiles, masked to the overlapping illuminated area using the scikit-image
+package {[}\protect\hyperlink{ref-stvWEJeu}{18}{]} was used to calculate refined offsets .
+The coordinates \(\mathbf{c}_{i}\) were then refined by a least-square minimization against \(\mathbf{r}_{i,j}\):
+
+\[ \displaystyle{\min_{\mathbf{c}} \sum_{pairs}{(\mathbf{r}_{i,j} - (\mathbf{c}_i-\mathbf{c}_j))^2}}\]
+
+using the scipy package {[}\protect\hyperlink{ref-8Miti2Gz}{19}{]}. The masked cross-correlation and the least-square minimization was repeated once more to arrive at the final tile alignment.
+
+The x,y coordinates of target \(n\) detected by 2DTM in the tile \(i\),
+\(\textbf{m}^\textrm{T}_{n,i}\), was transformed into the montage frame by adding
+the coordinate of the tile.
+
+\[ \textbf{m}^\textrm{M}_n = \textbf{m}^\textrm{T}_{n,i} + \textbf{c}_i\]
+
+The z coordinate of each target was calculated as the sum of the defocus offset
+for the target, the estimated defocus of the tile, and the nominal defocus of
+the microscope when the tile was acquired.
+
+Images were rendered using UCSF ChimeraX {[}\protect\hyperlink{ref-cYCuuZxG}{20}{]}. The Python scripts used for data processing are available
+under {[}repolink{]}.
 
@@
 
-\hypertarget{dtm-detects-large-ribosomal-subunits-in-cryo-fib-lamella-of-mammalian-cells}{%
-\subsubsection{2DTM detects large ribosomal subunits in cryo-FIB lamella of mammalian cells}\label{dtm-detects-large-ribosomal-subunits-in-cryo-fib-lamella-of-mammalian-cells}}
+\hypertarget{dtm-detects-large-ribosomal-subunits-in-cryo-fib-lamellae-of-mammalian-cells}{%
+\subsubsection{2DTM detects large ribosomal subunits in cryo-FIB lamellae of mammalian cells}\label{dtm-detects-large-ribosomal-subunits-in-cryo-fib-lamellae-of-mammalian-cells}}
 
 To test whether we could detect individual ribosomes in mammalian cells we
-prepared cryo-lamella of mouse neutrophil-like cells. Low-magnification images
-of these lamellas clearly shows cellular features consistent with a
+prepared cryo-lamellae of mouse neutrophil-like cells. An overview image
+of a representative lamella clearly shows cellular features consistent with a
 neutrophil-like phenotype, mainly a segmented nucleus and a plethora of
 membrane-organelles, corresponding to the granules and secretory vesicles of
-neutrophils (Fig. \ref{fig:initmatching}A). We then proceeded to acquire
-micrographs on this lamella with a defocus of 0.5-1.0 um, 30 e/A2/s exposure and
-1.5 A pixelsize. We manually selected multiple locations in the lamella and
-focused using standard low-dose techniques where focusing is performed on a sacrificial area. The resulting micrographs showed no signs of
-crystalline ice and had Thon-rings to resolution, indicating successful
-vitrification.
+neutrophils (Fig. {[}\ref{fig:initmatching}{]}A). We then proceeded to acquire
+micrographs on this lamella with a defocus of 0.5-1.0 μm, 30 e\textsuperscript{-}/Å\(^2\)/s
+exposure and 1.76 Å pixel size. We manually selected multiple locations in the
+lamella and acquired micrographs using standard low-dose techniques where
+focusing is performed on a sacrificial area. The resulting micrographs showed
+smooth bilayered membranes and no signs of crystalline ice (Fig.
+{[}\ref{fig:initmatching}{]}C,D), indicating successful vitrification throughout the
+lamella. Successful vitrification is facilitated by the small size (\textasciitilde8 μm diameter) of these cells.
 
-We used an atomic model of the 60S mouse ribosomal subunit (6SWA) for 2D
-template matching. In a subset of images the distribution of cross-correlation
-scores significantly exceeded the distribution expected from non-signifcant
-matching. In the resulting scaled maximum-intensity maps, clear peaks
-with SNR thresholds up to 10 were apparent (Fig. \ref{fig:initmatching2}A). By
-using the criterion described by for thresholding potential matches we found
-that in images of cytosolic compartments we found evidence of 10-500 ribosomes in
-the imaged areas. Notably we found no matches in images that were taken in the
-nuclear compartment. In the cytosolic areas we found a drastically different
-number of matches, In some areas we found only \textasciitilde{} 50 matches er image area, while
-in another area we found more than 500 matches . This ten-fold difference in
-local ribosome concentration , but we realized that current data acquistion
-protocols are limited in that only a small area of the lamella is actually
-imaged and, due to the manual selection of acquision positions based on the
-overview image, might be biased towards cellular region that appear appealing to
-the experimentalist. We therefore set out to collect cryo-EM data for 2DTM from
-mammalian lamella in a high-throughput unbiased fashion.
-\#\#\# DECO-LACE for 2D imaging of whole lamella
+We used an atomic model of the 60S mouse ribosomal subunit (6SWA) for 2DTM {[}\protect\hyperlink{ref-sbkam02a}{21}{]}. In a
+subset of images, the distribution of cross-correlation scores significantly
+exceeded the distribution expected from images devoid of detectable targets. In the
+resulting scaled maximum-intensity projections (MIPs), clear peaks with SNR
+values up to 10 were apparent (Fig. {[}\ref{fig:initmatching2}{]}A). Using a
+threshold criterion to select significant targets (see Methods), we found that in
+images of cytosolic compartments there were 10-500 ribosomes within one micrograph
+(Fig. {[}\ref{fig:initmatching}{]}B-E). Notably, we found no targets in areas
+corresponding to the nucleus (Fig. {[}\ref{fig:initmatching}{]}B) or mitochondria
+(Fig. \protect\hyperlink{fig:initmatching}{1}D). In the cytoplasm, we found a highly variable
+number of targets, only \textasciitilde{} 50 in some exposures (Fig. {[}\ref{fig:initmatching}{]}E) and
+up to 500 in others (Fig. {[}\ref{fig:initmatching}{]}C). This is a ten-fold
+difference in local ribosome concentration, highlighting the importance of
+imaging larger areas of a lamella to gain a complete picture of target
+distributions. We therefore set out to collect cryo-EM data for 2DTM from
+mammalian cell lamellae in a high-throughput unbiased fashion.
 
-In order to obtain high-resolution data for complete lamella we used a new
-approach for data collection. This approach uses three key strategies: (1)
-ensures that every electron that exposes the sample is collected on the camera
-(2) uses beam-image shift to precisely and quickly raster the surface of the
-lamella and (3) uses a focusing strategy that does not rely on a sacrificial
-area.
+\hypertarget{deco-lace-for-2d-imaging-of-whole-lamellae}{%
+\subsubsection{DeCo-LACE for 2D imaging of whole lamellae}\label{deco-lace-for-2d-imaging-of-whole-lamellae}}
 
-To ensure that every electron exposing the sample was captured by the detector,
-we focused the electron beam so that the entire beam was placed on the detector.
-During canonical low-dose imaging the microscope is configured so that the focal
-plan is identical to the eucentric plane of the specimen stage. This leaves the
-C2 aperture out of focus, resulting in ripples at the edge of the beam (Figure
-2B). While these ripples are low-resolution features that might not interfere
-with 2D template matching, which is designed to be robust to low-resolution
-noise, we also tested collecting data under a condition where the C2 aperture is
-in focus (Figure 2C).
+In order to obtain high-resolution data from complete lamellae, we used a new
+approach for data collection. This approach uses three key strategies: (1) every
+electron that exposes a fresh area of the sample is collected on the camera (2)
+image shift is used to precisely and quickly raster the surface of a lamella and
+(3) focusing is done without using a sacrificial area (Fig. {[}\ref{fig:approach}{]}A).
 
-We then centered a lamella under the electron beam and used beam-image shift of
-the microscope to systematically raster the whole surface of the lamella in a
-hexagonal pattern. Instead of focusing in a sacrificial area, we determined the
-defocus after every exposure using a routine implemented in SerialEM modeled
-after CTFFind. The focus was then adjusted based on the difference between
-desired and measured defocus. Since we used a serpentine pattern for data
-collection every exposure is close to the previous exposure making drastic
-changes in the defocus unlikely. Furthermore we started our acquisition pattern
-on the platinum deposition edge, so the initial exposure where the defocus was
-not yet adjusted did not contain any biologically relevant information.
+To ensure that every electron exposing a fresh area of the sample is captured by
+the detector, we adjusted the electron beam size to be entirely contained by the
+detector area. During canonical low-dose imaging, the microscope is configured so
+that the focal plane is identical to the eucentric plane of the specimen stage.
+This leaves the C2 aperture out of focus, resulting in ripples at the edge of
+the beam (Fig. {[}\ref{fig:approach}{]}D). While these ripples are low-resolution
+features that likely do not interfere with 2DTM {[}cite{]}, we also tested data
+collection under conditions where the C2 aperture is in focus (``fringe-free'',
+Fig. {[}\ref{fig:approach}{]}E).
 
-We used this strategy to collect data on 8 lamella, 4 using the eucentric focus
-condition and 4 using the fringe-free condition. We were able to highly
-consistently collect data with a defocus of 8 um (Figure 2D), both in the
-eucentric focus and fringe-free focus condition. Together with the nominal
-defocus of the microscope this data results in a topological map of the lamella.
-To ensure that data was collected consistently, we mapped defocus values as a
-function of the applied Beam-image shift (Figure 2E). This demonstrated that the
-defocus was consistent over the lamella, with outliers only at isolated images
-and in images containing contamination. We also plotted the measure objective
-astigmatism of the lamella and found that it varies with the applied Beam-image
-shift, become more astigmatic mostly due to beam-image shift in the X
-direction. While approaches exist to correct this during the data-collection, we
-opted to not use these mechanism for these early experiments and instead rely on
-computational correction of these aberrations in order to characterize them.
+We then centered a lamella on the optical axis of the microscope and used the
+image shift controls of the microscope to systematically scan the whole surface
+of the lamella in a hexagonal pattern (Fig. {[}\ref{fig:approach}{]}A,C). Instead of
+focusing on a sacrificial area, we determined the defocus from every exposure
+after it was taken. The defocus was then adjusted based on the difference
+between desired and measured defocus (Fig. {[}\ref{fig:approach}{]}B). Since we used a
+serpentine pattern for data collection, every exposure was close to the previous
+exposure, making large changes in the defocus unlikely. Furthermore, we started
+our acquisition pattern on the platinum deposition edge to make sure that the
+initial exposure where the defocus was not yet adjusted did not contain any
+biologically relevant information.
 
-\hypertarget{d-template-matching-of-cryo-emilia-data-reveals-ribosome-distribution}{%
-\subsubsection{2D-Template matching of cryo-EMILIA data reveals ribosome distribution}\label{d-template-matching-of-cryo-emilia-data-reveals-ribosome-distribution}}
+We used this strategy to collect data on eight lamellae, four using the
+eucentric focus condition, hereafter referred to as Lamella\textsubscript{EUC}, and four using
+the fringe-free condition, hereafter referred to as Lamella\textsubscript{FFF}(Fig.
+{[}\ref{fig:assembly}{]} A+D, Fig.
+{[}\ref{fig:lamella_images}{]}A). We were able to collect data with a highly
+consistent defocus of 800 nm (Fig. {[}\ref{fig:approach}{]}F), both in the eucentric
+focus and fringe-free focus condition. To ensure that data were collected
+consistently, we mapped defocus values as a function of the applied image shift
+(Fig. {[}\ref{fig:lamella_spatial_info}{]}A). This demonstrated that the defocus was
+consistent across a lamella, except for rare outliers and in images containing
+contamination. We also plotted the measured objective astigmatism of each
+lamella and found that it varies with the applied image shift, becoming more
+astigmatic mostly due to image shift in the x direction (Fig.
+{[}\ref{fig:lamella_spatial_info}{]}B). While approaches exist to correct for this
+during the data collection {[}\protect\hyperlink{ref-APSL9LmU}{22}{]}, we opted to not use these approaches in our
+initial experiments. We reasoned that because 2DTM depends on high-resolution
+information, this would be an excellent test of how much these aberration affect
+imaging.
 
-We developed customized preprocessing protocol to images obtained by cryo-EMILIA
-to enable their use for 2D-template matching. First we restricted calculation of
-cross-correlation coefficients between individual movie frames to the central
-portion of the image to prevent artifacts from the beam edges on estimation of
-motion. Then we calculated a mask that defined the illuminated area of the
-micrographs and used it to fill non-illumated areas with gaussian noise,
-matching mean and standard deviation to the illuminated signal (Figure 3A). The
-so processed images were suitable for 2D-template matching and we were able to
-obtained matches with the same model used for the data in Figure 1.
+We assembled the tile micrographs into a montage using the image-shift values
+and the SerialEM calibration followed by cross-correlation based refinement (see
+Methods). In the resulting montages, the same cellular features visible in the
+overview images are apparent (Fig. {[}\ref{fig:assembly}{]}B+E, Fig. {[}\ref{fig:lamella_images}{]}B), however
+due to the high magnification and low defocus many more details, such as the
+membrane bilayer separation, can be observed (Fig. {[}\ref{fig:assembly}{]}C+F). For montages collected using the
+eucentric condition, there are clearly visible fringes at the edges between the
+tiles (Fig. {[}\ref{fig:assembly}{]}C), which are absent in the fringe-free focus montages (Fig. {[}\ref{fig:assembly}{]}F). In our analysis
+below, we show that these fringes do not impede target detection by 2DTM, making
+them primarily an aesthetic issue. We also note that the tiling
+pattern is visible in the montages (Fig. {[}\ref{fig:assembly}{]}B+E), which we believe is due to the non-linear
+behavior of the K3 camera since we can observe these shading artifacts in micrographs of a condensed beam over vacuum (Fig. {[}\ref{fig:gain}{]}).
 
-\hypertarget{quantitative-analysis-of-translation-activity}{%
-\subsubsection{Quantitative analysis of translation activity}\label{quantitative-analysis-of-translation-activity}}
+The montages show membrane vesicles and granules with highly variable sizes and
+density. We found that a substantial number of granules, which are characterized by higher
+density inside the the surrounding cytosol {[}\protect\hyperlink{ref-xE2EhAcH}{23}{]}, seemed to contain a membrane-enclosed inclusion with density similar to
+the surrounding cytosol (Fig. {[}\ref{fig:lamella_images}{]}C) and could therefore be formed
+by an autophagy-like pathway. These granules were
+150-300 nm in diameter and the inclusions were 100-200 nm in diameter. Based on
+these dimensions the granules are either azurophil or specific granules {[}\protect\hyperlink{ref-xE2EhAcH}{23}{]}. To our
+knowledge, these inclusion have not been described in granulocytes and are
+further described and discussed below.
+
+\hypertarget{dtm-of-deco-lace-data-reveals-ribosome-distribution-in-cellular-cross-sections}{%
+\subsubsection{2DTM of DeCo-LACE data reveals ribosome distribution in cellular cross-sections}\label{dtm-of-deco-lace-data-reveals-ribosome-distribution-in-cellular-cross-sections}}
+
+In our initial attempts of using 2DTM on micrographs acquired with the DeCo-LACE
+protocol, we did not observe any SNR peaks above threshold using the large
+subunit of the mouse ribosome (Fig. {[}\ref{fig:crop_unblur}{]}A). We reasoned that
+the edges of the beam might interfere with motion-correction of the movies as
+they represent strong low-resolution features that do not move with the sample.
+When we cropped the movie frames to exclude the beam edges, the estimated amount
+of motion increased (Fig. {[}\ref{fig:crop_unblur}{]}B), consistent with successful
+tracking of sample motion. Furthermore, in the motion-corrected average we could
+identify significant SNR peaks (Fig. {[}\ref{fig:crop_unblur}{]}B), confirming to
+high sensitivity of 2DTM to the presents of high-resolution signal preserved in
+the images by the motion correction. To streamline data processing, we
+implemented a function in unblur to consider only a defined central area of a
+movie for estimation of sample motion, while still averaging the complete movie
+frames (Fig. {[}\ref{fig:crop_unblur}{]}C). Using this approach, we motion-corrected
+all tiles in the eight lamellae and found consistently total motion below 1 Å
+per frame (Fig. {[}\ref{fig:lamella_motion_thickness}{]} A). In some lamellae we
+found increased motion in the lamella center, which indicates areas of variable
+mechanical stability within FIB-milled lamellae. In some micrographs we also
+observed that the beam edges gave rise to artifacts in the MIP and numerous
+false-positive detections at the edge of the illuminated area (Fig. {[}\ref{fig:crop_unblur}{]}D). A
+similar phenomenon was observed on isolated ``hot'' pixels in unilluminated areas.
+To overcome this issue we implemented a function in unblur to replace
+dark areas in the micrograph with Gaussian noise (see Methods), with
+mean and standard deviation matching the illuminated portion of the micrograph
+(Fig. {[}\ref{fig:crop_unblur}{]}D+E). Together, these pre-processing steps enabled us to perform 2DTM on
+all tiles of the eight lamellae.
+
+We used the refined tile positions to calculate the positions of the detected
+LSUs in the lamellae (Fig. {[}\ref{fig:matching_euc}{]}A, Fig. {[}\ref{fig:matching_fff}{]}A). Overlaying these positions of the lamellae montages reveal ribosome
+distribution throughout the FIB-milled slices of individual cells. Organelles
+like the nucleus and mitochondria only showed sporadic targets detected with low
+SNRs, consistent with the estimated false-positive rate of one per tile. For
+each detected target we also calculated the Z positions from the individual
+estimated defocus and defocus offset for each tile. When viewed from the side,
+the ribosome positions therefore show the slight tilts of the lamellae relative
+to the microscope frame of reference (Fig. {[}\ref{fig:matching_euc}{]}B, Fig.
+{[}\ref{fig:matching_fff}{]}B). Furthermore, the side views indicated that lamellae
+were thinner at the leading edge. Indeed, when plotting the transmitted beam
+intensities in individual tiles as a function of beam image-shift, we observed
+substantially higher intensities at the leading edge (Fig. {[}\ref{fig:lamella_motion_thickness}{]}B), which in energy-filtered
+TEM indicates a thinner sample {[}\protect\hyperlink{ref-17IP4Lhz1}{24}{]}. Even though we prepared the lamellae
+with the ``overtilt'' approach {[}\protect\hyperlink{ref-hr3dyUeI}{25}{]}, this means that ribosome densities across
+the lamellae can be skewed by a change in thickness, and better sample
+preparation methods are needed to generate more even samples.
+
+Close inspection of the ribosome positions in the lamellae revealed several
+interesting features. Ribosomes could be seen associating with membranes, in
+patterns reminiscent of the rough endoplasmic reticulum (Fig.
+{[}\ref{fig:matching_euc}{]}C, Fig. {[}\ref{fig:matching_fff}{]}C) or the outer nuclear
+membrane (Fig. {[}\ref{fig:matching_euc}{]}D). We also observed ribosomes forming
+ring-like structures (Fig. {[}\ref{fig:matching_euc}{]}E), potentially indicating
+circularized mRNAs {[}\protect\hyperlink{ref-cie13Q8F}{26}{]}. While ribosomes were for the most part excluded
+from the numerous granules observed in the cytoplasm, in some cases we observed
+clusters of ribosomes in the inclusions of double-membraned granules
+described earlier (Fig. {[}\ref{fig:matching_euc}{]}F, Fig. {[}\ref{fig:matching_fff}{]}D,E). It is, in principle, possible that these targets are situated above or
+below the imaged granules, since the granule positions in z cannot be determined
+using 2D projections. However, in the case of Fig. {[}\ref{fig:matching_fff}{]}E, the
+detected ribosomes span the whole lamella in the z direction (Fig. {[}\ref{fig:matching_fff}{]}F), while positions
+above or below a granule would result in ribosomes situated exlusively at the
+top or bottom of the lamella. This conclusive evidence of ribosomes in
+inclusions is consistent with the earlier hypothesis that the inclusions are of
+cytoplasmic origin.
+
+\hypertarget{does-deco-lace-induce-aberrations-that-affect-2dtm}{%
+\subsubsection{Does DeCo-LACE induce aberrations that affect 2DTM?}\label{does-deco-lace-induce-aberrations-that-affect-2dtm}}
+
+Within the eight lamellae we found different number of detected targets (Fig.
+{[}\ref{fig:matching_stat}{]}A). Lamella\textsubscript{EUC} 1 had the most detected targets, but also has
+the largest surface area and contained cytoplasm from two cells. Lamella\textsubscript{FFF} 4
+had the fewest detected targets, but this particular lamella was dominated by a
+circular section of the nucleus, with only small pockets of cytoplasm (Fig.
+{[}\ref{fig:lamella_images}{]}). In an attempt to normalize for these differences in
+area containing cytoplasm, we compared the number of detected targets per tile in
+tiles that contained more than one target, which should exclude tiles with
+non-cytosolic content (Fig. {[}\ref{fig:matching_stat}{]}B). While this measure had
+less variability, there were still differences. Lamella\textsubscript{EUC} 4 had not only the
+fewest targets, but also the lowest density, which could be due to this lamella being the
+thinnest, or due to it sectioning the cell in an area with a lower concentration of
+ribosomes. Lamella\textsubscript{FFF} 3 had a substantially higher number of ribosomes per
+tile. Since all of these lamellae were made from a cell-line under identical
+conditions, this underscores the necessity to collect data from large numbers of
+lamellae to overcome the inherent variability. When comparing the distribution of
+scores between lamellae, we found them to be fairly comparable with median
+SNRs ranging from 8.7 to 9.7 (Fig. {[}\ref{fig:matching_stat}{]}C). Lamella\textsubscript{EUC} 1 had slightly lower scores compared
+to
+the rest, potentially due to its large size and connected mechanical instability
+during imaging. Overall, we did not observe differences in the number or SNR of
+detected targets between eucentric or fringe-free illumination conditions that
+were bigger than the observed inter-lamella variability.
+
+Since the SNR values of 2DTM are highly sensitive to image quality, we reasoned
+we could use them to verify that DeCo-LACE does not introduce a systematic loss
+of image quality. We considered non-parallel illumination introduced by the
+unusually condensed beam and uncharacterized aberrations near the beam
+periphery. When plotting the SNR values of detected targets in all eight
+lamellae as a function of their location in the tiles, we found uniformly high
+SNR values throughout the illuminated areas for both eucentric and fringe-free
+focus illumination, demonstrating that both illumination schemed are suitable
+for DeCo-LACE (Fig. {[}\ref{fig:matching_stat}{]}D).
+
+We also wondered whether large image shifts would lead aberration due to
+astigmatism or beam tilt {[}\protect\hyperlink{ref-APSL9LmU}{22}{]}. We reasoned that if
+that was the case the number of detected targets should be highest in the center of the
+lamella where the applied beam image-shift is 0. Instead we observed that in
+both eucentric and fring-free focus conditions more target where detected at the
+``back'' edge of the lamella (Fig. {[}\ref{fig:matching_stat}{]}E{]}). This may be due to the center of the cell being predominantly
+occupied by the nucleus, despite its segmentation in neutrophil-like cells. The
+increase in matches at the ``back'' of the lamellae compared to the ``front'' can also
+be explained by the thickness gradient of the lamellae (Fig. {[}\ref{fig:lamella_motion_thickness}{]}B,
+Fig. {[}\ref{fig:matching_euc}{]}B, Fig. {[}\ref{fig:matching_fff}{]}B). In addition, aberrations would be expected to cause average 2DTM SNRs to be higher when beam-image shift
+values are small. Instead, we found that SNRs where on average the highes at the
+``front'' edge of the lamellae, presumably due to the thinner sample. We therefore
+conclude that factors other that beam image-shift or beam
+condensation aberrations are limiting 2DTM SNRS, predominantly the thickness of
+the lamellae.
+
+\hypertarget{computation-is-the-bottleneck-of-visual-proteomics}{%
+\subsubsection{Computation is the bottleneck of visual proteomics}\label{computation-is-the-bottleneck-of-visual-proteomics}}
+
+As described above, the variability of lamellae, both in terms of experimental
+parameters including area, thickness and mechanical stability, and in terms of
+biology, such as selection of cell type and location of the section within the
+cell, requires collection of orders of magnitude more data than in this study to draw quantitative
+and statistically relevant conclusions about the number and location of
+molecules under different experimental conditions. The samples used were
+prepared in two 24 h sessions on a FIB/SEM instrument, and imaging was performed
+during another two 24h session on the TEM microscope. Inspections of the
+timestamps of the raw data files revealed that the milling time per lamella was
+\textasciitilde30 minutes and TEM imaging was accomplished in \textasciitilde10 seconds per tile or 90
+minutes for a \textasciitilde{} 6x6 μm lamella. Processing of the data, however, took
+substantially longer. Specifically, 2DTM of all tiles took approximately one
+week per lamella on 32 A100 GPUs. Computation is therefore a bottleneck in our
+current workflow, and further optimizations of the algorithm may be necessary
+increase throughput. Alternatively, this bottleneck could be reduced by
+increasing the number of processing units.
 
@@
 
-\begin{itemize}
-\item
-  Elizabeth Wright and Grant Jensen Montage tomography papers
-\item
-  Waffle method for higher throughput, automation of fib-milling
-\item
-  Throughput and bottlenecks
-\item
-  Visual proteomics
-\item
-  Granules containing ribosomes?
-\item
-  Threshold implications (no matches on most images)
-\end{itemize}
+In this study we developed an approach to image entire cellular cross-section using cryo-EM at high enough resolution to allow for 2DTM detection of the LSU.
+The two main advantages compared to previous approaches are a high throughput of imaging and the biological context for detected molecules.
+The requirement to increase throughput in cryo-EM data collection of cellular samples has been recognized in the recent literature.
+Most approaches describeb so far are tailored towards tomography.
+Peck et al.
+{[}\protect\hyperlink{ref-1GPPSX111}{27}{]} and Yang et al.
+{[}\protect\hyperlink{ref-ujizcpVn}{28}{]} developed approaches to increase the FOV of tomogram data-collection by using a montaging technique.
+Peck et al.~used a similar ``condensed-beam'' approach as described here.
+However, the montages are substantially smaller in scope, covering carbon film holes of 2 um diameter.
+Bouvette et al.
+{[}\protect\hyperlink{ref-1Gwx5ScUa}{29}{]} and Eisenstein et al.
+{[}\protect\hyperlink{ref-xvouNMBy}{30}{]} are using beam image-shift to collect tilt-series in multiple locations in parallel to increase throughput.
+However, none of these approaches provide the full coverage of a cellular cross-section that can be achieved using DeCo-Lace.
+
+Since we observed substantial variation in ribosome density within and between lamellae, visual proteomics studies that use cryo-EM to establish changes in molecular organization within cells will require orders of magnitude more data than used in this study.
+One milestone would be to image enough data to represent one cellular volume, which for a small eukaryotic cells requires imaging approximately 100 lamella.
+While data collection throughput on the TEM is fundamentally limited by the exposure time, this amount of data could be collected within 12 hour by improving the data acquisition scheme to perform all necessary calculation in parallel with actual exposure of the camera.
+Sample preparation using a FIB/SEM is also currently a bottleneck, but preparation of large lamellae with multiple cellular cross-sections using methods like WAFFLE {[}\protect\hyperlink{ref-17H2LWiIu}{31}{]} might allow sufficient throughput.
+As stated in the results, at least for 2DTM computation will remain challenging and approximately 17,000 GPU hours would be required for a 100 lamellae dataset.
+
+As described in {[}\protect\hyperlink{ref-Ynb3IP6I}{7}{]} the 2DTM SNR threshold for detecting a target is chosen to result in one false positive detection per image searched.
+We would therefore expect to find one false positive detection per tile.
+We reasoned that the large nuclear area imaged by DeCo-Lace could be used to test whether this assumption is true.
+In the 670 tiles containing exclusively nucleus (as manually annotated from the overview image) we detected 247 targets, making the false-positive rate more than twofold lower than expected.
+Since earlier work shows that 2DTM with the LSU can produce matches to nuclear ribosome biogenesis intermediates {[}\protect\hyperlink{ref-T1Qr0xyP}{32}{]}, this could even be an overestimate of the false-positive rate.
+This suggests that the detection threshold could be even lower, which is an area of ongoing research.
+
+We found that even though we used beam image-shift extensively (up to 7 um), we did not see substantially reduced 2DTM SNR values in tiles acquired at high beam image-shift compared to tiles acquired with low or no beam image-shift.
+This is in contrast to reports in single-particle analysis (SPA) {[}\protect\hyperlink{ref-44fG6kcy}{33}{]} where the induced beam tilt substantially reduced the resolution if it was not corrected during processing.
+It is possible that 2DTM is less sensitive to beam-tilt aberrations, since the template is free of any aberration and only the image is distorted, while in SPA the beam tilt will affect both the images and the reconstructed template.
+
+As mentioned in the results, we found a consistent shading artifact pattern in our montages, that we believe is the result of non-linear behavior of the K3 camera.
+Indeed, when we average images with a condensed beam taken over vacuum we found in both focus conditions a consistent background pattern with a brighter region on the periphery of the illuminated area (Fig {[}\ref{fig:gain}{]}).
+This might be caused by dynamic adjustment of the internal camera counting threshold which expects columns of the sensor to be evenly illuminated as is the case for SPA applications.
+Since the signal of this pattern has mainly low-resolution components it is unlikely to affect 2DTM.
+However, it highlights that the non-linear behavior of the camera has to be taken into account when imaging samples with strongly varying density and unusual illumination schemes.
+
+Unexpectedly, we observed granules containing a vesicle of putative cytosolic origin.
+We speculate that upon degranulation, the process in which granules fuse with the plasma membrane, these vesicles would be released into the extracelullar space.
+The main types of extracellular vesicles of this size are exosomes, up to 100 nm large vesicles derived from fusion of multivesicular bodies with the plasma membrane, and microvesicles, which are derived from direct budding of the plasma membrane {[}\protect\hyperlink{ref-kncnYGLD}{34}{]}.
+We suggest that granulocytes could release a third type of extracellular vesicle, granule-derived vesicles (GDV), into the extracellular space.
+2DTM showed that a subset of GDVs can contain ribosomes (Fig.
+{[}\ref{fig:matching_euc}{]}F, Fig.
+{[}\ref{fig:matching_fff}{]}D,E).
+This could indicate that these vesicles are transporting translation-capable mRNAs, as has been described for exosomes {[}\protect\hyperlink{ref-agVdpX76}{35}{]}.
+Further studies will be necessary to confirm the existence of GDVs in granulocytes isolated from mammals and to understand their functional significance.
+
+\begin{figure}
+\hypertarget{fig:deco_lace_workflow}{%
+\centering
+\includegraphics{figures/deco_lace_workflow.png}
+\caption{Workflow of DeCo-Lace processing}\label{fig:deco_lace_workflow}
+}
+\end{figure}
 
@@
 Major cellular regions are labeled, as Nucleus (Nuc), Mitochondria (M), and granular cytoplasm (GrCyt).
-FOVs where high-magnification images for template matching where acquired are indicated as boxes with the number of matches indicated on the bottom right.
+FOVs where high-magnification images for template matching where acquired are indicated as boxes with the number of detected targets indicated on the bottom right.
 FOVs displayed in Panels B-E are color-coded.
-(B-E) FOVs with projection of ribosome LSU matches shown in green.
-(B) Perinuclear region, the only matches are in the cytoplasmic half.
-(C) Cytoplasmic region with high density of ribosomes (D) Mitochondrium, as expected there are only matches in the cytoplasmic region (E) Cytoplasm, with low density of ribosomes.}\label{fig:initmatching}
+Scalebar corresponds to 1 μm.
+(B-E) FOVs with projection of detected LSUs shown in cyan.
+(B) Perinuclear region, the only detected targets are in the cytoplasmic half.
+(C) Cytoplasmic region with high density of ribosomes (D) Mitochondrium, as expected there are only detected LSUs in the cytoplasmic region (E) Cytoplasm, with low density of ribosomes.}\label{fig:initmatching}
 }
@@
 
-\begin{fignos:tagged-figure}[S1]
+\begin{fignos:tagged-figure}[2 - figure supplement 1]
 
@@
 \centering
-\includegraphics{figures/initmatching2.pdf}
-\caption{Maximum intensity projection cross-correlation map of micrograph shown in Figure \ref{fig:initmatching}}\label{fig:initmatching2}
+\includegraphics{figures/initmatching2.png}
+\caption{2D template matching of the large subunit of the ribosome in fib-milled
+neutrophil-like cells (A) Maximum intensity projection (MIP) cross-correlation map of
+micrograph shown in Figure
+\ref{fig:initmatching} (B+C) 3D plot of MIP regions indicated by color boxes in Panel A}\label{fig:initmatching2}
 }
@@
 \centering
-\includegraphics{figures/approach.pdf}
-\caption{DeCo-LACE approach (A) Graphic demonstrating the data-collection strategy for DeCo-LACE}\label{fig:approach}
+\includegraphics{figures/approach.png}
+\caption{DeCo-LACE approach (A) Graphic demonstrating the data-collection strategy for
+DeCo-LACE. The electron beam is condensed to a diameter \(D_{Beam}\) that allows captured of
+the whole illuminated area on the camera. Beam-image shift along X and Y
+(\(BIS_X\),\$\(BIS_Y\)) is used to scan the whole lamella
+(B) Diagram of the collection algorithm
+(C) Example overview image of a lamella with the designated acquisition
+positions and the used beam diameter indicated with red circles. Scalebar corresponds to 1 μm.
+(D+E) Representative micrographs takne with a condensed beam at eucentric focus
+(D) or fringe-free focus (E). Scalebar corresponds to 100 nm.
+(F) Boxplot of defocus measured by ctffind of micrographs taken by the DeCo-Lace
+approach on four lamellae images at eucentric focus and four lamellae imaged with
+fringe-free focus.}\label{fig:approach}
+}
+\end{figure}
+
+\begin{fignos:tagged-figure}[3 - figure supplement 1]
+
+\begin{figure}
+\hypertarget{fig:lamella_spatial_info}{%
+\centering
+\includegraphics{figures/lamella_spatial_info.png}
+\caption{Defocus estimation of individual tiles of DeCo-Lace montages
+(A) Defocus values of individual micrographs taken using the DeCo-Lace approach
+plotted as a function of the beam image-shift values.
+(B) Defocus astigmatism of individual micrographs taken using the DeCo-Lace approach
+plotted as a function of the beam image-shift values.}\label{fig:lamella_spatial_info}
+}
+\end{figure}
+
+\end{fignos:tagged-figure}
+
+\begin{figure}
+\hypertarget{fig:assembly}{%
+\centering
+\includegraphics{figures/assembly.png}
+\caption{Assembling DeCo-LACE exposures into montages (A) Overview
+image of Lamella\textsubscript{EUC} 1 taken at low magnification. Scalebar corresponds to 1 μm. (B) Overview of Lamella\textsubscript{EUC} 1 created by
+montaging high magnification images taken with the DeCo-Lace approach.
+Scalebar corresponds to 1 μm.
+(C) Zoom-in into red box in panel B.
+Slight beam-fringe artifacts are visible.
+Scalebar corresponds to 100 nm.
+(D) Overview
+image of Lamella\textsubscript{FFF} 4 taken at low magnification. Scalebar corresponds to 1 μm. (E) Overview of Lamella\textsubscript{FFF} 4 created by
+montaging high magnification images taken with the DeCo-Lace approach.
+Scalebar corresponds to 1 μm.
+(F) Zoom-in into red box in panel E.
+No beam-fringe artifacts are visible.
+Scalebar corresponds to 100 nm.}\label{fig:assembly}
+}
+\end{figure}
+
+\begin{fignos:tagged-figure}[4 - figure supplement 1]
+
+\begin{figure}
+\hypertarget{fig:crop_unblur}{%
+\centering
+\includegraphics{figures/crop_unblur.png}
+\caption{Motion correction of movies with condensed beams.
+At the top of each panel is an average of the movie that was motion-corrected
+with a red dashed box indicating the region that was used to estimate shifts.
+Below is a graph indicating the estimated shifts of the individual frames of the
+movie. Below this is the MIP of 2DTM using the large subunit of the mouse ribosome.
+(A) Motion correction of the whole movie
+(B) Notion correction of a cropped region of the movie that eliminates the beam
+edges
+(C) Motion correction of the whole movie, using only the central region to
+estimate the shifts}\label{fig:crop_unblur}
+}
+\end{figure}
+
+\end{fignos:tagged-figure}
+
+\begin{fignos:tagged-figure}[4 - figure supplement 2]
+
+\begin{figure}
+\hypertarget{fig:lamella_motion_thickness}{%
+\centering
+\includegraphics{figures/lamella_motion_thickness.png}
+\caption{Motion correction of individual tiles imaged using the DeCo-LACE approach
+(A) Total estimated motion of individual micrographs taken using the DeCo-Lace approach
+plotted as a function of the beam image-shift values.
+(B) Electron intensity of individual micrographs taken using the DeCo-Lace approach
+plotted as a function of the beam image-shift values.}\label{fig:lamella_motion_thickness}
+}
+\end{figure}
+
+\end{fignos:tagged-figure}
+
+\begin{fignos:tagged-figure}[4 - figure supplement 3]
+
+\begin{figure}
+\hypertarget{fig:gain}{%
+\centering
+\includegraphics{figures/gain.png}
+\caption{Averages of micrographs taken with a condensed beam over vacuum using a Gatan K3 detector.
+Contrast and Brightness have been adjusted to highlight uneven dose response.
+(A) Eucentric Focus (B) Fringe-free Focus}\label{fig:gain}
+}
+\end{figure}
+
+\end{fignos:tagged-figure}
+
+\begin{fignos:tagged-figure}[4 - figure supplement 4]
+
+\begin{figure}
+\hypertarget{fig:lamella_images}{%
+\centering
+\includegraphics{figures/lamella_images.png}
+\caption{Overview images of lamellae imaged using the DeCo-LACE approach taken at low-magnification (A) Overviews taken at low magnification.
+Scalebar corresponds to 1 μm.
+(B) Overviews assembled using the DeCo-LACE approach.
+Scalebar corresponds to 1 μm.
+(C) Representative examples of a class of granules containing a putatively cytosolic inclusion.
+Scalebar corresponds to 100 nm.}\label{fig:lamella_images}
+}
+\end{figure}
+
+\end{fignos:tagged-figure}
+
+\begin{figure}
+\hypertarget{fig:matching_stat}{%
+\centering
+\includegraphics{figures/matching_stat.png}
+\caption{Statistics of 2DTM on lamella imaged using DeCo-LACE (A) Number of detected targets in
+each lamella (B) Distribution of targets per tile in each lamella. Only tiles
+with two or more detected targets were included (C) Distribution of SNRs in each lamella
+(D) For each lamella an average of all tiles is shown. Overlaid is a scatterplot
+of all detected targets in these tiles according to their in-tile coordinates.
+Scatterplot is colored according to the 2DTM SNR. There are no detected targets in the top
+circle-circle intersection due to radiation damage from previous exposures.
+(E) 2D histogram of number of detected targets as a function of beam-image shift (F) Mean 2DTM SNR as a function of beam-image shift}\label{fig:matching_stat}
 }
@@
 \begin{figure}
-\hypertarget{fig:lamella_spatial_info}{%
+\hypertarget{fig:matching_euc}{%
 \centering
-\includegraphics{figures/lamella_spatial_info.pdf}
-\caption{This is an example-figurern}\label{fig:lamella_spatial_info}
+\includegraphics{figures/matching_euc.png}
+\caption{Template matching in lamella imaged using the DeCo-Lace approach at eucentric
+focus (A) Montage of Lamella\(_\textrm{EUC}\) 1 overlaid with detected targets according to
+their montage coordinates colored in orange. Scalebar corresponds to 1 μm. (B) Side view of detected targets in the lamella, such that the
+direction of the electron beam is horizontal. (C-F) Magnified area of panel A
+showing rough ER with associated ribosomes(C), outer nuclear membrane with
+associated ribosomes (D), ribsomes arranged in a circular fashion(E), ribosomes
+enclosed in a less electron dense inclusion in a granule(F).
+Ribosomes are colored in white with the surface of the peptide exit tunnel colored in green and the A, P, and E sites colored in blue, purple, and red, respectively.Scalebar corresponds to 100 nm.}\label{fig:matching_euc}
 }
@@
 \begin{figure}
-\hypertarget{fig:approach3}{%
+\hypertarget{fig:matching_fff}{%
 \centering
-\includegraphics{figures/example-figure3.pdf}
-\caption{This is an example-figurern}\label{fig:approach3}
-}
-\end{figure}
-
-\begin{figure}
-\hypertarget{fig:approach4}{%
-\centering
-\includegraphics{figures/example-figure4.pdf}
-\caption{This is an example-figurern}\label{fig:approach4}
-}
-\end{figure}
-
-\begin{figure}
-\hypertarget{fig:matching}{%
-\centering
-\includegraphics{figures/matching.pdf}
-\caption{This is an example-figurern}\label{fig:matching}
-}
-\end{figure}
-
-\begin{figure}
-\hypertarget{fig:deco_lace_workflow}{%
-\centering
-\includegraphics{figures/deco_lace_workflow.pdf}
-\caption{Workflow of DeCo-Lace processing}\label{fig:deco_lace_workflow}
+\includegraphics{figures/matching_fff.png}
+\caption{Template matching in lamella imaged using the DeCo-Lace approach at fringe-free
+focus (A) Montage of Lamella\(_\textrm{FFF}\) 4 overlaid with detected targets according to
+their montage coordinates colored in orange. Scalebar corresponds to 1 μm. (B) Side view of detected targets in the lamella, such that the
+direction of the electron beam is horizontal. (C-E) Magnified area of panel A
+showing rough ER with associated ribosomes(C) and ribosomes
+enclosed in a less electron dense inclusion in a granule(D,E). (F) Side view of
+panel E.
+Ribosomes are colored in white with the surface of the peptide exit tunnel colored in green and the A, P, and E sites colored in blue, purple, and red, respectively.
+Scalebar corresponds to 100 nm.}\label{fig:matching_fff}
 }
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-1B9Vt9eYu}{}}%
+\CSLLeftMargin{10. }%
+\CSLRightInline{\textbf{Inhibition of Dihydroorotate Dehydrogenase Overcomes Differentiation Blockade in Acute Myeloid Leukemia}
+\CSLBlock{David B Sykes, Youmna S Kfoury, François E Mercier, Mathias J Wawer, Jason M Law, Mark K Haynes, Timothy A Lewis, Amir Schajnovitz, Esha Jain, Dongjun Lee, \ldots{} David T Scadden} \emph{Cell} (2016-09) \url{https://doi.org/f3r5jr}
+\CSLBlock{DOI: \href{https://doi.org/10.1016/j.cell.2016.08.057}{10.1016/j.cell.2016.08.057} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/27641501}{27641501} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7360335}{PMC7360335}}}
+
 \leavevmode\vadjust pre{\hypertarget{ref-gRoY21jY}{}}%
-\CSLLeftMargin{10. }
+\CSLLeftMargin{11. }%
 \CSLRightInline{\textbf{Hallmarks of ribosomopathies}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-KAJ7221k}{}}%
-\CSLLeftMargin{11. }
+\CSLLeftMargin{12. }%
 \CSLRightInline{\textbf{Diagnostic and prognostic implications of ribosomal protein transcript expression patterns in human cancers}
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-1B9Vt9eYu}{}}%
-\CSLLeftMargin{12. }
-\CSLRightInline{\textbf{Inhibition of Dihydroorotate Dehydrogenase Overcomes Differentiation Blockade in Acute Myeloid Leukemia}
-\CSLBlock{David B Sykes, Youmna S Kfoury, François E Mercier, Mathias J Wawer, Jason M Law, Mark K Haynes, Timothy A Lewis, Amir Schajnovitz, Esha Jain, Dongjun Lee, \ldots{} David T Scadden} \emph{Cell} (2016-09) \url{https://doi.org/f3r5jr}
-\CSLBlock{DOI: \href{https://doi.org/10.1016/j.cell.2016.08.057}{10.1016/j.cell.2016.08.057} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/27641501}{27641501} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7360335}{PMC7360335}}}
+\leavevmode\vadjust pre{\hypertarget{ref-19ZFerhph}{}}%
+\CSLLeftMargin{13. }%
+\CSLRightInline{\textbf{Automated electron microscope tomography using robust prediction of specimen movements}
+\CSLBlock{David N Mastronarde} \emph{Journal of Structural Biology} (2005-10) \url{https://doi.org/ff7gzx}
+\CSLBlock{DOI: \href{https://doi.org/10.1016/j.jsb.2005.07.007}{10.1016/j.jsb.2005.07.007} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/16182563}{16182563}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-MUY42yxp}{}}%
+\CSLLeftMargin{14. }%
+\CSLRightInline{\textbf{cisTEM, user-friendly software for single-particle image processing}
+\CSLBlock{Timothy Grant, Alexis Rohou, Nikolaus Grigorieff} \emph{eLife} (2018-03-07) \url{https://doi.org/gf5cq7}
+\CSLBlock{DOI: \href{https://doi.org/10.7554/elife.35383}{10.7554/elife.35383} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/29513216}{29513216} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5854467}{PMC5854467}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-1G4Y94qCy}{}}%
+\CSLLeftMargin{15. }%
+\CSLRightInline{\textbf{Measuring the optimal exposure for single particle cryo-EM using a 2.6 Å reconstruction of rotavirus VP6}
+\CSLBlock{Timothy Grant, Nikolaus Grigorieff} \emph{eLife} (2015-05-29) \url{https://doi.org/gf5cm7}
+\CSLBlock{DOI: \href{https://doi.org/10.7554/elife.06980}{10.7554/elife.06980} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/26023829}{26023829} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4471936}{PMC4471936}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-n43f3Sqs}{}}%
+\CSLLeftMargin{16. }%
+\CSLRightInline{\textbf{CTFFIND4: Fast and accurate defocus estimation from electron micrographs}
+\CSLBlock{Alexis Rohou, Nikolaus Grigorieff} \emph{Journal of Structural Biology} (2015-11) \url{https://doi.org/f7xzgv}
+\CSLBlock{DOI: \href{https://doi.org/10.1016/j.jsb.2015.08.008}{10.1016/j.jsb.2015.08.008} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/26278980}{26278980} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6760662}{PMC6760662}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-q2PSamkS}{}}%
+\CSLLeftMargin{17. }%
+\CSLRightInline{\textbf{Cryo-TEM simulations of amorphous radiation-sensitive samples using multislice wave propagation}
+\CSLBlock{Benjamin Himes, Nikolaus Grigorieff} \emph{IUCrJ} (2021-09-30) \url{https://doi.org/gpzs9r}
+\CSLBlock{DOI: \href{https://doi.org/10.1107/s2052252521008538}{10.1107/s2052252521008538} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/34804546}{34804546} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC8562658}{PMC8562658}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-stvWEJeu}{}}%
+\CSLLeftMargin{18. }%
+\CSLRightInline{\textbf{scikit-image: image processing in Python}
+\CSLBlock{Stéfan van der Walt, Johannes L Schönberger, Juan Nunez-Iglesias, François Boulogne, Joshua D Warner, Neil Yager, Emmanuelle Gouillart, Tony Yu} \emph{PeerJ} (2014-06-19) \url{https://doi.org/gftp3s}
+\CSLBlock{DOI: \href{https://doi.org/10.7717/peerj.453}{10.7717/peerj.453} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/25024921}{25024921} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4081273}{PMC4081273}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-8Miti2Gz}{}}%
+\CSLLeftMargin{19. }%
+\CSLRightInline{\textbf{SciPy 1.0: fundamental algorithms for scientific computing in Python}
+\CSLBlock{Pauli Virtanen, Ralf Gommers, Travis E Oliphant, Matt Haberland, Tyler Reddy, David Cournapeau, Evgeni Burovski, Pearu Peterson, Warren Weckesser, Jonathan Bright, \ldots{} } \emph{Nature Methods} (2020-02-03) \url{https://doi.org/ggj45f}
+\CSLBlock{DOI: \href{https://doi.org/10.1038/s41592-019-0686-2}{10.1038/s41592-019-0686-2} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/32015543}{32015543} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7056644}{PMC7056644}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-cYCuuZxG}{}}%
+\CSLLeftMargin{20. }%
+\CSLRightInline{\textbf{\textless scp\textgreater UCSF ChimeraX\textless/scp\textgreater{}
+: Structure visualization for researchers, educators, and developers}
+\CSLBlock{Eric F Pettersen, Thomas D Goddard, Conrad C Huang, Elaine C Meng, Gregory S Couch, Tristan I Croll, John H Morris, Thomas E Ferrin} \emph{Protein Science} (2020-10-22) \url{https://doi.org/ghr6mn}
+\CSLBlock{DOI: \href{https://doi.org/10.1002/pro.3943}{10.1002/pro.3943} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/32881101}{32881101} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7737788}{PMC7737788}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sbkam02a}{}}%
+\CSLLeftMargin{21. }%
+\CSLRightInline{\textbf{Protein Synthesis in the Developing Neocortex at Near-Atomic Resolution Reveals Ebp1-Mediated Neuronal Proteostasis at the 60S Tunnel Exit}
+\CSLBlock{Matthew L Kraushar, Ferdinand Krupp, Dermot Harnett, Paul Turko, Mateusz C Ambrozkiewicz, Thiemo Sprink, Koshi Imami, Manuel Günnigmann, Ulrike Zinnall, Carlos H Vieira-Vieira, \ldots{} Christian MT Spahn} \emph{Molecular Cell} (2021-01) \url{https://doi.org/gh7d72}
+\CSLBlock{DOI: \href{https://doi.org/10.1016/j.molcel.2020.11.037}{10.1016/j.molcel.2020.11.037} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/33357414}{33357414} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC8163098}{PMC8163098}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-APSL9LmU}{}}%
+\CSLLeftMargin{22. }%
+\CSLRightInline{\textbf{High-quality, high-throughput cryo-electron microscopy data collection via beam tilt and astigmatism-free beam-image shift}
+\CSLBlock{Chunling Wu, Xiaojun Huang, Jing Cheng, Dongjie Zhu, Xinzheng Zhang} \emph{Journal of Structural Biology} (2019-12) \url{https://doi.org/gp2nq9}
+\CSLBlock{DOI: \href{https://doi.org/10.1016/j.jsb.2019.09.013}{10.1016/j.jsb.2019.09.013} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/31562921}{31562921}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-xE2EhAcH}{}}%
+\CSLLeftMargin{23. }%
+\CSLRightInline{\textbf{THE DEVELOPMENT OF NEUTROPHILIC POLYMORPHONUCLEAR LEUKOCYTES IN HUMAN BONE MARROW}
+\CSLBlock{Dorothy Ford Bainton, Joan L Ullyot, Marilyn G Farquhar} \emph{Journal of Experimental Medicine} (1971-10-01) \url{https://doi.org/chkbcm}
+\CSLBlock{DOI: \href{https://doi.org/10.1084/jem.134.4.907}{10.1084/jem.134.4.907} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/4106490}{4106490} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2138991}{PMC2138991}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-17IP4Lhz1}{}}%
+\CSLLeftMargin{24. }%
+\CSLRightInline{\textbf{Routine determination of ice thickness for cryo-EM grids}
+\CSLBlock{William J Rice, Anchi Cheng, Alex J Noble, Edward T Eng, Laura Y Kim, Bridget Carragher, Clinton S Potter} \emph{Journal of Structural Biology} (2018-10) \url{https://doi.org/gfbpj2}
+\CSLBlock{DOI: \href{https://doi.org/10.1016/j.jsb.2018.06.007}{10.1016/j.jsb.2018.06.007} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/29981485}{29981485} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6119488}{PMC6119488}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hr3dyUeI}{}}%
+\CSLLeftMargin{25. }%
+\CSLRightInline{\textbf{Optimized cryo-focused ion beam sample preparation aimed at in situ structural studies of membrane proteins}
+\CSLBlock{Miroslava Schaffer, Julia Mahamid, Benjamin D Engel, Tim Laugks, Wolfgang Baumeister, Jürgen M Plitzko} \emph{Journal of Structural Biology} (2017-02) \url{https://doi.org/f9qfr6}
+\CSLBlock{DOI: \href{https://doi.org/10.1016/j.jsb.2016.07.010}{10.1016/j.jsb.2016.07.010} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/27444390}{27444390}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-cie13Q8F}{}}%
+\CSLLeftMargin{26. }%
+\CSLRightInline{\textbf{Circularization of mRNA by eukaryotic translation initiation factors.}
+\CSLBlock{SE Wells, PE Hillner, RD Vale, AB Sachs} \emph{Molecular cell} (1998-07) \url{https://www.ncbi.nlm.nih.gov/pubmed/9702200}
+\CSLBlock{DOI: \href{https://doi.org/10.1016/s1097-2765(00)80122-7}{10.1016/s1097-2765(00)80122-7} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/9702200}{9702200}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-1GPPSX111}{}}%
+\CSLLeftMargin{27. }%
+\CSLRightInline{\textbf{Montage electron tomography of vitrified specimens}
+\CSLBlock{Ariana Peck, Stephen D Carter, Huanghao Mai, Songye Chen, Alister Burt, Grant J Jensen} \emph{Journal of Structural Biology} (2022-06) \url{https://doi.org/gp4qrs}
+\CSLBlock{DOI: \href{https://doi.org/10.1016/j.jsb.2022.107860}{10.1016/j.jsb.2022.107860} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/35487464}{35487464}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ujizcpVn}{}}%
+\CSLLeftMargin{28. }%
+\CSLRightInline{\textbf{Correlative cryogenic montage electron tomography for comprehensive in-situ whole-cell structural studies}
+\CSLBlock{Jie E Yang, Matthew R Larson, Bryan S Sibert, Joseph Y Kim, Daniel Parrell, Juan C Sanchez, Victoria Pappas, Anil Kumar, Kai Cai, Keith Thompson, Elizabeth R Wright} \emph{Cold Spring Harbor Laboratory} (2022-01-02) \url{https://doi.org/gp4qrv}
+\CSLBlock{DOI: \href{https://doi.org/10.1101/2021.12.31.474669}{10.1101/2021.12.31.474669}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-1Gwx5ScUa}{}}%
+\CSLLeftMargin{29. }%
+\CSLRightInline{\textbf{Beam image-shift accelerated data acquisition for near-atomic resolution single-particle cryo-electron tomography}
+\CSLBlock{Jonathan Bouvette, Hsuan-Fu Liu, Xiaochen Du, Ye Zhou, Andrew P Sikkema, Juliana da Fonseca Rezende e Mello, Bradley P Klemm, Rick Huang, Roel M Schaaper, Mario J Borgnia, Alberto Bartesaghi} \emph{Nature Communications} (2021-03-30) \url{https://doi.org/gjphkb}
+\CSLBlock{DOI: \href{https://doi.org/10.1038/s41467-021-22251-8}{10.1038/s41467-021-22251-8} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/33785757}{33785757} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC8009872}{PMC8009872}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-xvouNMBy}{}}%
+\CSLLeftMargin{30. }%
+\CSLRightInline{\textbf{Parallel cryo electron tomography on \textless i\textgreater in situ\textless/i\textgreater{} lamellae}
+\CSLBlock{Fabian Eisenstein, Haruaki Yanagisawa, Hiroka Kashihara, Masahide Kikkawa, Sachiko Tsukita, Radostin Danev} \emph{Cold Spring Harbor Laboratory} (2022-04-08) \url{https://doi.org/gp4qrw}
+\CSLBlock{DOI: \href{https://doi.org/10.1101/2022.04.07.487557}{10.1101/2022.04.07.487557}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-17H2LWiIu}{}}%
+\CSLLeftMargin{31. }%
+\CSLRightInline{\textbf{Waffle Method: A general and flexible approach for improving throughput in FIB-milling}
+\CSLBlock{Kotaro Kelley, Ashleigh M Raczkowski, Oleg Klykov, Pattana Jaroenlak, Daija Bobe, Mykhailo Kopylov, Edward T Eng, Gira Bhabha, Clinton S Potter, Bridget Carragher, Alex J Noble} \emph{Nature Communications} (2022-04-06) \url{https://doi.org/gp4qrt}
+\CSLBlock{DOI: \href{https://doi.org/10.1038/s41467-022-29501-3}{10.1038/s41467-022-29501-3} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/35387991}{35387991} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC8987090}{PMC8987090}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-T1Qr0xyP}{}}%
+\CSLLeftMargin{32. }%
+\CSLRightInline{\textbf{\textless i\textgreater In situ\textless/i\textgreater{} single particle classification reveals distinct 60S maturation intermediates in cells}
+\CSLBlock{Bronwyn A Lucas, Kexin Zhang, Sarah Loerch, Nikolaus Grigorieff} \emph{Cold Spring Harbor Laboratory} (2022-04-10) \url{https://doi.org/gp4qrx}
+\CSLBlock{DOI: \href{https://doi.org/10.1101/2022.04.10.487797}{10.1101/2022.04.10.487797}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-44fG6kcy}{}}%
+\CSLLeftMargin{33. }%
+\CSLRightInline{\textbf{High-resolution cryo-EM using beam-image shift at 200 keV}
+\CSLBlock{Jennifer N Cash, Sarah Kearns, Yilai Li, Michael A Cianfrocco} \emph{IUCrJ} (2020-10-29) \url{https://doi.org/gjwcfq}
+\CSLBlock{DOI: \href{https://doi.org/10.1107/s2052252520013482}{10.1107/s2052252520013482} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/33209328}{33209328} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7642776}{PMC7642776}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kncnYGLD}{}}%
+\CSLLeftMargin{34. }%
+\CSLRightInline{\textbf{Shedding light on the cell biology of extracellular vesicles}
+\CSLBlock{Guillaume van Niel, Gisela D'Angelo, Graça Raposo} \emph{Nature Reviews Molecular Cell Biology} (2018-01-17) \url{https://doi.org/gct4df}
+\CSLBlock{DOI: \href{https://doi.org/10.1038/nrm.2017.125}{10.1038/nrm.2017.125} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/29339798}{29339798}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-agVdpX76}{}}%
+\CSLLeftMargin{35. }%
+\CSLRightInline{\textbf{Exosome-mediated transfer of mRNAs and microRNAs is a novel mechanism of genetic exchange between cells}
+\CSLBlock{Hadi Valadi, Karin Ekström, Apostolos Bossios, Margareta Sjöstrand, James J Lee, Jan O Lötvall} \emph{Nature Cell Biology} (2007-05-07) \url{https://doi.org/d5df4s}
+\CSLBlock{DOI: \href{https://doi.org/10.1038/ncb1596}{10.1038/ncb1596} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/17486113}{17486113}}}
 

### 2022-05-19 ci/deploy.sh
Deploy webpage

@@ -84,13 +84,13 @@ ghp-import \
   output
 
 # Deploy the webpage directory to gh-pages
-# ghp-import \
-#  --no-jekyll \
-#  --follow-links \
-#  --push \
-#  --branch=gh-pages \
-#  --message="$MESSAGE" \
-#  webpage
+ghp-import \
+  --no-jekyll \
+  --follow-links \
+  --push \
+  --branch=gh-pages \
+  --message="$MESSAGE" \
+  webpage
 
 if [ $MANUBOT_DEPLOY_VIA_SSH = "true" ]; then
   # Workaround https://github.com/travis-ci/travis-ci/issues/8082

### 2022-05-19 manuscript.tex
Deploy webpage [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/9e84ed3862d1eaba8f35e633a0051d4314907579.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/9e84ed3862d1eaba8f35e633a0051d4314907579/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2354626619

@@
 This manuscript
-(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/5f9575bbee2059d4e92d5c821f29682c4a661e49/}{permalink})
+(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/9e84ed3862d1eaba8f35e633a0051d4314907579/}{permalink})
 was automatically generated
-from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/5f9575bbee2059d4e92d5c821f29682c4a661e49}{jojoelfe/deco\_lace\_template\_matching\_manuscript@5f9575b}
+from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/9e84ed3862d1eaba8f35e633a0051d4314907579}{jojoelfe/deco\_lace\_template\_matching\_manuscript@9e84ed3}
 on May 19, 2022.

### 2022-05-20 ci/deploy.sh
custom deploy

@@ -63,6 +63,16 @@ manubot webpage \
   --checkout=gh-pages \
   --version="$COMMIT"
 
+rm webpage/images
+rm webpage/index.html
+rm webpage/manuscript.pdf
+
+mkdir webpage/output
+ln -s output/manuscript.html webpage/index.html
+ln -s output/manuscript.pdf webpage/manuscript.pdf
+ln -s output/manuscript.docx webpage/manuscript.docx
+ln -s output/figures webpage/output/figures
+
 # Commit message
 MESSAGE="\
 $(git log --max-count=1 --format='%s')

### 2022-05-20 manuscript.tex
custom deploy [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/6a99bb6d7d1ae0bbee70874ab4b79ba22f7fe1ce.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/6a99bb6d7d1ae0bbee70874ab4b79ba22f7fe1ce/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2355345427

@@
 This manuscript
-(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/9e84ed3862d1eaba8f35e633a0051d4314907579/}{permalink})
+(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/6a99bb6d7d1ae0bbee70874ab4b79ba22f7fe1ce/}{permalink})
 was automatically generated
-from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/9e84ed3862d1eaba8f35e633a0051d4314907579}{jojoelfe/deco\_lace\_template\_matching\_manuscript@9e84ed3}
-on May 19, 2022.
+from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/6a99bb6d7d1ae0bbee70874ab4b79ba22f7fe1ce}{jojoelfe/deco\_lace\_template\_matching\_manuscript@6a99bb6}
+on May 20, 2022.
 

### 2022-05-20 ci/deploy.sh
Maybe that works

@@ -68,10 +68,10 @@ rm webpage/index.html
 rm webpage/manuscript.pdf
 
 mkdir webpage/output
-ln -s output/manuscript.html webpage/index.html
-ln -s output/manuscript.pdf webpage/manuscript.pdf
-ln -s output/manuscript.docx webpage/manuscript.docx
-ln -s output/figures webpage/output/figures
+ln -s ../output/manuscript.html webpage/index.html
+ln -s ../output/manuscript.pdf webpage/manuscript.pdf
+ln -s ../output/manuscript.docx webpage/manuscript.docx
+ln -s ../output/figures webpage/output/figures
 
 # Commit message
 MESSAGE="\

### 2022-05-20 manuscript.tex
Maybe that works [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/61d15f13d08e1198660b00662e93261a41553a44.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/61d15f13d08e1198660b00662e93261a41553a44/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2355403292

@@
 This manuscript
-(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/6a99bb6d7d1ae0bbee70874ab4b79ba22f7fe1ce/}{permalink})
+(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/61d15f13d08e1198660b00662e93261a41553a44/}{permalink})
 was automatically generated
-from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/6a99bb6d7d1ae0bbee70874ab4b79ba22f7fe1ce}{jojoelfe/deco\_lace\_template\_matching\_manuscript@6a99bb6}
+from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/61d15f13d08e1198660b00662e93261a41553a44}{jojoelfe/deco\_lace\_template\_matching\_manuscript@61d15f1}
 on May 20, 2022.

### 2022-05-20 ci/deploy.sh
Another attempt

@@ -71,7 +71,7 @@ mkdir webpage/output
 ln -s ../output/manuscript.html webpage/index.html
 ln -s ../output/manuscript.pdf webpage/manuscript.pdf
 ln -s ../output/manuscript.docx webpage/manuscript.docx
-ln -s ../output/figures webpage/output/figures
+ln -s ../../output/figures webpage/output/figures
 
 # Commit message
 MESSAGE="\

### 2022-05-20 manuscript.tex
Another attempt [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/9f26f343eb6707bf20436bc0f58fa1c34dc74c00.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/9f26f343eb6707bf20436bc0f58fa1c34dc74c00/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2355455976

@@
 This manuscript
-(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/61d15f13d08e1198660b00662e93261a41553a44/}{permalink})
+(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/9f26f343eb6707bf20436bc0f58fa1c34dc74c00/}{permalink})
 was automatically generated
-from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/61d15f13d08e1198660b00662e93261a41553a44}{jojoelfe/deco\_lace\_template\_matching\_manuscript@61d15f1}
+from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/9f26f343eb6707bf20436bc0f58fa1c34dc74c00}{jojoelfe/deco\_lace\_template\_matching\_manuscript@9f26f34}
 on May 20, 2022.

### 2022-05-20 output/figures/matching_stat.tex
Another attempt [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/9f26f343eb6707bf20436bc0f58fa1c34dc74c00.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/9f26f343eb6707bf20436bc0f58fa1c34dc74c00/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2355455976

--- 2022-04-07 figures/matching_stat.tex
@@
 \node[labelNode] {B};
-\node[graphicNode] (panel) {\includegraphics[width=4.5cm]{content/code/img/scores_plot.png}};
+\node[graphicNode] (panel) {\includegraphics[width=4.5cm]{content/code/img/matches_per_tile_plot.png}};
 \node (anchor) at ([shift={(0.5cm,0.0)}]panel.north east) {}; 
 \node[labelNode] {C};
-\node[graphicNode] {\includegraphics[width=4.5cm]{content/code/img/matches_per_tile_plot.png}};
-\node (anchor) at ([shift={(0.0cm,-1.0)}]0.5,2.5 |- panel.south east) {}; 
+\node[graphicNode] (panel) {\includegraphics[width=4.5cm]{content/code/img/scores_plot.png}};
+\node (anchor) at ([shift={(0.0cm,-0.2)}]0.5,2.5 |- panel.south east) {}; 
 \node[labelNode] {D};
-\node[graphicNode] {\includegraphics[width=14cm]{content/code/img/micrograph_with_matches.png}};
+\node[graphicNode] (panel) {\includegraphics[width=14cm]{content/code/img/micrograph_with_matches.png}};
+
+\node (anchor) at ([shift={(0.0cm,-0.2)}]0.5,2.5 |- panel.south east) {}; 
+\node[labelNode] {E};
+\node[graphicNode] (panel) {\includegraphics[width=6cm]{content/code/img/num_matches_vs_bis.png}};
+
+\node (anchor) at ([shift={(1.0cm,0.0)}]panel.north east) {}; 
+\node[labelNode] {F};
+\node[graphicNode] {\includegraphics[width=6cm]{content/code/img/snrs_vs_bis.png}};
+
     \iftoggle{draft}{\draw[lightgray,step=1] (0,0) grid (\figwidth,\figheight);}{};

### 2022-05-20 ci/deploy.sh
Final fix

@@ -67,11 +67,10 @@ rm webpage/images
 rm webpage/index.html
 rm webpage/manuscript.pdf
 
-mkdir webpage/output
 ln -s ../output/manuscript.html webpage/index.html
 ln -s ../output/manuscript.pdf webpage/manuscript.pdf
 ln -s ../output/manuscript.docx webpage/manuscript.docx
-ln -s ../../output/figures webpage/output/figures
+ln -s ../output/figures webpage/figures
 
 # Commit message
 MESSAGE="\

### 2022-05-20 manuscript.tex
Final fix [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/e94f17b00fe53a7b703becda30c7a1b1503e6e7e.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/e94f17b00fe53a7b703becda30c7a1b1503e6e7e/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2355518964

@@
 This manuscript
-(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/9f26f343eb6707bf20436bc0f58fa1c34dc74c00/}{permalink})
+(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/e94f17b00fe53a7b703becda30c7a1b1503e6e7e/}{permalink})
 was automatically generated
-from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/9f26f343eb6707bf20436bc0f58fa1c34dc74c00}{jojoelfe/deco\_lace\_template\_matching\_manuscript@9f26f34}
+from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/e94f17b00fe53a7b703becda30c7a1b1503e6e7e}{jojoelfe/deco\_lace\_template\_matching\_manuscript@e94f17b}
 on May 20, 2022.

### 2022-05-20 figures/initmatching.tex
Final fix [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/e94f17b00fe53a7b703becda30c7a1b1503e6e7e.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/e94f17b00fe53a7b703becda30c7a1b1503e6e7e/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2355518964

@@
 \node[labelNode] {B};
+\node (img) [graphicNode]  {\includegraphics[height=4cm]{content/images/30_matches_m.png}};
 \node (img) [graphicNode]  {\includegraphics[height=4cm]{content/images/30_matches.png}};
@@
 \node[labelNode] {C};
+\node (img) [graphicNode]  {\includegraphics[height=4cm]{content/images/506_matches_m.png}};
 \node (img) [graphicNode]  {\includegraphics[height=4cm]{content/images/506_matches.png}};
@@
 \node[labelNode] {D};
+\node (img) [graphicNode]  {\includegraphics[height=4cm]{content/images/17_matches_m.png}};
 \node (img) [graphicNode]  {\includegraphics[height=4cm]{content/images/17_matches.png}};
@@
 \node[labelNode] {E};
+\node (img) [graphicNode]  {\includegraphics[height=4cm]{content/images/52_matches_m.png}};
 \node (img) [graphicNode]  {\includegraphics[height=4cm]{content/images/52_matches.png}};

### 2022-05-20 figures/lamella_images.tex
Final fix [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/e94f17b00fe53a7b703becda30c7a1b1503e6e7e.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/e94f17b00fe53a7b703becda30c7a1b1503e6e7e/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2355518964

@@
 
-    \def\panelheight{4.6cm}
+    \newlength{\panelheight}
+\setlength{\panelheight}{4.4cm}
 
@@
 \node[labelNode] {A};
-\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/slicer000.png}};
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/euc_lamella1_view.png}};
+% Title
+\node[anchor=center,align=center] at ([shift={(0.0cm,0.3cm)}]panel.north) {Lamella$_\textrm{EUC}$ 1};
+% scalebar - physical height is 12810 nm
+\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 12.81 , yshift=0.3cm]panel.south west);
+\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 12.81, yshift=0.3cm]panel.south west);
 \node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
-\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/slicer001.png}};
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/euc_lamella2_view.png}};
+% Title
+\node[anchor=center,align=center] at ([shift={(0.0cm,0.3cm)}]panel.north) {Lamella$_\textrm{EUC}$ 2};
+% scalebar - physical height is 7027.5 nm
+\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 7.0275 , yshift=0.3cm]panel.south west);
+\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 7.0275, yshift=0.3cm]panel.south west);
 \node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
-\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/slicer002.png}};
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/euc_lamella3_view.png}};
+% Title
+\node[anchor=center,align=center] at ([shift={(0.0cm,0.3cm)}]panel.north) {Lamella$_\textrm{EUC}$ 3};
+% scalebar - physical height is 9615 nm
+\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 9.615 , yshift=0.3cm]panel.south west);
+\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 9.615, yshift=0.3cm]panel.south west);
 \node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
-\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/slicer003.png}};
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/euc_lamella4_view.png}};
+% Title
+\node[anchor=center,align=center] at ([shift={(0.0cm,0.3cm)}]panel.north) {Lamella$_\textrm{EUC}$ 4};
+% scalebar - physical height is 8625 nm
+\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 8.625 , yshift=0.3cm]panel.south west);
+\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 8.625, yshift=0.3cm]panel.south west);
 
 \node (anchor) at ([shift={(0.0cm,-0.5cm)}]0.5,0 |- panel.south) {}; 
-\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/images/slicer005.png}};
+\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/images/fff_lamella1_view.png}};
+% Title
+\node[anchor=center,align=center] at ([shift={(0.0cm,0.3cm)}]panel.north) {Lamella$_\textrm{FFF}$ 1};
+% scalebar - physical height is 8032.5 nm
+\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 8.0325 , yshift=0.3cm]panel.south west);
+\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 8.0325, yshift=0.3cm]panel.south west);
 \node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
-\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/images/slicer006.png}};
+\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/images/fff_lamella2_view.png}};
+% Title
+\node[anchor=center,align=center] at ([shift={(0.0cm,0.3cm)}]panel.north) {Lamella$_\textrm{FFF}$ 2};
+% scalebar - physical height is 10000.5 nm
+\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 10.0005 , yshift=0.3cm]panel.south west);
+\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 10.0005, yshift=0.3cm]panel.south west);
 \node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
-\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/images/slicer007.png}};
+\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/images/fff_lamella3_view.png}};
+% Title
+\node[anchor=center,align=center] at ([shift={(0.0cm,0.3cm)}]panel.north) {Lamella$_\textrm{FFF}$ 3};
+% scalebar - physical height is 9975 nm
+\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 9.975 , yshift=0.3cm]panel.south west);
+\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 9.975, yshift=0.3cm]panel.south west);
 \node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
-\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/images/slicer008.png}};
+\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/images/fff_lamella4_view.png}};
+% Title
+\node[anchor=center,align=center] at ([shift={(0.0cm,0.3cm)}]panel.north) {Lamella$_\textrm{FFF}$ 4};
+% scalebar - physical height is 9337.5 nm
+\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 9.3375 , yshift=0.3cm]panel.south west);
+\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 9.3375, yshift=0.3cm]panel.south west);
+
+\node (anchor) at ([shift={(0.0cm,-1.0cm)}]0.5,0 |- panel.south) {}; 
+\node[labelNode] {B};
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/euc_lamella1_assm.png}};
+% Title
+\node[anchor=center,align=center] at ([shift={(0.0cm,0.3cm)}]panel.north) {Lamella$_\textrm{EUC}$ 1: 909 tiles};
+% scalebar - physical height is 12810 nm
+\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 12.81 , yshift=0.3cm]panel.south west);
+\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 12.81, yshift=0.3cm]panel.south west);
+\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/euc_lamella2_assm.png}};
+% Title
+\node[anchor=center,align=center] at ([shift={(0.0cm,0.3cm)}]panel.north) {Lamella$_\textrm{EUC}$ 2: 451 tiles};
+% scalebar - physical height is 7027.5 nm
+\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 7.0275 , yshift=0.3cm]panel.south west);
+\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 7.0275, yshift=0.3cm]panel.south west);
+\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/euc_lamella3_assm.png}};
+% Title
+\node[anchor=center,align=center] at ([shift={(0.0cm,0.3cm)}]panel.north) {Lamella$_\textrm{EUC}$ 3: 513 tiles};
+% scalebar - physical height is 9615 nm
+\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 9.615 , yshift=0.3cm]panel.south west);
+\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 9.615, yshift=0.3cm]panel.south west);
+\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/euc_lamella4_assm.png}};
+% Title
+\node[anchor=center,align=center] at ([shift={(0.0cm,0.3cm)}]panel.north) {Lamella$_\textrm{EUC}$ 4: 497 tiles};
+% scalebar - physical height is 8625 nm
+\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 8.625 , yshift=0.3cm]panel.south west);
+\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 8.625, yshift=0.3cm]panel.south west);
+
+\node (anchor) at ([shift={(0.0cm,-0.5cm)}]0.5,0 |- panel.south) {}; 
+\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/images/fff_lamella1_assm.png}};
+% Title
+\node[anchor=center,align=center] at ([shift={(0.0cm,0.3cm)}]panel.north) {Lamella$_\textrm{FFF}$ 1: 438 tiles};
+% scalebar - physical height is 10000.5 nm
+\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 10.0005 , yshift=0.3cm]panel.south west);
+\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 10.0005, yshift=0.3cm]panel.south west);
+\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
+\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/images/fff_lamella2_assm.png}};
+% Title
+\node[anchor=center,align=center] at ([shift={(0.0cm,0.3cm)}]panel.north) {Lamella$_\textrm{FFF}$ 2: 474 tiles};
+% scalebar - physical height is 10000.5 nm
+\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 10.0005 , yshift=0.3cm]panel.south west);
+\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 10.0005, yshift=0.3cm]panel.south west);
+\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
+\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/images/fff_lamella3_assm.png}};
+% Title
+\node[anchor=center,align=center] at ([shift={(0.0cm,0.3cm)}]panel.north) {Lamella$_\textrm{FFF}$ 3: 501 tiles};
+% scalebar - physical height is 9975 nm
+\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 9.975 , yshift=0.3cm]panel.south west);
+\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 9.975, yshift=0.3cm]panel.south west);
+\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
+\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/images/fff_lamella4_assm.png}};
+% Title
+\node[anchor=center,align=center] at ([shift={(0.0cm,0.3cm)}]panel.north) {Lamella$_\textrm{FFF}$ 4: 425 tiles};
+% scalebar - physical height is 9337.5 nm
+\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 9.3375 , yshift=0.3cm]panel.south west);
+\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + \panelheight / 9.3375, yshift=0.3cm]panel.south west);
+
+\newlength{\padding}
+\setlength{\padding}{0.2cm}
+\node (anchor) at ([shift={(0.0cm,-1.0cm)}]0.5,0 |- panel.south) {}; 
+\node[labelNode] {C};
+\node[graphicNode] (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap004.png}};
+\node (anchor) at ([shift={(\padding,0.0cm)}]panel.north east) {}; 
+\node[graphicNode] (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap012.png}};
+\node (anchor) at ([shift={(\padding,0.0cm)}]panel.north east) {}; 
+\node[graphicNode] (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap015.png}};
+\node (anchor) at ([shift={(\padding,0.0cm)}]panel.north east) {}; 
+\node[graphicNode] (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap020.png}};
+\node (anchor) at ([shift={(\padding,0.0cm)}]panel.north east) {}; 
+\node[graphicNode] (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap006.png}};
+
+\node (anchor) at ([shift={(0.0cm,-\padding)}]0.5,0 |- panel.south) {}; 
+\node[graphicNode]  (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap021.png}};
+\node (anchor) at ([shift={(\padding,0.0cm)}]panel.north east) {}; 
+\node[graphicNode]  (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap022.png}};
+\node (anchor) at ([shift={(\padding,0.0cm)}]panel.north east) {}; 
+\node[graphicNode]  (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap027.png}};
+\node (anchor) at ([shift={(\padding,0.0cm)}]panel.north east) {}; 
+\node[graphicNode]  (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap029.png}};
+\node (anchor) at ([shift={(\padding,0.0cm)}]panel.north east) {}; 
+\node[graphicNode]  (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap023.png}};
+% scalebar - physical height is 375 nm
+\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + 0.75\panelheight / 3.75 , yshift=0.3cm]panel.south west);
+\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]panel.south west) -- ([xshift=0.5cm + 0.75\panelheight / 3.75, yshift=0.3cm]panel.south west);
 

### 2022-05-20 figures/matching_euc.tex
Final fix [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/e94f17b00fe53a7b703becda30c7a1b1503e6e7e.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/e94f17b00fe53a7b703becda30c7a1b1503e6e7e/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2355518964

@@
 
+    \newlength{\panelheight}
+\setlength{\panelheight}{12cm}
+
 \node (anchor) at (0.5,9.5) {}; 
 \node[labelNode] {A};
-\node[graphicNode] {\includegraphics[height=12cm]{content/images/euc_lamella1_1000px.png}};
-\node[graphicNode] {\includegraphics[height=12cm]{content/images/euc_lamella1_just_matches.png}};
+\node[graphicNode] (assm) {\includegraphics[height=\panelheight]{content/images/euc_lamella1_assm.png}};
+\node[graphicNode] {\includegraphics[height=\panelheight]{content/images/euc_lamella1.png}};
+\node (rect) at (7.4,3.5) [anchor=center,draw,thick,minimum width=0.3cm,minimum height=0.3cm,color=red] {};
+\node (rect) at (1.75,4.5) [anchor=center,draw,thick,minimum width=0.3cm,minimum height=0.3cm,color=green] {};
+\node (rect) at (7.2,2.15) [anchor=center,draw,thick,minimum width=0.3cm,minimum height=0.3cm,color=blue!60] {};
+\node (rect) at (6.45,6.0) [anchor=center,draw,thick,minimum width=0.47cm,minimum height=0.47cm,color=cyan] {};
+% scalebar - physical height is 12810 nm
+\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]assm.south west) -- ([xshift=0.5cm + \panelheight / 12.81 , yshift=0.3cm]assm.south west);
+\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]assm.south west) -- ([xshift=0.5cm + \panelheight / 12.81, yshift=0.3cm]assm.south west);
 
@@
 \node[labelNode] {B};
-\node[anchor=north west, below right=0cm and -4.5cm of anchor] {\includegraphics[height=12cm]{content/images/euc_lamella1_just_matches_side.png}};
+\node[anchor=north west, below right=0cm and 0.0cm of anchor] (side) {\includegraphics[height=12cm, trim=20.5cm 0 2cm 0]{content/images/euc_lamella1_side.png}};
 
+\draw [->, thick] ($ (assm.east) + (0.1,0) $) -- node[above=0.2cm, align=center] (c) {} ($ (side.west) + (0.2,0) $);
+
+\centerarc [canvas is zx plane at y=0.75, ->](c.center)(-90:180:0.15);
+\draw [very thick] ($ (c.center) + (0,-0.1) $) -- ($ (c.center) + (0,0.2) $);
+\node at ($ (c.center) + (0.5,0) $) {90°};
+
+\newlength{\panelheightm}
+\setlength{\panelheightm}{2.8cm}
 \node (anchor) at (13.0,9.5) {}; 
 \node[labelNode] {C};
-\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/euc_lamella1_just_matches_er_ribos.png}};
+\node[graphicNode] (pan) {\includegraphics[height=\panelheightm]{content/images/euc_lamella1_detail1.png}};
+\node (n3) [box=red, fit=(pan)] {};
+% scalebar - physical height is 300 nm
+\draw [line width=1.55mm,white] ([xshift=0.2cm, yshift=0.2cm]pan.south west) -- ([xshift=0.2cm + \panelheightm / 3 , yshift=0.2cm]pan.south west);
+\draw [line width=0.7mm,black] ([xshift=0.2cm, yshift=0.2cm]pan.south west) -- ([xshift=0.2cm + \panelheightm / 3, yshift=0.2cm]pan.south west);
 
@@
 \node[labelNode] {D};
-\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/euc_lamella1_just_matches_nucleus.png}};
+\node[graphicNode] (pan) {\includegraphics[height=\panelheightm]{content/images/euc_lamella1_detail2.png}};
+\node (n3) [box=green, fit=(pan)] {};
+
+% scalebar - physical height is 300 nm
+\draw [line width=1.55mm,white] ([xshift=0.2cm, yshift=0.2cm]pan.south west) -- ([xshift=0.2cm + \panelheightm / 3 , yshift=0.2cm]pan.south west);
+\draw [line width=0.7mm,black] ([xshift=0.2cm, yshift=0.2cm]pan.south west) -- ([xshift=0.2cm + \panelheightm / 3, yshift=0.2cm]pan.south west);
 
@@
 \node[labelNode] {E};
-\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/euc_lamella1_just_matches_circle.png}};
+\node[graphicNode] (pan) {\includegraphics[height=\panelheightm]{content/images/euc_lamella1_detail3.png}};
+\node (n3) [box=blue!60, fit=(pan)] {};
+
+% scalebar - physical height is 300 nm
+\draw [line width=1.55mm,white] ([xshift=0.2cm, yshift=0.2cm]pan.south west) -- ([xshift=0.2cm + \panelheightm / 3 , yshift=0.2cm]pan.south west);
+\draw [line width=0.7mm,black] ([xshift=0.2cm, yshift=0.2cm]pan.south west) -- ([xshift=0.2cm + \panelheightm / 3, yshift=0.2cm]pan.south west);
 
@@
 \node[labelNode] {F};
-\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/euc_lamella1_just_matches_contained.png}};
+\node[graphicNode] (pan) {\includegraphics[height=\panelheightm]{content/images/euc_lamella1_detail4.png}};
+\node (n3) [box=cyan, fit=(pan)] {};
+
+% scalebar - physical height is 500 nm
+\draw [line width=1.55mm,white] ([xshift=0.2cm, yshift=0.2cm]pan.south west) -- ([xshift=0.2cm + \panelheightm / 5 , yshift=0.2cm]pan.south west);
+\draw [line width=0.7mm,black] ([xshift=0.2cm, yshift=0.2cm]pan.south west) -- ([xshift=0.2cm + \panelheightm / 5, yshift=0.2cm]pan.south west);
 

### 2022-05-27 build/build.sh
deploy movies

@@ -38,10 +38,13 @@ manubot process \
 # Make output directory
 mkdir -p output
 mkdir -p output/figures
+mkdir -p output/movies
 
 # Generate the figures
 
 cp content/figures/* output/figures/
+cp content/movies/* output/movies/
+
 
 pandoc --verbose \
   --data-dir="$PANDOC_DATA_DIR" \

### 2022-05-27 ci/deploy.sh

@@ -71,6 +71,7 @@ ln -s ../output/manuscript.html webpage/index.html
 ln -s ../output/manuscript.pdf webpage/manuscript.pdf
 ln -s ../output/manuscript.docx webpage/manuscript.docx
 ln -s ../output/figures webpage/figures
+ln -s ../output/movies webpage/movies
 
 # Commit message
 MESSAGE="\

### 2022-05-27 manuscript.tex
deploy movies [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/26bf17f811e80363e8f38656b89bbae2c14147f8.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/26bf17f811e80363e8f38656b89bbae2c14147f8/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2398856270

@@
   pdftitle={Defocus Corrected Large Area Cryo-EM (DeCo-LACE) for Label-Free Detection of Molecules across Entire Cell Sections},
-  pdfauthor={Johannes ElferichNikolaus Grigorieff},
+  pdfauthor={Johannes ElferichGiulia SchiroliDavid ScaddenNikolaus Grigorieff},
   pdflang={en-US},
@@
 This manuscript
-(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/e94f17b00fe53a7b703becda30c7a1b1503e6e7e/}{permalink})
+(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/26bf17f811e80363e8f38656b89bbae2c14147f8/}{permalink})
 was automatically generated
-from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/e94f17b00fe53a7b703becda30c7a1b1503e6e7e}{jojoelfe/deco\_lace\_template\_matching\_manuscript@e94f17b}
-on May 20, 2022.
+from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/26bf17f811e80363e8f38656b89bbae2c14147f8}{jojoelfe/deco\_lace\_template\_matching\_manuscript@26bf17f}
+on May 27, 2022.
 
@@
   RNA Therapeutic Institute, UMass Chan Medical School; HHMI
+\item
+  \textbf{Giulia Schiroli}
+  None
+\item
+  \textbf{David Scadden}
+  None
 \item
@@
 
-\hypertarget{materials-and-methods}{%
-\subsection{Materials and Methods}\label{materials-and-methods}}
-
-\hypertarget{grid-preparation}{%
-\subsubsection{Grid preparation}\label{grid-preparation}}
-
-ER-HoxA9 cells were maintained in RPMI medium supplemented with 10\% FBS,
-penicillin/streptomycin, SCF, and estrogen {[}\protect\hyperlink{ref-1B9Vt9eYu}{10}{]} at
-37 °C and 5\% CO2. 120 h prior to grid preparation, cells were washed twice in PBS
-and cultured in the same medium except without estrogen. Differentiation was
-verified by staining with Hoechst-dye and inspection of nuclear morphology.
-Cells were then counted and diluted to \(1\cdot10^6\) cells/ml. Grids (either 200
-mesh copper grids, with a sillicone-oxide and 2 µm holes with a 2 µm spacing or
-200 mesh gold grids with a thin gold film and 2 µm holes in 2 µm spacing) were
-glow-discharged from both sides using a 15 mA for 45 s. 3.5 µl of cell suspension
-was added to grids on the thin-film side and grids were blotted from the back
-side using a GP2 cryoplunger (Leica) for 8 s and rapidly plunged into liquid
-ethane at -185 °C.
-
-\hypertarget{fib-milling}{%
-\subsubsection{FIB-milling}\label{fib-milling}}
-
-Grids were loaded into an Aquilos 2 FIB/SEM (Thermo Fisher) instrument with a
-stage cooled to -190 °C. Grids were sputter-coated with platinum for 15 s at 45 mA
-and then coated with a layer of platinum-precursor by opening the GIS-valve for
-45 s. An overview of the grid was created by montaging SEM images and isolated
-cells at the center of gridsquares were selected for FIB-milling. Lamellae were
-generated automatically using the AutoTEM software (Thermo Fisher), with the
-following parameters:
-
-\begin{itemize}
-\tightlist
-\item
-  Milling angle: 20°
-\item
-  Rough milling: 3.2 µm thickness, 0.5 nA current
-\item
-  Medium milling: 1.8 µm thickness, 0.3 nA current, 1.0° overtilt
-\item
-  Fine milling: 1.0 µm tchickness, 0.1 nA current, 0.5° overtilt
-\item
-  Finer milling: 700 nm thickness, 0.1 nA curent, 0.2° overtilt
-\item
-  Polish 1: 450 nm thickness, 50 pA current
-\item
-  Polish 2: 200 nm thickness, 30 pA current
-\end{itemize}
-
-This resulted in 6-10 µm wide lamella with 150-250 nm thickness as determined by
-FIB-imaging of the lamella edges.
-
-\hypertarget{data-collection}{%
-\subsubsection{Data collection}\label{data-collection}}
-
-Grids were loaded into a Titan Krios TEM (Thermo Fisher) operated at 300 keV and
-equipped with a BioQuantum energy filter (Gatan) and K3 camera (Gatan). The
-microscope was aligned using a cross-grating grid on the stage. Prior to each
-session, we carefully performed the ``Image/Beam'' calibration in nanoprobe. We
-set the magnification to a pixel size of 1.76 Å and condensed the beam to \textasciitilde{} 900 nm
-diameter, resulting in the beam being completely visible on the camera. To
-establish fringe-free conditions, the ``Fine eucentric'' procedure of SerialEM {[}\protect\hyperlink{ref-19ZFerhph}{13}{]} was
-used to move a square of the cross-grating grid to the eucentric position of the
-microscope. The effective defocus was then set to 2 µm, using the ``autofocus''
-routine of SerialEM. The objective focus of the microscope was changed until no
-fringes were visible. The stage was then moved in Z until images had an apparent
-defocus of 2 µm. The difference in stage Z-position between the eucentric and
-fringe-free conditions was used to move other areas into fringe-free condition.
-
-Low magnification montages were used to find lamellae and lamellae that were
-sufficiently thin and free of contamination were selected for automated data
-collection. Overview images of each lamella were taken at 2250x magnification
-(38 Å pixel size). The corners of the lamella in the overview image were manually
-annotated in SerialEM and translated into beam image-shift values using SerialEM's
-calibration. A hexagonal pattern of beam image-shift positions was calculated
-that covered the area between the four corners in a serpentine way, with a
-\(\sqrt{3}\cdot425\) nm horizontal spacing and \(3/4\cdot 850\) nm vertical spacing. Exposures were
-taken at each position with a 30 e\textsuperscript{-}/Å\(^2\) total dose. After each exposure, the
-defocus was estimated using the ctffind function of SerialEM and the focus for
-the next exposure was corrected by the difference between the estimated focus
-and the desired defocus of 800 nm. Furthermore, after each exposure the
-deviation of the beam from the center of the camera was measured and corrected
-using the ``CenterBeamFromImage'' command of SerialEM.
-
-After data collection, a 20 s exposure at 2250x magnification of the lamella at
-200 μm defocus was taken for visualization purposes. A Python script implementing
-this procedure is available at {[}Link to repo{]}.
-
-\hypertarget{deco-lace-data-processing}{%
-\subsubsection{DeCo-LACE data processing}\label{deco-lace-data-processing}}
-
-An overview of the data analysis pipeline is shown in Fig.
-\ref{fig:deco_lace_workflow}.
-
-\hypertarget{pre-processing}{%
-\paragraph{Pre-processing}\label{pre-processing}}
-
-Motion-correction, dose weighting and other preprocessing as detailed below was performed using \emph{cis}TEM {[}\protect\hyperlink{ref-MUY42yxp}{14}{]}.
-To avoid influence of the beam-edge on motion-correction, only a quarter of the
-movie in the center of the camera was considered for calculation of the
-estimated motion. After movie frames were aligned and summed, a mask for the
-illuminated area was calculated by lowpass filtering the image with a 100 Å
-resolution cutoff, thresholding the image at 10\% of the maximal value and then lowpass
-filtering the mask again with a 100 Å resolution cutoff to smooth the mask edges. This mask was
-then used to select dark areas in the image and fill the pixels with
-Gaussian noise, with the same mean and standard deviation as the illuminated
-area. A custom version of the unblur program {[}\protect\hyperlink{ref-1G4Y94qCy}{15}{]}
-implementing this procedure is available at {[}link to decolace branch{]}. During motion correction images were resampled to a pixel size of 1.5 Å. The
-contrast-transfer function (CTF) was estimated using ctffind
-{[}\protect\hyperlink{ref-n43f3Sqs}{16}{]}, searching between 0.2 and 2 μm defocus.
-
-\hypertarget{dtm}{%
-\paragraph{2DTM}\label{dtm}}
-
-The search template was generated from the atomic model of the mouse LSU
-(PDB 6SWA, exluding the Epb1 subunit) using the cryo-EM simulator implemented in \emph{cis}TEM
-{[}\protect\hyperlink{ref-q2PSamkS}{17}{]}. The
-match\_template program {[}\protect\hyperlink{ref-10bXZuF3G}{9}{]} was used to search for this
-template in the movie-aligned, exposure-filtered and masked images, using a 1.5°
-angular step in out-of-plane angles and a 1.0° angular step in-plane. 11 defocus
-planes in 20 nm steps centered around the ctffind-determined defocus were searched. Targets
-were defined as detected when their matches with the template produced peaks
-with a singal-to-noise ratio (SNR) above a threshold of 7.75, which was chosen
-based on the one-false-positive-per-tile criterion {[}\protect\hyperlink{ref-Ynb3IP6I}{7}{]}.
-
-\hypertarget{montage-assembly}{%
-\paragraph{Montage assembly}\label{montage-assembly}}
-
-The coordinates of each tile \(i\),
-\(\mathbf{c}_{i}\) {[}2D Vector in pixels{]} were initialized using beam image-shift of the tile, \(\mathbf{b}_i\) {[}2D Vector in μm{]},
-and the ISToCamera matrix \(\mathbf{IC}\), as calibrated by SerialEM:
-
-\[\mathbf{c}_{i} = \mathbf{IC} \cdot \mathbf{b}_i\]
-
-A list of tile pairs \(i,j\) that overlap were assembled by selecting images where
-\(|\mathbf{c}_i-\mathbf{c}_j| < D_{Beam}\).
-In order to calculate the precise offset between tiles \(i\) and \(j\), \(\mathbf{r}_{i,j}\), we calculated the cross-correlation between the two tiles, masked to the overlapping illuminated area using the scikit-image
-package {[}\protect\hyperlink{ref-stvWEJeu}{18}{]} was used to calculate refined offsets .
-The coordinates \(\mathbf{c}_{i}\) were then refined by a least-square minimization against \(\mathbf{r}_{i,j}\):
-
-\[ \displaystyle{\min_{\mathbf{c}} \sum_{pairs}{(\mathbf{r}_{i,j} - (\mathbf{c}_i-\mathbf{c}_j))^2}}\]
-
-using the scipy package {[}\protect\hyperlink{ref-8Miti2Gz}{19}{]}. The masked cross-correlation and the least-square minimization was repeated once more to arrive at the final tile alignment.
-
-The x,y coordinates of target \(n\) detected by 2DTM in the tile \(i\),
-\(\textbf{m}^\textrm{T}_{n,i}\), was transformed into the montage frame by adding
-the coordinate of the tile.
-
-\[ \textbf{m}^\textrm{M}_n = \textbf{m}^\textrm{T}_{n,i} + \textbf{c}_i\]
-
-The z coordinate of each target was calculated as the sum of the defocus offset
-for the target, the estimated defocus of the tile, and the nominal defocus of
-the microscope when the tile was acquired.
-
-Images were rendered using UCSF ChimeraX {[}\protect\hyperlink{ref-cYCuuZxG}{20}{]}. The Python scripts used for data processing are available
-under {[}repolink{]}.
-
 \hypertarget{results}{%
@@
 
-We used an atomic model of the 60S mouse ribosomal subunit (6SWA) for 2DTM {[}\protect\hyperlink{ref-sbkam02a}{21}{]}. In a
+We used an atomic model of the 60S mouse ribosomal subunit (6SWA) for 2DTM {[}\protect\hyperlink{ref-sbkam02a}{13}{]}. In a
 subset of images, the distribution of cross-correlation scores significantly
@@
 {[}\ref{fig:lamella_spatial_info}{]}B). While approaches exist to correct for this
-during the data collection {[}\protect\hyperlink{ref-APSL9LmU}{22}{]}, we opted to not use these approaches in our
+during the data collection {[}\protect\hyperlink{ref-APSL9LmU}{14}{]}, we opted to not use these approaches in our
 initial experiments. We reasoned that because 2DTM depends on high-resolution
@@
 density. We found that a substantial number of granules, which are characterized by higher
-density inside the the surrounding cytosol {[}\protect\hyperlink{ref-xE2EhAcH}{23}{]}, seemed to contain a membrane-enclosed inclusion with density similar to
+density inside the the surrounding cytosol {[}\protect\hyperlink{ref-xE2EhAcH}{15}{]}, seemed to contain a membrane-enclosed inclusion with density similar to
 the surrounding cytosol (Fig. {[}\ref{fig:lamella_images}{]}C) and could therefore be formed
@@
 150-300 nm in diameter and the inclusions were 100-200 nm in diameter. Based on
-these dimensions the granules are either azurophil or specific granules {[}\protect\hyperlink{ref-xE2EhAcH}{23}{]}. To our
+these dimensions the granules are either azurophil or specific granules {[}\protect\hyperlink{ref-xE2EhAcH}{15}{]}. To our
 knowledge, these inclusion have not been described in granulocytes and are
@@
 substantially higher intensities at the leading edge (Fig. {[}\ref{fig:lamella_motion_thickness}{]}B), which in energy-filtered
-TEM indicates a thinner sample {[}\protect\hyperlink{ref-17IP4Lhz1}{24}{]}. Even though we prepared the lamellae
-with the ``overtilt'' approach {[}\protect\hyperlink{ref-hr3dyUeI}{25}{]}, this means that ribosome densities across
+TEM indicates a thinner sample {[}\protect\hyperlink{ref-17IP4Lhz1}{16}{]}. Even though we prepared the lamellae
+with the ``overtilt'' approach {[}\protect\hyperlink{ref-hr3dyUeI}{17}{]}, this means that ribosome densities across
 the lamellae can be skewed by a change in thickness, and better sample
@@
 ring-like structures (Fig. {[}\ref{fig:matching_euc}{]}E), potentially indicating
-circularized mRNAs {[}\protect\hyperlink{ref-cie13Q8F}{26}{]}. While ribosomes were for the most part excluded
+circularized mRNAs {[}\protect\hyperlink{ref-cie13Q8F}{18}{]}. While ribosomes were for the most part excluded
 from the numerous granules observed in the cytoplasm, in some cases we observed
@@
 We also wondered whether large image shifts would lead aberration due to
-astigmatism or beam tilt {[}\protect\hyperlink{ref-APSL9LmU}{22}{]}. We reasoned that if
+astigmatism or beam tilt {[}\protect\hyperlink{ref-APSL9LmU}{14}{]}. We reasoned that if
 that was the case the number of detected targets should be highest in the center of the
@@
 Peck et al.
-{[}\protect\hyperlink{ref-1GPPSX111}{27}{]} and Yang et al.
-{[}\protect\hyperlink{ref-ujizcpVn}{28}{]} developed approaches to increase the FOV of tomogram data-collection by using a montaging technique.
+{[}\protect\hyperlink{ref-1GPPSX111}{19}{]} and Yang et al.
+{[}\protect\hyperlink{ref-ujizcpVn}{20}{]} developed approaches to increase the FOV of tomogram data-collection by using a montaging technique.
 Peck et al.~used a similar ``condensed-beam'' approach as described here.
@@
 Bouvette et al.
-{[}\protect\hyperlink{ref-1Gwx5ScUa}{29}{]} and Eisenstein et al.
-{[}\protect\hyperlink{ref-xvouNMBy}{30}{]} are using beam image-shift to collect tilt-series in multiple locations in parallel to increase throughput.
+{[}\protect\hyperlink{ref-1Gwx5ScUa}{21}{]} and Eisenstein et al.
+{[}\protect\hyperlink{ref-xvouNMBy}{22}{]} are using beam image-shift to collect tilt-series in multiple locations in parallel to increase throughput.
 However, none of these approaches provide the full coverage of a cellular cross-section that can be achieved using DeCo-Lace.
@@
 While data collection throughput on the TEM is fundamentally limited by the exposure time, this amount of data could be collected within 12 hour by improving the data acquisition scheme to perform all necessary calculation in parallel with actual exposure of the camera.
-Sample preparation using a FIB/SEM is also currently a bottleneck, but preparation of large lamellae with multiple cellular cross-sections using methods like WAFFLE {[}\protect\hyperlink{ref-17H2LWiIu}{31}{]} might allow sufficient throughput.
+Sample preparation using a FIB/SEM is also currently a bottleneck, but preparation of large lamellae with multiple cellular cross-sections using methods like WAFFLE {[}\protect\hyperlink{ref-17H2LWiIu}{23}{]} might allow sufficient throughput.
 As stated in the results, at least for 2DTM computation will remain challenging and approximately 17,000 GPU hours would be required for a 100 lamellae dataset.
@@
 In the 670 tiles containing exclusively nucleus (as manually annotated from the overview image) we detected 247 targets, making the false-positive rate more than twofold lower than expected.
-Since earlier work shows that 2DTM with the LSU can produce matches to nuclear ribosome biogenesis intermediates {[}\protect\hyperlink{ref-T1Qr0xyP}{32}{]}, this could even be an overestimate of the false-positive rate.
+Since earlier work shows that 2DTM with the LSU can produce matches to nuclear ribosome biogenesis intermediates {[}\protect\hyperlink{ref-T1Qr0xyP}{24}{]}, this could even be an overestimate of the false-positive rate.
 This suggests that the detection threshold could be even lower, which is an area of ongoing research.
@@
 We found that even though we used beam image-shift extensively (up to 7 um), we did not see substantially reduced 2DTM SNR values in tiles acquired at high beam image-shift compared to tiles acquired with low or no beam image-shift.
-This is in contrast to reports in single-particle analysis (SPA) {[}\protect\hyperlink{ref-44fG6kcy}{33}{]} where the induced beam tilt substantially reduced the resolution if it was not corrected during processing.
+This is in contrast to reports in single-particle analysis (SPA) {[}\protect\hyperlink{ref-44fG6kcy}{25}{]} where the induced beam tilt substantially reduced the resolution if it was not corrected during processing.
 It is possible that 2DTM is less sensitive to beam-tilt aberrations, since the template is free of any aberration and only the image is distorted, while in SPA the beam tilt will affect both the images and the reconstructed template.
@@
 We speculate that upon degranulation, the process in which granules fuse with the plasma membrane, these vesicles would be released into the extracelullar space.
-The main types of extracellular vesicles of this size are exosomes, up to 100 nm large vesicles derived from fusion of multivesicular bodies with the plasma membrane, and microvesicles, which are derived from direct budding of the plasma membrane {[}\protect\hyperlink{ref-kncnYGLD}{34}{]}.
+The main types of extracellular vesicles of this size are exosomes, up to 100 nm large vesicles derived from fusion of multivesicular bodies with the plasma membrane, and microvesicles, which are derived from direct budding of the plasma membrane {[}\protect\hyperlink{ref-kncnYGLD}{26}{]}.
 We suggest that granulocytes could release a third type of extracellular vesicle, granule-derived vesicles (GDV), into the extracellular space.
@@
 {[}\ref{fig:matching_fff}{]}D,E).
-This could indicate that these vesicles are transporting translation-capable mRNAs, as has been described for exosomes {[}\protect\hyperlink{ref-agVdpX76}{35}{]}.
+This could indicate that these vesicles are transporting translation-capable mRNAs, as has been described for exosomes {[}\protect\hyperlink{ref-agVdpX76}{27}{]}.
 Further studies will be necessary to confirm the existence of GDVs in granulocytes isolated from mammals and to understand their functional significance.
 
-\begin{figure}
-\hypertarget{fig:deco_lace_workflow}{%
-\centering
-\includegraphics{figures/deco_lace_workflow.png}
-\caption{Workflow of DeCo-Lace processing}\label{fig:deco_lace_workflow}
-}
-\end{figure}
+\hypertarget{materials-and-methods}{%
+\subsection{Materials and Methods}\label{materials-and-methods}}
+
+\hypertarget{grid-preparation}{%
+\subsubsection{Grid preparation}\label{grid-preparation}}
+
+ER-HoxA9 cells were maintained in RPMI medium supplemented with 10\% FBS,
+penicillin/streptomycin, SCF, and estrogen {[}\protect\hyperlink{ref-1B9Vt9eYu}{10}{]} at
+37 °C and 5\% CO2. 120 h prior to grid preparation, cells were washed twice in PBS
+and cultured in the same medium except without estrogen. Differentiation was
+verified by staining with Hoechst-dye and inspection of nuclear morphology.
+Cells were then counted and diluted to \(1\cdot10^6\) cells/ml. Grids (either 200
+mesh copper grids, with a sillicone-oxide and 2 µm holes with a 2 µm spacing or
+200 mesh gold grids with a thin gold film and 2 µm holes in 2 µm spacing) were
+glow-discharged from both sides using a 15 mA for 45 s. 3.5 µl of cell suspension
+was added to grids on the thin-film side and grids were blotted from the back
+side using a GP2 cryoplunger (Leica) for 8 s and rapidly plunged into liquid
+ethane at -185 °C.
+
+\hypertarget{fib-milling}{%
+\subsubsection{FIB-milling}\label{fib-milling}}
+
+Grids were loaded into an Aquilos 2 FIB/SEM (Thermo Fisher) instrument with a
+stage cooled to -190 °C. Grids were sputter-coated with platinum for 15 s at 45 mA
+and then coated with a layer of platinum-precursor by opening the GIS-valve for
+45 s. An overview of the grid was created by montaging SEM images and isolated
+cells at the center of gridsquares were selected for FIB-milling. Lamellae were
+generated automatically using the AutoTEM software (Thermo Fisher), with the
+following parameters:
+
+\begin{itemize}
+\tightlist
+\item
+  Milling angle: 20°
+\item
+  Rough milling: 3.2 µm thickness, 0.5 nA current
+\item
+  Medium milling: 1.8 µm thickness, 0.3 nA current, 1.0° overtilt
+\item
+  Fine milling: 1.0 µm tchickness, 0.1 nA current, 0.5° overtilt
+\item
+  Finer milling: 700 nm thickness, 0.1 nA curent, 0.2° overtilt
+\item
+  Polish 1: 450 nm thickness, 50 pA current
+\item
+  Polish 2: 200 nm thickness, 30 pA current
+\end{itemize}
+
+This resulted in 6-10 µm wide lamella with 150-250 nm thickness as determined by
+FIB-imaging of the lamella edges.
+
+\hypertarget{data-collection}{%
+\subsubsection{Data collection}\label{data-collection}}
+
+Grids were loaded into a Titan Krios TEM (Thermo Fisher) operated at 300 keV and
+equipped with a BioQuantum energy filter (Gatan) and K3 camera (Gatan). The
+microscope was aligned using a cross-grating grid on the stage. Prior to each
+session, we carefully performed the ``Image/Beam'' calibration in nanoprobe. We
+set the magnification to a pixel size of 1.76 Å and condensed the beam to \textasciitilde{} 900 nm
+diameter, resulting in the beam being completely visible on the camera. To
+establish fringe-free conditions, the ``Fine eucentric'' procedure of SerialEM {[}\protect\hyperlink{ref-19ZFerhph}{28}{]} was
+used to move a square of the cross-grating grid to the eucentric position of the
+microscope. The effective defocus was then set to 2 µm, using the ``autofocus''
+routine of SerialEM. The objective focus of the microscope was changed until no
+fringes were visible. The stage was then moved in Z until images had an apparent
+defocus of 2 µm. The difference in stage Z-position between the eucentric and
+fringe-free conditions was used to move other areas into fringe-free condition.
+
+Low magnification montages were used to find lamellae and lamellae that were
+sufficiently thin and free of contamination were selected for automated data
+collection. Overview images of each lamella were taken at 2250x magnification
+(38 Å pixel size). The corners of the lamella in the overview image were manually
+annotated in SerialEM and translated into beam image-shift values using SerialEM's
+calibration. A hexagonal pattern of beam image-shift positions was calculated
+that covered the area between the four corners in a serpentine way, with a
+\(\sqrt{3}\cdot425\) nm horizontal spacing and \(3/4\cdot 850\) nm vertical spacing. Exposures were
+taken at each position with a 30 e\textsuperscript{-}/Å\(^2\) total dose. After each exposure, the
+defocus was estimated using the ctffind function of SerialEM and the focus for
+the next exposure was corrected by the difference between the estimated focus
+and the desired defocus of 800 nm. Furthermore, after each exposure the
+deviation of the beam from the center of the camera was measured and corrected
+using the ``CenterBeamFromImage'' command of SerialEM.
+
+After data collection, a 20 s exposure at 2250x magnification of the lamella at
+200 μm defocus was taken for visualization purposes. A Python script implementing
+this procedure is available at {[}Link to repo{]}.
+
+\hypertarget{deco-lace-data-processing}{%
+\subsubsection{DeCo-LACE data processing}\label{deco-lace-data-processing}}
+
+An overview of the data analysis pipeline is shown in Fig.
+\ref{fig:deco_lace_workflow}.
+
+\hypertarget{pre-processing}{%
+\paragraph{Pre-processing}\label{pre-processing}}
+
+Motion-correction, dose weighting and other preprocessing as detailed below was performed using \emph{cis}TEM {[}\protect\hyperlink{ref-MUY42yxp}{29}{]}.
+To avoid influence of the beam-edge on motion-correction, only a quarter of the
+movie in the center of the camera was considered for calculation of the
+estimated motion. After movie frames were aligned and summed, a mask for the
+illuminated area was calculated by lowpass filtering the image with a 100 Å
+resolution cutoff, thresholding the image at 10\% of the maximal value and then lowpass
+filtering the mask again with a 100 Å resolution cutoff to smooth the mask edges. This mask was
+then used to select dark areas in the image and fill the pixels with
+Gaussian noise, with the same mean and standard deviation as the illuminated
+area. A custom version of the unblur program {[}\protect\hyperlink{ref-1G4Y94qCy}{30}{]}
+implementing this procedure is available at {[}link to decolace branch{]}. During motion correction images were resampled to a pixel size of 1.5 Å. The
+contrast-transfer function (CTF) was estimated using ctffind
+{[}\protect\hyperlink{ref-n43f3Sqs}{31}{]}, searching between 0.2 and 2 μm defocus.
+
+\hypertarget{dtm}{%
+\paragraph{2DTM}\label{dtm}}
+
+The search template was generated from the atomic model of the mouse LSU
+(PDB 6SWA, exluding the Epb1 subunit) using the cryo-EM simulator implemented in \emph{cis}TEM
+{[}\protect\hyperlink{ref-q2PSamkS}{32}{]}. The
+match\_template program {[}\protect\hyperlink{ref-10bXZuF3G}{9}{]} was used to search for this
+template in the movie-aligned, exposure-filtered and masked images, using a 1.5°
+angular step in out-of-plane angles and a 1.0° angular step in-plane. 11 defocus
+planes in 20 nm steps centered around the ctffind-determined defocus were searched. Targets
+were defined as detected when their matches with the template produced peaks
+with a singal-to-noise ratio (SNR) above a threshold of 7.75, which was chosen
+based on the one-false-positive-per-tile criterion {[}\protect\hyperlink{ref-Ynb3IP6I}{7}{]}.
+
+\hypertarget{montage-assembly}{%
+\paragraph{Montage assembly}\label{montage-assembly}}
+
+The coordinates of each tile \(i\),
+\(\mathbf{c}_{i}\) {[}2D Vector in pixels{]} were initialized using beam image-shift of the tile, \(\mathbf{b}_i\) {[}2D Vector in μm{]},
+and the ISToCamera matrix \(\mathbf{IC}\), as calibrated by SerialEM:
+
+\[\mathbf{c}_{i} = \mathbf{IC} \cdot \mathbf{b}_i\]
+
+A list of tile pairs \(i,j\) that overlap were assembled by selecting images where
+\(|\mathbf{c}_i-\mathbf{c}_j| < D_{Beam}\).
+In order to calculate the precise offset between tiles \(i\) and \(j\), \(\mathbf{r}_{i,j}\), we calculated the cross-correlation between the two tiles, masked to the overlapping illuminated area using the scikit-image
+package {[}\protect\hyperlink{ref-stvWEJeu}{33}{]} was used to calculate refined offsets .
+The coordinates \(\mathbf{c}_{i}\) were then refined by a least-square minimization against \(\mathbf{r}_{i,j}\):
+
+\[ \displaystyle{\min_{\mathbf{c}} \sum_{pairs}{(\mathbf{r}_{i,j} - (\mathbf{c}_i-\mathbf{c}_j))^2}}\]
+
+using the scipy package {[}\protect\hyperlink{ref-8Miti2Gz}{34}{]}. The masked cross-correlation and the least-square minimization was repeated once more to arrive at the final tile alignment.
+
+The x,y coordinates of target \(n\) detected by 2DTM in the tile \(i\),
+\(\textbf{m}^\textrm{T}_{n,i}\), was transformed into the montage frame by adding
+the coordinate of the tile.
+
+\[ \textbf{m}^\textrm{M}_n = \textbf{m}^\textrm{T}_{n,i} + \textbf{c}_i\]
+
+The z coordinate of each target was calculated as the sum of the defocus offset
+for the target, the estimated defocus of the tile, and the nominal defocus of
+the microscope when the tile was acquired.
+
+Images were rendered using UCSF ChimeraX {[}\protect\hyperlink{ref-cYCuuZxG}{35}{]} using a custom extension to render 2DTM results available at {[}https://github.com/jojoelfe/tempest{]}.
+The Python scripts used for data processing are available
+under {[}https://github.com/jojoelfe/deco\_lace\_template\_matching\_manuscript{]}.
+
+\hypertarget{acknowledgments}{%
+\subsection{Acknowledgments}\label{acknowledgments}}
+
+The authors would like to thank Bronwyn Lucas, Carsten Sachse, and Chen Xue for helpful suggestions and careful reading of the manuscript.
+Data was collected at the UMass Chan medical School CryoEM core with help by Kankang song, Christna, and Chen Xue.
+
+\hypertarget{data-availability}{%
+\subsection{Data availability}\label{data-availability}}
+
+Cryo-EM movies, motion-corrected images and template matching results have been deposited in EMPIAR under accession code {[}CODE{]}.
+The custom cisTEM version is available here {[}{]} until features have been integrated into a cisTEM release.
+The ChimeraX extension for rendering is avaibale here {[}{]}.
+This manuscript was prepared using the manubot package {[}@ cite{]} .
+Custom python scripts and all files nescessary for manuscript generation are available here {[}{]}.
 
@@
 \begin{figure}
-\hypertarget{fig:matching_stat}{%
-\centering
-\includegraphics{figures/matching_stat.png}
-\caption{Statistics of 2DTM on lamella imaged using DeCo-LACE (A) Number of detected targets in
-each lamella (B) Distribution of targets per tile in each lamella. Only tiles
-with two or more detected targets were included (C) Distribution of SNRs in each lamella
-(D) For each lamella an average of all tiles is shown. Overlaid is a scatterplot
-of all detected targets in these tiles according to their in-tile coordinates.
-Scatterplot is colored according to the 2DTM SNR. There are no detected targets in the top
-circle-circle intersection due to radiation damage from previous exposures.
-(E) 2D histogram of number of detected targets as a function of beam-image shift (F) Mean 2DTM SNR as a function of beam-image shift}\label{fig:matching_stat}
-}
-\end{figure}
-
-\begin{figure}
 \hypertarget{fig:matching_euc}{%
@@
 
+\begin{figure}
+\hypertarget{fig:matching_stat}{%
+\centering
+\includegraphics{figures/matching_stat.png}
+\caption{Statistics of 2DTM on lamella imaged using DeCo-LACE (A) Number of detected targets in
+each lamella (B) Distribution of targets per tile in each lamella. Only tiles
+with two or more detected targets were included (C) Distribution of SNRs in each lamella
+(D) For each lamella an average of all tiles is shown. Overlaid is a scatterplot
+of all detected targets in these tiles according to their in-tile coordinates.
+Scatterplot is colored according to the 2DTM SNR. There are no detected targets in the top
+circle-circle intersection due to radiation damage from previous exposures.
+(E) 2D histogram of number of detected targets as a function of beam-image shift (F) Mean 2DTM SNR as a function of beam-image shift}\label{fig:matching_stat}
+}
+\end{figure}
+
+\begin{figure}
+\hypertarget{fig:deco_lace_workflow}{%
+\centering
+\includegraphics{figures/deco_lace_workflow.png}
+\caption{Workflow of DeCo-Lace processing}\label{fig:deco_lace_workflow}
+}
+\end{figure}
+
 \hypertarget{references}{%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-sbkam02a}{}}%
+\CSLLeftMargin{13. }%
+\CSLRightInline{\textbf{Protein Synthesis in the Developing Neocortex at Near-Atomic Resolution Reveals Ebp1-Mediated Neuronal Proteostasis at the 60S Tunnel Exit}
+\CSLBlock{Matthew L Kraushar, Ferdinand Krupp, Dermot Harnett, Paul Turko, Mateusz C Ambrozkiewicz, Thiemo Sprink, Koshi Imami, Manuel Günnigmann, Ulrike Zinnall, Carlos H Vieira-Vieira, \ldots{} Christian MT Spahn} \emph{Molecular Cell} (2021-01) \url{https://doi.org/gh7d72}
+\CSLBlock{DOI: \href{https://doi.org/10.1016/j.molcel.2020.11.037}{10.1016/j.molcel.2020.11.037} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/33357414}{33357414} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC8163098}{PMC8163098}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-APSL9LmU}{}}%
+\CSLLeftMargin{14. }%
+\CSLRightInline{\textbf{High-quality, high-throughput cryo-electron microscopy data collection via beam tilt and astigmatism-free beam-image shift}
+\CSLBlock{Chunling Wu, Xiaojun Huang, Jing Cheng, Dongjie Zhu, Xinzheng Zhang} \emph{Journal of Structural Biology} (2019-12) \url{https://doi.org/gp2nq9}
+\CSLBlock{DOI: \href{https://doi.org/10.1016/j.jsb.2019.09.013}{10.1016/j.jsb.2019.09.013} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/31562921}{31562921}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-xE2EhAcH}{}}%
+\CSLLeftMargin{15. }%
+\CSLRightInline{\textbf{THE DEVELOPMENT OF NEUTROPHILIC POLYMORPHONUCLEAR LEUKOCYTES IN HUMAN BONE MARROW}
+\CSLBlock{Dorothy Ford Bainton, Joan L Ullyot, Marilyn G Farquhar} \emph{Journal of Experimental Medicine} (1971-10-01) \url{https://doi.org/chkbcm}
+\CSLBlock{DOI: \href{https://doi.org/10.1084/jem.134.4.907}{10.1084/jem.134.4.907} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/4106490}{4106490} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2138991}{PMC2138991}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-17IP4Lhz1}{}}%
+\CSLLeftMargin{16. }%
+\CSLRightInline{\textbf{Routine determination of ice thickness for cryo-EM grids}
+\CSLBlock{William J Rice, Anchi Cheng, Alex J Noble, Edward T Eng, Laura Y Kim, Bridget Carragher, Clinton S Potter} \emph{Journal of Structural Biology} (2018-10) \url{https://doi.org/gfbpj2}
+\CSLBlock{DOI: \href{https://doi.org/10.1016/j.jsb.2018.06.007}{10.1016/j.jsb.2018.06.007} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/29981485}{29981485} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6119488}{PMC6119488}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hr3dyUeI}{}}%
+\CSLLeftMargin{17. }%
+\CSLRightInline{\textbf{Optimized cryo-focused ion beam sample preparation aimed at in situ structural studies of membrane proteins}
+\CSLBlock{Miroslava Schaffer, Julia Mahamid, Benjamin D Engel, Tim Laugks, Wolfgang Baumeister, Jürgen M Plitzko} \emph{Journal of Structural Biology} (2017-02) \url{https://doi.org/f9qfr6}
+\CSLBlock{DOI: \href{https://doi.org/10.1016/j.jsb.2016.07.010}{10.1016/j.jsb.2016.07.010} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/27444390}{27444390}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-cie13Q8F}{}}%
+\CSLLeftMargin{18. }%
+\CSLRightInline{\textbf{Circularization of mRNA by eukaryotic translation initiation factors.}
+\CSLBlock{SE Wells, PE Hillner, RD Vale, AB Sachs} \emph{Molecular cell} (1998-07) \url{https://www.ncbi.nlm.nih.gov/pubmed/9702200}
+\CSLBlock{DOI: \href{https://doi.org/10.1016/s1097-2765(00)80122-7}{10.1016/s1097-2765(00)80122-7} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/9702200}{9702200}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-1GPPSX111}{}}%
+\CSLLeftMargin{19. }%
+\CSLRightInline{\textbf{Montage electron tomography of vitrified specimens}
+\CSLBlock{Ariana Peck, Stephen D Carter, Huanghao Mai, Songye Chen, Alister Burt, Grant J Jensen} \emph{Journal of Structural Biology} (2022-06) \url{https://doi.org/gp4qrs}
+\CSLBlock{DOI: \href{https://doi.org/10.1016/j.jsb.2022.107860}{10.1016/j.jsb.2022.107860} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/35487464}{35487464}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ujizcpVn}{}}%
+\CSLLeftMargin{20. }%
+\CSLRightInline{\textbf{Correlative cryogenic montage electron tomography for comprehensive in-situ whole-cell structural studies}
+\CSLBlock{Jie E Yang, Matthew R Larson, Bryan S Sibert, Joseph Y Kim, Daniel Parrell, Juan C Sanchez, Victoria Pappas, Anil Kumar, Kai Cai, Keith Thompson, Elizabeth R Wright} \emph{Cold Spring Harbor Laboratory} (2022-01-02) \url{https://doi.org/gp4qrv}
+\CSLBlock{DOI: \href{https://doi.org/10.1101/2021.12.31.474669}{10.1101/2021.12.31.474669}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-1Gwx5ScUa}{}}%
+\CSLLeftMargin{21. }%
+\CSLRightInline{\textbf{Beam image-shift accelerated data acquisition for near-atomic resolution single-particle cryo-electron tomography}
+\CSLBlock{Jonathan Bouvette, Hsuan-Fu Liu, Xiaochen Du, Ye Zhou, Andrew P Sikkema, Juliana da Fonseca Rezende e Mello, Bradley P Klemm, Rick Huang, Roel M Schaaper, Mario J Borgnia, Alberto Bartesaghi} \emph{Nature Communications} (2021-03-30) \url{https://doi.org/gjphkb}
+\CSLBlock{DOI: \href{https://doi.org/10.1038/s41467-021-22251-8}{10.1038/s41467-021-22251-8} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/33785757}{33785757} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC8009872}{PMC8009872}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-xvouNMBy}{}}%
+\CSLLeftMargin{22. }%
+\CSLRightInline{\textbf{Parallel cryo electron tomography on \textless i\textgreater in situ\textless/i\textgreater{} lamellae}
+\CSLBlock{Fabian Eisenstein, Haruaki Yanagisawa, Hiroka Kashihara, Masahide Kikkawa, Sachiko Tsukita, Radostin Danev} \emph{Cold Spring Harbor Laboratory} (2022-04-08) \url{https://doi.org/gp4qrw}
+\CSLBlock{DOI: \href{https://doi.org/10.1101/2022.04.07.487557}{10.1101/2022.04.07.487557}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-17H2LWiIu}{}}%
+\CSLLeftMargin{23. }%
+\CSLRightInline{\textbf{Waffle Method: A general and flexible approach for improving throughput in FIB-milling}
+\CSLBlock{Kotaro Kelley, Ashleigh M Raczkowski, Oleg Klykov, Pattana Jaroenlak, Daija Bobe, Mykhailo Kopylov, Edward T Eng, Gira Bhabha, Clinton S Potter, Bridget Carragher, Alex J Noble} \emph{Nature Communications} (2022-04-06) \url{https://doi.org/gp4qrt}
+\CSLBlock{DOI: \href{https://doi.org/10.1038/s41467-022-29501-3}{10.1038/s41467-022-29501-3} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/35387991}{35387991} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC8987090}{PMC8987090}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-T1Qr0xyP}{}}%
+\CSLLeftMargin{24. }%
+\CSLRightInline{\textbf{\textless i\textgreater In situ\textless/i\textgreater{} single particle classification reveals distinct 60S maturation intermediates in cells}
+\CSLBlock{Bronwyn A Lucas, Kexin Zhang, Sarah Loerch, Nikolaus Grigorieff} \emph{Cold Spring Harbor Laboratory} (2022-04-10) \url{https://doi.org/gp4qrx}
+\CSLBlock{DOI: \href{https://doi.org/10.1101/2022.04.10.487797}{10.1101/2022.04.10.487797}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-44fG6kcy}{}}%
+\CSLLeftMargin{25. }%
+\CSLRightInline{\textbf{High-resolution cryo-EM using beam-image shift at 200 keV}
+\CSLBlock{Jennifer N Cash, Sarah Kearns, Yilai Li, Michael A Cianfrocco} \emph{IUCrJ} (2020-10-29) \url{https://doi.org/gjwcfq}
+\CSLBlock{DOI: \href{https://doi.org/10.1107/s2052252520013482}{10.1107/s2052252520013482} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/33209328}{33209328} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7642776}{PMC7642776}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kncnYGLD}{}}%
+\CSLLeftMargin{26. }%
+\CSLRightInline{\textbf{Shedding light on the cell biology of extracellular vesicles}
+\CSLBlock{Guillaume van Niel, Gisela D'Angelo, Graça Raposo} \emph{Nature Reviews Molecular Cell Biology} (2018-01-17) \url{https://doi.org/gct4df}
+\CSLBlock{DOI: \href{https://doi.org/10.1038/nrm.2017.125}{10.1038/nrm.2017.125} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/29339798}{29339798}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-agVdpX76}{}}%
+\CSLLeftMargin{27. }%
+\CSLRightInline{\textbf{Exosome-mediated transfer of mRNAs and microRNAs is a novel mechanism of genetic exchange between cells}
+\CSLBlock{Hadi Valadi, Karin Ekström, Apostolos Bossios, Margareta Sjöstrand, James J Lee, Jan O Lötvall} \emph{Nature Cell Biology} (2007-05-07) \url{https://doi.org/d5df4s}
+\CSLBlock{DOI: \href{https://doi.org/10.1038/ncb1596}{10.1038/ncb1596} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/17486113}{17486113}}}
+
 \leavevmode\vadjust pre{\hypertarget{ref-19ZFerhph}{}}%
-\CSLLeftMargin{13. }%
+\CSLLeftMargin{28. }%
 \CSLRightInline{\textbf{Automated electron microscope tomography using robust prediction of specimen movements}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-MUY42yxp}{}}%
-\CSLLeftMargin{14. }%
+\CSLLeftMargin{29. }%
 \CSLRightInline{\textbf{cisTEM, user-friendly software for single-particle image processing}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1G4Y94qCy}{}}%
-\CSLLeftMargin{15. }%
+\CSLLeftMargin{30. }%
 \CSLRightInline{\textbf{Measuring the optimal exposure for single particle cryo-EM using a 2.6 Å reconstruction of rotavirus VP6}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-n43f3Sqs}{}}%
-\CSLLeftMargin{16. }%
+\CSLLeftMargin{31. }%
 \CSLRightInline{\textbf{CTFFIND4: Fast and accurate defocus estimation from electron micrographs}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-q2PSamkS}{}}%
-\CSLLeftMargin{17. }%
+\CSLLeftMargin{32. }%
 \CSLRightInline{\textbf{Cryo-TEM simulations of amorphous radiation-sensitive samples using multislice wave propagation}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-stvWEJeu}{}}%
-\CSLLeftMargin{18. }%
+\CSLLeftMargin{33. }%
 \CSLRightInline{\textbf{scikit-image: image processing in Python}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-8Miti2Gz}{}}%
-\CSLLeftMargin{19. }%
+\CSLLeftMargin{34. }%
 \CSLRightInline{\textbf{SciPy 1.0: fundamental algorithms for scientific computing in Python}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-cYCuuZxG}{}}%
-\CSLLeftMargin{20. }%
+\CSLLeftMargin{35. }%
 \CSLRightInline{\textbf{\textless scp\textgreater UCSF ChimeraX\textless/scp\textgreater{}
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-sbkam02a}{}}%
-\CSLLeftMargin{21. }%
-\CSLRightInline{\textbf{Protein Synthesis in the Developing Neocortex at Near-Atomic Resolution Reveals Ebp1-Mediated Neuronal Proteostasis at the 60S Tunnel Exit}
-\CSLBlock{Matthew L Kraushar, Ferdinand Krupp, Dermot Harnett, Paul Turko, Mateusz C Ambrozkiewicz, Thiemo Sprink, Koshi Imami, Manuel Günnigmann, Ulrike Zinnall, Carlos H Vieira-Vieira, \ldots{} Christian MT Spahn} \emph{Molecular Cell} (2021-01) \url{https://doi.org/gh7d72}
-\CSLBlock{DOI: \href{https://doi.org/10.1016/j.molcel.2020.11.037}{10.1016/j.molcel.2020.11.037} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/33357414}{33357414} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC8163098}{PMC8163098}}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-APSL9LmU}{}}%
-\CSLLeftMargin{22. }%
-\CSLRightInline{\textbf{High-quality, high-throughput cryo-electron microscopy data collection via beam tilt and astigmatism-free beam-image shift}
-\CSLBlock{Chunling Wu, Xiaojun Huang, Jing Cheng, Dongjie Zhu, Xinzheng Zhang} \emph{Journal of Structural Biology} (2019-12) \url{https://doi.org/gp2nq9}
-\CSLBlock{DOI: \href{https://doi.org/10.1016/j.jsb.2019.09.013}{10.1016/j.jsb.2019.09.013} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/31562921}{31562921}}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-xE2EhAcH}{}}%
-\CSLLeftMargin{23. }%
-\CSLRightInline{\textbf{THE DEVELOPMENT OF NEUTROPHILIC POLYMORPHONUCLEAR LEUKOCYTES IN HUMAN BONE MARROW}
-\CSLBlock{Dorothy Ford Bainton, Joan L Ullyot, Marilyn G Farquhar} \emph{Journal of Experimental Medicine} (1971-10-01) \url{https://doi.org/chkbcm}
-\CSLBlock{DOI: \href{https://doi.org/10.1084/jem.134.4.907}{10.1084/jem.134.4.907} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/4106490}{4106490} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2138991}{PMC2138991}}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-17IP4Lhz1}{}}%
-\CSLLeftMargin{24. }%
-\CSLRightInline{\textbf{Routine determination of ice thickness for cryo-EM grids}
-\CSLBlock{William J Rice, Anchi Cheng, Alex J Noble, Edward T Eng, Laura Y Kim, Bridget Carragher, Clinton S Potter} \emph{Journal of Structural Biology} (2018-10) \url{https://doi.org/gfbpj2}
-\CSLBlock{DOI: \href{https://doi.org/10.1016/j.jsb.2018.06.007}{10.1016/j.jsb.2018.06.007} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/29981485}{29981485} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6119488}{PMC6119488}}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hr3dyUeI}{}}%
-\CSLLeftMargin{25. }%
-\CSLRightInline{\textbf{Optimized cryo-focused ion beam sample preparation aimed at in situ structural studies of membrane proteins}
-\CSLBlock{Miroslava Schaffer, Julia Mahamid, Benjamin D Engel, Tim Laugks, Wolfgang Baumeister, Jürgen M Plitzko} \emph{Journal of Structural Biology} (2017-02) \url{https://doi.org/f9qfr6}
-\CSLBlock{DOI: \href{https://doi.org/10.1016/j.jsb.2016.07.010}{10.1016/j.jsb.2016.07.010} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/27444390}{27444390}}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cie13Q8F}{}}%
-\CSLLeftMargin{26. }%
-\CSLRightInline{\textbf{Circularization of mRNA by eukaryotic translation initiation factors.}
-\CSLBlock{SE Wells, PE Hillner, RD Vale, AB Sachs} \emph{Molecular cell} (1998-07) \url{https://www.ncbi.nlm.nih.gov/pubmed/9702200}
-\CSLBlock{DOI: \href{https://doi.org/10.1016/s1097-2765(00)80122-7}{10.1016/s1097-2765(00)80122-7} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/9702200}{9702200}}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-1GPPSX111}{}}%
-\CSLLeftMargin{27. }%
-\CSLRightInline{\textbf{Montage electron tomography of vitrified specimens}
-\CSLBlock{Ariana Peck, Stephen D Carter, Huanghao Mai, Songye Chen, Alister Burt, Grant J Jensen} \emph{Journal of Structural Biology} (2022-06) \url{https://doi.org/gp4qrs}
-\CSLBlock{DOI: \href{https://doi.org/10.1016/j.jsb.2022.107860}{10.1016/j.jsb.2022.107860} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/35487464}{35487464}}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ujizcpVn}{}}%
-\CSLLeftMargin{28. }%
-\CSLRightInline{\textbf{Correlative cryogenic montage electron tomography for comprehensive in-situ whole-cell structural studies}
-\CSLBlock{Jie E Yang, Matthew R Larson, Bryan S Sibert, Joseph Y Kim, Daniel Parrell, Juan C Sanchez, Victoria Pappas, Anil Kumar, Kai Cai, Keith Thompson, Elizabeth R Wright} \emph{Cold Spring Harbor Laboratory} (2022-01-02) \url{https://doi.org/gp4qrv}
-\CSLBlock{DOI: \href{https://doi.org/10.1101/2021.12.31.474669}{10.1101/2021.12.31.474669}}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-1Gwx5ScUa}{}}%
-\CSLLeftMargin{29. }%
-\CSLRightInline{\textbf{Beam image-shift accelerated data acquisition for near-atomic resolution single-particle cryo-electron tomography}
-\CSLBlock{Jonathan Bouvette, Hsuan-Fu Liu, Xiaochen Du, Ye Zhou, Andrew P Sikkema, Juliana da Fonseca Rezende e Mello, Bradley P Klemm, Rick Huang, Roel M Schaaper, Mario J Borgnia, Alberto Bartesaghi} \emph{Nature Communications} (2021-03-30) \url{https://doi.org/gjphkb}
-\CSLBlock{DOI: \href{https://doi.org/10.1038/s41467-021-22251-8}{10.1038/s41467-021-22251-8} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/33785757}{33785757} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC8009872}{PMC8009872}}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-xvouNMBy}{}}%
-\CSLLeftMargin{30. }%
-\CSLRightInline{\textbf{Parallel cryo electron tomography on \textless i\textgreater in situ\textless/i\textgreater{} lamellae}
-\CSLBlock{Fabian Eisenstein, Haruaki Yanagisawa, Hiroka Kashihara, Masahide Kikkawa, Sachiko Tsukita, Radostin Danev} \emph{Cold Spring Harbor Laboratory} (2022-04-08) \url{https://doi.org/gp4qrw}
-\CSLBlock{DOI: \href{https://doi.org/10.1101/2022.04.07.487557}{10.1101/2022.04.07.487557}}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-17H2LWiIu}{}}%
-\CSLLeftMargin{31. }%
-\CSLRightInline{\textbf{Waffle Method: A general and flexible approach for improving throughput in FIB-milling}
-\CSLBlock{Kotaro Kelley, Ashleigh M Raczkowski, Oleg Klykov, Pattana Jaroenlak, Daija Bobe, Mykhailo Kopylov, Edward T Eng, Gira Bhabha, Clinton S Potter, Bridget Carragher, Alex J Noble} \emph{Nature Communications} (2022-04-06) \url{https://doi.org/gp4qrt}
-\CSLBlock{DOI: \href{https://doi.org/10.1038/s41467-022-29501-3}{10.1038/s41467-022-29501-3} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/35387991}{35387991} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC8987090}{PMC8987090}}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-T1Qr0xyP}{}}%
-\CSLLeftMargin{32. }%
-\CSLRightInline{\textbf{\textless i\textgreater In situ\textless/i\textgreater{} single particle classification reveals distinct 60S maturation intermediates in cells}
-\CSLBlock{Bronwyn A Lucas, Kexin Zhang, Sarah Loerch, Nikolaus Grigorieff} \emph{Cold Spring Harbor Laboratory} (2022-04-10) \url{https://doi.org/gp4qrx}
-\CSLBlock{DOI: \href{https://doi.org/10.1101/2022.04.10.487797}{10.1101/2022.04.10.487797}}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-44fG6kcy}{}}%
-\CSLLeftMargin{33. }%
-\CSLRightInline{\textbf{High-resolution cryo-EM using beam-image shift at 200 keV}
-\CSLBlock{Jennifer N Cash, Sarah Kearns, Yilai Li, Michael A Cianfrocco} \emph{IUCrJ} (2020-10-29) \url{https://doi.org/gjwcfq}
-\CSLBlock{DOI: \href{https://doi.org/10.1107/s2052252520013482}{10.1107/s2052252520013482} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/33209328}{33209328} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7642776}{PMC7642776}}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kncnYGLD}{}}%
-\CSLLeftMargin{34. }%
-\CSLRightInline{\textbf{Shedding light on the cell biology of extracellular vesicles}
-\CSLBlock{Guillaume van Niel, Gisela D'Angelo, Graça Raposo} \emph{Nature Reviews Molecular Cell Biology} (2018-01-17) \url{https://doi.org/gct4df}
-\CSLBlock{DOI: \href{https://doi.org/10.1038/nrm.2017.125}{10.1038/nrm.2017.125} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/29339798}{29339798}}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-agVdpX76}{}}%
-\CSLLeftMargin{35. }%
-\CSLRightInline{\textbf{Exosome-mediated transfer of mRNAs and microRNAs is a novel mechanism of genetic exchange between cells}
-\CSLBlock{Hadi Valadi, Karin Ekström, Apostolos Bossios, Margareta Sjöstrand, James J Lee, Jan O Lötvall} \emph{Nature Cell Biology} (2007-05-07) \url{https://doi.org/d5df4s}
-\CSLBlock{DOI: \href{https://doi.org/10.1038/ncb1596}{10.1038/ncb1596} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/17486113}{17486113}}}
-
 \end{CSLReferences}

### 2022-06-06 manuscript.tex
Incorporating more suggestions [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a321def4b341f6e6f2c8d66936f53cf5e9398eae.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a321def4b341f6e6f2c8d66936f53cf5e9398eae/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2448512939

@@
 This manuscript
-(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/26bf17f811e80363e8f38656b89bbae2c14147f8/}{permalink})
+(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/a321def4b341f6e6f2c8d66936f53cf5e9398eae/}{permalink})
 was automatically generated
-from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/26bf17f811e80363e8f38656b89bbae2c14147f8}{jojoelfe/deco\_lace\_template\_matching\_manuscript@26bf17f}
-on May 27, 2022.
+from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/a321def4b341f6e6f2c8d66936f53cf5e9398eae}{jojoelfe/deco\_lace\_template\_matching\_manuscript@a321def}
+on June 6, 2022.
 
@@
   \href{https://github.com/jojoelfe}{jojoelfe}
-  RNA Therapeutic Institute, UMass Chan Medical School; HHMI
+  RNA Therapeutics Institute, University of Massachusetts Chan Medical School, Worcester, MA, USA; Howard Hughes Medical Institute, Ashburn, VA, USA
 \item
   \textbf{Giulia Schiroli}
-  None
+  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.pdf}
+  \href{https://orcid.org/0000-0002-9812-8728}{0000-0002-9812-8728}
+  Center for Regenerative Medicine, Massachusetts General Hospital, Boston, MA 02114, USA
 \item
   \textbf{David Scadden}
-  None
+  Center for Regenerative Medicine, Massachusetts General Hospital, Boston, MA 02114, USA; Harvard Stem Cell Institute, Cambridge, MA 02138, USA; Department of Stem Cell and Regenerative Biology, Harvard University, Cambridge, MA 02138, USA
 \item
@@
   \href{https://github.com/nikogrigorieff}{nikogrigorieff}
-  RNA Therapeutic Institute, UMass Chan Medical School; HHMI
+  RNA Therapeutics Institute, University of Massachusetts Chan Medical School, Worcester, MA, USA; Howard Hughes Medical Institute, Ashburn, VA, USA
 \end{itemize}
@@
 
-Localization of biomolecules inside a cell is an important goal of biological
-imaging. Fluorescence microscopy can localize biomolecules inside whole cells
+A major goal of biological imaging is localization of biomolecules inside a cell. Fluorescence microscopy can localize biomolecules inside whole cells
 and tissues, but its ability to count biomolecules and accuracy of the spatial
@@
 scheme called ``Defocus-Corrected Large-Area cryo-EM'' (DeCo-LACE) to collect
-high-resolution cryo-EM data over entire sections (100 -- 200 nm thick lamellae)
+high-resolution images of entire sections (100 -- 200 nm thick lamellae)
 of neutrophil-like mouse cells, representing 1-2\% of the total cellular
-volume. We use 2D template matching (2DTM) to determine localization and orientation
-of the large ribosomal subunit in these sections. These data provide ``maps'' of translational activity across
-sections of mammalian cells. This new high-throughput cryo-EM
-data collection approach together with 2DTM will advance visual
-proteomics and complement other single-cell ``omics'' techniques, such as
-flow-cytometry and single-cell sequencing.
+volume.
+We use 2D template matching (2DTM) to determine localization and orientation of the large ribosomal subunit in these sections.
+These data provide ``maps'' of ribosomes across entire sections of mammalian cells.
+This high-throughput cryo-EM data collection approach together with 2DTM will advance visual proteomics and provide biological insight that cannot be obtained by other methods.
 
@@
 thousands of molecules, while label-dependent techniques offer highly specific
-information for a few molecules. Especially spatial information can
-often only be achieved using label-dependent techniques, such as
+information for a few molecules. in particular, spatial information is primarily achieved using label-dependent techniques, such as
 fluorescence microscopy {[}\protect\hyperlink{ref-VBmW7Aot}{2}{]}.
@@
 
-Here we apply 2DTM of the ribosome large subunit (LSU) to cryo-FIB milled
-neutrophil-like murine cells {[}\protect\hyperlink{ref-1B9Vt9eYu}{10}{]}. We chose these
+Here we apply 2DTM of the ribosome large subunit (LSU) to conditionally immortalized \emph{mus musculus} (mouse) cell line that gives rise to functional mature neutrophils {[}\protect\hyperlink{ref-1B9Vt9eYu}{10}{]} after thinning using cryo-FIB milling.
+We chose these
 cells because genetic defects in the ribosome machinery often leads to
@@
 
-To test whether we could detect individual ribosomes in mammalian cells we
-prepared cryo-lamellae of mouse neutrophil-like cells. An overview image
+FIB-milled \emph{Saccharomyces cerevisiae} (yeast) cells are sufficiently well preserved to permit localization of 60S ribosomal subunits with 2DTM {[}\protect\hyperlink{ref-T1Qr0xyP}{13}{]}.
+Due to the larger size of mammalian cells compared to yeast cells, it was unclear whether plunge freezing would be adequate to produce vitreous ice across the whole volume of the cell.
+To test this we prepared cryo-lamellae of mouse neutrophil cells.
+A low magnification image
 of a representative lamella clearly shows cellular features consistent with a
-neutrophil-like phenotype, mainly a segmented nucleus and a plethora of
+neutrophile-like phenotype, mainly a segmented nucleus and a plethora of
 membrane-organelles, corresponding to the granules and secretory vesicles of
@@
 {[}\ref{fig:initmatching}{]}C,D), indicating successful vitrification throughout the
-lamella. Successful vitrification is facilitated by the small size (\textasciitilde8 μm diameter) of these cells.
-
-We used an atomic model of the 60S mouse ribosomal subunit (6SWA) for 2DTM {[}\protect\hyperlink{ref-sbkam02a}{13}{]}. In a
+lamella.
+
+We used an atomic model of the 60S mouse ribosomal subunit (6SWA) for 2DTM {[}\protect\hyperlink{ref-sbkam02a}{14}{]}. In a
 subset of images, the distribution of cross-correlation scores significantly
@@
 number of targets, only \textasciitilde{} 50 in some exposures (Fig. {[}\ref{fig:initmatching}{]}E) and
-up to 500 in others (Fig. {[}\ref{fig:initmatching}{]}C). This is a ten-fold
-difference in local ribosome concentration, highlighting the importance of
-imaging larger areas of a lamella to gain a complete picture of target
-distributions. We therefore set out to collect cryo-EM data for 2DTM from
-mammalian cell lamellae in a high-throughput unbiased fashion.
+up to 500 in others (Fig.
+{[}\ref{fig:initmatching}{]}C).
+However, it is unclear whether this ten-fold difference in local ribosome concentration is due to technical variation, such as sample thickness, or biological variation.
+To differentiate between the two we reasoned it was important to not manually choose imaging regions and to collect larger amounts of data.
+We therefore set out to collect cryo-EM data for 2DTM from mammalian cell lamellae in a high-throughput unbiased fashion.
 
@@
 
-In order to obtain high-resolution data from complete lamellae, we used a new
+In order to obtain high-resolution data from complete lamellae, we developed a new
 approach for data collection. This approach uses three key strategies: (1) every
@@
 the beam (Fig. {[}\ref{fig:approach}{]}D). While these ripples are low-resolution
-features that likely do not interfere with 2DTM {[}cite{]}, we also tested data
+features that likely do not interfere with 2DTM {[}\protect\hyperlink{ref-Ynb3IP6I}{7}{]}, we also tested data
 collection under conditions where the C2 aperture is in focus (``fringe-free'',
-Fig. {[}\ref{fig:approach}{]}E).
+Fig. {[}\ref{fig:approach}{]}E) {[}\protect\hyperlink{ref-wsFP5c54}{15}{]}.
 
@@
 {[}\ref{fig:lamella_spatial_info}{]}B). While approaches exist to correct for this
-during the data collection {[}\protect\hyperlink{ref-APSL9LmU}{14}{]}, we opted to not use these approaches in our
+during the data collection {[}\protect\hyperlink{ref-APSL9LmU}{16}{]}, we opted to not use these approaches in our
 initial experiments. We reasoned that because 2DTM depends on high-resolution
@@
 density. We found that a substantial number of granules, which are characterized by higher
-density inside the the surrounding cytosol {[}\protect\hyperlink{ref-xE2EhAcH}{15}{]}, seemed to contain a membrane-enclosed inclusion with density similar to
+density inside the the surrounding cytosol {[}\protect\hyperlink{ref-xE2EhAcH}{17}{]}, seemed to contain a membrane-enclosed inclusion with density similar to
 the surrounding cytosol (Fig. {[}\ref{fig:lamella_images}{]}C) and could therefore be formed
-by an autophagy-like pathway. These granules were
+by inward budding of the granule membrane. These granules were
 150-300 nm in diameter and the inclusions were 100-200 nm in diameter. Based on
-these dimensions the granules are either azurophil or specific granules {[}\protect\hyperlink{ref-xE2EhAcH}{15}{]}. To our
+these dimensions the granules are either azurophil or specific granules {[}\protect\hyperlink{ref-xE2EhAcH}{17}{]}. To our
 knowledge, these inclusion have not been described in granulocytes and are
@@
 
-\hypertarget{dtm-of-deco-lace-data-reveals-ribosome-distribution-in-cellular-cross-sections}{%
-\subsubsection{2DTM of DeCo-LACE data reveals ribosome distribution in cellular cross-sections}\label{dtm-of-deco-lace-data-reveals-ribosome-distribution-in-cellular-cross-sections}}
+\hypertarget{dtm-of-deco-lace-data-reveals-large-ribosomal-subunit-distribution-in-cellular-cross-sections}{%
+\subsubsection{2DTM of DeCo-LACE data reveals large ribosomal subunit distribution in cellular cross-sections}\label{dtm-of-deco-lace-data-reveals-large-ribosomal-subunit-distribution-in-cellular-cross-sections}}
 
@@
 tracking of sample motion. Furthermore, in the motion-corrected average we could
-identify significant SNR peaks (Fig. {[}\ref{fig:crop_unblur}{]}B), confirming to
-high sensitivity of 2DTM to the presents of high-resolution signal preserved in
+identify significant SNR peaks (Fig. {[}\ref{fig:crop_unblur}{]}B), confirming the
+high sensitivity of 2DTM to the presence of high-resolution signal preserved in
 the images by the motion correction. To streamline data processing, we
@@
 
-We used the refined tile positions to calculate the positions of the detected
-LSUs in the lamellae (Fig. {[}\ref{fig:matching_euc}{]}A, Fig. {[}\ref{fig:matching_fff}{]}A). Overlaying these positions of the lamellae montages reveal ribosome
-distribution throughout the FIB-milled slices of individual cells. Organelles
+We used the tile positions to calculate the positions of the detected
+LSUs in the lamellae (Fig. {[}\ref{fig:matching_euc}{]}A, Fig. {[}\ref{fig:matching_fff}{]}A). Overlaying these positions of the lamellae montages reveals LSU
+distribution throughout the FIB-milled slices of individual cells. Consistent with prior observations imaging selected views in yeast {[}\protect\hyperlink{ref-T1Qr0xyP}{13}{]}, organelles
 like the nucleus and mitochondria only showed sporadic targets detected with low
@@
 substantially higher intensities at the leading edge (Fig. {[}\ref{fig:lamella_motion_thickness}{]}B), which in energy-filtered
-TEM indicates a thinner sample {[}\protect\hyperlink{ref-17IP4Lhz1}{16}{]}. Even though we prepared the lamellae
-with the ``overtilt'' approach {[}\protect\hyperlink{ref-hr3dyUeI}{17}{]}, this means that ribosome densities across
+TEM indicates a thinner sample {[}\protect\hyperlink{ref-17IP4Lhz1}{18}{]}. Even though we prepared the lamellae
+with the ``overtilt'' approach {[}\protect\hyperlink{ref-hr3dyUeI}{19}{]}, this means that LSU densities across
 the lamellae can be skewed by a change in thickness, and better sample
@@
 
-Close inspection of the ribosome positions in the lamellae revealed several
-interesting features. Ribosomes could be seen associating with membranes, in
+Close inspection of the LSU positions in the lamellae revealed several
+interesting features. LSUs could be seen associating with membranes, in
 patterns reminiscent of the rough endoplasmic reticulum (Fig.
 {[}\ref{fig:matching_euc}{]}C, Fig. {[}\ref{fig:matching_fff}{]}C) or the outer nuclear
-membrane (Fig. {[}\ref{fig:matching_euc}{]}D). We also observed ribosomes forming
+membrane (Fig. {[}\ref{fig:matching_euc}{]}D). We also observed LSUs forming
 ring-like structures (Fig. {[}\ref{fig:matching_euc}{]}E), potentially indicating
-circularized mRNAs {[}\protect\hyperlink{ref-cie13Q8F}{18}{]}. While ribosomes were for the most part excluded
+circularized mRNAs {[}\protect\hyperlink{ref-cie13Q8F}{20}{]}. While ribosomes were for the most part excluded
 from the numerous granules observed in the cytoplasm, in some cases we observed
-clusters of ribosomes in the inclusions of double-membraned granules
+clusters of LSUs in the inclusions of double-membraned granules
 described earlier (Fig. {[}\ref{fig:matching_euc}{]}F, Fig. {[}\ref{fig:matching_fff}{]}D,E). It is, in principle, possible that these targets are situated above or
@@
 using 2D projections. However, in the case of Fig. {[}\ref{fig:matching_fff}{]}E, the
-detected ribosomes span the whole lamella in the z direction (Fig. {[}\ref{fig:matching_fff}{]}F), while positions
-above or below a granule would result in ribosomes situated exlusively at the
-top or bottom of the lamella. This conclusive evidence of ribosomes in
-inclusions is consistent with the earlier hypothesis that the inclusions are of
+detected LSUs span the whole lamella in the z direction (Fig. {[}\ref{fig:matching_fff}{]}F), while positions
+above or below a granule would result in LSUs situated exlusively at the
+top or bottom of the lamella. This is consistent with the earlier hypothesis that the inclusions are of
 cytoplasmic origin.
@@
 
-Within the eight lamellae we found different number of detected targets (Fig.
+Within the eight lamellae we found different numbers of detected targets, ranging from 1089 to 6433 per lamella (Fig.
 {[}\ref{fig:matching_stat}{]}A). Lamella\textsubscript{EUC} 1 had the most detected targets, but also has
@@
 We also wondered whether large image shifts would lead aberration due to
-astigmatism or beam tilt {[}\protect\hyperlink{ref-APSL9LmU}{14}{]}. We reasoned that if
+astigmatism or beam tilt {[}\protect\hyperlink{ref-APSL9LmU}{16}{]}. We reasoned that if
 that was the case the number of detected targets should be highest in the center of the
-lamella where the applied beam image-shift is 0. Instead we observed that in
-both eucentric and fring-free focus conditions more target where detected at the
+lamella where the applied beam image-shift is 0. Instead, we observed that in
+both eucentric and fringe-free focus conditions more targets were detected at the
 ``back'' edge of the lamella (Fig. {[}\ref{fig:matching_stat}{]}E{]}). This may be due to the center of the cell being predominantly
@@
 Fig. {[}\ref{fig:matching_euc}{]}B, Fig. {[}\ref{fig:matching_fff}{]}B). In addition, aberrations would be expected to cause average 2DTM SNRs to be higher when beam-image shift
-values are small. Instead, we found that SNRs where on average the highes at the
+values are small. Instead, we found that SNRs where on average the highest at the
 ``front'' edge of the lamellae, presumably due to the thinner sample. We therefore
@@
 
-As described above, the variability of lamellae, both in terms of experimental
-parameters including area, thickness and mechanical stability, and in terms of
-biology, such as selection of cell type and location of the section within the
-cell, requires collection of orders of magnitude more data than in this study to draw quantitative
-and statistically relevant conclusions about the number and location of
-molecules under different experimental conditions. The samples used were
+All lamellae described above were derived from a clonal cell line under identical condition and thinned with the same parameters.
+This means that the substantial variability of detected targets between the lamellae must be due to
+technical variability, including area, thickness, mechanical stability, and location of the section within the cell.
+We therefore predict that further studies that want to draw quantitative and statistically relevant conclusions about the number and location of
+molecules under different experimental conditions, will require collection of orders of magnitude more data than in this study to gain enough statistical power given this variability.
+The samples used were
 prepared in two 24 h sessions on a FIB/SEM instrument, and imaging was performed
@@
 substantially longer. Specifically, 2DTM of all tiles took approximately one
-week per lamella on 32 A100 GPUs. Computation is therefore a bottleneck in our
+week per lamella on 32 Nvidia A6000 GPUs. Computation is therefore a bottleneck in our
 current workflow, and further optimizations of the algorithm may be necessary
@@
 The requirement to increase throughput in cryo-EM data collection of cellular samples has been recognized in the recent literature.
-Most approaches describeb so far are tailored towards tomography.
+Most approaches described so far are tailored towards tomography.
 Peck et al.
-{[}\protect\hyperlink{ref-1GPPSX111}{19}{]} and Yang et al.
-{[}\protect\hyperlink{ref-ujizcpVn}{20}{]} developed approaches to increase the FOV of tomogram data-collection by using a montaging technique.
+{[}\protect\hyperlink{ref-1GPPSX111}{21}{]} and Yang et al.
+{[}\protect\hyperlink{ref-ujizcpVn}{22}{]} developed approaches to increase the FOV of tomogram data-collection by using a montaging technique.
 Peck et al.~used a similar ``condensed-beam'' approach as described here.
@@
 Bouvette et al.
-{[}\protect\hyperlink{ref-1Gwx5ScUa}{21}{]} and Eisenstein et al.
-{[}\protect\hyperlink{ref-xvouNMBy}{22}{]} are using beam image-shift to collect tilt-series in multiple locations in parallel to increase throughput.
+{[}\protect\hyperlink{ref-1Gwx5ScUa}{23}{]} and Eisenstein et al.
+{[}\protect\hyperlink{ref-xvouNMBy}{24}{]} are using beam image-shift to collect tilt-series in multiple locations in parallel to increase throughput.
 However, none of these approaches provide the full coverage of a cellular cross-section that can be achieved using DeCo-Lace.
 
-Since we observed substantial variation in ribosome density within and between lamellae, visual proteomics studies that use cryo-EM to establish changes in molecular organization within cells will require orders of magnitude more data than used in this study.
+Since we observed substantial variation in LSU density within and between lamellae, visual proteomics studies that use cryo-EM to establish changes in molecular organization within cells will require orders of magnitude more data than used in this study.
 One milestone would be to image enough data to represent one cellular volume, which for a small eukaryotic cells requires imaging approximately 100 lamella.
-While data collection throughput on the TEM is fundamentally limited by the exposure time, this amount of data could be collected within 12 hour by improving the data acquisition scheme to perform all necessary calculation in parallel with actual exposure of the camera.
-Sample preparation using a FIB/SEM is also currently a bottleneck, but preparation of large lamellae with multiple cellular cross-sections using methods like WAFFLE {[}\protect\hyperlink{ref-17H2LWiIu}{23}{]} might allow sufficient throughput.
+While data collection throughput on the TEM is fundamentally limited by the exposure time, this amount of data could be collected within 12 hours by improving the data acquisition scheme to perform all necessary calculations in parallel with actual exposure of the camera.
+Sample preparation using a FIB/SEM is also currently a bottleneck, but preparation of large lamellae with multiple cellular cross-sections using methods like WAFFLE {[}\protect\hyperlink{ref-17H2LWiIu}{25}{]} might allow sufficient throughput.
 As stated in the results, at least for 2DTM computation will remain challenging and approximately 17,000 GPU hours would be required for a 100 lamellae dataset.
@@
 In the 670 tiles containing exclusively nucleus (as manually annotated from the overview image) we detected 247 targets, making the false-positive rate more than twofold lower than expected.
-Since earlier work shows that 2DTM with the LSU can produce matches to nuclear ribosome biogenesis intermediates {[}\protect\hyperlink{ref-T1Qr0xyP}{24}{]}, this could even be an overestimate of the false-positive rate.
+Since earlier work shows that 2DTM with the LSU can produce matches to nuclear ribosome biogenesis intermediates {[}\protect\hyperlink{ref-T1Qr0xyP}{13}{]}, this could even be an overestimate of the false-positive rate.
 This suggests that the detection threshold could be even lower, which is an area of ongoing research.
@@
 We found that even though we used beam image-shift extensively (up to 7 um), we did not see substantially reduced 2DTM SNR values in tiles acquired at high beam image-shift compared to tiles acquired with low or no beam image-shift.
-This is in contrast to reports in single-particle analysis (SPA) {[}\protect\hyperlink{ref-44fG6kcy}{25}{]} where the induced beam tilt substantially reduced the resolution if it was not corrected during processing.
+This is in contrast to reports in single-particle analysis (SPA) {[}\protect\hyperlink{ref-44fG6kcy}{26}{]} where the induced beam tilt substantially reduced the resolution if it was not corrected during processing.
 It is possible that 2DTM is less sensitive to beam-tilt aberrations, since the template is free of any aberration and only the image is distorted, while in SPA the beam tilt will affect both the images and the reconstructed template.
@@
 
-Unexpectedly, we observed granules containing a vesicle of putative cytosolic origin.
+We observed granules containing a vesicle of putative cytosolic origin.
 We speculate that upon degranulation, the process in which granules fuse with the plasma membrane, these vesicles would be released into the extracelullar space.
-The main types of extracellular vesicles of this size are exosomes, up to 100 nm large vesicles derived from fusion of multivesicular bodies with the plasma membrane, and microvesicles, which are derived from direct budding of the plasma membrane {[}\protect\hyperlink{ref-kncnYGLD}{26}{]}.
+The main types of extracellular vesicles of this size are exosomes, up to 100 nm large vesicles derived from fusion of multivesicular bodies with the plasma membrane, and microvesicles, which are derived from direct budding of the plasma membrane {[}\protect\hyperlink{ref-kncnYGLD}{27}{]}.
 We suggest that granulocytes could release a third type of extracellular vesicle, granule-derived vesicles (GDV), into the extracellular space.
@@
 {[}\ref{fig:matching_fff}{]}D,E).
-This could indicate that these vesicles are transporting translation-capable mRNAs, as has been described for exosomes {[}\protect\hyperlink{ref-agVdpX76}{27}{]}.
+This could indicate that these vesicles are transporting translation-capable mRNAs, as has been described for exosomes {[}\protect\hyperlink{ref-agVdpX76}{28}{]}.
 Further studies will be necessary to confirm the existence of GDVs in granulocytes isolated from mammals and to understand their functional significance.
@@
 
-ER-HoxA9 cells were maintained in RPMI medium supplemented with 10\% FBS,
+ER-HoxB8 cells were maintained in RPMI medium supplemented with 10\% FBS,
 penicillin/streptomycin, SCF, and estrogen {[}\protect\hyperlink{ref-1B9Vt9eYu}{10}{]} at
@@
 diameter, resulting in the beam being completely visible on the camera. To
-establish fringe-free conditions, the ``Fine eucentric'' procedure of SerialEM {[}\protect\hyperlink{ref-19ZFerhph}{28}{]} was
+establish fringe-free conditions, the ``Fine eucentric'' procedure of SerialEM {[}\protect\hyperlink{ref-19ZFerhph}{29}{]} was
 used to move a square of the cross-grating grid to the eucentric position of the
@@
 
-Motion-correction, dose weighting and other preprocessing as detailed below was performed using \emph{cis}TEM {[}\protect\hyperlink{ref-MUY42yxp}{29}{]}.
+Motion-correction, dose weighting and other preprocessing as detailed below was performed using \emph{cis}TEM {[}\protect\hyperlink{ref-MUY42yxp}{30}{]}.
 To avoid influence of the beam-edge on motion-correction, only a quarter of the
@@
 Gaussian noise, with the same mean and standard deviation as the illuminated
-area. A custom version of the unblur program {[}\protect\hyperlink{ref-1G4Y94qCy}{30}{]}
+area. A custom version of the unblur program {[}\protect\hyperlink{ref-1G4Y94qCy}{31}{]}
 implementing this procedure is available at {[}link to decolace branch{]}. During motion correction images were resampled to a pixel size of 1.5 Å. The
 contrast-transfer function (CTF) was estimated using ctffind
-{[}\protect\hyperlink{ref-n43f3Sqs}{31}{]}, searching between 0.2 and 2 μm defocus.
+{[}\protect\hyperlink{ref-n43f3Sqs}{32}{]}, searching between 0.2 and 2 μm defocus.
 
@@
 (PDB 6SWA, exluding the Epb1 subunit) using the cryo-EM simulator implemented in \emph{cis}TEM
-{[}\protect\hyperlink{ref-q2PSamkS}{32}{]}. The
+{[}\protect\hyperlink{ref-q2PSamkS}{33}{]}. The
 match\_template program {[}\protect\hyperlink{ref-10bXZuF3G}{9}{]} was used to search for this
@@
 In order to calculate the precise offset between tiles \(i\) and \(j\), \(\mathbf{r}_{i,j}\), we calculated the cross-correlation between the two tiles, masked to the overlapping illuminated area using the scikit-image
-package {[}\protect\hyperlink{ref-stvWEJeu}{33}{]} was used to calculate refined offsets .
+package {[}\protect\hyperlink{ref-stvWEJeu}{34}{]} was used to calculate refined offsets .
 The coordinates \(\mathbf{c}_{i}\) were then refined by a least-square minimization against \(\mathbf{r}_{i,j}\):
@@
 
-using the scipy package {[}\protect\hyperlink{ref-8Miti2Gz}{34}{]}. The masked cross-correlation and the least-square minimization was repeated once more to arrive at the final tile alignment.
+using the scipy package {[}\protect\hyperlink{ref-8Miti2Gz}{35}{]}. The masked cross-correlation and the least-square minimization was repeated once more to arrive at the final tile alignment.
 
@@
 
-Images were rendered using UCSF ChimeraX {[}\protect\hyperlink{ref-cYCuuZxG}{35}{]} using a custom extension to render 2DTM results available at {[}https://github.com/jojoelfe/tempest{]}.
+Images were rendered using UCSF ChimeraX {[}\protect\hyperlink{ref-cYCuuZxG}{36}{]} using a custom extension to render 2DTM results available at {[}https://github.com/jojoelfe/tempest{]}.
 The Python scripts used for data processing are available
@@
 \caption{Template matching in lamella imaged using the DeCo-Lace approach at eucentric
-focus (A) Montage of Lamella\(_\textrm{EUC}\) 1 overlaid with detected targets according to
-their montage coordinates colored in orange. Scalebar corresponds to 1 μm. (B) Side view of detected targets in the lamella, such that the
+focus (A) Montage of Lamella\(_\textrm{EUC}\) 1 overlaid with detected targets colored in orange. Scalebar corresponds to 1 μm. (B) Side view of detected targets in the lamella, such that the
 direction of the electron beam is horizontal. (C-F) Magnified area of panel A
-showing rough ER with associated ribosomes(C), outer nuclear membrane with
-associated ribosomes (D), ribsomes arranged in a circular fashion(E), ribosomes
-enclosed in a less electron dense inclusion in a granule(F).
+showing rough ER with associated ribosomes (C), outer nuclear membrane with
+associated ribosomes (D), ribsomes arranged in a circular fashion (E), ribosomes
+enclosed in a less electron dense inclusion in a granule (F).
 Ribosomes are colored in white with the surface of the peptide exit tunnel colored in green and the A, P, and E sites colored in blue, purple, and red, respectively.Scalebar corresponds to 100 nm.}\label{fig:matching_euc}
@@
 \caption{Template matching in lamella imaged using the DeCo-Lace approach at fringe-free
-focus (A) Montage of Lamella\(_\textrm{FFF}\) 4 overlaid with detected targets according to
-their montage coordinates colored in orange. Scalebar corresponds to 1 μm. (B) Side view of detected targets in the lamella, such that the
+focus (A) Montage of Lamella\(_\textrm{FFF}\) 4 overlaid with detected targets colored in orange. Scalebar corresponds to 1 μm. (B) Side view of detected targets in the lamella, such that the
 direction of the electron beam is horizontal. (C-E) Magnified area of panel A
-showing rough ER with associated ribosomes(C) and ribosomes
-enclosed in a less electron dense inclusion in a granule(D,E). (F) Side view of
+showing rough ER with associated ribosomes (C) and ribosomes
+enclosed in a less electron dense inclusion in a granule (D,E). (F) Side view of
 panel E.
@@
 
+\begin{fignos:tagged-figure}[Movie 1]
+
+\begin{figure}
+\hypertarget{fig:movie1}{%
+\centering
+\includegraphics{images/1x1-00000000.png}
+\caption{Movie of detected LSU targets in Lamella\(_\textrm{EUC}\) 1, corresponding to Figure 5}\label{fig:movie1}
+}
+\end{figure}
+
+\end{fignos:tagged-figure}
+
+\begin{fignos:tagged-figure}[Movie 2]
+
+\begin{figure}
+\hypertarget{fig:movie2}{%
+\centering
+\includegraphics{images/1x1-00000000.png}
+\caption{Movie of detected LSU targets in Lamella\(_\textrm{FFF}\) 4, corresponding to Figure 6}\label{fig:movie2}
+}
+\end{figure}
+
+\end{fignos:tagged-figure}
+
 \hypertarget{references}{%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-T1Qr0xyP}{}}%
+\CSLLeftMargin{13. }%
+\CSLRightInline{\textbf{\textless i\textgreater In situ\textless/i\textgreater{} single particle classification reveals distinct 60S maturation intermediates in cells}
+\CSLBlock{Bronwyn A Lucas, Kexin Zhang, Sarah Loerch, Nikolaus Grigorieff} \emph{Cold Spring Harbor Laboratory} (2022-04-10) \url{https://doi.org/gp4qrx}
+\CSLBlock{DOI: \href{https://doi.org/10.1101/2022.04.10.487797}{10.1101/2022.04.10.487797}}}
+
 \leavevmode\vadjust pre{\hypertarget{ref-sbkam02a}{}}%
-\CSLLeftMargin{13. }%
+\CSLLeftMargin{14. }%
 \CSLRightInline{\textbf{Protein Synthesis in the Developing Neocortex at Near-Atomic Resolution Reveals Ebp1-Mediated Neuronal Proteostasis at the 60S Tunnel Exit}
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-wsFP5c54}{}}%
+\CSLLeftMargin{15. }%
+\CSLRightInline{\textbf{Advances in Single Particle Analysis Data Acquisition}
+\CSLBlock{Stan Konings, Maarten Kuijper, Jeroen Keizer, Fanis Grollios, Tjerk Spanjer, Peter Tiemeijer} \emph{Microscopy and Microanalysis} (2019-08) \url{https://doi.org/gp9bqm}
+\CSLBlock{DOI: \href{https://doi.org/10.1017/s1431927619005798}{10.1017/s1431927619005798}}}
+
 \leavevmode\vadjust pre{\hypertarget{ref-APSL9LmU}{}}%
-\CSLLeftMargin{14. }%
+\CSLLeftMargin{16. }%
 \CSLRightInline{\textbf{High-quality, high-throughput cryo-electron microscopy data collection via beam tilt and astigmatism-free beam-image shift}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-xE2EhAcH}{}}%
-\CSLLeftMargin{15. }%
+\CSLLeftMargin{17. }%
 \CSLRightInline{\textbf{THE DEVELOPMENT OF NEUTROPHILIC POLYMORPHONUCLEAR LEUKOCYTES IN HUMAN BONE MARROW}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-17IP4Lhz1}{}}%
-\CSLLeftMargin{16. }%
+\CSLLeftMargin{18. }%
 \CSLRightInline{\textbf{Routine determination of ice thickness for cryo-EM grids}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-hr3dyUeI}{}}%
-\CSLLeftMargin{17. }%
+\CSLLeftMargin{19. }%
 \CSLRightInline{\textbf{Optimized cryo-focused ion beam sample preparation aimed at in situ structural studies of membrane proteins}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-cie13Q8F}{}}%
-\CSLLeftMargin{18. }%
+\CSLLeftMargin{20. }%
 \CSLRightInline{\textbf{Circularization of mRNA by eukaryotic translation initiation factors.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1GPPSX111}{}}%
-\CSLLeftMargin{19. }%
+\CSLLeftMargin{21. }%
 \CSLRightInline{\textbf{Montage electron tomography of vitrified specimens}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ujizcpVn}{}}%
-\CSLLeftMargin{20. }%
+\CSLLeftMargin{22. }%
 \CSLRightInline{\textbf{Correlative cryogenic montage electron tomography for comprehensive in-situ whole-cell structural studies}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1Gwx5ScUa}{}}%
-\CSLLeftMargin{21. }%
+\CSLLeftMargin{23. }%
 \CSLRightInline{\textbf{Beam image-shift accelerated data acquisition for near-atomic resolution single-particle cryo-electron tomography}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-xvouNMBy}{}}%
-\CSLLeftMargin{22. }%
+\CSLLeftMargin{24. }%
 \CSLRightInline{\textbf{Parallel cryo electron tomography on \textless i\textgreater in situ\textless/i\textgreater{} lamellae}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-17H2LWiIu}{}}%
-\CSLLeftMargin{23. }%
+\CSLLeftMargin{25. }%
 \CSLRightInline{\textbf{Waffle Method: A general and flexible approach for improving throughput in FIB-milling}
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-T1Qr0xyP}{}}%
-\CSLLeftMargin{24. }%
-\CSLRightInline{\textbf{\textless i\textgreater In situ\textless/i\textgreater{} single particle classification reveals distinct 60S maturation intermediates in cells}
-\CSLBlock{Bronwyn A Lucas, Kexin Zhang, Sarah Loerch, Nikolaus Grigorieff} \emph{Cold Spring Harbor Laboratory} (2022-04-10) \url{https://doi.org/gp4qrx}
-\CSLBlock{DOI: \href{https://doi.org/10.1101/2022.04.10.487797}{10.1101/2022.04.10.487797}}}
-
 \leavevmode\vadjust pre{\hypertarget{ref-44fG6kcy}{}}%
-\CSLLeftMargin{25. }%
+\CSLLeftMargin{26. }%
 \CSLRightInline{\textbf{High-resolution cryo-EM using beam-image shift at 200 keV}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-kncnYGLD}{}}%
-\CSLLeftMargin{26. }%
+\CSLLeftMargin{27. }%
 \CSLRightInline{\textbf{Shedding light on the cell biology of extracellular vesicles}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-agVdpX76}{}}%
-\CSLLeftMargin{27. }%
+\CSLLeftMargin{28. }%
 \CSLRightInline{\textbf{Exosome-mediated transfer of mRNAs and microRNAs is a novel mechanism of genetic exchange between cells}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-19ZFerhph}{}}%
-\CSLLeftMargin{28. }%
+\CSLLeftMargin{29. }%
 \CSLRightInline{\textbf{Automated electron microscope tomography using robust prediction of specimen movements}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-MUY42yxp}{}}%
-\CSLLeftMargin{29. }%
+\CSLLeftMargin{30. }%
 \CSLRightInline{\textbf{cisTEM, user-friendly software for single-particle image processing}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1G4Y94qCy}{}}%
-\CSLLeftMargin{30. }%
+\CSLLeftMargin{31. }%
 \CSLRightInline{\textbf{Measuring the optimal exposure for single particle cryo-EM using a 2.6 Å reconstruction of rotavirus VP6}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-n43f3Sqs}{}}%
-\CSLLeftMargin{31. }%
+\CSLLeftMargin{32. }%
 \CSLRightInline{\textbf{CTFFIND4: Fast and accurate defocus estimation from electron micrographs}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-q2PSamkS}{}}%
-\CSLLeftMargin{32. }%
+\CSLLeftMargin{33. }%
 \CSLRightInline{\textbf{Cryo-TEM simulations of amorphous radiation-sensitive samples using multislice wave propagation}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-stvWEJeu}{}}%
-\CSLLeftMargin{33. }%
+\CSLLeftMargin{34. }%
 \CSLRightInline{\textbf{scikit-image: image processing in Python}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-8Miti2Gz}{}}%
-\CSLLeftMargin{34. }%
+\CSLLeftMargin{35. }%
 \CSLRightInline{\textbf{SciPy 1.0: fundamental algorithms for scientific computing in Python}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-cYCuuZxG}{}}%
-\CSLLeftMargin{35. }%
+\CSLLeftMargin{36. }%
 \CSLRightInline{\textbf{\textless scp\textgreater UCSF ChimeraX\textless/scp\textgreater{}

### 2022-06-13 ci/deploy.sh
Place movies into html version

@@ -71,6 +71,7 @@ ln -s ../output/manuscript.html webpage/index.html
 ln -s ../output/manuscript.pdf webpage/manuscript.pdf
 ln -s ../output/manuscript.docx webpage/manuscript.docx
 ln -s ../output/figures webpage/figures
+ln -s ../output/images webpage/images
 ln -s ../output/movies webpage/movies
 
 # Commit message

### 2022-06-14 manuscript.tex
Place movies into html version [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/009ecfe7c505910c424b8f1b31b59f44373441da.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/009ecfe7c505910c424b8f1b31b59f44373441da/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2491907565

@@
 \usepackage{cleveref}
+\usepackage{fontspec}
+\setmainfont{texgyrepagella}[
+  Extension = .otf,
+  UprightFont = *-regular,
+  BoldFont = *-bold,
+  ItalicFont = *-italic,
+  BoldItalicFont = *-bolditalic,
+]
+\usepackage{float}
+\floatplacement{figure}{H}
+\usepackage{caption}
+\captionsetup[figure]{font={stretch=1.2}}
 
@@
 
-This manuscript
-(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/a321def4b341f6e6f2c8d66936f53cf5e9398eae/}{permalink})
-was automatically generated
-from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/a321def4b341f6e6f2c8d66936f53cf5e9398eae}{jojoelfe/deco\_lace\_template\_matching\_manuscript@a321def}
-on June 6, 2022.
-
 \hypertarget{authors}{%
@@
   \textbf{Johannes Elferich}
-  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.pdf}
+  \includegraphics[width=0.16667in,height=0.16667in]{images/envelope.pdf}\includegraphics[width=0.16667in,height=0.16667in]{images/orcid.pdf}
   \href{https://orcid.org/0000-0002-9911-706X}{0000-0002-9911-706X}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.pdf}
-  \href{https://github.com/jojoelfe}{jojoelfe}
-  RNA Therapeutics Institute, University of Massachusetts Chan Medical School, Worcester, MA, USA; Howard Hughes Medical Institute, Ashburn, VA, USA
+
+  RNA Therapeutics Institute, University of Massachusetts Chan Medical School, Worcester, MA, USA; Howard Hughes Medical Institute, USA
 \item
@@
   \href{https://orcid.org/0000-0002-9812-8728}{0000-0002-9812-8728}
-  Center for Regenerative Medicine, Massachusetts General Hospital, Boston, MA 02114, USA
+
+  Center for Regenerative Medicine, Massachusetts General Hospital, Boston, MA, USA; Harvard Stem Cell Institute, Cambridge, MA, USA; Department of Stem Cell and Regenerative Biology, Harvard University, Cambridge, MA, USA
 \item
   \textbf{David Scadden}
-  Center for Regenerative Medicine, Massachusetts General Hospital, Boston, MA 02114, USA; Harvard Stem Cell Institute, Cambridge, MA 02138, USA; Department of Stem Cell and Regenerative Biology, Harvard University, Cambridge, MA 02138, USA
+  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.pdf}
+  \href{https://orcid.org/0000-0001-9821-7133}{0000-0001-9821-7133}
+
+  Center for Regenerative Medicine, Massachusetts General Hospital, Boston, MA, USA; Harvard Stem Cell Institute, Cambridge, MA, USA; Department of Stem Cell and Regenerative Biology, Harvard University, Cambridge, MA, USA
 \item
   \textbf{Nikolaus Grigorieff}
-  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.pdf}
+  \includegraphics[width=0.16667in,height=0.16667in]{images/envelope.pdf}\includegraphics[width=0.16667in,height=0.16667in]{images/orcid.pdf}
   \href{https://orcid.org/0000-0002-1506-909X}{0000-0002-1506-909X}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.pdf}
-  \href{https://github.com/nikogrigorieff}{nikogrigorieff}
-  RNA Therapeutics Institute, University of Massachusetts Chan Medical School, Worcester, MA, USA; Howard Hughes Medical Institute, Ashburn, VA, USA
+
+  RNA Therapeutics Institute, University of Massachusetts Chan Medical School, Worcester, MA, USA; Howard Hughes Medical Institute, USA
 \end{itemize}
+
+\leavevmode\vadjust pre{\hypertarget{correspondence}{}}%
+\includegraphics[width=0.16667in,height=0.16667in]{images/envelope.pdf} --- correspondence preferred via \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/issues}{GitHub Issues}.
+Otherwise, address correspondence to \href{mailto:johannes.elferich@umassmed.edu}{\nolinkurl{johannes.elferich@umassmed.edu}} and \href{mailto:niko@grigorieff.org}{\nolinkurl{niko@grigorieff.org}}.
 
@@
 
-Here we apply 2DTM of the ribosome large subunit (LSU) to conditionally immortalized \emph{mus musculus} (mouse) cell line that gives rise to functional mature neutrophils {[}\protect\hyperlink{ref-1B9Vt9eYu}{10}{]} after thinning using cryo-FIB milling.
+Here we apply 2DTM of the ribosome large subunit (LSU) to a conditionally immortalized \emph{mus musculus} (mouse) cell line that gives rise to functional mature neutrophils {[}\protect\hyperlink{ref-1B9Vt9eYu}{10}{]}.
 We chose these
@@
 We used the tile positions to calculate the positions of the detected
-LSUs in the lamellae (Fig. {[}\ref{fig:matching_euc}{]}A, Fig. {[}\ref{fig:matching_fff}{]}A). Overlaying these positions of the lamellae montages reveals LSU
+LSUs in the lamellae (Fig. {[}\ref{fig:matching_euc}{]}A, Fig. {[}\ref{fig:matching_fff}{]}A, Movie 1, Movie 2). Overlaying these positions of the lamellae montages reveals LSU
 distribution throughout the FIB-milled slices of individual cells. Consistent with prior observations imaging selected views in yeast {[}\protect\hyperlink{ref-T1Qr0xyP}{13}{]}, organelles
@@
 to the microscope frame of reference (Fig. {[}\ref{fig:matching_euc}{]}B, Fig.
-{[}\ref{fig:matching_fff}{]}B). Furthermore, the side views indicated that lamellae
+{[}\ref{fig:matching_fff}{]}B, Movie 1, Movie 2). Furthermore, the side views indicated that lamellae
 were thinner at the leading edge. Indeed, when plotting the transmitted beam
@@
 preparation methods are needed to generate more even samples.
+
+As described in {[}\protect\hyperlink{ref-Ynb3IP6I}{7}{]} the 2DTM SNR threshold for detecting a target is chosen to result in one false positive detection per image searched.
+We would therefore expect to find one false positive detection per tile.
+We reasoned that the large nuclear area imaged by DeCo-LACE could be used to test whether this assumption is true.
+In the 670 tiles containing exclusively nucleus (as manually annotated from the overview image) we detected 247 targets, making the false-positive rate more than twofold lower than expected.
+Since earlier work shows that 2DTM with the LSU can produce matches to nuclear ribosome biogenesis intermediates {[}\protect\hyperlink{ref-T1Qr0xyP}{13}{]}, this could even be an overestimate of the false-positive rate.
+This suggests that the detection threshold could be even lower, which is an area of ongoing research.
 
@@
 SNR values throughout the illuminated areas for both eucentric and fringe-free
-focus illumination, demonstrating that both illumination schemed are suitable
+focus illumination, demonstrating that both illumination schemes are suitable
 for DeCo-LACE (Fig. {[}\ref{fig:matching_stat}{]}D).
 
-We also wondered whether large image shifts would lead aberration due to
+We also wondered whether large image shifts would lead to aberrations due to
 astigmatism or beam tilt {[}\protect\hyperlink{ref-APSL9LmU}{16}{]}. We reasoned that if
@@
 In this study we developed an approach to image entire cellular cross-section using cryo-EM at high enough resolution to allow for 2DTM detection of the LSU.
-The two main advantages compared to previous approaches are a high throughput of imaging and the biological context for detected molecules.
+The two main advantages compared to previous approaches are high throughput of imaging and biological context for detected molecules.
 The requirement to increase throughput in cryo-EM data collection of cellular samples has been recognized in the recent literature.
@@
 Peck et al.~used a similar ``condensed-beam'' approach as described here.
-However, the montages are substantially smaller in scope, covering carbon film holes of 2 um diameter.
+However, the montages are substantially smaller in scope, covering carbon film holes of 2 µm diameter.
 Bouvette et al.
@@
 {[}\protect\hyperlink{ref-xvouNMBy}{24}{]} are using beam image-shift to collect tilt-series in multiple locations in parallel to increase throughput.
-However, none of these approaches provide the full coverage of a cellular cross-section that can be achieved using DeCo-Lace.
-
-Since we observed substantial variation in LSU density within and between lamellae, visual proteomics studies that use cryo-EM to establish changes in molecular organization within cells will require orders of magnitude more data than used in this study.
-One milestone would be to image enough data to represent one cellular volume, which for a small eukaryotic cells requires imaging approximately 100 lamella.
-While data collection throughput on the TEM is fundamentally limited by the exposure time, this amount of data could be collected within 12 hours by improving the data acquisition scheme to perform all necessary calculations in parallel with actual exposure of the camera.
-Sample preparation using a FIB/SEM is also currently a bottleneck, but preparation of large lamellae with multiple cellular cross-sections using methods like WAFFLE {[}\protect\hyperlink{ref-17H2LWiIu}{25}{]} might allow sufficient throughput.
-As stated in the results, at least for 2DTM computation will remain challenging and approximately 17,000 GPU hours would be required for a 100 lamellae dataset.
-
-As described in {[}\protect\hyperlink{ref-Ynb3IP6I}{7}{]} the 2DTM SNR threshold for detecting a target is chosen to result in one false positive detection per image searched.
-We would therefore expect to find one false positive detection per tile.
-We reasoned that the large nuclear area imaged by DeCo-Lace could be used to test whether this assumption is true.
-In the 670 tiles containing exclusively nucleus (as manually annotated from the overview image) we detected 247 targets, making the false-positive rate more than twofold lower than expected.
-Since earlier work shows that 2DTM with the LSU can produce matches to nuclear ribosome biogenesis intermediates {[}\protect\hyperlink{ref-T1Qr0xyP}{13}{]}, this could even be an overestimate of the false-positive rate.
-This suggests that the detection threshold could be even lower, which is an area of ongoing research.
-
-We found that even though we used beam image-shift extensively (up to 7 um), we did not see substantially reduced 2DTM SNR values in tiles acquired at high beam image-shift compared to tiles acquired with low or no beam image-shift.
-This is in contrast to reports in single-particle analysis (SPA) {[}\protect\hyperlink{ref-44fG6kcy}{26}{]} where the induced beam tilt substantially reduced the resolution if it was not corrected during processing.
-It is possible that 2DTM is less sensitive to beam-tilt aberrations, since the template is free of any aberration and only the image is distorted, while in SPA the beam tilt will affect both the images and the reconstructed template.
+However, none of these approaches provide the full coverage of a cellular cross-section that can be achieved using DeCo-LACE.
+
+We observed granules containing a vesicle of putative cytosolic origin.
+We speculate that upon degranulation, the process in which granules fuse with the plasma membrane, these vesicles would be released into the extracelullar space.
+The main types of extracellular vesicles of this size are exosomes, up to 100 nm large vesicles derived from fusion of multivesicular bodies with the plasma membrane, and microvesicles, which are derived from direct budding of the plasma membrane {[}\protect\hyperlink{ref-kncnYGLD}{25}{]}.
+We suggest that granulocytes could release a third type of extracellular vesicle, granule-derived vesicles (GDV), into the extracellular space.
+2DTM showed that a subset of GDVs can contain ribosomes (Fig.
+{[}\ref{fig:matching_euc}{]}F, Fig.
+{[}\ref{fig:matching_fff}{]}D,E).
+This could indicate that these vesicles are transporting translation-capable mRNAs, as has been described for exosomes {[}\protect\hyperlink{ref-agVdpX76}{26}{]}.
+Further studies will be necessary to confirm the existence of GDVs in granulocytes isolated from mammals and to understand their functional significance.
 
@@
 
-We observed granules containing a vesicle of putative cytosolic origin.
-We speculate that upon degranulation, the process in which granules fuse with the plasma membrane, these vesicles would be released into the extracelullar space.
-The main types of extracellular vesicles of this size are exosomes, up to 100 nm large vesicles derived from fusion of multivesicular bodies with the plasma membrane, and microvesicles, which are derived from direct budding of the plasma membrane {[}\protect\hyperlink{ref-kncnYGLD}{27}{]}.
-We suggest that granulocytes could release a third type of extracellular vesicle, granule-derived vesicles (GDV), into the extracellular space.
-2DTM showed that a subset of GDVs can contain ribosomes (Fig.
-{[}\ref{fig:matching_euc}{]}F, Fig.
-{[}\ref{fig:matching_fff}{]}D,E).
-This could indicate that these vesicles are transporting translation-capable mRNAs, as has been described for exosomes {[}\protect\hyperlink{ref-agVdpX76}{28}{]}.
-Further studies will be necessary to confirm the existence of GDVs in granulocytes isolated from mammals and to understand their functional significance.
+We found that even though we used beam image-shift extensively (up to 7 um), we did not see substantially reduced 2DTM SNR values in tiles acquired at high beam image-shift compared to tiles acquired with low or no beam image-shift.
+This is in contrast to reports in single-particle analysis (SPA) {[}\protect\hyperlink{ref-44fG6kcy}{27}{]} where the induced beam tilt substantially reduced the resolution if it was not corrected during processing.
+It is possible that 2DTM is less sensitive to beam-tilt aberrations, since the template is free of any aberration and only the image is distorted, while in SPA the beam tilt will affect both the images and the reconstructed template.
+
+Since we observed substantial variation in LSU density within and between lamellae, visual proteomics studies that use cryo-EM to establish changes in molecular organization within cells will require orders of magnitude more data than used in this study.
+One milestone would be to image enough data to represent one cellular volume, which for a small eukaryotic cells requires imaging approximately 100 lamellae.
+While data collection throughput on the TEM is fundamentally limited by the exposure time, this amount of data could be collected within 12 hours by improving the data acquisition scheme to perform all necessary calculations in parallel with actual exposure of the camera.
+Sample preparation using a FIB/SEM is also currently a bottleneck, but preparation of large lamellae with multiple cellular cross-sections using methods like WAFFLE {[}\protect\hyperlink{ref-17H2LWiIu}{28}{]} might allow sufficient throughput.
+As stated in the results, at least for 2DTM computation will remain challenging and approximately 17,000 GPU hours would be required for a 100 lamellae dataset.
 
@@
 was added to grids on the thin-film side and grids were blotted from the back
-side using a GP2 cryoplunger (Leica) for 8 s and rapidly plunged into liquid
+side using a GP2 cryoplunger (Leica, Wetzlar, Germany) for 8 s and rapidly plunged into liquid
 ethane at -185 °C.
@@
 
-Grids were loaded into an Aquilos 2 FIB/SEM (Thermo Fisher) instrument with a
+Grids were loaded into an Aquilos 2 FIB/SEM (Thermo Fisher, Waltham, MA) instrument with a
 stage cooled to -190 °C. Grids were sputter-coated with platinum for 15 s at 45 mA
@@
 Grids were loaded into a Titan Krios TEM (Thermo Fisher) operated at 300 keV and
-equipped with a BioQuantum energy filter (Gatan) and K3 camera (Gatan). The
+equipped with a BioQuantum energy filter (Gatan, Pleasanton, CA) and K3 camera (Gatan). The
 microscope was aligned using a cross-grating grid on the stage. Prior to each
@@
 200 μm defocus was taken for visualization purposes. A Python script implementing
-this procedure is available at {[}Link to repo{]}.
+this procedure is available at \url{https://github.com/jojoelfe/deco_lace_template_matching_manuscript}.
 
@@
 
-Images were rendered using UCSF ChimeraX {[}\protect\hyperlink{ref-cYCuuZxG}{36}{]} using a custom extension to render 2DTM results available at {[}https://github.com/jojoelfe/tempest{]}.
+Images were rendered using UCSF ChimeraX {[}\protect\hyperlink{ref-cYCuuZxG}{36}{]} using a custom extension to render 2DTM results available at \url{https://github.com/jojoelfe/tempest}.
 The Python scripts used for data processing are available
-under {[}https://github.com/jojoelfe/deco\_lace\_template\_matching\_manuscript{]}.
+under \url{https://github.com/jojoelfe/deco_lace_template_matching_manuscript}.
 
@@
 
-The authors would like to thank Bronwyn Lucas, Carsten Sachse, and Chen Xue for helpful suggestions and careful reading of the manuscript.
-Data was collected at the UMass Chan medical School CryoEM core with help by Kankang song, Christna, and Chen Xue.
+The authors would like to thank Bronwyn Lucas, Carsten Sachse, and Chen Xu for helpful suggestions and careful reading of the manuscriptas as well as members of the Grigorieff lab for helpful discussions.
+Data was collected at the UMass Chan Medical School Cryo-EM core with help by Kankang Song, Christna Ouch, and Chen Xu.
 
@@
 
-Cryo-EM movies, motion-corrected images and template matching results have been deposited in EMPIAR under accession code {[}CODE{]}.
-The custom cisTEM version is available here {[}{]} until features have been integrated into a cisTEM release.
-The ChimeraX extension for rendering is avaibale here {[}{]}.
-This manuscript was prepared using the manubot package {[}@ cite{]} .
-Custom python scripts and all files nescessary for manuscript generation are available here {[}{]}.
+Cryo-EM movies, motion-corrected images and 2DTM results have been deposited in EMPIAR under accession code {[}will be inserted{]}.
+The custom cisTEM version is available under \url{https://github.com/jojoelfe/cisTEM/tree/2574dbdf6161658fd177660b3a841100a792f61b} until features have been integrated into a cisTEM release.
+The ChimeraX extension for rendering is available under \url{https://github.com/jojoelfe/tempest}.
+This manuscript was prepared using the manubot package {[}\protect\hyperlink{ref-YuJbg3zO}{37}{]} .
+The corresponding repository containing all scripts used for figure generation can be found under \url{https://github.com/jojoelfe/deco_lace_template_matching_manuscript}.
+
+\hypertarget{conflicts-of-interest}{%
+\subsection{Conflicts of interest}\label{conflicts-of-interest}}
+
+The Authors declare that there is no conflict of interest.
 
@@
 (D) or fringe-free focus (E). Scalebar corresponds to 100 nm.
-(F) Boxplot of defocus measured by ctffind of micrographs taken by the DeCo-Lace
+(F) Boxplot of defocus measured by ctffind of micrographs taken by the DeCo-LACE
 approach on four lamellae images at eucentric focus and four lamellae imaged with
@@
 \includegraphics{figures/lamella_spatial_info.png}
-\caption{Defocus estimation of individual tiles of DeCo-Lace montages
-(A) Defocus values of individual micrographs taken using the DeCo-Lace approach
+\caption{Defocus estimation of individual tiles of DeCo-LACE montages
+(A) Defocus values of individual micrographs taken using the DeCo-LACE approach
 plotted as a function of the beam image-shift values.
-(B) Defocus astigmatism of individual micrographs taken using the DeCo-Lace approach
+(B) Defocus astigmatism of individual micrographs taken using the DeCo-LACE approach
 plotted as a function of the beam image-shift values.}\label{fig:lamella_spatial_info}
@@
 image of Lamella\textsubscript{EUC} 1 taken at low magnification. Scalebar corresponds to 1 μm. (B) Overview of Lamella\textsubscript{EUC} 1 created by
-montaging high magnification images taken with the DeCo-Lace approach.
+montaging high magnification images taken with the DeCo-LACE approach.
 Scalebar corresponds to 1 μm.
@@
 image of Lamella\textsubscript{FFF} 4 taken at low magnification. Scalebar corresponds to 1 μm. (E) Overview of Lamella\textsubscript{FFF} 4 created by
-montaging high magnification images taken with the DeCo-Lace approach.
+montaging high magnification images taken with the DeCo-LACE approach.
 Scalebar corresponds to 1 μm.
@@
 \caption{Motion correction of individual tiles imaged using the DeCo-LACE approach
-(A) Total estimated motion of individual micrographs taken using the DeCo-Lace approach
+(A) Total estimated motion of individual micrographs taken using the DeCo-LACE approach
 plotted as a function of the beam image-shift values.
-(B) Electron intensity of individual micrographs taken using the DeCo-Lace approach
+(B) Electron intensity of individual micrographs taken using the DeCo-LACE approach
 plotted as a function of the beam image-shift values.}\label{fig:lamella_motion_thickness}
@@
 \centering
-\includegraphics{figures/lamella_images.png}
+\includegraphics[width=\textwidth,height=23cm]{figures/lamella_images.png}
 \caption{Overview images of lamellae imaged using the DeCo-LACE approach taken at low-magnification (A) Overviews taken at low magnification.
@@
 \includegraphics{figures/matching_euc.png}
-\caption{Template matching in lamella imaged using the DeCo-Lace approach at eucentric
+\caption{Template matching in lamella imaged using the DeCo-LACE approach at eucentric
 focus (A) Montage of Lamella\(_\textrm{EUC}\) 1 overlaid with detected targets colored in orange. Scalebar corresponds to 1 μm. (B) Side view of detected targets in the lamella, such that the
@@
 \includegraphics{figures/matching_fff.png}
-\caption{Template matching in lamella imaged using the DeCo-Lace approach at fringe-free
+\caption{Template matching in lamella imaged using the DeCo-LACE approach at fringe-free
 focus (A) Montage of Lamella\(_\textrm{FFF}\) 4 overlaid with detected targets colored in orange. Scalebar corresponds to 1 μm. (B) Side view of detected targets in the lamella, such that the
@@
 \includegraphics{figures/deco_lace_workflow.png}
-\caption{Workflow of DeCo-Lace processing}\label{fig:deco_lace_workflow}
+\caption{Workflow of DeCo-LACE processing}\label{fig:deco_lace_workflow}
 }
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-kncnYGLD}{}}%
+\CSLLeftMargin{25. }%
+\CSLRightInline{\textbf{Shedding light on the cell biology of extracellular vesicles}
+\CSLBlock{Guillaume van Niel, Gisela D'Angelo, Graça Raposo} \emph{Nature Reviews Molecular Cell Biology} (2018-01-17) \url{https://doi.org/gct4df}
+\CSLBlock{DOI: \href{https://doi.org/10.1038/nrm.2017.125}{10.1038/nrm.2017.125} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/29339798}{29339798}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-agVdpX76}{}}%
+\CSLLeftMargin{26. }%
+\CSLRightInline{\textbf{Exosome-mediated transfer of mRNAs and microRNAs is a novel mechanism of genetic exchange between cells}
+\CSLBlock{Hadi Valadi, Karin Ekström, Apostolos Bossios, Margareta Sjöstrand, James J Lee, Jan O Lötvall} \emph{Nature Cell Biology} (2007-05-07) \url{https://doi.org/d5df4s}
+\CSLBlock{DOI: \href{https://doi.org/10.1038/ncb1596}{10.1038/ncb1596} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/17486113}{17486113}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-44fG6kcy}{}}%
+\CSLLeftMargin{27. }%
+\CSLRightInline{\textbf{High-resolution cryo-EM using beam-image shift at 200 keV}
+\CSLBlock{Jennifer N Cash, Sarah Kearns, Yilai Li, Michael A Cianfrocco} \emph{IUCrJ} (2020-10-29) \url{https://doi.org/gjwcfq}
+\CSLBlock{DOI: \href{https://doi.org/10.1107/s2052252520013482}{10.1107/s2052252520013482} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/33209328}{33209328} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7642776}{PMC7642776}}}
+
 \leavevmode\vadjust pre{\hypertarget{ref-17H2LWiIu}{}}%
-\CSLLeftMargin{25. }%
+\CSLLeftMargin{28. }%
 \CSLRightInline{\textbf{Waffle Method: A general and flexible approach for improving throughput in FIB-milling}
@@
 \CSLBlock{DOI: \href{https://doi.org/10.1038/s41467-022-29501-3}{10.1038/s41467-022-29501-3} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/35387991}{35387991} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC8987090}{PMC8987090}}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-44fG6kcy}{}}%
-\CSLLeftMargin{26. }%
-\CSLRightInline{\textbf{High-resolution cryo-EM using beam-image shift at 200 keV}
-\CSLBlock{Jennifer N Cash, Sarah Kearns, Yilai Li, Michael A Cianfrocco} \emph{IUCrJ} (2020-10-29) \url{https://doi.org/gjwcfq}
-\CSLBlock{DOI: \href{https://doi.org/10.1107/s2052252520013482}{10.1107/s2052252520013482} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/33209328}{33209328} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7642776}{PMC7642776}}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kncnYGLD}{}}%
-\CSLLeftMargin{27. }%
-\CSLRightInline{\textbf{Shedding light on the cell biology of extracellular vesicles}
-\CSLBlock{Guillaume van Niel, Gisela D'Angelo, Graça Raposo} \emph{Nature Reviews Molecular Cell Biology} (2018-01-17) \url{https://doi.org/gct4df}
-\CSLBlock{DOI: \href{https://doi.org/10.1038/nrm.2017.125}{10.1038/nrm.2017.125} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/29339798}{29339798}}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-agVdpX76}{}}%
-\CSLLeftMargin{28. }%
-\CSLRightInline{\textbf{Exosome-mediated transfer of mRNAs and microRNAs is a novel mechanism of genetic exchange between cells}
-\CSLBlock{Hadi Valadi, Karin Ekström, Apostolos Bossios, Margareta Sjöstrand, James J Lee, Jan O Lötvall} \emph{Nature Cell Biology} (2007-05-07) \url{https://doi.org/d5df4s}
-\CSLBlock{DOI: \href{https://doi.org/10.1038/ncb1596}{10.1038/ncb1596} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/17486113}{17486113}}}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-YuJbg3zO}{}}%
+\CSLLeftMargin{37. }%
+\CSLRightInline{\textbf{Open collaborative writing with Manubot}
+\CSLBlock{Daniel S Himmelstein, Vincent Rubinetti, David R Slochower, Dongbo Hu, Venkat S Malladi, Casey S Greene, Anthony Gitter} \emph{PLOS Computational Biology} (2019-06-24) \url{https://doi.org/c7np}
+\CSLBlock{DOI: \href{https://doi.org/10.1371/journal.pcbi.1007128}{10.1371/journal.pcbi.1007128} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/31233491}{31233491} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6611653}{PMC6611653}}}
+
 \end{CSLReferences}

### 2022-06-14 serialem_scripts/original/fowl_20211029.py
Collection scripts

@@ -1,0 +1,592 @@
+import numpy as np
+import glob
+import time
+import os
+import math
+import matplotlib.pyplot as plt
+from shapely.geometry import Point
+from shapely.geometry.polygon import Polygon
+import json
+
+import sys
+sys.path.insert(0, 'C:\Program Files\SerialEM\PythonModules')
+import serialem
+
+# TODO:
+#    - Switch to no tilt angles (X)
+#    - Read form spceific Navigator item (x)
+#    - Calibration images better chosen (x)
+#    - Write grid manager
+#    - Write inital alignment
+#    - Extrapolate calibration (x)     
+#    - Graceful stop (now will always extrapolate )
+#    - Save view image (x)
+#   
+
+class fowl_grid:
+    def __init__(self,name,directory,beam_radius,load_from_file=False, defocus=-5.0,start_from=0.0, numtilts=41, tiltstep=3.0):
+        self.state = {}
+        self.name = name
+        self.directory = directory
+
+        self.state["acquisition_areas"] = []
+        self.state["microscope_settings"] = {}
+
+    def write_to_disk(self):
+        timestr = time.strftime("%Y%m%d-%H%M%S")
+        filename = f"{self.name}_{timestr}.npy"
+        filename = os.path.join(self.directory, filename)
+        np.save(filename, self.state)
+   
+    def load_from_disk(self):
+        potential_files = glob.glob(os.path.join(
+            self.directory, self.name+"_*.npy"))
+        if len(potential_files) < 1:
+            raise(FileNotFoundError("Couldn't find saved files"))
+        most_recent = sorted(potential_files)[-1]
+        print(f"Loading file {most_recent}")
+        self.state = np.load(most_recent, allow_pickle=True).item()
+
+    def add_current_setting(self, name, fringe_free=False):
+
+        settings = {}
+        settings["magnification"] = serialem.ReportMag()
+        settings["magnification_index"] = serialem.ReportMagIndex()
+        settings["spot_size"] = serialem.ReportSpotSize()
+        settings["illuminated_area"] = serialem.ReportIlluminatedArea()
+        settings["beam_tilt"] = serialem.ReportBeamTilt()
+        settings["objective_stigmator"] = serialem.ReportObjectiveStigmator()
+        settings["fringe_free"] = fringe_free
+
+        if fringe_free:
+            settings["fringe_free_nominal_defocus_c2aperture"] = serialem.ReportDefocus()
[…]

### 2022-06-14 serialem_scripts/original/fowl_20211108.py

@@ -1,0 +1,640 @@
+import numpy as np
+import glob
+import time
+import os
+import math
+import matplotlib.pyplot as plt
+from shapely.geometry import Point
+from shapely.geometry.polygon import Polygon
+import json
+from pathlib import Path
+
+import sys
+sys.path.insert(0, 'C:\Program Files\SerialEM\PythonModules')
+import serialem
+
+# TODO:
+#    - Switch to no tilt angles (X)
+#    - Read form spceific Navigator item (x)
+#    - Calibration images better chosen (x)
+#    - Write grid manager
+#    - Write inital alignment
+#    - Extrapolate calibration (x)     
+#    - Graceful stop (now will always extrapolate )
+#    - Save view image (x)
+#   
+
+
+class fowl_session:
+    def __init__(self,name,directory,load_from_file=False):
+        self.state = {}
+        self.name = name
+        self.directory = directory
+
+        self.state["grids"] = []
+        self.state["microscope_settings"] = {}
+
+    def write_to_disk(self):
+        timestr = time.strftime("%Y%m%d-%H%M%S")
+        filename = f"{self.name}_{timestr}.npy"
+        filename = os.path.join(self.directory, filename)
+        np.save(filename, self.state)
+   
+    def load_from_disk(self):
+        potential_files = glob.glob(os.path.join(
+            self.directory, self.name+"_*.npy"))
+        if len(potential_files) < 1:
+            raise(FileNotFoundError("Couldn't find saved files"))
+        most_recent = sorted(potential_files)[-1]
+        print(f"Loading file {most_recent}")
+        self.state = np.load(most_recent, allow_pickle=True).item()
+    def add_current_setting(self, name, fringe_free=False):
+
+        settings = {}
+        settings["magnification"] = serialem.ReportMag()
+        settings["magnification_index"] = serialem.ReportMagIndex()
+        settings["spot_size"] = serialem.ReportSpotSize()
+        settings["illuminated_area"] = serialem.ReportIlluminatedArea()
+        settings["beam_tilt"] = serialem.ReportBeamTilt()
+        settings["objective_stigmator"] = serialem.ReportObjectiveStigmator()
+        settings["fringe_free"] = fringe_free
+
+        if fringe_free:
+            settings["fringe_free_nominal_defocus_c2aperture"] = serialem.ReportDefocus()
+            settings["fringe_free_stage_z_diff"] = serialem.ReportStageXYZ()[2] - self.eucentric_z
+
+        self.state["microscope_settings"][name] = settings
+
+
[…]

### 2022-11-03 reviews/submitted.tex
almost there

--- 2022-06-14 manuscript.tex
@@
 
+¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶
+¶ ¶
+
 \hypertarget{authors}{%
@@
 \CSLRightInline{\textbf{Shedding light on the cell biology of extracellular vesicles}
-\CSLBlock{Guillaume van Niel, Gisela D'Angelo, Graça Raposo} \emph{Nature Reviews Molecular Cell Biology} (2018-01-17) \url{https://doi.org/gct4df}
+\CSLBlock{Guillaume van Niel, Gisela D\textquotesingle Angelo, Graça Raposo} \emph{Nature Reviews Molecular Cell Biology} (2018-01-17) \url{https://doi.org/gct4df}
 \CSLBlock{DOI: \href{https://doi.org/10.1038/nrm.2017.125}{10.1038/nrm.2017.125} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/29339798}{29339798}}}

### 2022-11-03 build/build.sh

@@ -145,6 +145,9 @@ if [ "${BUILD_LATEX}" = "true" ]; then
     --defaults=common.yaml \
     --defaults=latex.yaml
   tectonic output/manuscript.tex
+
+  ~/sw/latexdiff/latexdiff reviews/submitted.tex output/manuscript.tex > output/diff.tex
+  tectonic output/diff.tex
   rm images
   rm output/graphics
   rm graphics

### 2022-11-04 content/coverletter/build_revision_coverletter.sh
Minor polish, sent to niko

@@ -1,0 +1,3 @@
+cat coverletter_revision.md ../../reviews/elife_answers.md > assm.md
+
+pandoc --pdf-engine=tectonic --template=template-letter.tex assm.md -o coverletter_revision.pdf

### 2022-11-14 elife_submission/figures/gain.tex
Minor adjustments to submission

--- 2022-04-07 figures/lamella_images.tex
@@
     \setlist{nosep,leftmargin=*}
-    \newcommand{\figwidth}{20.0cm} 
-    \newcommand{\figheight}{5cm} 
+    \newcommand{\figwidth}{10.0cm} 
+    \newcommand{\figheight}{2cm} 
     \newcommand{\fontselect}{\large\bf} 
@@
 
-    \def\panelheight{4.6cm}
+    \newlength{\panelheight}
+\setlength{\panelheight}{7cm}
 
-\node (anchor) at (0.5,4.5) {}; 
+\node (anchor) at (0.5,3.5) {}; 
 \node[labelNode] {A};
-\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/slicer000.png}};
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/euc_gain.png}};
+
 \node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
-\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/slicer001.png}};
-\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
-\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/slicer002.png}};
-\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
-\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/slicer003.png}};
-
-\node (anchor) at ([shift={(0.0cm,-0.5cm)}]0.5,0 |- panel.south) {}; 
-\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/images/slicer005.png}};
-\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
-\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/images/slicer006.png}};
-\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
-\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/images/slicer007.png}};
-\node (anchor) at ([shift={(0.5cm,0.0cm)}]panel.north east) {}; 
-\node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/images/slicer008.png}};
-
+\node[labelNode] {B};
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/images/fff_gain.png}};
     \iftoggle{draft}{\draw[lightgray,step=1] (0,0) grid (\figwidth,\figheight);}{};

### 2022-11-14 elife_submission/figures/initmatching.tex
Minor adjustments to submission

--- 2022-05-20 figures/initmatching.tex
@@
 \node[labelNode] {A};
-\node[graphicNode] {\includegraphics[height=9cm]{content/images/the_lamella.png}};
+\node[graphicNode] (panel) {\includegraphics[height=9cm]{content/images/the_lamella.png}};
 
@@
 \node[annotNode] at (4.5,3.5) {\contour{white}{GrCyt}};
+
+% scalebar - physical height is 12810 nm
+\draw [line width=1.55mm,white] ([xshift=-0.05cm, yshift=0.1cm]panel.south east) -- ([xshift=-1.25cm  , yshift=0.1cm]panel.south east);
+\draw [line width=0.7mm,black] ([xshift=-0.05cm, yshift=0.1cm]panel.south east) -- ([xshift=-1.25cm , yshift=0.1cm]panel.south east);
 

### 2022-11-14 elife_submission/figures/lamella_images.tex
Minor adjustments to submission

--- 2022-05-20 figures/lamella_images.tex
@@
 \node[labelNode] {C};
-\node[graphicNode] (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap004.png}};
+\node[graphicNode] (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap004_lp.png}};
 \node (anchor) at ([shift={(\padding,0.0cm)}]panel.north east) {}; 
-\node[graphicNode] (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap012.png}};
+\node[graphicNode] (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap012_lp.png}};
 \node (anchor) at ([shift={(\padding,0.0cm)}]panel.north east) {}; 
-\node[graphicNode] (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap015.png}};
+\node[graphicNode] (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap015_lp.png}};
 \node (anchor) at ([shift={(\padding,0.0cm)}]panel.north east) {}; 
-\node[graphicNode] (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap020.png}};
+\node[graphicNode] (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap020_lp.png}};
 \node (anchor) at ([shift={(\padding,0.0cm)}]panel.north east) {}; 
-\node[graphicNode] (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap006.png}};
+\node[graphicNode] (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap006_lp.png}};
 
 \node (anchor) at ([shift={(0.0cm,-\padding)}]0.5,0 |- panel.south) {}; 
-\node[graphicNode]  (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap021.png}};
+\node[graphicNode]  (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap021_lp.png}};
 \node (anchor) at ([shift={(\padding,0.0cm)}]panel.north east) {}; 
-\node[graphicNode]  (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap022.png}};
+\node[graphicNode]  (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap022_lp.png}};
 \node (anchor) at ([shift={(\padding,0.0cm)}]panel.north east) {}; 
-\node[graphicNode]  (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap027.png}};
+\node[graphicNode]  (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap027_lp.png}};
 \node (anchor) at ([shift={(\padding,0.0cm)}]panel.north east) {}; 
-\node[graphicNode]  (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap029.png}};
+\node[graphicNode]  (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap029_lp.png}};
 \node (anchor) at ([shift={(\padding,0.0cm)}]panel.north east) {}; 
-\node[graphicNode]  (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap023.png}};
+\node[graphicNode]  (panel) {\includegraphics[height=0.75\panelheight]{content/images/granules/zap023_lp.png}};
 % scalebar - physical height is 375 nm

### 2022-11-14 elife_submission/figures/lamella_motion_thickness.tex
Minor adjustments to submission

--- 2022-04-07 figures/lamella_motion_thickness.tex
@@
 
-    \def\panelheight{4.6cm}
+    \newlength{\panelheight}
+\setlength{\panelheight}{4.6cm}
 
@@
 \node[graphicNode]  (panel) {\includegraphics[height=\panelheight]{content/code/img/movement_vs_bs_plot_fff_lamella4.png}};
-\node (anchor) at ([shift={(-1.0cm,4.0cm)}]panel.north east) {}; 
+\node (anchor) at ([shift={(-0.5cm,4.0cm)}]panel.north east) {}; 
+\begin{scope}[on background layer]
 \node[graphicNode] (key) {\includegraphics[height=\panelheight]{content/code/img/movement_vs_bs_plot_colorbar.png}};
+\end{scope}
 
@@
 \node[labelNode] {B};
-\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/thickness_by_intensity_vs_bs_plot_euc_lamella1.png}};
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/thickness_by_intensity_vs_bs_plot_euc_lamella1_lblaw.png}};
 \node (anchor) at ([shift={(-0.4cm,0.0cm)}]panel.north east) {}; 
-\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/thickness_by_intensity_vs_bs_plot_euc_lamella2.png}};
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/thickness_by_intensity_vs_bs_plot_euc_lamella2_lblaw.png}};
 \node (anchor) at ([shift={(-0.4cm,0.0cm)}]panel.north east) {}; 
-\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/thickness_by_intensity_vs_bs_plot_euc_lamella3.png}};
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/thickness_by_intensity_vs_bs_plot_euc_lamella3_lblaw.png}};
 \node (anchor) at ([shift={(-0.4cm,0.0cm)}]panel.north east) {}; 
-\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/thickness_by_intensity_vs_bs_plot_euc_lamella4.png}};
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/thickness_by_intensity_vs_bs_plot_euc_lamella4_lblaw.png}};
 
 \node (anchor) at ([shift={(0.0cm,-0.5cm)}]0.5,0 |- panel.south) {}; 
-\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/thickness_by_intensity_vs_bs_plot_fff_lamella1.png}};
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/thickness_by_intensity_vs_bs_plot_fff_lamella1_lblaw.png}};
 \node (anchor) at ([shift={(-0.4cm,0.0cm)}]panel.north east) {}; 
-\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/thickness_by_intensity_vs_bs_plot_fff_lamella2.png}};
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/thickness_by_intensity_vs_bs_plot_fff_lamella2_lblaw.png}};
 \node (anchor) at ([shift={(-0.4cm,0.0cm)}]panel.north east) {}; 
-\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/thickness_by_intensity_vs_bs_plot_fff_lamella3.png}};
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/thickness_by_intensity_vs_bs_plot_fff_lamella3_lblaw.png}};
 \node (anchor) at ([shift={(-0.4cm,0.0cm)}]panel.north east) {}; 
-\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/thickness_by_intensity_vs_bs_plot_fff_lamella4.png}};
-\node (anchor) at ([shift={(-1.0cm,4.0cm)}]panel.north east) {}; 
-\node[graphicNode] (key) {\includegraphics[height=\panelheight]{content/code/img/thickness_by_intensity_vs_bs_plot_colorbar.png}};
-
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/thickness_by_intensity_vs_bs_plot_fff_lamella4_lblaw.png}};
+\node (anchor) at ([shift={(-0.5cm,4.0cm)}]panel.north east) {}; 
+\begin{scope}[on background layer]
+\node[graphicNode] (key) {\includegraphics[height=\panelheight]{content/code/img/thickness_by_intensity_vs_bs_plot_colorbar_lblaw.png}};
+\end{scope}
+\node (anchor) at ([shift={(0.0cm,-1.0cm)}]0.5,0 |- panel.south) {}; 
+\node[labelNode] {C};
+\node[graphicNode] (panel) {\includegraphics[height=\panelheight]{content/code/img/matchrange_vs_thickness_plot.png}};
     \iftoggle{draft}{\draw[lightgray,step=1] (0,0) grid (\figwidth,\figheight);}{};

### 2022-11-14 elife_submission/manuscript.tex
Minor adjustments to submission

--- 2022-06-14 manuscript.tex
@@
 \urlstyle{same} % disable monospaced font for URLs
+\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
 \usepackage{graphicx}
@@
   }
+
+%% pandoc-tablenos: required package
+\usepackage{caption}
+
+%% pandoc-tablenos: environment to disable table caption prefixes
+\makeatletter
+\newcounter{tableno}
+\newenvironment{tablenos:no-prefix-table-caption}{
+    \let\oldthetable\thetable
+    \let\oldtheHtable\theHtable
+    \renewcommand{\thetable}{tableno:\thetableno}
+    \renewcommand{\theHtable}{tableno:\thetableno}
+    \stepcounter{tableno}
+    \captionsetup{labelformat=empty}
+
+}{
+    \captionsetup{labelformat=default}
+    \let\thetable\oldthetable
+    \let\theHtable\oldtheHtable
+    \addtocounter{table}{-1}
+
+}
+\makeatother
 \ifLuaTeX
@@
 
-  RNA Therapeutics Institute, University of Massachusetts Chan Medical School, Worcester, MA, USA; Howard Hughes Medical Institute, USA
+  RNA Therapeutics Institute, University of
+  Massachusetts Chan Medical School, Worcester, MA, USA; Howard Hughes
+  Medical Institute, USA
 \item
-  \textbf{Giulia Schiroli}
-  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.pdf}
+  \textbf{Giulia Schiroli} \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.pdf}
   \href{https://orcid.org/0000-0002-9812-8728}{0000-0002-9812-8728}
 
-  Center for Regenerative Medicine, Massachusetts General Hospital, Boston, MA, USA; Harvard Stem Cell Institute, Cambridge, MA, USA; Department of Stem Cell and Regenerative Biology, Harvard University, Cambridge, MA, USA
+  Center for Regenerative Medicine, Massachusetts
+  General Hospital, Boston, MA, USA; Harvard Stem Cell Institute,
+  Cambridge, MA, USA; Department of Stem Cell and Regenerative
+  Biology, Harvard University, Cambridge, MA, USA
 \item
-  \textbf{David Scadden}
-  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.pdf}
+  \textbf{David Scadden} \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.pdf}
   \href{https://orcid.org/0000-0001-9821-7133}{0000-0001-9821-7133}
 
-  Center for Regenerative Medicine, Massachusetts General Hospital, Boston, MA, USA; Harvard Stem Cell Institute, Cambridge, MA, USA; Department of Stem Cell and Regenerative Biology, Harvard University, Cambridge, MA, USA
+  Center for Regenerative Medicine, Massachusetts
+  General Hospital, Boston, MA, USA; Harvard Stem Cell Institute,
+  Cambridge, MA, USA; Department of Stem Cell and Regenerative
+  Biology, Harvard University, Cambridge, MA, USA
 \item
@@
 
-  RNA Therapeutics Institute, University of Massachusetts Chan Medical School, Worcester, MA, USA; Howard Hughes Medical Institute, USA
+  RNA Therapeutics Institute, University of
+  Massachusetts Chan Medical School, Worcester, MA, USA; Howard Hughes
+  Medical Institute, USA
 \end{itemize}
@@
 \leavevmode\vadjust pre{\hypertarget{correspondence}{}}%
-\includegraphics[width=0.16667in,height=0.16667in]{images/envelope.pdf} --- correspondence preferred via \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/issues}{GitHub Issues}.
-Otherwise, address correspondence to \href{mailto:johannes.elferich@umassmed.edu}{\nolinkurl{johannes.elferich@umassmed.edu}} and \href{mailto:niko@grigorieff.org}{\nolinkurl{niko@grigorieff.org}}.
+\includegraphics[width=0.16667in,height=0.16667in]{images/envelope.pdf} --- correspondence preferred via \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/issues}{GitHub
+Issues}.
+Otherwise, address correspondence to \href{mailto:johannes.elferich@umassmed.edu}{\nolinkurl{johannes.elferich@umassmed.edu}}
+and \href{mailto:niko@grigorieff.org}{\nolinkurl{niko@grigorieff.org}}.
 
@@
 
-A major goal of biological imaging is localization of biomolecules inside a cell. Fluorescence microscopy can localize biomolecules inside whole cells
-and tissues, but its ability to count biomolecules and accuracy of the spatial
-coordinates is limited by the wavelength of visible light. Cryo-electron
-microscopy (cryo-EM) provides highly accurate position and orientation
-information of biomolecules but is often confined to small fields of view inside
-a cell, limiting biological context. In this study we use a new data-acquisition
-scheme called ``Defocus-Corrected Large-Area cryo-EM'' (DeCo-LACE) to collect
-high-resolution images of entire sections (100 -- 200 nm thick lamellae)
+A major goal of biological imaging is localization of biomolecules
+inside a cell. Fluorescence microscopy can localize biomolecules inside
+whole cells and tissues, but its ability to count biomolecules and
+accuracy of the spatial coordinates is limited by the wavelength of
+visible light. Cryo-electron microscopy (cryo-EM) provides highly
+accurate position and orientation information of biomolecules but is
+often confined to small fields of view inside a cell, limiting
+biological context. In this study we use a new data-acquisition scheme
+called ``Defocus-Corrected Large-Area cryo-EM'' (DeCo-LACE) to collect
+high-resolution images of entire sections (100 -- 250 nm thick lamellae)
 of neutrophil-like mouse cells, representing 1-2\% of the total cellular
-volume.
-We use 2D template matching (2DTM) to determine localization and orientation of the large ribosomal subunit in these sections.
-These data provide ``maps'' of ribosomes across entire sections of mammalian cells.
-This high-throughput cryo-EM data collection approach together with 2DTM will advance visual proteomics and provide biological insight that cannot be obtained by other methods.
+volume. We use 2D template matching (2DTM) to determine localization and
+orientation of the large ribosomal subunit in these sections. These data
+provide ``maps'' of ribosomes across entire sections of mammalian cells.
+This high-throughput cryo-EM data collection approach together with 2DTM
+will advance visual proteomics and provide biological insight that
+cannot be obtained by other methods.
 
@@
 techniques a probe is physically attached to a molecule of interest that
-is able to be detected by its strong signal, such as a
-fluorescent molecule. In label-free techniques, the physical properties
-of molecules themselves are used for detection. An example for this is
-proteomics using mass-spectrometry {[}\protect\hyperlink{ref-tSXIKPl7}{1}{]}. The advantage
-of label-free techniques is that they can provide information over
-thousands of molecules, while label-dependent techniques offer highly specific
-information for a few molecules. in particular, spatial information is primarily achieved using label-dependent techniques, such as
-fluorescence microscopy {[}\protect\hyperlink{ref-VBmW7Aot}{2}{]}.
-
-Cryo-electron microscopy (cryo-EM) has the potential to directly visualize the
-arrangement of atoms that compose biomolecules inside of cells, thereby
-allowing label-free detection with high spatial accuracy. This has been
-called ``visual proteomics'' {[}\protect\hyperlink{ref-tGQ6TSUo}{3}{]}. Since cryo-EM
-requires thin samples (\textless500nm), imaging of biomolecules inside cells is
-restricted to small organisms, thin regions of cells, or samples that
-have been suitably thinned. Thinning can be achieved either by
-mechanical sectioning {[}\protect\hyperlink{ref-g8QavfwP}{4}{]} or by
-milling using a focused ion beam (FIB) {[}\protect\hyperlink{ref-16IhS1Nc4}{5}{]}. This complex workflow
-leads to a low throughput of cryo-EM imaging of cells and is further
-limited by the fact that at the required magnifications, typical fields
-of view (FOV) are very small compared to mammalian cells, and the FOV
-achieved by label-dependent techniques such as fluorescence light microscopy. The
-predominant cryo-EM technique for the localization of biomolecules of
-defined size and shape inside cells is cryo-electron tomography {[}\protect\hyperlink{ref-Rksh2dxu}{6}{]}. However, the requirement of a tilt series at
-every imaged location and subsequent image alignment, severely limits
-the throughput for molecular localization.
+is able to be detected by its strong signal, such as a fluorescent
+molecule. In label-free techniques, the physical properties of molecules
+themselves are used for detection. An example for this is proteomics
+using mass-spectrometry {[}\protect\hyperlink{ref-tSXIKPl7}{1}{]}. The advantage of
+label-free techniques is that they can provide information over
+thousands of molecules, while label-dependent techniques offer highly
+specific information for a few molecules. in particular, spatial
+information is primarily achieved using label-dependent techniques, such
+as fluorescence microscopy {[}\protect\hyperlink{ref-VBmW7Aot}{2}{]}.
+
+Cryo-electron microscopy (cryo-EM) has the potential to directly
+visualize the arrangement of atoms that compose biomolecules inside of
+cells, thereby allowing label-free detection with high spatial accuracy.
+This has been called ``visual proteomics'' {[}\protect\hyperlink{ref-tGQ6TSUo}{3}{]}. Since
+cryo-EM requires thin samples (\textless500nm), imaging of biomolecules inside
+cells is restricted to small organisms, thin regions of cells, or
+samples that have been suitably thinned. Thinning can be achieved either
+by mechanical sectioning {[}\protect\hyperlink{ref-g8QavfwP}{4}{]} or by
+milling using a focused ion beam (FIB) {[}\protect\hyperlink{ref-16IhS1Nc4}{5}{]}.
+This complex workflow leads to a low throughput of cryo-EM imaging of
+cells and is further limited by the fact that at the required
+magnifications, typical fields of view (FOV) are very small compared to
+mammalian cells, and the FOV achieved by label-dependent techniques such
+as fluorescence light microscopy. The predominant cryo-EM technique for
+the localization of biomolecules of defined size and shape inside cells
+is cryo-electron tomography {[}\protect\hyperlink{ref-Rksh2dxu}{6}{]}. However,
+the requirement of a tilt series at every imaged location and subsequent
+image alignment, severely limits the throughput for molecular
+localization.
 
@@
 ``fingerprint'' in single projection using ``2D template-matching'' (2DTM)
-{[}\protect\hyperlink{ref-Ynb3IP6I}{7},\protect\hyperlink{ref-18KGpXYPE}{8},\protect\hyperlink{ref-10bXZuF3G}{9}{]}. In this
-method, a 3D model of a biomolecule is used as a template to find 2D
-projections that match the molecules visible in the electron
+{[}\protect\hyperlink{ref-Ynb3IP6I}{7},\protect\hyperlink{ref-18KGpXYPE}{8},\protect\hyperlink{ref-10bXZuF3G}{9}{]}.
+In this method, a 3D model of a biomolecule is used as a template to
+find 2D projections that match the molecules visible in the electron
 micrographs. This method requires a projection search on a fine angular
@@
 method can be used to calculate complete 3D coordinates and orientations
-of a biomolecule in a cellular sample
-{[}\protect\hyperlink{ref-18KGpXYPE}{8}{]}.
-
-Here we apply 2DTM of the ribosome large subunit (LSU) to a conditionally immortalized \emph{mus musculus} (mouse) cell line that gives rise to functional mature neutrophils {[}\protect\hyperlink{ref-1B9Vt9eYu}{10}{]}.
-We chose these
-cells because genetic defects in the ribosome machinery often leads to
-hematopoietic disease {[}\protect\hyperlink{ref-gRoY21jY}{11}{]} and direct quantification of
-ribosome location, number and conformational states in hematopoietic cells could
-lead to new insight into hematopoietic disease {[}\protect\hyperlink{ref-KAJ7221k}{12}{]}.
-To increase the amount of collected data and to provide unbiased sampling of the
-whole lamella, we devised a new data-acquisition scheme, ``Defocus-Corrected
-Large Area Cryo-Electron microscopy'' (DeCo-LACE). 2DTM allows us to test whether
-aberrations caused by large beam-image shifts and highly condensed beams
-deteriorate the high-resolution signal. We find that these aberrations do not
-impede LSU detection by 2DTM. The resulting data provide a description of
-ribosome distribution in an entire lamella, which represent 1-2\% of the cellular
-volume. We find a highly heterogeneous density of ribosomes within the cell.
-Analysis of the throughput in this method suggests that for the foreseeable
-future computation will be the bottleneck for visual proteomics.
+of a biomolecule in a cellular sample {[}\protect\hyperlink{ref-18KGpXYPE}{8}{]}.
+
+Here we apply 2DTM of the ribosome large subunit (LSU) to a
+conditionally immortalized \emph{mus musculus} (mouse) cell line that gives
+rise to functional mature neutrophils {[}\protect\hyperlink{ref-1B9Vt9eYu}{10}{]}.
+We chose these cells because genetic defects in the ribosome machinery
+often leads to hematopoietic disease {[}\protect\hyperlink{ref-gRoY21jY}{11}{]} and
+direct quantification of ribosome location, number and conformational
+states in hematopoietic cells could lead to new insight into
+hematopoietic disease {[}\protect\hyperlink{ref-KAJ7221k}{12}{]}. To increase the
+amount of collected data and to provide unbiased sampling of the whole
+lamella, we devised a new data-acquisition scheme, ``Defocus-Corrected
+Large Area Cryo-Electron microscopy'' (DeCo-LACE). 2DTM allows us to test
+whether aberrations caused by large beam-image shifts and highly
+condensed beams deteriorate the high-resolution signal. We find that
+these aberrations do not impede LSU detection by 2DTM. The resulting
+data provide a description of ribosome distribution in an entire
+lamella, which represent 1-2\% of the cellular volume. We find a highly
+heterogeneous density of ribosomes within the cell. Analysis of the
+throughput in this method suggests that for the foreseeable future
+computation will be the bottleneck for visual proteomics.
 
@@
 
-FIB-milled \emph{Saccharomyces cerevisiae} (yeast) cells are sufficiently well preserved to permit localization of 60S ribosomal subunits with 2DTM {[}\protect\hyperlink{ref-T1Qr0xyP}{13}{]}.
-Due to the larger size of mammalian cells compared to yeast cells, it was unclear whether plunge freezing would be adequate to produce vitreous ice across the whole volume of the cell.
-To test this we prepared cryo-lamellae of mouse neutrophil cells.
-A low magnification image
-of a representative lamella clearly shows cellular features consistent with a
-neutrophile-like phenotype, mainly a segmented nucleus and a plethora of
-membrane-organelles, corresponding to the granules and secretory vesicles of
-neutrophils (Fig. {[}\ref{fig:initmatching}{]}A). We then proceeded to acquire
-micrographs on this lamella with a defocus of 0.5-1.0 μm, 30 e\textsuperscript{-}/Å\(^2\)/s
-exposure and 1.76 Å pixel size. We manually selected multiple locations in the
-lamella and acquired micrographs using standard low-dose techniques where
-focusing is performed on a sacrificial area. The resulting micrographs showed
-smooth bilayered membranes and no signs of crystalline ice (Fig.
-{[}\ref{fig:initmatching}{]}C,D), indicating successful vitrification throughout the
-lamella.
-
-We used an atomic model of the 60S mouse ribosomal subunit (6SWA) for 2DTM {[}\protect\hyperlink{ref-sbkam02a}{14}{]}. In a
-subset of images, the distribution of cross-correlation scores significantly
-exceeded the distribution expected from images devoid of detectable targets. In the
-resulting scaled maximum-intensity projections (MIPs), clear peaks with SNR
-values up to 10 were apparent (Fig. {[}\ref{fig:initmatching2}{]}A). Using a
-threshold criterion to select significant targets (see Methods), we found that in
-images of cytosolic compartments there were 10-500 ribosomes within one micrograph
-(Fig. {[}\ref{fig:initmatching}{]}B-E). Notably, we found no targets in areas
-corresponding to the nucleus (Fig. {[}\ref{fig:initmatching}{]}B) or mitochondria
-(Fig. \protect\hyperlink{fig:initmatching}{1}D). In the cytoplasm, we found a highly variable
-number of targets, only \textasciitilde{} 50 in some exposures (Fig. {[}\ref{fig:initmatching}{]}E) and
-up to 500 in others (Fig.
-{[}\ref{fig:initmatching}{]}C).
-However, it is unclear whether this ten-fold difference in local ribosome concentration is due to technical variation, such as sample thickness, or biological variation.
-To differentiate between the two we reasoned it was important to not manually choose imaging regions and to collect larger amounts of data.
-We therefore set out to collect cryo-EM data for 2DTM from mammalian cell lamellae in a high-throughput unbiased fashion.
+FIB-milled \emph{Saccharomyces cerevisiae} (yeast) cells are sufficiently
+well preserved to permit localization of 60S ribosomal subunits with
+2DTM {[}\protect\hyperlink{ref-T1Qr0xyP}{13}{]}. Due to the larger size of
+mammalian cells compared to yeast cells, it was unclear whether plunge
+freezing would be adequate to produce vitreous ice across the whole
+volume of the cell. To test this we prepared cryo-lamellae of mouse
+neutrophil cells. A low magnification image of a representative lamella
+clearly shows cellular features consistent with a neutrophile-like
+phenotype, mainly a segmented nucleus and a plethora of
+membrane-organelles, corresponding to the granules and secretory
+vesicles of neutrophils (Fig. {[}\ref{fig:initmatching}{]}A). We then proceeded
+to acquire micrographs on this lamella with a defocus of 0.5-1.0 μm, 30
+e\textsuperscript{-}/Å\(^2\)/s exposure and 1.76 Å pixel size. We manually selected
+multiple locations in the lamella and acquired micrographs using
+standard low-dose techniques where focusing is performed on a
+sacrificial area. The resulting micrographs showed smooth bilayered
+membranes and no signs of crystalline ice (Fig. {[}\ref{fig:initmatching}{]}C,D),
+indicating successful vitrification throughout the lamella.
+
+We used an atomic model of the 60S mouse ribosomal subunit (6SWA) for
+2DTM {[}\protect\hyperlink{ref-sbkam02a}{14}{]}. In a subset of images, the
+distribution of cross-correlation scores significantly exceeded the
+distribution expected from images devoid of detectable targets. In the
+resulting scaled maximum-intensity projections (MIPs), clear peaks with
+SNR values up to 10 were apparent (Fig. {[}\ref{fig:initmatching2}{]}A). Using a
+threshold criterion to select significant targets (see Methods), we
+found that in images of cytosolic compartments there were 10-500
+ribosomes within one micrograph (Fig. {[}\ref{fig:initmatching}{]}B-E). Notably,
+we found no targets in areas corresponding to the nucleus (Fig.
+{[}\ref{fig:initmatching}{]}B) or mitochondria (Fig. \protect\hyperlink{fig:initmatching}{1}D). In
+the cytoplasm, we found a highly variable number of targets, only \textasciitilde{} 50
+in some exposures (Fig. {[}\ref{fig:initmatching}{]}E) and up to 500 in others
+(Fig. {[}\ref{fig:initmatching}{]}C). However, it is unclear whether this
+ten-fold difference in local ribosome concentration is due to technical
+variation, such as sample thickness, or biological variation. To
+differentiate between the two we reasoned it was important to not
+manually choose imaging regions and to collect larger amounts of data.
+We therefore set out to collect cryo-EM data for 2DTM from mammalian
+cell lamellae in a high-throughput unbiased fashion.
 
@@
 
-In order to obtain high-resolution data from complete lamellae, we developed a new
-approach for data collection. This approach uses three key strategies: (1) every
-electron that exposes a fresh area of the sample is collected on the camera (2)
-image shift is used to precisely and quickly raster the surface of a lamella and
-(3) focusing is done without using a sacrificial area (Fig. {[}\ref{fig:approach}{]}A).
-
-To ensure that every electron exposing a fresh area of the sample is captured by
-the detector, we adjusted the electron beam size to be entirely contained by the
-detector area. During canonical low-dose imaging, the microscope is configured so
-that the focal plane is identical to the eucentric plane of the specimen stage.
-This leaves the C2 aperture out of focus, resulting in ripples at the edge of
-the beam (Fig. {[}\ref{fig:approach}{]}D). While these ripples are low-resolution
-features that likely do not interfere with 2DTM {[}\protect\hyperlink{ref-Ynb3IP6I}{7}{]}, we also tested data
-collection under conditions where the C2 aperture is in focus (``fringe-free'',
-Fig. {[}\ref{fig:approach}{]}E) {[}\protect\hyperlink{ref-wsFP5c54}{15}{]}.
-
-We then centered a lamella on the optical axis of the microscope and used the
-image shift controls of the microscope to systematically scan the whole surface
-of the lamella in a hexagonal pattern (Fig. {[}\ref{fig:approach}{]}A,C). Instead of
-focusing on a sacrificial area, we determined the defocus from every exposure
-after it was taken. The defocus was then adjusted based on the difference
-between desired and measured defocus (Fig. {[}\ref{fig:approach}{]}B). Since we used a
-serpentine pattern for data collection, every exposure was close to the previous
-exposure, making large changes in the defocus unlikely. Furthermore, we started
-our acquisition pattern on the platinum deposition edge to make sure that the
-initial exposure where the defocus was not yet adjusted did not contain any
-biologically relevant information.
+In order to obtain high-resolution data from complete lamellae, we
+developed a new approach for data collection. This approach uses three
+key strategies: (1) every electron that exposes a fresh area of the
+sample is collected on the camera (2) image shift is used to precisely
+and quickly raster the surface of a lamella and (3) focusing is done
+without using a sacrificial area (Fig. {[}\ref{fig:approach}{]}A).
+
+To ensure that every electron exposing a fresh area of the sample is
+captured by the detector, we adjusted the electron beam size to be
+entirely contained by the detector area. During canonical low-dose
+imaging, the microscope is configured so that the focal plane is
+identical to the eucentric plane of the specimen stage. This leaves the
+C2 aperture out of focus, resulting in ripples at the edge of the beam
+(Fig. {[}\ref{fig:approach}{]}D). While these ripples are low-resolution features
+that likely do not interfere with 2DTM {[}\protect\hyperlink{ref-Ynb3IP6I}{7}{]}, we
+also tested data collection under conditions where the C2 aperture is in
+focus (``fringe-free'', Fig. {[}\ref{fig:approach}{]}E)
+{[}\protect\hyperlink{ref-wsFP5c54}{15}{]}.
+
+We then centered a lamella on the optical axis of the microscope and
+used the image shift controls of the microscope to systematically scan
+the whole surface of the lamella in a hexagonal pattern (Fig.
+{[}\ref{fig:approach}{]}A,C). Instead of focusing on a sacrificial area, we
+determined the defocus from every exposure after it was taken. The
+defocus was then adjusted based on the difference between desired and
+measured defocus (Fig. {[}\ref{fig:approach}{]}B). Since we used a serpentine
+pattern for data collection, every exposure was close to the previous
+exposure, making large changes in the defocus unlikely. Furthermore, we
+started our acquisition pattern on the platinum deposition edge to make
+sure that the initial exposure where the defocus was not yet adjusted
+did not contain any biologically relevant information.
 
 We used this strategy to collect data on eight lamellae, four using the
-eucentric focus condition, hereafter referred to as Lamella\textsubscript{EUC}, and four using
-the fringe-free condition, hereafter referred to as Lamella\textsubscript{FFF}(Fig.
-{[}\ref{fig:assembly}{]} A+D, Fig.
-{[}\ref{fig:lamella_images}{]}A). We were able to collect data with a highly
-consistent defocus of 800 nm (Fig. {[}\ref{fig:approach}{]}F), both in the eucentric
-focus and fringe-free focus condition. To ensure that data were collected
-consistently, we mapped defocus values as a function of the applied image shift
-(Fig. {[}\ref{fig:lamella_spatial_info}{]}A). This demonstrated that the defocus was
-consistent across a lamella, except for rare outliers and in images containing
-contamination. We also plotted the measured objective astigmatism of each
-lamella and found that it varies with the applied image shift, becoming more
-astigmatic mostly due to image shift in the x direction (Fig.
-{[}\ref{fig:lamella_spatial_info}{]}B). While approaches exist to correct for this
-during the data collection {[}\protect\hyperlink{ref-APSL9LmU}{16}{]}, we opted to not use these approaches in our
-initial experiments. We reasoned that because 2DTM depends on high-resolution
-information, this would be an excellent test of how much these aberration affect
-imaging.
-
-We assembled the tile micrographs into a montage using the image-shift values
-and the SerialEM calibration followed by cross-correlation based refinement (see
-Methods). In the resulting montages, the same cellular features visible in the
-overview images are apparent (Fig. {[}\ref{fig:assembly}{]}B+E, Fig. {[}\ref{fig:lamella_images}{]}B), however
-due to the high magnification and low defocus many more details, such as the
-membrane bilayer separation, can be observed (Fig. {[}\ref{fig:assembly}{]}C+F). For montages collected using the
-eucentric condition, there are clearly visible fringes at the edges between the
-tiles (Fig. {[}\ref{fig:assembly}{]}C), which are absent in the fringe-free focus montages (Fig. {[}\ref{fig:assembly}{]}F). In our analysis
-below, we show that these fringes do not impede target detection by 2DTM, making
-them primarily an aesthetic issue. We also note that the tiling
-pattern is visible in the montages (Fig. {[}\ref{fig:assembly}{]}B+E), which we believe is due to the non-linear
-behavior of the K3 camera since we can observe these shading artifacts in micrographs of a condensed beam over vacuum (Fig. {[}\ref{fig:gain}{]}).
-
-The montages show membrane vesicles and granules with highly variable sizes and
-density. We found that a substantial number of granules, which are characterized by higher
-density inside the the surrounding cytosol {[}\protect\hyperlink{ref-xE2EhAcH}{17}{]}, seemed to contain a membrane-enclosed inclusion with density similar to
-the surrounding cytosol (Fig. {[}\ref{fig:lamella_images}{]}C) and could therefore be formed
-by inward budding of the granule membrane. These granules were
-150-300 nm in diameter and the inclusions were 100-200 nm in diameter. Based on
-these dimensions the granules are either azurophil or specific granules {[}\protect\hyperlink{ref-xE2EhAcH}{17}{]}. To our
-knowledge, these inclusion have not been described in granulocytes and are
-further described and discussed below.
+eucentric focus condition, hereafter referred to as Lamella\textsubscript{EUC}, and
+four using the fringe-free condition, hereafter referred to as
+Lamella\textsubscript{FFF}(Fig. {[}\ref{fig:assembly}{]} A+D, Fig. {[}\ref{fig:lamella_images}{]}A). We
+were able to collect data with a highly consistent defocus of 800 nm
+(Fig. {[}\ref{fig:approach}{]}F), both in the eucentric focus and fringe-free
+focus condition. To ensure that data were collected consistently, we
+mapped defocus values as a function of the applied image shift (Fig.
+{[}\ref{fig:lamella_spatial_info}{]}A). This demonstrated that the defocus was
+consistent across a lamella, except for rare outliers and in images
+containing contamination. We also plotted the measured objective
+astigmatism of each lamella and found that it varies with the applied
+image shift, becoming more astigmatic mostly due to image shift in the x
+direction (Fig. {[}\ref{fig:lamella_spatial_info}{]}B). While approaches exist to
+correct for this during the data collection
+{[}\protect\hyperlink{ref-APSL9LmU}{16}{]}, we opted to not use these approaches
+in our initial experiments. We reasoned that because 2DTM depends on
+high-resolution information, this would be an excellent test of how much
+these aberration affect imaging.
+
+We assembled the tile micrographs into a montage using the image-shift
+values and the SerialEM calibration followed by cross-correlation based
+refinement (see Methods). In the resulting montages, the same cellular
+features visible in the overview images are apparent (Fig.
+{[}\ref{fig:assembly}{]}B+E, Fig. {[}\ref{fig:lamella_images}{]}B), however due to the
+high magnification and low defocus many more details, such as the
+membrane bilayer separation, can be observed (Fig. {[}\ref{fig:assembly}{]}C+F).
+For montages collected using the eucentric condition, there are clearly
+visible fringes at the edges between the tiles (Fig. {[}\ref{fig:assembly}{]}C),
+which are absent in the fringe-free focus montages (Fig.
+{[}\ref{fig:assembly}{]}F). In our analysis below, we show that these fringes do
+not impede target detection by 2DTM, making them primarily an aesthetic
+issue. We also note that the tiling pattern is visible in the montages
+(Fig. {[}\ref{fig:assembly}{]}B+E), which we believe is due to the non-linear
+behavior of the K3 camera since we can observe these shading artifacts
+in micrographs of a condensed beam over vacuum (Fig. {[}\ref{fig:gain}{]}).
+
+The montages show membrane vesicles and granules with highly variable
+sizes and density. We found that a substantial number of granules, which
+are characterized by higher density inside the the surrounding cytosol
+{[}\protect\hyperlink{ref-xE2EhAcH}{17}{]}, seemed to contain a membrane-enclosed
+inclusion with density similar to the surrounding cytosol (Fig.
+{[}\ref{fig:lamella_images}{]}C) and could therefore be formed by inward budding
+of the granule membrane. These granules were 150-300 nm in diameter and
+the inclusions were 100-200 nm in diameter. Based on these dimensions
+the granules are either azurophil or specific granules
+{[}\protect\hyperlink{ref-xE2EhAcH}{17}{]}. To our knowledge, these inclusion have not
+been described in granulocytes and are further described and discussed
+below.
 
@@
 
-In our initial attempts of using 2DTM on micrographs acquired with the DeCo-LACE
-protocol, we did not observe any SNR peaks above threshold using the large
-subunit of the mouse ribosome (Fig. {[}\ref{fig:crop_unblur}{]}A). We reasoned that
-the edges of the beam might interfere with motion-correction of the movies as
-they represent strong low-resolution features that do not move with the sample.
-When we cropped the movie frames to exclude the beam edges, the estimated amount
-of motion increased (Fig. {[}\ref{fig:crop_unblur}{]}B), consistent with successful
-tracking of sample motion. Furthermore, in the motion-corrected average we could
-identify significant SNR peaks (Fig. {[}\ref{fig:crop_unblur}{]}B), confirming the
-high sensitivity of 2DTM to the presence of high-resolution signal preserved in
-the images by the motion correction. To streamline data processing, we
-implemented a function in unblur to consider only a defined central area of a
-movie for estimation of sample motion, while still averaging the complete movie
-frames (Fig. {[}\ref{fig:crop_unblur}{]}C). Using this approach, we motion-corrected
-all tiles in the eight lamellae and found consistently total motion below 1 Å
-per frame (Fig. {[}\ref{fig:lamella_motion_thickness}{]} A). In some lamellae we
-found increased motion in the lamella center, which indicates areas of variable
-mechanical stability within FIB-milled lamellae. In some micrographs we also
-observed that the beam edges gave rise to artifacts in the MIP and numerous
-false-positive detections at the edge of the illuminated area (Fig. {[}\ref{fig:crop_unblur}{]}D). A
-similar phenomenon was observed on isolated ``hot'' pixels in unilluminated areas.
-To overcome this issue we implemented a function in unblur to replace
-dark areas in the micrograph with Gaussian noise (see Methods), with
-mean and standard deviation matching the illuminated portion of the micrograph
-(Fig. {[}\ref{fig:crop_unblur}{]}D+E). Together, these pre-processing steps enabled us to perform 2DTM on
-all tiles of the eight lamellae.
+In our initial attempts of using 2DTM on micrographs acquired with the
+DeCo-LACE protocol, we did not observe any SNR peaks above threshold
+using the large subunit of the mouse ribosome (Fig.
+{[}\ref{fig:crop_unblur}{]}A). We reasoned that the edges of the beam might
+interfere with motion-correction of the movies as they represent strong
+low-resolution features that do not move with the sample. When we
+cropped the movie frames to exclude the beam edges, the estimated amount
+of motion increased (Fig. {[}\ref{fig:crop_unblur}{]}B), consistent with
+successful tracking of sample motion. Furthermore, in the
+motion-corrected average we could identify significant SNR peaks (Fig.
+{[}\ref{fig:crop_unblur}{]}B), confirming the high sensitivity of 2DTM to the
+presence of high-resolution signal preserved in the images by the motion
+correction. To streamline data processing, we implemented a function in
+unblur to consider only a defined central area of a movie for estimation
+of sample motion, while still averaging the complete movie frames (Fig.
+{[}\ref{fig:crop_unblur}{]}C). Using this approach, we motion-corrected all tiles
+in the eight lamellae and found consistently total motion below 1 Å per
+frame (Fig. {[}\ref{fig:lamella_motion_thickness}{]} A). In some lamellae we
+found increased motion in the lamella center, which indicates areas of
+variable mechanical stability within FIB-milled lamellae. In some
+micrographs we also observed that the beam edges gave rise to artifacts
+in the MIP and numerous false-positive detections at the edge of the
+illuminated area (Fig. {[}\ref{fig:crop_unblur}{]}D). A similar phenomenon was
+observed on isolated ``hot'' pixels in unilluminated areas. To overcome
+this issue we implemented a function in unblur to replace dark areas in
+the micrograph with Gaussian noise (see Methods), with mean and standard
+deviation matching the illuminated portion of the micrograph (Fig.
+{[}\ref{fig:crop_unblur}{]}D+E). Together, these pre-processing steps enabled us
+to perform 2DTM on all tiles of the eight lamellae.
 
 We used the tile positions to calculate the positions of the detected
-LSUs in the lamellae (Fig. {[}\ref{fig:matching_euc}{]}A, Fig. {[}\ref{fig:matching_fff}{]}A, Movie 1, Movie 2). Overlaying these positions of the lamellae montages reveals LSU
-distribution throughout the FIB-milled slices of individual cells. Consistent with prior observations imaging selected views in yeast {[}\protect\hyperlink{ref-T1Qr0xyP}{13}{]}, organelles
-like the nucleus and mitochondria only showed sporadic targets detected with low
-SNRs, consistent with the estimated false-positive rate of one per tile. For
-each detected target we also calculated the Z positions from the individual
-estimated defocus and defocus offset for each tile. When viewed from the side,
-the ribosome positions therefore show the slight tilts of the lamellae relative
-to the microscope frame of reference (Fig. {[}\ref{fig:matching_euc}{]}B, Fig.
-{[}\ref{fig:matching_fff}{]}B, Movie 1, Movie 2). Furthermore, the side views indicated that lamellae
-were thinner at the leading edge. Indeed, when plotting the transmitted beam
-intensities in individual tiles as a function of beam image-shift, we observed
-substantially higher intensities at the leading edge (Fig. {[}\ref{fig:lamella_motion_thickness}{]}B), which in energy-filtered
-TEM indicates a thinner sample {[}\protect\hyperlink{ref-17IP4Lhz1}{18}{]}. Even though we prepared the lamellae
-with the ``overtilt'' approach {[}\protect\hyperlink{ref-hr3dyUeI}{19}{]}, this means that LSU densities across
-the lamellae can be skewed by a change in thickness, and better sample
-preparation methods are needed to generate more even samples.
-
-As described in {[}\protect\hyperlink{ref-Ynb3IP6I}{7}{]} the 2DTM SNR threshold for detecting a target is chosen to result in one false positive detection per image searched.
-We would therefore expect to find one false positive detection per tile.
-We reasoned that the large nuclear area imaged by DeCo-LACE could be used to test whether this assumption is true.
-In the 670 tiles containing exclusively nucleus (as manually annotated from the overview image) we detected 247 targets, making the false-positive rate more than twofold lower than expected.
-Since earlier work shows that 2DTM with the LSU can produce matches to nuclear ribosome biogenesis intermediates {[}\protect\hyperlink{ref-T1Qr0xyP}{13}{]}, this could even be an overestimate of the false-positive rate.
-This suggests that the detection threshold could be even lower, which is an area of ongoing research.
+LSUs in the lamellae (Fig. {[}\ref{fig:matching_euc}{]}A, Fig.
+{[}\ref{fig:matching_fff}{]}A, Fig. {[}\ref{fig:matching_euc}{]}-video 1, Fig.
+{[}\ref{fig:matching_fff}{]}-video 1). Overlaying these positions of
+the lamellae montages reveals LSU distribution throughout the FIB-milled
+slices of individual cells. Consistent with prior observations imaging
+selected views in yeast {[}\protect\hyperlink{ref-T1Qr0xyP}{13}{]}, organelles
+like the nucleus and mitochondria only showed sporadic targets detected
+with low SNRs, consistent with the estimated false-positive rate of one
+per tile. For each detected target we also calculated the Z positions
+from the individual estimated defocus and defocus offset for each tile.
+When viewed from the side, the ribosome positions therefore show the
+slight tilts of the lamellae relative to the microscope frame of
+reference (Fig. {[}\ref{fig:matching_euc}{]}B, Fig.
+{[}\ref{fig:matching_fff}{]}B, 
+Fig. {[}\ref{fig:matching_euc}{]}-video 1, Fig.
+{[}\ref{fig:matching_fff}{]}-video 1). Furthermore, the side views indicated that lamellae were
+thinner at the leading edge. To confirm this we estimated the ice
+thickness in individual tiles using the Beer-Lambert law
+{[}\protect\hyperlink{ref-17IP4Lhz1}{18}{]} with 322 nm as coefficient
+{[}\protect\hyperlink{ref-17IP4Lhz1}{18}{]} (Fig.
+{[}\ref{fig:lamella_motion_thickness}{]}B). We found that the thickness of the
+lamellae varied between 100 and 250 nm, with consistently thinner ice at
+the leading edge even though we prepared the lamellae with the
+``overtilt'' approach {[}\protect\hyperlink{ref-hr3dyUeI}{19}{]}. To further confirm
+the relationship of the range in Z-positions of detections and sample
+thickness we plotted the range in Z-positions as a function of the
+estimated sample thickness (Fig. {[}\ref{fig:lamella_motion_thickness}{]}C). For
+most tiles, the apparent thickness of LSU detections was at least 70 nm
+less than the estimated sample thickness, indicating that no detections
+were being made within 35 nm of the lamella edge. It is possible that
+this is caused by sample damage during FIB-milling as similar values for
+damaged areas in FIB-milled lamellae have been estimated from
+sub-tomogram averaging {[}\protect\hyperlink{ref-SDMGf7aG}{20}{]}. This means that
+LSU detections across the lamellae can be skewed by a change in
+thickness and sample damage. Therefore, better sample preparation
+methods together with a better understanding of the damage to the sample
+during FIB-milling are needed to accurately quantify molecular
+concentrations.
+
+As described in {[}\protect\hyperlink{ref-Ynb3IP6I}{7}{]} the 2DTM SNR threshold for
+detecting a target is chosen to result in one false positive detection
+per image searched. We would therefore expect to find one false positive
+detection per tile. We reasoned that the large nuclear area imaged by
+DeCo-LACE could be used to test whether this assumption is true. In the
+670 tiles containing exclusively nucleus (as manually annotated from the
+overview image) we detected 247 targets, making the false-positive rate
+more than twofold lower than expected. Since earlier work shows that
+2DTM with the LSU can produce matches to nuclear ribosome biogenesis
+intermediates {[}\protect\hyperlink{ref-T1Qr0xyP}{13}{]}, this could even be an
+overestimate of the false-positive rate. This suggests that the
+detection threshold could be even lower, which is an area of ongoing
+research.
 
@@
 ring-like structures (Fig. {[}\ref{fig:matching_euc}{]}E), potentially indicating
-circularized mRNAs {[}\protect\hyperlink{ref-cie13Q8F}{20}{]}. While ribosomes were for the most part excluded
-from the numerous granules observed in the cytoplasm, in some cases we observed
-clusters of LSUs in the inclusions of double-membraned granules
-described earlier (Fig. {[}\ref{fig:matching_euc}{]}F, Fig. {[}\ref{fig:matching_fff}{]}D,E). It is, in principle, possible that these targets are situated above or
-below the imaged granules, since the granule positions in z cannot be determined
-using 2D projections. However, in the case of Fig. {[}\ref{fig:matching_fff}{]}E, the
-detected LSUs span the whole lamella in the z direction (Fig. {[}\ref{fig:matching_fff}{]}F), while positions
-above or below a granule would result in LSUs situated exlusively at the
-top or bottom of the lamella. This is consistent with the earlier hypothesis that the inclusions are of
-cytoplasmic origin.
+circularized mRNAs {[}\protect\hyperlink{ref-cie13Q8F}{21}{]}. While ribosomes were for the most
+part excluded from the numerous granules observed in the cytoplasm, in
+some cases we observed clusters of LSUs in the inclusions of
+double-membraned granules described earlier (Fig. {[}\ref{fig:matching_euc}{]}F,
+Fig. {[}\ref{fig:matching_fff}{]}D,E). It is, in principle, possible that these
+targets are situated above or below the imaged granules, since the
+granule positions in z cannot be determined using 2D projections.
+However, in the case of Fig. {[}\ref{fig:matching_fff}{]}E, the detected LSUs
+span the whole lamella in the z direction (Fig. {[}\ref{fig:matching_fff}{]}F),
+while positions above or below a granule would result in LSUs situated
+exclusively at the top or bottom of the lamella. This is consistent with
+the earlier hypothesis that the inclusions are of cytoplasmic origin.
 
@@
 
-Within the eight lamellae we found different numbers of detected targets, ranging from 1089 to 6433 per lamella (Fig.
-{[}\ref{fig:matching_stat}{]}A). Lamella\textsubscript{EUC} 1 had the most detected targets, but also has
-the largest surface area and contained cytoplasm from two cells. Lamella\textsubscript{FFF} 4
-had the fewest detected targets, but this particular lamella was dominated by a
-circular section of the nucleus, with only small pockets of cytoplasm (Fig.
-{[}\ref{fig:lamella_images}{]}). In an attempt to normalize for these differences in
-area containing cytoplasm, we compared the number of detected targets per tile in
-tiles that contained more than one target, which should exclude tiles with
-non-cytosolic content (Fig. {[}\ref{fig:matching_stat}{]}B). While this measure had
-less variability, there were still differences. Lamella\textsubscript{EUC} 4 had not only the
-fewest targets, but also the lowest density, which could be due to this lamella being the
-thinnest, or due to it sectioning the cell in an area with a lower concentration of
-ribosomes. Lamella\textsubscript{FFF} 3 had a substantially higher number of ribosomes per
-tile. Since all of these lamellae were made from a cell-line under identical
-conditions, this underscores the necessity to collect data from large numbers of
-lamellae to overcome the inherent variability. When comparing the distribution of
-scores between lamellae, we found them to be fairly comparable with median
-SNRs ranging from 8.7 to 9.7 (Fig. {[}\ref{fig:matching_stat}{]}C). Lamella\textsubscript{EUC} 1 had slightly lower scores compared
-to
-the rest, potentially due to its large size and connected mechanical instability
-during imaging. Overall, we did not observe differences in the number or SNR of
-detected targets between eucentric or fringe-free illumination conditions that
-were bigger than the observed inter-lamella variability.
-
-Since the SNR values of 2DTM are highly sensitive to image quality, we reasoned
-we could use them to verify that DeCo-LACE does not introduce a systematic loss
-of image quality. We considered non-parallel illumination introduced by the
-unusually condensed beam and uncharacterized aberrations near the beam
-periphery. When plotting the SNR values of detected targets in all eight
-lamellae as a function of their location in the tiles, we found uniformly high
-SNR values throughout the illuminated areas for both eucentric and fringe-free
-focus illumination, demonstrating that both illumination schemes are suitable
-for DeCo-LACE (Fig. {[}\ref{fig:matching_stat}{]}D).
-
-We also wondered whether large image shifts would lead to aberrations due to
-astigmatism or beam tilt {[}\protect\hyperlink{ref-APSL9LmU}{16}{]}. We reasoned that if
-that was the case the number of detected targets should be highest in the center of the
-lamella where the applied beam image-shift is 0. Instead, we observed that in
-both eucentric and fringe-free focus conditions more targets were detected at the
-``back'' edge of the lamella (Fig. {[}\ref{fig:matching_stat}{]}E{]}). This may be due to the center of the cell being predominantly
-occupied by the nucleus, despite its segmentation in neutrophil-like cells. The
-increase in matches at the ``back'' of the lamellae compared to the ``front'' can also
-be explained by the thickness gradient of the lamellae (Fig. {[}\ref{fig:lamella_motion_thickness}{]}B,
-Fig. {[}\ref{fig:matching_euc}{]}B, Fig. {[}\ref{fig:matching_fff}{]}B). In addition, aberrations would be expected to cause average 2DTM SNRs to be higher when beam-image shift
-values are small. Instead, we found that SNRs where on average the highest at the
-``front'' edge of the lamellae, presumably due to the thinner sample. We therefore
-conclude that factors other that beam image-shift or beam
-condensation aberrations are limiting 2DTM SNRS, predominantly the thickness of
-the lamellae.
+Within the eight lamellae we found different numbers of detected
+targets, ranging from 1089 to 6433 per lamella (Fig.
+{[}\ref{fig:matching_stat}{]}A). Lamella\textsubscript{EUC} 1 had the most detected targets,
+but also has the largest surface area and contained cytoplasm from two
+cells. Lamella\textsubscript{FFF} 4 had the fewest detected targets, but this
+particular lamella was dominated by a circular section of the nucleus,
+with only small pockets of cytoplasm (Fig. {[}\ref{fig:lamella_images}{]}). In an
+attempt to normalize for these differences in area containing cytoplasm,
+we compared the number of detected targets per tile in tiles that
+contained more than one target, which should exclude tiles with
+non-cytosolic content (Fig. {[}\ref{fig:matching_stat}{]}B). While this measure
+had less variability, there were still differences. Lamella\textsubscript{EUC} 4 had
+not only the fewest targets, but also the lowest density, which could be
+due to this lamella being the thinnest, or due to it sectioning the cell
+in an area with a lower concentration of ribosomes. Lamella\textsubscript{FFF} 3 had a
+substantially higher number of ribosomes per tile. Since all of these
+lamellae were made from a cell-line under identical conditions, this
+underscores the necessity to collect data from large numbers of lamellae
+to overcome the inherent variability. When comparing the distribution of
+scores between lamellae, we found them to be fairly comparable with
+median SNRs ranging from 8.7 to 9.7 (Fig. {[}\ref{fig:matching_stat}{]}C).
+Lamella\textsubscript{EUC} 1 had slightly lower scores compared to the rest,
+potentially due to its large size and connected mechanical instability
+during imaging. Overall, we did not observe differences in the number or
+SNR of detected targets between eucentric or fringe-free illumination
+conditions that were bigger than the observed inter-lamella variability.
+
+Since the SNR values of 2DTM are highly sensitive to image quality, we
+reasoned we could use them to verify that DeCo-LACE does not introduce a
+systematic loss of image quality. We considered non-parallel
+illumination introduced by the unusually condensed beam and
+uncharacterized aberrations near the beam periphery. When plotting the
+SNR values of detected targets in all eight lamellae as a function of
+their location in the tiles, we found uniformly high SNR values
+throughout the illuminated areas for both eucentric and fringe-free
+focus illumination, demonstrating that both illumination schemes are
+suitable for DeCo-LACE (Fig. {[}\ref{fig:matching_stat}{]}D).
+
+We also wondered whether large image shifts would lead to aberrations
+due to astigmatism or beam tilt {[}\protect\hyperlink{ref-APSL9LmU}{16}{]}. We
+reasoned that if that was the case the number of detected targets should
+be highest in the center of the lamella where the applied beam
+image-shift is 0. Instead, we observed that in both eucentric and
+fringe-free focus conditions more targets were detected at the ``back''
+edge of the lamella (Fig. {[}\ref{fig:matching_stat}{]}E{]}). This may be due to
+the center of the cell being predominantly occupied by the nucleus,
+despite its segmentation in neutrophil-like cells. The increase in
+matches at the ``back'' of the lamellae compared to the ``front'' can also
+be explained by the thickness gradient of the lamellae (Fig.
+{[}\ref{fig:lamella_motion_thickness}{]}B, Fig. {[}\ref{fig:matching_euc}{]}B, Fig.
+{[}\ref{fig:matching_fff}{]}B). In addition, aberrations would be expected to
+cause average 2DTM SNRs to be higher when beam-image shift values are
+small. Instead, we found that SNRs where on average the highest at the
+``front'' edge of the lamellae, presumably due to the thinner sample. We
+therefore conclude that factors other that beam image-shift or beam
+condensation aberrations are limiting 2DTM SNRS, predominantly the
+thickness of the lamellae.
 
@@
 
-All lamellae described above were derived from a clonal cell line under identical condition and thinned with the same parameters.
-This means that the substantial variability of detected targets between the lamellae must be due to
-technical variability, including area, thickness, mechanical stability, and location of the section within the cell.
-We therefore predict that further studies that want to draw quantitative and statistically relevant conclusions about the number and location of
-molecules under different experimental conditions, will require collection of orders of magnitude more data than in this study to gain enough statistical power given this variability.
-The samples used were
-prepared in two 24 h sessions on a FIB/SEM instrument, and imaging was performed
-during another two 24h session on the TEM microscope. Inspections of the
-timestamps of the raw data files revealed that the milling time per lamella was
-\textasciitilde30 minutes and TEM imaging was accomplished in \textasciitilde10 seconds per tile or 90
-minutes for a \textasciitilde{} 6x6 μm lamella. Processing of the data, however, took
-substantially longer. Specifically, 2DTM of all tiles took approximately one
-week per lamella on 32 Nvidia A6000 GPUs. Computation is therefore a bottleneck in our
-current workflow, and further optimizations of the algorithm may be necessary
-increase throughput. Alternatively, this bottleneck could be reduced by
-increasing the number of processing units.
+All lamellae described above were derived from a clonal cell line under
+identical condition and thinned with the same parameters. This means
+that the substantial variability of detected targets between the
+lamellae must be due to technical variability, including area,
+thickness, mechanical stability, and location of the section within the
+cell. We therefore predict that further studies that want to draw
+quantitative and statistically relevant conclusions about the number and
+location of molecules under different experimental conditions, will
+require collection of orders of magnitude more data than in this study
+to gain enough statistical power given this variability. The samples
+used were prepared in two 24 h sessions on a FIB/SEM instrument, and
+imaging was performed during another two 24h session on the TEM
+microscope. Inspections of the timestamps of the raw data files revealed
+that the milling time per lamella was \textasciitilde30 minutes and TEM imaging was
+accomplished in \textasciitilde10 seconds per tile or 90 minutes for a \textasciitilde{} 6x6 μm
+lamella. Processing of the data, however, took substantially longer.
+Specifically, 2DTM of all tiles took approximately one week per lamella
+on 32 Nvidia A6000 GPUs. Computation is therefore a bottleneck in our
+current workflow, and further optimizations of the algorithm may be
+necessary increase throughput. Alternatively, this bottleneck could be
+reduced by increasing the number of processing units.
 
@@
 
-In this study we developed an approach to image entire cellular cross-section using cryo-EM at high enough resolution to allow for 2DTM detection of the LSU.
-The two main advantages compared to previous approaches are high throughput of imaging and biological context for detected molecules.
-The requirement to increase throughput in cryo-EM data collection of cellular samples has been recognized in the recent literature.
-Most approaches described so far are tailored towards tomography.
-Peck et al.
-{[}\protect\hyperlink{ref-1GPPSX111}{21}{]} and Yang et al.
-{[}\protect\hyperlink{ref-ujizcpVn}{22}{]} developed approaches to increase the FOV of tomogram data-collection by using a montaging technique.
-Peck et al.~used a similar ``condensed-beam'' approach as described here.
-However, the montages are substantially smaller in scope, covering carbon film holes of 2 µm diameter.
-Bouvette et al.
-{[}\protect\hyperlink{ref-1Gwx5ScUa}{23}{]} and Eisenstein et al.
-{[}\protect\hyperlink{ref-xvouNMBy}{24}{]} are using beam image-shift to collect tilt-series in multiple locations in parallel to increase throughput.
-However, none of these approaches provide the full coverage of a cellular cross-section that can be achieved using DeCo-LACE.
+In this study we developed an approach to image entire cellular
+cross-section using cryo-EM at high enough resolution to allow for 2DTM
+detection of the LSU. The two main advantages compared to previous
+approaches are high throughput of imaging and biological context for
+detected molecules. The requirement to increase throughput in cryo-EM
+data collection of cellular samples has been recognized in the recent
+literature. Most approaches described so far are tailored towards
+tomography. Peck et al. {[}\protect\hyperlink{ref-1GPPSX111}{22}{]} and Yang et al.
+{[}\protect\hyperlink{ref-ujizcpVn}{23}{]} developed approaches to increase the
+FOV of tomogram data-collection by using a montaging technique. Peck et
+al.~used a similar ``condensed-beam'' approach as described here. However,
+the montages are substantially smaller in scope, covering carbon film
+holes of 2 µm diameter. Bouvette et al.
+{[}\protect\hyperlink{ref-1Gwx5ScUa}{24}{]} and Eisenstein et al.
+{[}\protect\hyperlink{ref-xvouNMBy}{25}{]} are using beam image-shift to collect
+tilt-series in multiple locations in parallel to increase throughput.
+However, none of these approaches provide the full coverage of a
+cellular cross-section that can be achieved using DeCo-LACE.
 
 We observed granules containing a vesicle of putative cytosolic origin.
-We speculate that upon degranulation, the process in which granules fuse with the plasma membrane, these vesicles would be released into the extracelullar space.
-The main types of extracellular vesicles of this size are exosomes, up to 100 nm large vesicles derived from fusion of multivesicular bodies with the plasma membrane, and microvesicles, which are derived from direct budding of the plasma membrane {[}\protect\hyperlink{ref-kncnYGLD}{25}{]}.
-We suggest that granulocytes could release a third type of extracellular vesicle, granule-derived vesicles (GDV), into the extracellular space.
-2DTM showed that a subset of GDVs can contain ribosomes (Fig.
-{[}\ref{fig:matching_euc}{]}F, Fig.
-{[}\ref{fig:matching_fff}{]}D,E).
-This could indicate that these vesicles are transporting translation-capable mRNAs, as has been described for exosomes {[}\protect\hyperlink{ref-agVdpX76}{26}{]}.
-Further studies will be necessary to confirm the existence of GDVs in granulocytes isolated from mammals and to understand their functional significance.
-
-As mentioned in the results, we found a consistent shading artifact pattern in our montages, that we believe is the result of non-linear behavior of the K3 camera.
-Indeed, when we average images with a condensed beam taken over vacuum we found in both focus conditions a consistent background pattern with a brighter region on the periphery of the illuminated area (Fig {[}\ref{fig:gain}{]}).
-This might be caused by dynamic adjustment of the internal camera counting threshold which expects columns of the sensor to be evenly illuminated as is the case for SPA applications.
-Since the signal of this pattern has mainly low-resolution components it is unlikely to affect 2DTM.
-However, it highlights that the non-linear behavior of the camera has to be taken into account when imaging samples with strongly varying density and unusual illumination schemes.
-
-We found that even though we used beam image-shift extensively (up to 7 um), we did not see substantially reduced 2DTM SNR values in tiles acquired at high beam image-shift compared to tiles acquired with low or no beam image-shift.
-This is in contrast to reports in single-particle analysis (SPA) {[}\protect\hyperlink{ref-44fG6kcy}{27}{]} where the induced beam tilt substantially reduced the resolution if it was not corrected during processing.
-It is possible that 2DTM is less sensitive to beam-tilt aberrations, since the template is free of any aberration and only the image is distorted, while in SPA the beam tilt will affect both the images and the reconstructed template.
-
-Since we observed substantial variation in LSU density within and between lamellae, visual proteomics studies that use cryo-EM to establish changes in molecular organization within cells will require orders of magnitude more data than used in this study.
-One milestone would be to image enough data to represent one cellular volume, which for a small eukaryotic cells requires imaging approximately 100 lamellae.
-While data collection throughput on the TEM is fundamentally limited by the exposure time, this amount of data could be collected within 12 hours by improving the data acquisition scheme to perform all necessary calculations in parallel with actual exposure of the camera.
-Sample preparation using a FIB/SEM is also currently a bottleneck, but preparation of large lamellae with multiple cellular cross-sections using methods like WAFFLE {[}\protect\hyperlink{ref-17H2LWiIu}{28}{]} might allow sufficient throughput.
-As stated in the results, at least for 2DTM computation will remain challenging and approximately 17,000 GPU hours would be required for a 100 lamellae dataset.
+We speculate that upon degranulation, the process in which granules fuse
+with the plasma membrane, these vesicles would be released into the
+extracelullar space. The main types of extracellular vesicles of this
+size are exosomes, up to 100 nm large vesicles derived from fusion of
+multivesicular bodies with the plasma membrane, and microvesicles, which
+are derived from direct budding of the plasma membrane
+{[}\protect\hyperlink{ref-kncnYGLD}{26}{]}. We suggest that granulocytes could release
+a third type of extracellular vesicle, granule-derived vesicles (GDV),
+into the extracellular space. 2DTM showed that a subset of GDVs can
+contain ribosomes (Fig. {[}\ref{fig:matching_euc}{]}F, Fig.
+{[}\ref{fig:matching_fff}{]}D,E). This could indicate that these vesicles are
+transporting translation-capable mRNAs, as has been described for
+exosomes {[}\protect\hyperlink{ref-agVdpX76}{27}{]}. Further studies will be necessary to
+confirm the existence of GDVs in granulocytes isolated from mammals and
+to understand their functional significance.
+
+As mentioned in the results, we found a consistent shading artifact
+pattern in our montages, that we believe is the result of non-linear
+behavior of the K3 camera. Indeed, when we average images with a
+condensed beam taken over vacuum we found in both focus conditions a
+consistent background pattern with a brighter region on the periphery of
+the illuminated area (Fig {[}\ref{fig:gain}{]}). This might be caused by dynamic
+adjustment of the internal camera counting threshold which expects
+columns of the sensor to be evenly illuminated as is the case for SPA
+applications. Since the signal of this pattern has mainly low-resolution
+components it is unlikely to affect 2DTM. However, it highlights that
+the non-linear behavior of the camera has to be taken into account when
+imaging samples with strongly varying density and unusual illumination
+schemes.
+
+We found that even though we used beam image-shift extensively (up to 7
+um), we did not see substantially reduced 2DTM SNR values in tiles
+acquired at high beam image-shift compared to tiles acquired with low or
+no beam image-shift. This is unexpected because beam image-shift is
+though to degrade the high-resolution signal due to the introduction of
+beam-tilt, as has been observed in single particle analysis
+{[}\protect\hyperlink{ref-44fG6kcy}{28},\protect\hyperlink{ref-wy8cRzrH}{29}{]}. The
+signal detected by 2DTM is target and sample dependent and has been
+shown to be sensitive to a resolution up to 3 Å, but in practice is
+limited by the B-factor applied to the template
+{[}\protect\hyperlink{ref-Ynb3IP6I}{7}{]}. In our case, we used a structure of the
+mouse LSU that was deposited into the PDB with atoms having a median
+B-factor of \textasciitilde{} 80 Å\(^2\), which we multiplied by 1.5 before generating
+the density map. This value was chosen empirically early in the study to
+optimize the number of detections. The resulting median B-factor of 120
+Å\(^2\) is equivalent to a Gaussian lowpass filter with a filter constant
+of 7.7 Å. We did not measure the beam-tilt caused by beam-image shift on
+the microscope to acquire our data, but Cheng et. al.~report that in
+their measurements Krios Titan columns exhibited a beam-tilt of
+0.17-0.25 mrad per μm of beam image-shift
+{[}\protect\hyperlink{ref-wy8cRzrH}{29}{]}. We therefore expect a worst-case
+beam-tilt of 1.75 mrad. At this beam-tilt we expect a phase error of
+larger than π/4 at resolutions higher than 5.75 Å
+{[}\protect\hyperlink{ref-wy8cRzrH}{29}{]}, which exceeds the resolution of our
+2DTM template. We conclude that the beam-tilt caused by beam-image shift
+did not strongly affect detections in the present study, but it might be
+important to consider when imaging at even higher beam-image shift
+values or when using higher resolution signal in 2DTM.
+
+We used 2DTM of the ribosome LSU to verify the image quality of
+DeCo-LACE data. However, 2DTM has the potential to detect many other
+protein complexes. The model of the ribosomal LSU used in this
+manuscript has a molecular weight of \textasciitilde2 MDa, \textasciitilde1.3 MDa of which is
+nucleic acid. The higher scattering density of nucleic acid compared to
+protein {[}\protect\hyperlink{ref-13fhsbtxo}{30}{]} may mean that a biomolecular complex of equal
+size consisting of only protein would result in lower SNR values. Many
+biological complexes are smaller and do not contain nucleic acid, but
+simulations of 2DTM {[}\protect\hyperlink{ref-Ynb3IP6I}{7}{]} suggest that it should be
+possible to detect protein molecules as small as 300 kDa in an crowded
+environment. Besides the molecular weight we expect that the
+conformational homogeneity of a protein complex will affect the ability
+to detect it and note that for complexes that occur at low
+concentrations inside the cell a higher detection threshold might be
+necessary to reduce the number of false positives among the few true
+targets that can be detected.
+
+Since we observed substantial variation in LSU density within and
+between lamellae, visual proteomics studies that use cryo-EM to
+establish changes in molecular organization within cells will require
+orders of magnitude more data than used in this study. One milestone
+would be to image enough data to represent one cellular volume, which
+for a small eukaryotic cells requires imaging approximately 100
+lamellae. While data collection throughput on the TEM is fundamentally
+limited by the exposure time, this amount of data could be collected
+within 12 hours by improving the data acquisition scheme to perform all
+necessary calculations in parallel with actual exposure of the camera.
+Sample preparation using a FIB/SEM is also currently a bottleneck, but
+preparation of large lamellae with multiple cellular cross-sections
+using methods like WAFFLE {[}\protect\hyperlink{ref-17H2LWiIu}{31}{]} might allow
+sufficient throughput. As stated in the results, at least for 2DTM
+computation will remain challenging and approximately 17,000 GPU hours
+would be required for a 100 lamellae dataset. It might be possible to
+increase the performance of 2DTM by improving the implementation of
+GPU-based fast Fourier transforms. Alternatively, strategies that
+initially search images at lower resolution and sparser rotational
+sampling, followed by refinement at higher resolution, could be more
+efficient, but it is yet unclear whether this is feasible in cellular
+samples with strong low-resolution background.
 
@@
 
+\hypertarget{key-resources-table}{%
+\subsubsection{Key Resources Table}\label{key-resources-table}}
+
+\begin{tablenos:no-prefix-table-caption}
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2139}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1148}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2451}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1148}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2951}}@{}}
+\toprule()
+\begin{minipage}[b]{\linewidth}\raggedright
+Reagent type
+(species)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Designation
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Source or reference
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Identifiers
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Additional Information
+\end{minipage} \\
+\midrule()
+\endhead
+cell line (\emph{mus
+musculus}) & ER-HoxB8 & {[}\protect\hyperlink{ref-1B9Vt9eYu}{10}{]} & & Generated from mouse bone marrow as
+described in
+{[}\protect\hyperlink{ref-1B9Vt9eYu}{10}{]} \\
+peptide, recombinant protein & SCF & {[}\protect\hyperlink{ref-1B9Vt9eYu}{10}{]} & & Generated from CHO-SCF cell line as
+described in
+{[}\protect\hyperlink{ref-1B9Vt9eYu}{10}{]} \\
+chemical compound,
+drug & Estrogen & Sigma & E8875 & \\
+\bottomrule()
+\end{longtable}
+
+\end{tablenos:no-prefix-table-caption}
+
 \hypertarget{grid-preparation}{%
@@
 
-ER-HoxB8 cells were maintained in RPMI medium supplemented with 10\% FBS,
-penicillin/streptomycin, SCF, and estrogen {[}\protect\hyperlink{ref-1B9Vt9eYu}{10}{]} at
-37 °C and 5\% CO2. 120 h prior to grid preparation, cells were washed twice in PBS
-and cultured in the same medium except without estrogen. Differentiation was
-verified by staining with Hoechst-dye and inspection of nuclear morphology.
-Cells were then counted and diluted to \(1\cdot10^6\) cells/ml. Grids (either 200
-mesh copper grids, with a sillicone-oxide and 2 µm holes with a 2 µm spacing or
-200 mesh gold grids with a thin gold film and 2 µm holes in 2 µm spacing) were
-glow-discharged from both sides using a 15 mA for 45 s. 3.5 µl of cell suspension
-was added to grids on the thin-film side and grids were blotted from the back
-side using a GP2 cryoplunger (Leica, Wetzlar, Germany) for 8 s and rapidly plunged into liquid
-ethane at -185 °C.
+ER-HoxB8 cells were generated as described by Wang et. al.
+{[}\protect\hyperlink{ref-1B9Vt9eYu}{10},\protect\hyperlink{ref-nSMAxqTD}{32}{]}
+and maintained in RPMI medium supplemented with 10\% FBS,
+penicillin/streptomycin, SCF, and estrogen
+ at 37 °C and 5\% CO2. 120 h prior to grid preparation, cells were washed twice in PBS and
+cultured in the same medium except without estrogen. The authenticity of the
+cells was verified by flow-cytometry and Giemsa staining after differentiation {[}\protect\hyperlink{ref-1B9Vt9eYu}{10},\protect\hyperlink{ref-nSMAxqTD}{32}{]}.
+Cells were then counted and diluted to \(1\cdot10^6\)
+cells/ml. Grids (either 200 mesh copper grids, with a sillicone-oxide
+and 2 µm holes with a 2 µm spacing or 200 mesh gold grids with a thin
+gold film and 2 µm holes in 2 µm spacing) were glow-discharged from both
+sides using a 15 mA for 45 s. 3.5 µl of cell suspension was added to
+grids on the thin-film side and grids were blotted from the back side
+using a GP2 cryoplunger (Leica, Wetzlar, Germany) for 8 s and rapidly
+plunged into liquid ethane at -185 °C.
 
@@
 
-Grids were loaded into an Aquilos 2 FIB/SEM (Thermo Fisher, Waltham, MA) instrument with a
-stage cooled to -190 °C. Grids were sputter-coated with platinum for 15 s at 45 mA
-and then coated with a layer of platinum-precursor by opening the GIS-valve for
-45 s. An overview of the grid was created by montaging SEM images and isolated
-cells at the center of gridsquares were selected for FIB-milling. Lamellae were
-generated automatically using the AutoTEM software (Thermo Fisher), with the
-following parameters:
+Grids were loaded into an Aquilos 2 FIB/SEM (Thermo Fisher, Waltham, MA)
+instrument with a stage cooled to -190 °C. Grids were sputter-coated
+with platinum for 15 s at 45 mA and then coated with a layer of
+platinum-precursor by opening the GIS-valve for 45 s. An overview of the
+grid was created by montaging SEM images and isolated cells at the
+center of gridsquares were selected for FIB-milling. Lamellae were
+generated automatically using the AutoTEM software (Thermo Fisher), with
+the following parameters:
 
@@
 
-This resulted in 6-10 µm wide lamella with 150-250 nm thickness as determined by
-FIB-imaging of the lamella edges.
+This resulted in 6-10 µm wide lamella with 150-250 nm thickness as
+determined by FIB-imaging of the lamella edges.
 
@@
 
-Grids were loaded into a Titan Krios TEM (Thermo Fisher) operated at 300 keV and
-equipped with a BioQuantum energy filter (Gatan, Pleasanton, CA) and K3 camera (Gatan). The
-microscope was aligned using a cross-grating grid on the stage. Prior to each
-session, we carefully performed the ``Image/Beam'' calibration in nanoprobe. We
-set the magnification to a pixel size of 1.76 Å and condensed the beam to \textasciitilde{} 900 nm
-diameter, resulting in the beam being completely visible on the camera. To
-establish fringe-free conditions, the ``Fine eucentric'' procedure of SerialEM {[}\protect\hyperlink{ref-19ZFerhph}{29}{]} was
-used to move a square of the cross-grating grid to the eucentric position of the
-microscope. The effective defocus was then set to 2 µm, using the ``autofocus''
-routine of SerialEM. The objective focus of the microscope was changed until no
-fringes were visible. The stage was then moved in Z until images had an apparent
-defocus of 2 µm. The difference in stage Z-position between the eucentric and
-fringe-free conditions was used to move other areas into fringe-free condition.
-
-Low magnification montages were used to find lamellae and lamellae that were
-sufficiently thin and free of contamination were selected for automated data
-collection. Overview images of each lamella were taken at 2250x magnification
-(38 Å pixel size). The corners of the lamella in the overview image were manually
-annotated in SerialEM and translated into beam image-shift values using SerialEM's
-calibration. A hexagonal pattern of beam image-shift positions was calculated
-that covered the area between the four corners in a serpentine way, with a
-\(\sqrt{3}\cdot425\) nm horizontal spacing and \(3/4\cdot 850\) nm vertical spacing. Exposures were
-taken at each position with a 30 e\textsuperscript{-}/Å\(^2\) total dose. After each exposure, the
-defocus was estimated using the ctffind function of SerialEM and the focus for
-the next exposure was corrected by the difference between the estimated focus
-and the desired defocus of 800 nm. Furthermore, after each exposure the
-deviation of the beam from the center of the camera was measured and corrected
-using the ``CenterBeamFromImage'' command of SerialEM.
-
-After data collection, a 20 s exposure at 2250x magnification of the lamella at
-200 μm defocus was taken for visualization purposes. A Python script implementing
-this procedure is available at \url{https://github.com/jojoelfe/deco_lace_template_matching_manuscript}.
+Grids were loaded into a Titan Krios TEM (Thermo Fisher) operated at 300
+keV and equipped with a BioQuantum energy filter (Gatan, Pleasanton, CA)
+and K3 camera (Gatan). The microscope was aligned using a cross-grating
+grid on the stage. Prior to each session, we carefully performed the
+``Image/Beam'' calibration in nanoprobe. We set the magnification to a
+pixel size of 1.76 Å and condensed the beam to \textasciitilde{} 900 nm diameter,
+resulting in the beam being completely visible on the camera. To
+establish fringe-free conditions, the ``Fine eucentric'' procedure of
+SerialEM {[}\protect\hyperlink{ref-19ZFerhph}{33}{]} was used to move a square of
+the cross-grating grid to the eucentric position of the microscope. The
+effective defocus was then set to 2 µm, using the ``autofocus'' routine of
+SerialEM. The objective focus of the microscope was changed until no
+fringes were visible. The stage was then moved in Z until images had an
+apparent defocus of 2 µm. The difference in stage Z-position between the
+eucentric and fringe-free conditions was used to move other areas into
+fringe-free condition.
+
+Low magnification montages were used to find lamellae and lamellae that
+were sufficiently thin and free of contamination were selected for
+automated data collection. Overview images of each lamella were taken at
+2250x magnification (38 Å pixel size). The corners of the lamella in the
+overview image were manually annotated in SerialEM and translated into
+beam image-shift values using SerialEM's calibration. A hexagonal
+pattern of beam image-shift positions was calculated that covered the
+area between the four corners in a serpentine way, with a
+\(\sqrt{3}\cdot 0.95 \cdot r\) horizontal spacing and
+\(3/2\cdot 0.95 \cdot r\) vertical spacing, where \(r\) is the radius of the
+illuminated area. For the fringe-free focus condition r was 250 nm and
+for the eucentric focus r was 230 nm. This resulted in a fractional
+overlap of adjacent tiles of 10.3\% for the fringe-free focus condition
+and 12.9 \% for the eucentric focus condition. Exposures were taken at
+each position with a 30 e\textsuperscript{-}/Å\(^2\) total dose. After each exposure, the
+defocus was estimated using the ctffind function of SerialEM and the
+focus for the next exposure was corrected by the difference between the
+estimated focus and the desired defocus of 800 nm. Furthermore, after
+each exposure the deviation of the beam from the center of the camera
+was measured and corrected using the ``CenterBeamFromImage'' command of
+SerialEM.
+
+After data collection, a 20 s exposure at 2250x magnification of the
+lamella at 200 μm defocus was taken for visualization purposes. A Python
+script implementing this procedure is available at
+\url{https://github.com/jojoelfe/deco_lace_template_matching_manuscript}.
 
@@
 
-Motion-correction, dose weighting and other preprocessing as detailed below was performed using \emph{cis}TEM {[}\protect\hyperlink{ref-MUY42yxp}{30}{]}.
-To avoid influence of the beam-edge on motion-correction, only a quarter of the
+Motion-correction, dose weighting and other preprocessing as detailed
+below was performed using \emph{cis}TEM {[}\protect\hyperlink{ref-MUY42yxp}{34}{]}. To avoid
+influence of the beam-edge on motion-correction, only a quarter of the
 movie in the center of the camera was considered for calculation of the
-estimated motion. After movie frames were aligned and summed, a mask for the
-illuminated area was calculated by lowpass filtering the image with a 100 Å
-resolution cutoff, thresholding the image at 10\% of the maximal value and then lowpass
-filtering the mask again with a 100 Å resolution cutoff to smooth the mask edges. This mask was
-then used to select dark areas in the image and fill the pixels with
-Gaussian noise, with the same mean and standard deviation as the illuminated
-area. A custom version of the unblur program {[}\protect\hyperlink{ref-1G4Y94qCy}{31}{]}
-implementing this procedure is available at {[}link to decolace branch{]}. During motion correction images were resampled to a pixel size of 1.5 Å. The
+estimated motion. After movie frames were aligned and summed, a mask for
+the illuminated area was calculated by lowpass filtering the image with
+a 100 Å resolution cutoff, thresholding the image at 10\% of the maximal
+value and then lowpass filtering the mask again with a 100 Å resolution
+cutoff to smooth the mask edges. This mask was then used to select dark
+areas in the image and fill the pixels with Gaussian noise, with the
+same mean and standard deviation as the illuminated area. A custom
+version of the unblur program {[}\protect\hyperlink{ref-1G4Y94qCy}{35}{]} implementing
+this procedure is available at {[}link to decolace branch{]}. During
+motion correction images were resampled to a pixel size of 1.5 Å. The
 contrast-transfer function (CTF) was estimated using ctffind
-{[}\protect\hyperlink{ref-n43f3Sqs}{32}{]}, searching between 0.2 and 2 μm defocus.
+{[}\protect\hyperlink{ref-n43f3Sqs}{36}{]}, searching between 0.2 and 2 μm
+defocus.
 
@@
 The search template was generated from the atomic model of the mouse LSU
-(PDB 6SWA, exluding the Epb1 subunit) using the cryo-EM simulator implemented in \emph{cis}TEM
-{[}\protect\hyperlink{ref-q2PSamkS}{33}{]}. The
-match\_template program {[}\protect\hyperlink{ref-10bXZuF3G}{9}{]} was used to search for this
-template in the movie-aligned, exposure-filtered and masked images, using a 1.5°
-angular step in out-of-plane angles and a 1.0° angular step in-plane. 11 defocus
-planes in 20 nm steps centered around the ctffind-determined defocus were searched. Targets
-were defined as detected when their matches with the template produced peaks
-with a singal-to-noise ratio (SNR) above a threshold of 7.75, which was chosen
-based on the one-false-positive-per-tile criterion {[}\protect\hyperlink{ref-Ynb3IP6I}{7}{]}.
+(PDB 6SWA, exluding the Epb1 subunit) using the cryo-EM simulator
+implemented in \emph{cis}TEM {[}\protect\hyperlink{ref-q2PSamkS}{37}{]}. The
+match\_template program {[}\protect\hyperlink{ref-10bXZuF3G}{9}{]} was used to search for
+this template in the movie-aligned, exposure-filtered and masked images,
+using a 1.5° angular step in out-of-plane angles and a 1.0° angular step
+in-plane. 11 defocus planes in 20 nm steps centered around the
+ctffind-determined defocus were searched. Targets were defined as
+detected when their matches with the template produced peaks with a
+singal-to-noise ratio (SNR) above a threshold of 7.75, which was chosen
+based on the one-false-positive-per-tile criterion
+{[}\protect\hyperlink{ref-Ynb3IP6I}{7}{]}.
 
@@
 
-The coordinates of each tile \(i\),
-\(\mathbf{c}_{i}\) {[}2D Vector in pixels{]} were initialized using beam image-shift of the tile, \(\mathbf{b}_i\) {[}2D Vector in μm{]},
-and the ISToCamera matrix \(\mathbf{IC}\), as calibrated by SerialEM:
+The coordinates of each tile \(i\), \(\mathbf{c}_{i}\) {[}2D Vector in
+pixels{]} were initialized using beam image-shift of the tile,
+\(\mathbf{b}_i\) {[}2D Vector in μm{]}, and the ISToCamera matrix
+\(\mathbf{IC}\), as calibrated by SerialEM:
 
@@
 
-A list of tile pairs \(i,j\) that overlap were assembled by selecting images where
-\(|\mathbf{c}_i-\mathbf{c}_j| < D_{Beam}\).
-In order to calculate the precise offset between tiles \(i\) and \(j\), \(\mathbf{r}_{i,j}\), we calculated the cross-correlation between the two tiles, masked to the overlapping illuminated area using the scikit-image
-package {[}\protect\hyperlink{ref-stvWEJeu}{34}{]} was used to calculate refined offsets .
-The coordinates \(\mathbf{c}_{i}\) were then refined by a least-square minimization against \(\mathbf{r}_{i,j}\):
+A list of tile pairs \(i,j\) that overlap were assembled by selecting
+images where \(|\mathbf{c}_i-\mathbf{c}_j| < D_{Beam}\). In order to
+calculate the precise offset between tiles \(i\) and \(j\),
+\(\mathbf{r}_{i,j}\), we calculated the cross-correlation between the two
+tiles, masked to the overlapping illuminated area using the scikit-image
+package {[}\protect\hyperlink{ref-stvWEJeu}{38}{]} was used to calculate refined offsets .
+The coordinates \(\mathbf{c}_{i}\) were then refined by a least-square
+minimization against \(\mathbf{r}_{i,j}\):
 
@@
 
-using the scipy package {[}\protect\hyperlink{ref-8Miti2Gz}{35}{]}. The masked cross-correlation and the least-square minimization was repeated once more to arrive at the final tile alignment.
+using the scipy package {[}\protect\hyperlink{ref-8Miti2Gz}{39}{]}. The masked
+cross-correlation and the least-square minimization was repeated once
+more to arrive at the final tile alignment.
 
 The x,y coordinates of target \(n\) detected by 2DTM in the tile \(i\),
-\(\textbf{m}^\textrm{T}_{n,i}\), was transformed into the montage frame by adding
-the coordinate of the tile.
+\(\textbf{m}^\textrm{T}_{n,i}\), was transformed into the montage frame by
+adding the coordinate of the tile.
 
@@
 
-The z coordinate of each target was calculated as the sum of the defocus offset
-for the target, the estimated defocus of the tile, and the nominal defocus of
-the microscope when the tile was acquired.
-
-Images were rendered using UCSF ChimeraX {[}\protect\hyperlink{ref-cYCuuZxG}{36}{]} using a custom extension to render 2DTM results available at \url{https://github.com/jojoelfe/tempest}.
-The Python scripts used for data processing are available
-under \url{https://github.com/jojoelfe/deco_lace_template_matching_manuscript}.
+The z coordinate of each target was calculated as the sum of the defocus
+offset for the target, the estimated defocus of the tile, and the
+nominal defocus of the microscope when the tile was acquired.
+
+Images were rendered using UCSF ChimeraX {[}\protect\hyperlink{ref-cYCuuZxG}{40}{]} using a
+custom extension to render 2DTM results available at
+\url{https://github.com/jojoelfe/tempest}. The Python scripts used for data
+processing are available under
+\url{https://github.com/jojoelfe/deco_lace_template_matching_manuscript}.
 
@@
 
-The authors would like to thank Bronwyn Lucas, Carsten Sachse, and Chen Xu for helpful suggestions and careful reading of the manuscriptas as well as members of the Grigorieff lab for helpful discussions.
-Data was collected at the UMass Chan Medical School Cryo-EM core with help by Kankang Song, Christna Ouch, and Chen Xu.
+The authors would like to thank Bronwyn Lucas, Carsten Sachse, and Chen
+Xu for helpful suggestions and careful reading of the manuscriptas as
+well as members of the Grigorieff lab for helpful discussions. Data was
+collected at the UMass Chan Medical School Cryo-EM core with help by
+Kankang Song, Christna Ouch, and Chen Xu.
 
@@
 
-Cryo-EM movies, motion-corrected images and 2DTM results have been deposited in EMPIAR under accession code {[}will be inserted{]}.
-The custom cisTEM version is available under \url{https://github.com/jojoelfe/cisTEM/tree/2574dbdf6161658fd177660b3a841100a792f61b} until features have been integrated into a cisTEM release.
-The ChimeraX extension for rendering is available under \url{https://github.com/jojoelfe/tempest}.
-This manuscript was prepared using the manubot package {[}\protect\hyperlink{ref-YuJbg3zO}{37}{]} .
-The corresponding repository containing all scripts used for figure generation can be found under \url{https://github.com/jojoelfe/deco_lace_template_matching_manuscript}.
+Cryo-EM movies, motion-corrected images and 2DTM results have been
+deposited in EMPIAR under accession code EMPIAR-11063. The custom cisTEM
+version is available under
+\url{https://github.com/jojoelfe/cisTEM/tree/2574dbdf6161658fd177660b3a841100a792f61b}
+until features have been integrated into a cisTEM release. The ChimeraX
+extension for rendering is available under
+\url{https://github.com/jojoelfe/tempest}. This manuscript was prepared
+using the manubot package {[}\protect\hyperlink{ref-YuJbg3zO}{41}{]} . The
+corresponding repository containing all scripts used for figure
+generation can be found under
+\url{https://github.com/jojoelfe/deco_lace_template_matching_manuscript}.
 
@@
 \includegraphics{figures/initmatching.png}
-\caption{2D template matching of the large subunit of the ribosome in fib-milled neutrophil-like cells
-(A) Overview image of the lamella.
-Major cellular regions are labeled, as Nucleus (Nuc), Mitochondria (M), and granular cytoplasm (GrCyt).
-FOVs where high-magnification images for template matching where acquired are indicated as boxes with the number of detected targets indicated on the bottom right.
-FOVs displayed in Panels B-E are color-coded.
-Scalebar corresponds to 1 μm.
-(B-E) FOVs with projection of detected LSUs shown in cyan.
-(B) Perinuclear region, the only detected targets are in the cytoplasmic half.
-(C) Cytoplasmic region with high density of ribosomes (D) Mitochondrium, as expected there are only detected LSUs in the cytoplasmic region (E) Cytoplasm, with low density of ribosomes.}\label{fig:initmatching}
+\caption{2D template matching of the large subunit of the ribosome in
+fib-milled neutrophil-like cells (A) Overview image of the lamella.
+Major cellular regions are labeled, as Nucleus (Nuc), Mitochondria (M),
+and granular cytoplasm (GrCyt). FOVs where high-magnification images for
+template matching where acquired are indicated as boxes with the number
+of detected targets indicated on the bottom right. FOVs displayed in
+Panels B-E are color-coded. Scalebar corresponds to 1 μm. (B-E) FOVs
+with projection of detected LSUs shown in cyan. (B) Perinuclear region,
+the only detected targets are in the cytoplasmic half. (C) Cytoplasmic
+region with high density of ribosomes (D) Mitochondrium, as expected
+there are only detected LSUs in the cytoplasmic region (E) Cytoplasm,
+with low density of
+ribosomes.}\label{fig:initmatching}
 }
@@
 
-\begin{fignos:tagged-figure}[2 - figure supplement 1]
+\begin{fignos:tagged-figure}[1 - figure supplement 1]
 
@@
 \includegraphics{figures/initmatching2.png}
-\caption{2D template matching of the large subunit of the ribosome in fib-milled
-neutrophil-like cells (A) Maximum intensity projection (MIP) cross-correlation map of
-micrograph shown in Figure
-\ref{fig:initmatching} (B+C) 3D plot of MIP regions indicated by color boxes in Panel A}\label{fig:initmatching2}
+\caption{2D template matching of the large subunit of the ribosome in
+fib-milled neutrophil-like cells (A) Maximum intensity projection (MIP)
+cross-correlation map of micrograph shown in Figure \ref{fig:initmatching}
+(B+C) 3D plot of MIP regions indicated by color boxes in Panel
+A}\label{fig:initmatching2}
 }
@@
 \includegraphics{figures/approach.png}
-\caption{DeCo-LACE approach (A) Graphic demonstrating the data-collection strategy for
-DeCo-LACE. The electron beam is condensed to a diameter \(D_{Beam}\) that allows captured of
-the whole illuminated area on the camera. Beam-image shift along X and Y
-(\(BIS_X\),\$\(BIS_Y\)) is used to scan the whole lamella
-(B) Diagram of the collection algorithm
-(C) Example overview image of a lamella with the designated acquisition
-positions and the used beam diameter indicated with red circles. Scalebar corresponds to 1 μm.
-(D+E) Representative micrographs takne with a condensed beam at eucentric focus
-(D) or fringe-free focus (E). Scalebar corresponds to 100 nm.
-(F) Boxplot of defocus measured by ctffind of micrographs taken by the DeCo-LACE
-approach on four lamellae images at eucentric focus and four lamellae imaged with
-fringe-free focus.}\label{fig:approach}
+\caption{DeCo-LACE approach (A) Graphic demonstrating the data-collection
+strategy for DeCo-LACE. The electron beam is condensed to a diameter
+\(D_{Beam}\) that allows captured of the whole illuminated area on the
+camera. Beam-image shift along X and Y (\(BIS_X\),\$\(BIS_Y\)) is used to
+scan the whole lamella (B) Diagram of the collection algorithm (C)
+Example overview image of a lamella with the designated acquisition
+positions and the used beam diameter indicated with red circles.
+Scalebar corresponds to 1 μm. (D+E) Representative micrographs takne
+with a condensed beam at eucentric focus (D) or fringe-free focus (E).
+Scalebar corresponds to 100 nm. (F) Boxplot of defocus measured by
+ctffind of micrographs taken by the DeCo-LACE approach on four lamellae
+images at eucentric focus and four lamellae imaged with fringe-free
+focus.}\label{fig:approach}
 }
@@
 
-\begin{fignos:tagged-figure}[3 - figure supplement 1]
+\begin{fignos:tagged-figure}[2 - figure supplement 1]
 
@@
 \includegraphics{figures/lamella_spatial_info.png}
-\caption{Defocus estimation of individual tiles of DeCo-LACE montages
-(A) Defocus values of individual micrographs taken using the DeCo-LACE approach
-plotted as a function of the beam image-shift values.
-(B) Defocus astigmatism of individual micrographs taken using the DeCo-LACE approach
-plotted as a function of the beam image-shift values.}\label{fig:lamella_spatial_info}
+\caption{Defocus estimation of individual tiles of DeCo-LACE montages (A)
+Defocus values of individual micrographs taken using the DeCo-LACE
+approach plotted as a function of the beam image-shift values. (B)
+Defocus astigmatism of individual micrographs taken using the DeCo-LACE
+approach plotted as a function of the beam image-shift
+values.}\label{fig:lamella_spatial_info}
 }
@@
 \includegraphics{figures/assembly.png}
-\caption{Assembling DeCo-LACE exposures into montages (A) Overview
-image of Lamella\textsubscript{EUC} 1 taken at low magnification. Scalebar corresponds to 1 μm. (B) Overview of Lamella\textsubscript{EUC} 1 created by
-montaging high magnification images taken with the DeCo-LACE approach.
-Scalebar corresponds to 1 μm.
-(C) Zoom-in into red box in panel B.
-Slight beam-fringe artifacts are visible.
-Scalebar corresponds to 100 nm.
-(D) Overview
-image of Lamella\textsubscript{FFF} 4 taken at low magnification. Scalebar corresponds to 1 μm. (E) Overview of Lamella\textsubscript{FFF} 4 created by
-montaging high magnification images taken with the DeCo-LACE approach.
-Scalebar corresponds to 1 μm.
-(F) Zoom-in into red box in panel E.
-No beam-fringe artifacts are visible.
-Scalebar corresponds to 100 nm.}\label{fig:assembly}
+\caption{Assembling DeCo-LACE exposures into montages (A) Overview image of
+Lamella\textsubscript{EUC} 1 taken at low magnification. Scalebar corresponds to 1 μm.
+(B) Overview of Lamella\textsubscript{EUC} 1 created by montaging high magnification
+images taken with the DeCo-LACE approach. Scalebar corresponds to 1 μm.
+(C) Zoom-in into red box in panel B. Slight beam-fringe artifacts are
+visible. Scalebar corresponds to 100 nm. (D) Overview image of
+Lamella\textsubscript{FFF} 4 taken at low magnification. Scalebar corresponds to 1 μm.
+(E) Overview of Lamella\textsubscript{FFF} 4 created by montaging high magnification
+images taken with the DeCo-LACE approach. Scalebar corresponds to 1 μm.
+(F) Zoom-in into red box in panel E. No beam-fringe artifacts are
+visible. Scalebar corresponds to 100
+nm.}\label{fig:assembly}
 }
@@
 
-\begin{fignos:tagged-figure}[4 - figure supplement 1]
+\begin{fignos:tagged-figure}[3 - figure supplement 1]
 
@@
 \centering
-\includegraphics{figures/crop_unblur.png}
-\caption{Motion correction of movies with condensed beams.
-At the top of each panel is an average of the movie that was motion-corrected
-with a red dashed box indicating the region that was used to estimate shifts.
-Below is a graph indicating the estimated shifts of the individual frames of the
-movie. Below this is the MIP of 2DTM using the large subunit of the mouse ribosome.
-(A) Motion correction of the whole movie
-(B) Notion correction of a cropped region of the movie that eliminates the beam
-edges
-(C) Motion correction of the whole movie, using only the central region to
-estimate the shifts}\label{fig:crop_unblur}
+\includegraphics[width=\textwidth,height=18cm]{figures/crop_unblur.png}
+\caption{Motion correction of movies with condensed beams. At the top of each
+panel is an average of the movie that was motion-corrected with a red
+dashed box indicating the region that was used to estimate shifts. Below
+is a graph indicating the estimated shifts of the individual frames of
+the movie. Below this is the MIP of 2DTM using the large subunit of the
+mouse ribosome. (A) Motion correction of the whole movie (B) Notion
+correction of a cropped region of the movie that eliminates the beam
+edges (C) Motion correction of the whole movie, using only the central
+region to estimate the shifts (D) Representative result of 2DTM (bottom)
+on uncorrected micrographs. Detections along the beam edge are artifacts
+due to the high-contrast signal. (E) Micrographs after preprocessing for
+2DTM (top). The micrograph has been cropped to the perimeter of the beam
+and unilluminated areas of the image have been replaced with Gaussian
+noise. After running 2DTM on this micrograph (bottom), no more
+artifactual detections are
+observed.}\label{fig:crop_unblur}
 }
@@
 
-\begin{fignos:tagged-figure}[4 - figure supplement 2]
+\begin{fignos:tagged-figure}[3 - figure supplement 2]
 
@@
 \centering
-\includegraphics{figures/lamella_motion_thickness.png}
-\caption{Motion correction of individual tiles imaged using the DeCo-LACE approach
-(A) Total estimated motion of individual micrographs taken using the DeCo-LACE approach
-plotted as a function of the beam image-shift values.
-(B) Electron intensity of individual micrographs taken using the DeCo-LACE approach
-plotted as a function of the beam image-shift values.}\label{fig:lamella_motion_thickness}
+\includegraphics[width=\textwidth,height=20cm]{figures/lamella_motion_thickness.png}
+\caption{Motion correction of individual tiles imaged using the DeCo-LACE
+approach (A) Total estimated motion of individual micrographs taken
+using the DeCo-LACE approach plotted as a function of the beam
+image-shift values. (B) Sample thickness estimate of individual
+micrographs taken using the DeCo-LACE approach plotted as a function of
+the beam image-shift values. Sample thickness was estimated using
+Lamber-Beers law using a coefficient of 322 nm
+{[}\protect\hyperlink{ref-17IP4Lhz1}{18}{]}. (C) Distance between highest and
+lowest LSU detection in each micrograph plotted as a function of
+estimated sample thickness. Dashed black line indicates unity and red
+dashed line is drawn in parallel with an x intercept of 70 nm. Most data
+points fall below the red dashed line, indicating that no detections
+occur within 35 nm of the lamella
+edge.}\label{fig:lamella_motion_thickness}
 }
@@
 
-\begin{fignos:tagged-figure}[4 - figure supplement 3]
+\begin{fignos:tagged-figure}[3 - figure supplement 3]
 
@@
 \includegraphics{figures/gain.png}
-\caption{Averages of micrographs taken with a condensed beam over vacuum using a Gatan K3 detector.
-Contrast and Brightness have been adjusted to highlight uneven dose response.
-(A) Eucentric Focus (B) Fringe-free Focus}\label{fig:gain}
+\caption{Averages of micrographs taken with a condensed beam over vacuum using
+a Gatan K3 detector. Contrast and Brightness have been adjusted to
+highlight uneven dose response. (A) Eucentric Focus (B) Fringe-free
+Focus}\label{fig:gain}
 }
@@
 
-\begin{fignos:tagged-figure}[4 - figure supplement 4]
+\begin{fignos:tagged-figure}[3 - figure supplement 4]
 
@@
 \includegraphics[width=\textwidth,height=23cm]{figures/lamella_images.png}
-\caption{Overview images of lamellae imaged using the DeCo-LACE approach taken at low-magnification (A) Overviews taken at low magnification.
-Scalebar corresponds to 1 μm.
-(B) Overviews assembled using the DeCo-LACE approach.
-Scalebar corresponds to 1 μm.
-(C) Representative examples of a class of granules containing a putatively cytosolic inclusion.
-Scalebar corresponds to 100 nm.}\label{fig:lamella_images}
+\caption{Overview images of lamellae imaged using the DeCo-LACE approach taken
+at low-magnification (A) Overviews taken at low magnification. Scalebar
+corresponds to 1 μm. (B) Overviews assembled using the DeCo-LACE
+approach. Scalebar corresponds to 1 μm. (C) Representative examples of a
+class of granules containing a putatively cytosolic inclusion. Scalebar
+corresponds to 100 nm.}\label{fig:lamella_images}
 }
@@
 \includegraphics{figures/matching_euc.png}
-\caption{Template matching in lamella imaged using the DeCo-LACE approach at eucentric
-focus (A) Montage of Lamella\(_\textrm{EUC}\) 1 overlaid with detected targets colored in orange. Scalebar corresponds to 1 μm. (B) Side view of detected targets in the lamella, such that the
-direction of the electron beam is horizontal. (C-F) Magnified area of panel A
-showing rough ER with associated ribosomes (C), outer nuclear membrane with
-associated ribosomes (D), ribsomes arranged in a circular fashion (E), ribosomes
-enclosed in a less electron dense inclusion in a granule (F).
-Ribosomes are colored in white with the surface of the peptide exit tunnel colored in green and the A, P, and E sites colored in blue, purple, and red, respectively.Scalebar corresponds to 100 nm.}\label{fig:matching_euc}
+\caption{Template matching in lamella imaged using the DeCo-LACE approach at
+eucentric focus (A) Montage of Lamella\(_\textrm{EUC}\) 1 overlaid with
+detected targets colored in orange. Scalebar corresponds to 1 μm. (B)
+Side view of detected targets in the lamella, such that the direction of
+the electron beam is horizontal. (C-F) Magnified area of panel A showing
+rough ER with associated ribosomes (C), outer nuclear membrane with
+associated ribosomes (D), ribsomes arranged in a circular fashion (E),
+ribosomes enclosed in a less electron dense inclusion in a granule (F).
+Ribosomes are colored in white with the surface of the peptide exit
+tunnel colored in green and the A, P, and E sites colored in blue,
+purple, and red, respectively.Scalebar corresponds to 100
+nm.}\label{fig:matching_euc}
 }
@@
 \includegraphics{figures/matching_fff.png}
-\caption{Template matching in lamella imaged using the DeCo-LACE approach at fringe-free
-focus (A) Montage of Lamella\(_\textrm{FFF}\) 4 overlaid with detected targets colored in orange. Scalebar corresponds to 1 μm. (B) Side view of detected targets in the lamella, such that the
-direction of the electron beam is horizontal. (C-E) Magnified area of panel A
-showing rough ER with associated ribosomes (C) and ribosomes
-enclosed in a less electron dense inclusion in a granule (D,E). (F) Side view of
-panel E.
-Ribosomes are colored in white with the surface of the peptide exit tunnel colored in green and the A, P, and E sites colored in blue, purple, and red, respectively.
-Scalebar corresponds to 100 nm.}\label{fig:matching_fff}
+\caption{Template matching in lamella imaged using the DeCo-LACE approach at
+fringe-free focus (A) Montage of Lamella\(_\textrm{FFF}\) 4 overlaid with
+detected targets colored in orange. Scalebar corresponds to 1 μm. (B)
+Side view of detected targets in the lamella, such that the direction of
+the electron beam is horizontal. (C-E) Magnified area of panel A showing
+rough ER with associated ribosomes (C) and ribosomes enclosed in a less
+electron dense inclusion in a granule (D,E). (F) Side view of panel E.
+Ribosomes are colored in white with the surface of the peptide exit
+tunnel colored in green and the A, P, and E sites colored in blue,
+purple, and red, respectively. Scalebar corresponds to 100
+nm.}\label{fig:matching_fff}
 }
@@
 \includegraphics{figures/matching_stat.png}
-\caption{Statistics of 2DTM on lamella imaged using DeCo-LACE (A) Number of detected targets in
-each lamella (B) Distribution of targets per tile in each lamella. Only tiles
-with two or more detected targets were included (C) Distribution of SNRs in each lamella
-(D) For each lamella an average of all tiles is shown. Overlaid is a scatterplot
-of all detected targets in these tiles according to their in-tile coordinates.
-Scatterplot is colored according to the 2DTM SNR. There are no detected targets in the top
-circle-circle intersection due to radiation damage from previous exposures.
-(E) 2D histogram of number of detected targets as a function of beam-image shift (F) Mean 2DTM SNR as a function of beam-image shift}\label{fig:matching_stat}
+\caption{Statistics of 2DTM on lamella imaged using DeCo-LACE (A) Number of
+detected targets in each lamella (B) Distribution of targets per tile in
+each lamella. Only tiles with two or more detected targets were included
+(C) Distribution of SNRs in each lamella (D) For each lamella an average
+of all tiles is shown. Overlaid is a scatterplot of all detected targets
+in these tiles according to their in-tile coordinates. Scatterplot is
+colored according to the 2DTM SNR. There are no detected targets in the
+top circle-circle intersection due to radiation damage from previous
+exposures. (E) 2D histogram of number of detected targets as a function
+of beam-image shift (F) Mean 2DTM SNR as a function of beam-image
+shift}\label{fig:matching_stat}
 }
@@
 \includegraphics{figures/deco_lace_workflow.png}
-\caption{Workflow of DeCo-LACE processing}\label{fig:deco_lace_workflow}
+\caption{Workflow of DeCo-LACE
+processing}\label{fig:deco_lace_workflow}
 }
@@
 
-\begin{fignos:tagged-figure}[Movie 1]
+\begin{fignos:tagged-figure}[Figure 4-video 1]
 
@@
 \includegraphics{images/1x1-00000000.png}
-\caption{Movie of detected LSU targets in Lamella\(_\textrm{EUC}\) 1, corresponding to Figure 5}\label{fig:movie1}
+\caption{Movie of detected LSU targets in Lamella\(_\textrm{EUC}\) 1,
+corresponding to Figure 4}\label{fig:movie1}
 }
@@
 
-\begin{fignos:tagged-figure}[Movie 2]
+\begin{fignos:tagged-figure}[Figure 5-video 1]
 
@@
 \includegraphics{images/1x1-00000000.png}
-\caption{Movie of detected LSU targets in Lamella\(_\textrm{FFF}\) 4, corresponding to Figure 6}\label{fig:movie2}
+\caption{Movie of detected LSU targets in Lamella\(_\textrm{FFF}\) 4,
+corresponding to Figure 5}\label{fig:movie2}
 }
@@
 \CSLLeftMargin{13. }%
-\CSLRightInline{\textbf{\textless i\textgreater In situ\textless/i\textgreater{} single particle classification reveals distinct 60S maturation intermediates in cells}
+\CSLRightInline{\textbf{ In situ single particle classification reveals distinct 60S maturation intermediates in cells}
 \CSLBlock{Bronwyn A Lucas, Kexin Zhang, Sarah Loerch, Nikolaus Grigorieff} \emph{Cold Spring Harbor Laboratory} (2022-04-10) \url{https://doi.org/gp4qrx}
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-SDMGf7aG}{}}%
+\CSLLeftMargin{20. }%
+\CSLRightInline{\textbf{Plasma FIB milling for the determination of structures \textless i\textgreater in situ\textless/i\textgreater{}}
+\CSLBlock{Casper Berger, Maud Dumoux, Thomas Glen, Neville B-y Yee, John M Mitchels, Zuzana Patáková, James H Naismith, Michael Grange} \emph{Cold Spring Harbor Laboratory} (2022-08-01) \url{https://doi.org/gq59b8}
+\CSLBlock{DOI: \href{https://doi.org/10.1101/2022.08.01.502333}{10.1101/2022.08.01.502333}}}
+
 \leavevmode\vadjust pre{\hypertarget{ref-cie13Q8F}{}}%
-\CSLLeftMargin{20. }%
+\CSLLeftMargin{21. }%
 \CSLRightInline{\textbf{Circularization of mRNA by eukaryotic translation initiation factors.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1GPPSX111}{}}%
-\CSLLeftMargin{21. }%
+\CSLLeftMargin{22. }%
 \CSLRightInline{\textbf{Montage electron tomography of vitrified specimens}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ujizcpVn}{}}%
-\CSLLeftMargin{22. }%
+\CSLLeftMargin{23. }%
 \CSLRightInline{\textbf{Correlative cryogenic montage electron tomography for comprehensive in-situ whole-cell structural studies}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1Gwx5ScUa}{}}%
-\CSLLeftMargin{23. }%
+\CSLLeftMargin{24. }%
 \CSLRightInline{\textbf{Beam image-shift accelerated data acquisition for near-atomic resolution single-particle cryo-electron tomography}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-xvouNMBy}{}}%
-\CSLLeftMargin{24. }%
+\CSLLeftMargin{25. }%
 \CSLRightInline{\textbf{Parallel cryo electron tomography on \textless i\textgreater in situ\textless/i\textgreater{} lamellae}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-kncnYGLD}{}}%
-\CSLLeftMargin{25. }%
+\CSLLeftMargin{26. }%
 \CSLRightInline{\textbf{Shedding light on the cell biology of extracellular vesicles}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-agVdpX76}{}}%
-\CSLLeftMargin{26. }%
+\CSLLeftMargin{27. }%
 \CSLRightInline{\textbf{Exosome-mediated transfer of mRNAs and microRNAs is a novel mechanism of genetic exchange between cells}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-44fG6kcy}{}}%
-\CSLLeftMargin{27. }%
+\CSLLeftMargin{28. }%
 \CSLRightInline{\textbf{High-resolution cryo-EM using beam-image shift at 200 keV}
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-wy8cRzrH}{}}%
+\CSLLeftMargin{29. }%
+\CSLRightInline{\textbf{High resolution single particle cryo-electron microscopy using beam-image shift}
+\CSLBlock{Anchi Cheng, Edward T Eng, Lambertus Alink, William J Rice, Kelsey D Jordan, Laura Y Kim, Clinton S Potter, Bridget Carragher} \emph{Journal of Structural Biology} (2018-11) \url{https://doi.org/gfg6vz}
+\CSLBlock{DOI: \href{https://doi.org/10.1016/j.jsb.2018.07.015}{10.1016/j.jsb.2018.07.015} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/30055234}{30055234} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6163078}{PMC6163078}}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-13fhsbtxo}{}}%
+\CSLLeftMargin{30. }%
+\CSLRightInline{\textbf{A method for differentiating proteins from nucleic acids in intermediate-resolution density maps: cryo-electron microscopy defines the quaternary structure of the Escherichia coli 70S ribosome.}
+\CSLBlock{CM Spahn, PA Penczek, A Leith, J Frank} \emph{Structure (London, England : 1993)} (2000-09-15) \url{https://www.ncbi.nlm.nih.gov/pubmed/10986461}
+\CSLBlock{DOI: \href{https://doi.org/10.1016/s0969-2126(00)00185-4}{10.1016/s0969-2126(00)00185-4} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/10986461}{10986461}}}
+
 \leavevmode\vadjust pre{\hypertarget{ref-17H2LWiIu}{}}%
-\CSLLeftMargin{28. }%
+\CSLLeftMargin{31. }%
 \CSLRightInline{\textbf{Waffle Method: A general and flexible approach for improving throughput in FIB-milling}
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-nSMAxqTD}{}}%
+\CSLLeftMargin{32. }%
+\CSLRightInline{\textbf{Quantitative production of macrophages or neutrophils ex vivo using conditional Hoxb8}
+\CSLBlock{Gang G Wang, Katherine R Calvo, Martina P Pasillas, David B Sykes, Hans Häcker, Mark P Kamps} \emph{Nature Methods} (2006-03-22) \url{https://doi.org/dgxn4m}
+\CSLBlock{DOI: \href{https://doi.org/10.1038/nmeth865}{10.1038/nmeth865} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/16554834}{16554834}}}
+
 \leavevmode\vadjust pre{\hypertarget{ref-19ZFerhph}{}}%
-\CSLLeftMargin{29. }%
+\CSLLeftMargin{33. }%
 \CSLRightInline{\textbf{Automated electron microscope tomography using robust prediction of specimen movements}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-MUY42yxp}{}}%
-\CSLLeftMargin{30. }%
+\CSLLeftMargin{34. }%
 \CSLRightInline{\textbf{cisTEM, user-friendly software for single-particle image processing}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1G4Y94qCy}{}}%
-\CSLLeftMargin{31. }%
+\CSLLeftMargin{35. }%
 \CSLRightInline{\textbf{Measuring the optimal exposure for single particle cryo-EM using a 2.6 Å reconstruction of rotavirus VP6}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-n43f3Sqs}{}}%
-\CSLLeftMargin{32. }%
+\CSLLeftMargin{36. }%
 \CSLRightInline{\textbf{CTFFIND4: Fast and accurate defocus estimation from electron micrographs}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-q2PSamkS}{}}%
-\CSLLeftMargin{33. }%
+\CSLLeftMargin{37. }%
 \CSLRightInline{\textbf{Cryo-TEM simulations of amorphous radiation-sensitive samples using multislice wave propagation}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-stvWEJeu}{}}%
-\CSLLeftMargin{34. }%
+\CSLLeftMargin{38. }%
 \CSLRightInline{\textbf{scikit-image: image processing in Python}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-8Miti2Gz}{}}%
-\CSLLeftMargin{35. }%
+\CSLLeftMargin{39. }%
 \CSLRightInline{\textbf{SciPy 1.0: fundamental algorithms for scientific computing in Python}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-cYCuuZxG}{}}%
-\CSLLeftMargin{36. }%
-\CSLRightInline{\textbf{\textless scp\textgreater UCSF ChimeraX\textless/scp\textgreater{}
+\CSLLeftMargin{40. }%
+\CSLRightInline{\textbf{UCSF ChimeraX
 : Structure visualization for researchers, educators, and developers}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-YuJbg3zO}{}}%
-\CSLLeftMargin{37. }%
+\CSLLeftMargin{41. }%
 \CSLRightInline{\textbf{Open collaborative writing with Manubot}
